### 2023-08-26 README.qmd
Initial commit

---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)

library(emoji)
```

# Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Lewis & Clark College  
[Marc Dotson](https://marriottschool.byu.edu/directory/details?id=50683) • Brigham Young University  
[Andrew Heiss](https://www.andrewheiss.com) • Georgia State University

<!-- badges: start -->
<!-- badges: end -->

---

## Abstract

As space for civil society has closed around the world, transnational NGOs have faced a crisis of funding. We explore how NGOs have shifted from traditionally Northern funding sources toward grassroots private philanthropic money. How do individual donors in the US feel about donating to legally besieged NGOs abroad? Do legal restrictions on NGOs influence donors’ decision to donate? We use a conjoint survey experiment to argue that domestic political environments of NGO host countries influence preferences of private donors and that legal crackdowns on NGOs serve as a heuristic of organizational deservingness.

### `r emoji_glue(":zipper_mouth_face::sun_behind_large_cloud::person_walking:")`: Note on "silent skywalk" project name

Because project titles change all the time with revisions, rewriting, and peer review, we used [{codename}](http://svmiller.com/codename/) to generate a [NICKA](https://en.wikipedia.org/wiki/List_of_U.S._Department_of_Defense_and_partner_code_names)-style internal-to-us project name that won't change.

```{r generate-code-name, eval=FALSE}
library(codename)
codename_message()
#> code name generated by {codename} v.0.5.0. R version 4.3.0 (2023-04-21).

codename(type = "nicka", seed = "why donors donate") |> 
#> [1] "silent skywalk"
```

## Licenses

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)).

**Code:** All code is licensed under the [MIT License](LICENSE.md).

## Contributions and Code of Conduct

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

### 2023-08-26 basic-amces-mms.qmd
Initial commit

---
title: Basic polisci-style AMCEs and MMs
format:
  html:
    code-fold: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "80%", collapse = TRUE,
  dev = "ragg_png"
)

options(
  digits = 3, width = 220,
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)
```

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(cregg)

results_long <- readRDS("original_data.rds") %>% 
  mutate(choice_binary = ifelse(choice == alt, 1, 0)) %>% 
  mutate(
    feat_transp = fct_relabel(feat_transp, ~paste("Transparency: ", .x)),
    feat_acc = fct_relabel(feat_acc, ~paste("Accountability: ", .x)),
  )
```

The `results_long` data frame contains 1 row per alternative, and features are stored as factors:

```{r show-structure}
results_long %>% count(id)
results_long %>% count(id, task)
```

In political science, we just want the AMCEs and marginal means, so this is all we really do:

```{r calculate-amces}
amces <- amce(
  results_long,
  choice_binary ~ feat_org + feat_issue + feat_transp + feat_acc + feat_funding + feat_govt,
  id = ~id
)

amces
```

```{r plot-amce, fig.width=7, fig.height=5}
plot(amces) + guides(color = "none")
```

```{r calculate-mm}
mms <- mm(
  results_long,
  choice_binary ~ feat_org + feat_issue + feat_transp + feat_acc + feat_funding + feat_govt,
  id = ~id
)

mms
```

```{r plot-mm, fig.width=7, fig.height=5}
plot(mms) + guides(color = "none") + geom_vline(xintercept = 0.25, linewidth = 0.25, color = "grey50")
```

### 2023-08-26 hypotheses.qmd
Initial commit

---
title: Hypotheses
format:
  html:
    code-fold: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "80%", collapse = TRUE,
  dev = "ragg_png"
)

options(
  digits = 3, width = 120,
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)
```

```{r libraries-functions, warning=FALSE, message=FALSE}
library(tidyverse)
library(scales)
library(glue)
library(here)
library(patchwork)
library(tidybayes)
library(gt)
library(gtExtras)
library(rcartocolor)
library(Matrix)

label_pp <- label_number(accuracy = 1, scale = 100, 
  suffix = " pp.", style_negative = "minus")

fmt_decimal <- label_number(accuracy = 0.001, style_negative = "minus")

build_ci <- function(lower, upper) {
  glue("[{fmt_decimal(lower)}, {fmt_decimal(upper)}]")
}

theme_nice <- function() {
  theme_minimal(base_family = "Clear Sans") +
    theme(panel.grid.minor = element_blank(),
      plot.title = element_text(family = "Clear Sans", face = "bold"),
      axis.title.x = element_text(hjust = 0),
      axis.title.y = element_text(hjust = 1),
      strip.text = element_text(family = "Clear Sans", face = "bold",
        size = rel(0.75), hjust = 0),
      strip.background = element_rect(fill = "grey90", color = NA))
}

opts_theme <- function(x) {
  x %>% 
    opt_table_font(font = "Inter") %>% 
    tab_options(column_labels.font.weight = "bold",
                row_group.font.weight = "bold")
}

theme_set(theme_nice())
prism <- carto_pal(name = "Prism")
peach <- carto_pal(name = "Peach")
```

```{r create-ref-grid}
all_combos <- expand_grid(
  feat_org = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"), 
  feat_issue = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  feat_transp = c("No", "Yes"), 
  feat_acc = c("No", "Yes"),
  feat_funding = c("Many small donors", "Handful of wealthy private donors", "Government grants"),
  feat_govt = c("Friendly", "Criticized", "Under crackdown")
) %>% 
  mutate(across(everything(), ~fct_inorder(.)))

all_combos_design_grid <- sparse.model.matrix(
  ~ 0 + feat_org + feat_issue + feat_transp + 
    feat_acc + feat_funding + feat_govt, 
  data = all_combos
)
```

```{r create-all-combos-means}
gammas_raw <- readRDS(here("data", "raw_data", "posterior_draws", "intercept.rds"))

all_combos_means <- gammas_raw %>% 
  pivot_wider(names_from = i, values_from = Gamma) %>% 
  group_by(j, .chain, .iteration, .draw) %>% 
  nest() %>% 
  mutate(pi = map(data, ~{
    preds <- as.numeric(all_combos_design_grid %*% as.numeric(.))
    all_combos %>% 
      mutate(
        .linpred = preds, 
        # fake bc it's not actually mean(posterior_predict(.))
        .epred = plogis(preds)
      )
  })) %>% 
  select(-data) %>% 
  unnest(pi)
```

# Model

TODO: Intercept only because (1) LOO is best, and (2) it makes most sense causally since all confounding arrows are deleted due to randomization

# Method: Marginal means

To find the causal effects defined in each of our estimands, we calculate estimated marginal means (EMMs) by finding the fitted values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (4 organizations × 4 issues × 2 transparency × 2 accountability × 3 funding × 3 government relationship = 576 rows). We transform these estimates to the probability scale in order to work directly with predicted probabilities rather than the link (logit) scale. We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.

TODO: Simple example here to just to illustrate the process—show literal marginal means in the margins of a balanced reference grid, then subtract them for the difference in marginal means, or AMCEs

Here's what the full grid of 576 options looks like, with posterior median predictions for each combination:

```{r}
#| column: screen-inset
all_combos_means %>% 
  group_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>% 
  summarize(avg = mean(.epred)) %>% 
  ungroup() %>% 
  gt() %>% 
  cols_align(align = "left") %>% 
  cols_label(
    feat_org = "Organization",
    feat_issue = "Issue",
    feat_transp = "Transparency",
    feat_acc = "Accountability",
    feat_funding = "Funding",
    feat_govt = "Relationship",
    avg = "Median probability"
  ) %>% 
  opts_theme() %>% 
  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, use_filters = TRUE)
```

# H~1~: Branding

::: {.callout-tip}
## H~1~: Branding

**Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace.**

*Mechanism: awareness of need and contentiousness of issue area*
:::

### Estimand

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Oxfam or Red Cross} \right) \bigr] - \\
&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Amnesty International or Greenpeace} \right) \bigr]
\end{aligned}
$$

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace. However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam. In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International.

![](img/contrasts_hypothesis01.png)
:::

```{r h1-calc-estimands}
h1_mms <- all_combos_means %>% 
  group_by(feat_org, .draw) %>% 
  summarize(avg = mean(.epred))

h1_amces <- h1_mms %>% 
  group_by(feat_org) %>% 
  compare_levels(variable = avg, by = feat_org, comparison = "control")
```

```{r plot-h1-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
#| column: body-outset
p_h1_mms <- h1_mms %>% 
  ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +
  stat_halfeye() +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = prism[c(1, 3, 5, 7)], guide = "none") +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  )

p_h1_amces <- h1_amces %>% 
  ungroup() %>% 
    separate_wider_delim(
    feat_org,
    delim = " - ", 
    names = c("feat_org", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_org = "Amnesty International") %>% 
  ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = prism[c(1, 3, 5, 7)], guide = "none") +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Average marginal component effects (AMCEs)"
  )

p_h1_mms | p_h1_amces
```

```{r table-h1-mm-amce}
#| column: body-outset
h1_tbl_mm <- h1_mms %>% 
  group_by(feat_org) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_org)) %>% 
  select(feat_org, nice)

h1_tbl_amces <- h1_amces %>% 
  group_by(feat_org) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>%
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
  mutate(feat_org = str_replace(feat_org, " - ", "−<br>")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
  arrange(desc(feat_org)) %>% 
  select(contrast = feat_org, amce_nice = nice, p_neq_0)

bind_cols(
  h1_tbl_mm, 
  add_row(h1_tbl_amces, contrast = "*(Reference)*")
) %>% 
  gt() %>% 
  sub_missing(columns = everything(), missing_text = "—") %>% 
  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
  cols_align(align = "center", columns = everything()) %>% 
  cols_align(align = "left", columns = c(feat_org, contrast)) %>% 
  cols_label(
    feat_org = "Organization", 
    nice = "Posterior EMM",
    contrast = "Contrast",
    amce_nice = "Posterior AMCE",
    p_neq_0 = "*p*~direction~",
    .fn = md
  ) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_footnote(
    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
    locations = cells_column_labels(columns = c(nice, amce_nice))
  ) %>% 
  tab_footnote(
    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
    locations = cells_column_labels(columns = p_neq_0)
  ) %>% 
  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
  opt_footnote_marks(marks = "standard") %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

# H~2~: Government crackdown

## H~2a~: Relationship with host government

::: {.callout-tip}
## H~2a~: Relationship with host government

**Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism.**

*Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively. This perception of efficacy leads to increased donations.*
:::

### Estimand

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Under crackdown} \right) \bigr] - 
\textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Friendly} \right) \bigr] \\[10pt]
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Criticized} \right) \bigr] - \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Friendly} \right) \bigr]
\end{aligned}
$$

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism. This decreased likelihood to donate is also greater for NGOs under crackdown compared to those under criticism.

![](img/contrasts_hypothesis02a.png)
:::

```{r h2a-calc-estimands}
h2a_mms <- all_combos_means %>% 
  group_by(feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

h2a_amces <- h2a_mms %>% 
  group_by(feat_govt) %>% 
  compare_levels(variable = avg, by = feat_govt, comparison = "control")
```

```{r plot-h2a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
#| column: body-outset
p_h2a_mms <- h2a_mms %>% 
  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
  stat_halfeye() +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  )

p_h2a_amces <- h2a_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_govt,
    delim = " - ", 
    names = c("feat_govt", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_govt = "Friendly") %>%
  mutate(feat_govt = factor(feat_govt, levels = levels(h2a_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Average marginal component effects (AMCEs)"
  )

p_h2a_mms | p_h2a_amces
```

```{r table-h2a-mm-amce}
#| column: body-outset
h2a_tbl_mm <- h2a_mms %>% 
  group_by(feat_govt) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_govt)) %>% 
  select(feat_govt, nice)

h2a_tbl_amces <- h2a_amces %>% 
  group_by(feat_govt) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>%
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
  mutate(feat_govt = str_replace(feat_govt, " - ", "−<br>")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
  arrange(desc(feat_govt)) %>% 
  select(contrast = feat_govt, amce_nice = nice, p_neq_0)

bind_cols(
  h2a_tbl_mm, 
  add_row(h2a_tbl_amces, contrast = "*(Reference)*")
) %>% 
  gt() %>% 
  sub_missing(columns = everything(), missing_text = "—") %>% 
  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
  cols_align(align = "center", columns = everything()) %>% 
  cols_align(align = "left", columns = c(feat_govt, contrast)) %>% 
  cols_label(
    feat_govt = "Relationship", 
    nice = "Posterior EMM",
    contrast = "Contrast",
    amce_nice = "Posterior AMCE",
    p_neq_0 = "*p*~direction~",
    .fn = md
  ) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_footnote(
    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
    locations = cells_column_labels(columns = c(nice, amce_nice))
  ) %>% 
  tab_footnote(
    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
    locations = cells_column_labels(columns = p_neq_0)
  ) %>% 
  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
  opt_footnote_marks(marks = "standard") %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

## H~2b~: Organization and relationship with host government

::: {.callout-tip}
## H~2b~: Organization and relationship with host government

**Donors will show increased willingness to donate to Oxfam and Red Cross when they are facing government crackdown or criticism compared to when Amnesty or Greenpeace is facing crackdown.**
:::

### Estimand

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Oxfam or Red Cross}  \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr] - \\
&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Amnesty International or Greenpeace} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr]
\end{aligned}
$$

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

These data don't support our hypothesis; the Red Cross brand has an insignificant impact on likelihood to donate compared to both Greenpeace and Amnesty. While the contrasts for Oxfam are closer to being statistically significant, the effect is working in the other direction--Greenpeace and Amnesty both induce increased likelihood to donate on behalf of donors.

![](img/contrasts_hypothesis02b.png)

![](img/contrasts_hypothesis02b_alt.png)
:::

```{r h2b-calc-estimands}
h2b_mms <- all_combos_means %>% 
  mutate(org_collapsed = fct_collapse(feat_org, 
    `Oxfam & Red Cross` = c("Oxfam", "Red Cross"),
    `Amnesty International & Greenpeace` = c("Amnesty International", "Greenpeace"))) %>% 
  group_by(org_collapsed, feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

h2b_amces <- h2b_mms %>% 
  group_by(feat_govt) %>% 
  compare_levels(variable = avg, by = org_collapsed, comparison = "control")
```

```{r plot-h2b-mm-amce, fig.width=6.5, fig.height=7, out.width="70%"}
#| column: body-outset
p_h2b_mms <- h2b_mms %>% 
  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
  stat_halfeye(aes(slab_alpha = org_collapsed)) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
  scale_slab_alpha_discrete(
    range = c(0.4, 1),
    guide = guide_legend(
      reverse = TRUE, override.aes = list(fill = "grey10"), 
      keywidth = 0.8, keyheight = 0.8, nrow = 1
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    slab_alpha = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )

p_h2b_amces <- h2b_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    org_collapsed,
    delim = " - ", 
    names = c("org_collapsed", "reference_level")
  ) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h2a_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
  facet_wrap(vars(paste(org_collapsed, "−", reference_level))) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means",
    subtitle = "Positive values indicate greater preference for Oxfam & Red Cross"
  )

(p_h2b_mms / plot_spacer() / p_h2b_amces) +
  plot_layout(ncol = 1, heights = c(0.49, 0.02, 0.49))
```

```{r table-h2b-mm-amce}
#| column: body-outset
h2b_tbl_mm <- h2b_mms %>% 
  group_by(feat_govt, org_collapsed) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_govt), desc(org_collapsed)) %>% 
  select(org_collapsed, feat_govt, nice)

h2b_tbl_amces <- h2b_amces %>% 
  group_by(feat_govt, org_collapsed) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>%
  ungroup() %>% 
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
  mutate(org_collapsed = str_replace(org_collapsed, " - ", "−<br>")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
  arrange(desc(feat_govt)) %>% 
  select(contrast = org_collapsed, diff_nice = nice, p_neq_0)

bind_cols(
  h2b_tbl_mm, 
  h2b_tbl_amces %>% 
    add_row(contrast = NA, .after = 1) %>% 
    add_row(contrast = NA, .after = 3) %>% 
    add_row(contrast = NA, .after = 5)
) %>% 
  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
  group_by(feat_govt) %>% 
  gt() %>% 
  sub_missing(columns = everything(), missing_text = "—") %>% 
  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
  cols_align(align = "center", columns = everything()) %>% 
  cols_align(align = "left", columns = c(org_collapsed, contrast)) %>% 
  cols_label(
    org_collapsed = "Organizations", 
    nice = "Posterior EMM",
    contrast = "Contrast",
    diff_nice = "Posterior ∆",
    p_neq_0 = "*p*~direction~",
    .fn = md
  ) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_style(
    style = cell_fill(color = "grey90"),
    locations = cells_row_groups()
  ) %>% 
  tab_footnote(
    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
    locations = cells_column_labels(columns = c(nice, diff_nice))
  ) %>% 
  tab_footnote(
    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
    locations = cells_column_labels(columns = p_neq_0)
  ) %>% 
  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
  opt_footnote_marks(marks = "standard") %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

# H~3~: Issue Area

## H~3a~: Issue area

::: {.callout-tip}
## H~3a~: Issue area

**Donors will show increased willingness to donate to NGOs working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights).**
:::

### Estimand

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{More contentious} \right) \bigr] -
\textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{Less contentious} \right) \bigr]
\end{aligned}
$$

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

Donors appear to be sensitive to NGO issue area when they are considering to donate. Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations. While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs, which was contrary to our expectations. It is worth noting that there is some overlap between the intervals of the issue areas, which would suggest that their effect isn't as significant as other factors.
:::

```{r h3a-calc-estimands}
h3a_mms <- all_combos_means %>% 
  group_by(feat_issue, .draw) %>% 
  summarize(avg = mean(.epred))

h3a_amces <- h3a_mms %>% 
  group_by(feat_issue) %>% 
  compare_levels(variable = avg, by = feat_issue, comparison = "control")
```

```{r plot-h3a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
#| column: body-outset
p_h3a_mms <- h3a_mms %>% 
  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
  stat_halfeye() +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  )

p_h3a_amces <- h3a_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_issue,
    delim = " - ", 
    names = c("feat_issue", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_issue = "Emergency response") %>%
  mutate(feat_issue = factor(feat_issue, levels = levels(h3a_mms$feat_issue))) %>% 
  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Average marginal component effects (AMCEs)"
  )

p_h3a_mms | p_h3a_amces
```

```{r table-h3a-mm-amce}
#| column: body-outset
h3a_tbl_mm <- h3a_mms %>% 
  group_by(feat_issue) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_issue)) %>% 
  select(feat_issue, nice)

h3a_tbl_amces <- h3a_amces %>% 
  group_by(feat_issue) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>%
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
  mutate(feat_issue = str_replace(feat_issue, " - ", "−<br>")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
  arrange(desc(feat_issue)) %>% 
  select(contrast = feat_issue, amce_nice = nice, p_neq_0)

bind_cols(
  h3a_tbl_mm, 
  add_row(h3a_tbl_amces, contrast = "*(Reference)*")
) %>% 
  gt() %>% 
  sub_missing(columns = everything(), missing_text = "—") %>% 
  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
  cols_align(align = "center", columns = everything()) %>% 
  cols_align(align = "left", columns = c(feat_issue, contrast)) %>% 
  cols_label(
    feat_issue = "Issue area", 
    nice = "Posterior EMM",
    contrast = "Contrast",
    amce_nice = "Posterior AMCE",
    p_neq_0 = "*p*~direction~",
    .fn = md
  ) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_footnote(
    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
    locations = cells_column_labels(columns = c(nice, amce_nice))
  ) %>% 
  tab_footnote(
    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
    locations = cells_column_labels(columns = p_neq_0)
  ) %>% 
  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
  opt_footnote_marks(marks = "standard") %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

## H~3b~: Relationship with host government and issue area

::: {.callout-tip}
## H~3b~: Relationship with host government and issue area

**Donors will show increased willingness to donate to NGOs facing government crackdown/criticism working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights)**

*Mechanisms: Perceptions of deservingness of NGOs dealing with emergency response and refugee relief. Donors are also more likely to donate to programs that are compatible with government preferences and have easily measurable outputs, which environment and human rights programs often lack. NGOs working on more contentious issue areas may be expelled or shut down, which would be a waste of donor resources, make it less likely that they donate to these groups.*
:::

### Estimand

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{More contentious}  \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr] - \\
&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{Less contentnious} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr]
\end{aligned}
$$

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

The generated contrasts don't provides results which are statistically significant. 0 is found within all intervals.

![](img/contrasts_hypothesis03b.png)
:::

```{r h3b-calc-estimands}
h3b_mms <- all_combos_means %>% 
  group_by(feat_issue, feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

h3b_amces <- h3b_mms %>% 
  group_by(feat_govt) %>% 
  compare_levels(variable = avg, by = feat_issue, comparison = "control")
```

```{r plot-h3b-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset
p_h3b_mms <- h3b_mms %>% 
  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
  stat_halfeye() +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
  facet_wrap(vars(feat_govt), ncol = 1) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )

p_h3b_amces <- h3b_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_issue,
    delim = " - ", 
    names = c("feat_issue", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Friendly") %>%
  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Criticized") %>%
  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Under crackdown") %>%
  mutate(feat_issue = factor(feat_issue, levels = levels(h3b_mms$feat_issue))) %>% 
  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
  facet_wrap(vars(feat_govt), ncol = 1) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

p_h3b_mms | p_h3b_amces
```

```{r table-h3b-mm-amce}
#| column: body-outset
h3b_tbl_mm <- h3b_mms %>% 
  group_by(feat_govt, feat_issue) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_govt), desc(feat_issue)) %>% 
  select(feat_issue, feat_govt, nice)

h3b_tbl_amces <- h3b_amces %>% 
  group_by(feat_govt, feat_issue) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>%
  ungroup() %>% 
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
  mutate(feat_issue = str_replace(feat_issue, " - ", "−<br>")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
  arrange(desc(feat_govt)) %>% 
  select(contrast = feat_issue, diff_nice = nice, p_neq_0)

bind_cols(
  h3b_tbl_mm, 
  h3b_tbl_amces %>% 
    add_row(contrast = NA, .after = 3) %>% 
    add_row(contrast = NA, .after = 7) %>% 
    add_row(contrast = NA, .after = 12)
) %>% 
  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
  group_by(feat_govt) %>% 
  gt() %>% 
  sub_missing(columns = everything(), missing_text = "—") %>% 
  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
  cols_align(align = "center", columns = everything()) %>% 
  cols_align(align = "left", columns = c(feat_issue, contrast)) %>% 
  cols_label(
    feat_issue = "Issue", 
    nice = "Posterior EMM",
    contrast = "Contrast",
    diff_nice = "Posterior ∆",
    p_neq_0 = "*p*~direction~",
    .fn = md
  ) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_style(
    style = cell_fill(color = "grey90"),
    locations = cells_row_groups()
  ) %>% 
  tab_footnote(
    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
    locations = cells_column_labels(columns = c(nice, diff_nice))
  ) %>% 
  tab_footnote(
    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
    locations = cells_column_labels(columns = p_neq_0)
  ) %>% 
  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
  opt_footnote_marks(marks = "standard") %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

# H~4~: Funding sources

## H~4a~: Funding sources

> Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealthy private donors and government grants [Mechanism: Perception of efficacy - your contribution matters as a small donor. Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.]

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

As stated in the hypothesis, donors show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants.

![](img/contrasts_hypothesis04.png)
:::

## H~4b~: Relationship with host government and funding sources

> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

The marginal posteriors for these contrasts are strange, but still tell us that the interaction between funding sources and government relationship produce no significant effects.

![](img/contrasts_hypothesis04b.png)
:::

## H~4c~: Relationship with host government, funding sources, and issue area

> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors and work in less contentious areas (emergency response and refugee relief)

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

Once again, we see some interesting distributions, but no results significant enough to confirm our hypothesis.

![](img/contrasts_hypothesis04c.png)
:::

# H~5~: Organizational practices

## H~5a~: Organizational practices

> Donors will show increased willingness to donate to NGOs that are financially transparent [Mechanism: Perception of efficacy]

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

Donors show an increased likelihood to donate to NGOs that are financially transparent, as hypothesized.

![](img/contrasts_hypothesis05.png)
:::

## H~5b~: Relationship with host government, organizational practices

> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent. However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.

![](img/contrasts_hypothesis05b.png)
:::

## H~5c~: Relationship with host government, organizational practices, and funding sources

> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and are funded primarily by numerous small private donors

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

These intervals are massive; 0 is well within them, leaving us with insufficient evidence to confirm the hypothesis.

![](img/contrasts_hypothesis05c.png)
:::

## H~5d~: Relationship with host government, organizational practices, and issue area

> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief)

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

The contrasts don't support the hypothesis, however, there is an interesting difference between emergency_environment_crackdown and emergency_environment_criticized.

![](img/contrasts_hypothesis05d.png)
:::

## H~5e~: Relationship with host government, organizational practices, issue area, and funding sources

> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

These marginal posteriors don't support our hypothesis, but again show an interesting difference between emergency_environment_criticized and emergency_environment_crackdown.

![](img/contrasts_hypothesis05e.png)
:::

## H~5f~: Organizational practices

> Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits [Mechanism: Donors don't necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks]

::: {.callout-note collapse="true"}
## Show results from `contrasts` branch

Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent. However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.

![](img/contrasts_hypothesis05f.png)
:::

### 2023-08-26 index.qmd
Initial commit

---
title: "Why Donors Donate"
author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
format:
  html:
    code-tools: false
    toc: false
---

## Abstract

Abstract goes here

## Code

All the raw code and data for this paper is available in a [GitHub repository](https://github.com/andrewheiss/silent-skywalk).

### 2023-08-26 deploy.sh

@@ -1,0 +1,7 @@
+REMOTE_HOST="cloud"
+REMOTE_DIR="~/sites/stats/public_html/silent-skywalk"
+REMOTE_DEST=$REMOTE_HOST:$REMOTE_DIR
+
+echo "Uploading new changes to remote server..."
+echo
+rsync -crvP --exclude '*_cache' --delete _site/ $REMOTE_DEST

### 2023-08-26 sandbox.R

@@ -1,0 +1,811 @@
+library(tidyverse)
+library(here)
+
+data <- read_csv(
+  here::here("data", "raw_data", "conjointqsf_final.csv"),
+  guess_max = 1500
+)
+
+data_clean <- data %>%
+  filter(V10 == 1) %>%         # Keep respondents who completed the entire survey
+  filter(Q1.1 == 1) %>%        # Keep respondents who gave consent
+  filter(Q2.5 %in% c(1:5)) %>% # Keep respondents who passed the screener
+  filter(Q2.11 == 3)           # Keep respondents who passed the attention check
+
+data_clean %>%
+  select(Q4.1:Q4.12) %>%
+  gather(key = "task", value = "choice") %>%
+  count(choice)
+
+design_orig <- read_csv(here("data", "derived_data", "design.csv")) %>% 
+  rename(
+    version = question_set,
+    task = question,
+    alt = choice
+  ) %>% 
+  gather(key = "atts", value = "levels", -c(version:alt))
+
+design_surv <- data_clean %>% 
+  select(contains("CBCONJOINT"), -revision_CBCONJOINT) %>% 
+  gather(key = "temp", value = "level_names", -vers_CBCONJOINT) %>% 
+  separate(temp, into = c("atts", "task", "alt"), sep = "\\.") %>% 
+  separate(alt, into = c("alt", "temp")) %>% 
+  select(vers_CBCONJOINT, task, alt, atts, level_names) %>% 
+  rename(version = vers_CBCONJOINT) %>% 
+  mutate(
+    task = as.numeric(task),
+    alt = as.numeric(alt),
+    atts = recode(
+      atts,
+      "732d72a6-25a3-4194-8416-461acae30837" = "Organization",
+      "bd54b90a-efb3-4ac8-b65a-1ebeefcaf703" = "Issue area",
+      "a6836e28-fd7a-4b71-b65e-f6269e5c883f" = "Financial transparency",
+      "c2249c1a-11fa-4395-a0a3-61d9648a2e55" = "Accountability",
+      "db44c406-390e-4fc4-875b-65796aa95ffa" = "Funding sources",
+      "85f14c50-61cc-461c-8e77-19453b83d76d" = "Relationship with host government"
+    )
+  ) %>%
+  distinct() %>% 
+  arrange(version, task, alt) %>% 
+  pivot_wider(names_from = atts, values_from = level_names)
+
+design_surv %>% 
[…]

### 2023-08-28 R/funs_graphics.R
targets-ification

@@ -1,0 +1,30 @@
+# Colors
+# https://carto.com/carto-colors/
+clrs <- list(
+  prism = rcartocolor::carto_pal(name = "Prism"),
+  peach = rcartocolor::carto_pal(name = "Peach")
+)
+
+
+# Theme stuff
+theme_ngo <- function() {
+  theme_minimal(base_family = "Clear Sans") +
+    theme(panel.grid.minor = element_blank(),
+      plot.title = element_text(family = "Clear Sans", face = "bold"),
+      axis.title.x = element_text(hjust = 0),
+      axis.title.y = element_text(hjust = 1),
+      strip.text = element_text(family = "Clear Sans", face = "bold",
+        size = rel(0.75), hjust = 0),
+      strip.background = element_rect(fill = "grey90", color = NA))
+}
+
+set_annotation_fonts <- function() {
+  ggplot2::update_geom_defaults("label", list(family = "Clear Sans", face = "plain"))
+  ggplot2::update_geom_defaults("text", list(family = "Clear Sans", face = "plain"))
+}
+
+
+# Labeling and formatting stuff
+build_ci <- function(lower, upper) {
+  glue::glue("[{fmt_decimal(lower)}, {fmt_decimal(upper)}]")
+}

### 2023-08-28 R/funs_grids.R

@@ -1,0 +1,21 @@
+create_ref_grid_features_only <- function() {
+  suppressPackageStartupMessages(library(Matrix))
+  
+  all_combos <- expand_grid(
+    feat_org = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"), 
+    feat_issue = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
+    feat_transp = c("No", "Yes"), 
+    feat_acc = c("No", "Yes"),
+    feat_funding = c("Many small donors", "Handful of wealthy private donors", "Government grants"),
+    feat_govt = c("Friendly", "Criticized", "Under crackdown")
+  ) %>% 
+    mutate(across(everything(), ~fct_inorder(.)))
+  
+  all_combos_design_grid <- sparse.model.matrix(
+    ~ 0 + feat_org + feat_issue + feat_transp + 
+      feat_acc + feat_funding + feat_govt, 
+    data = all_combos
+  )
+  
+  return(lst(all_combos, matrix = all_combos_design_grid))
+}

### 2023-08-28 R/funs_means.R

@@ -1,0 +1,23 @@
+calculate_grid_means <- function(draws, ref_grid) {
+  library(tidybayes)
+  
+  draws <- readRDS(draws)
+
+  grid_means <- draws %>% 
+    pivot_wider(names_from = i, values_from = Gamma) %>% 
+    group_by(j, .chain, .iteration, .draw) %>% 
+    nest() %>% 
+    mutate(pi = map(data, ~{
+      preds <- as.numeric(ref_grid$matrix %*% as.numeric(.))
+      ref_grid$all_combos %>% 
+        mutate(
+          .linpred = preds, 
+          # fake bc it's not actually mean(posterior_predict(.))
+          .epred = plogis(preds)
+        )
+    })) %>% 
+    select(-data) %>% 
+    unnest(pi)
+  
+  return(grid_means)
+}

### 2023-08-28 R/funs_tables.R

@@ -1,0 +1,11 @@
+opts_int <- function(x, ...) {
+  x %>% 
+    opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, ...)
+}
+
+opts_theme <- function(x) {
+  x %>% 
+    opt_table_font(font = "Inter") %>% 
+    tab_options(column_labels.font.weight = "bold",
+      row_group.font.weight = "bold")
+}

### 2023-08-28 _targets.R

@@ -1,0 +1,75 @@
+library(targets)
+library(tarchetypes)
+library(tibble)
+
+# Set the _targets store so that scripts in subdirectories can access targets
+# without using withr::with_dir() (see https://github.com/ropensci/targets/discussions/885)
+#
+# This hardcodes the absolute path in _targets.yaml, so to make this more
+# portable, we rewrite it every time this pipeline is run (and we don't track
+# _targets.yaml with git)
+tar_config_set(
+  store = here::here("_targets"),
+  script = here::here("_targets.R")
+)
+
+options(
+  tidyverse.quiet = TRUE,
+  dplyr.summarise.inform = FALSE
+)
+
+set.seed(265927) # From random.org
+
+tar_option_set(
+  packages = c("tidyverse", "Matrix"),
+  format = "qs"
+)
+
+# here::here() returns an absolute path, which then gets stored in tar_meta and
+# becomes computer-specific (i.e. /Users/andrew/Research/blah/thing.Rmd).
+# There's no way to get a relative path directly out of here::here(), but
+# fs::path_rel() works fine with it (see
+# https://github.com/r-lib/here/issues/36#issuecomment-530894167)
+here_rel <- function(...) {fs::path_rel(here::here(...))}
+
+# Load R scripts with functions to use in the pipeline
+lapply(list.files("R", full.names = TRUE, recursive = TRUE), source)
+
+# Actual pipeline ---------------------------------------------------------
+list(
+  ## Data and draws ----
+  tar_target(gammas_intercept_only,
+    here_rel("data", "raw_data", "posterior_draws", "intercept.rds"),
+    format = "file"
+  ),
+  
+  
+  ## Graphics and tables ----
+  tar_target(graphic_functions, lst(
+    theme_ngo, set_annotation_fonts, clrs, build_ci
+  )),
+  tar_target(table_functions, lst(opts_int, opts_theme)),
+  
+  
+  ## Create reference grid(s) ----
+  tar_target(ref_grid_features_only, create_ref_grid_features_only()),
+  
+  ## Calculate predicted values for reference grids ----
+  tar_target(means_features_only, calculate_grid_means(gammas_intercept_only, ref_grid_features_only))#,
+
+  ## Analysis ----
+  # tar_target(summary_activities, make_activities_summary(survey_orgs)),
+  # tar_target(models_activities, make_activities_models(summary_activities))#,
[…]

### 2023-08-28 notebook/results-branding.qmd
Divide results into separate notebook pages

--- 2023-08-26 hypotheses.qmd
@@
 ---
-title: Hypotheses
+title: "H~1~: Branding"
 format:
@@
 
-```{r libraries-functions, warning=FALSE, message=FALSE}
+```{r libraries-data, warning=FALSE, message=FALSE}
 library(tidyverse)
+library(targets)
+library(tidybayes)
+library(patchwork)
 library(scales)
 library(glue)
-library(here)
-library(patchwork)
-library(tidybayes)
 library(gt)
 library(gtExtras)
-library(rcartocolor)
-library(Matrix)
+library(here)
 
+# Helpful functions
 label_pp <- label_number(accuracy = 1, scale = 100, 
@@
 
-build_ci <- function(lower, upper) {
-  glue("[{fmt_decimal(lower)}, {fmt_decimal(upper)}]")
-}
+# Targets stuff
+tar_config_set(store = here('_targets'),
+               script = here('_targets.R'))
 
-theme_nice <- function() {
-  theme_minimal(base_family = "Clear Sans") +
-    theme(panel.grid.minor = element_blank(),
-      plot.title = element_text(family = "Clear Sans", face = "bold"),
-      axis.title.x = element_text(hjust = 0),
-      axis.title.y = element_text(hjust = 1),
-      strip.text = element_text(family = "Clear Sans", face = "bold",
-        size = rel(0.75), hjust = 0),
-      strip.background = element_rect(fill = "grey90", color = NA))
-}
+tar_load(c(means_features_only))
 
-opts_theme <- function(x) {
-  x %>% 
-    opt_table_font(font = "Inter") %>% 
-    tab_options(column_labels.font.weight = "bold",
-                row_group.font.weight = "bold")
-}
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
 
-theme_set(theme_nice())
-prism <- carto_pal(name = "Prism")
-peach <- carto_pal(name = "Peach")
+theme_set(theme_ngo())
 ```
-
-```{r create-ref-grid}
-all_combos <- expand_grid(
-  feat_org = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"), 
-  feat_issue = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-  feat_transp = c("No", "Yes"), 
-  feat_acc = c("No", "Yes"),
-  feat_funding = c("Many small donors", "Handful of wealthy private donors", "Government grants"),
-  feat_govt = c("Friendly", "Criticized", "Under crackdown")
-) %>% 
-  mutate(across(everything(), ~fct_inorder(.)))
-
-all_combos_design_grid <- sparse.model.matrix(
-  ~ 0 + feat_org + feat_issue + feat_transp + 
-    feat_acc + feat_funding + feat_govt, 
-  data = all_combos
-)
-```
-
-```{r create-all-combos-means}
-gammas_raw <- readRDS(here("data", "raw_data", "posterior_draws", "intercept.rds"))
-
-all_combos_means <- gammas_raw %>% 
-  pivot_wider(names_from = i, values_from = Gamma) %>% 
-  group_by(j, .chain, .iteration, .draw) %>% 
-  nest() %>% 
-  mutate(pi = map(data, ~{
-    preds <- as.numeric(all_combos_design_grid %*% as.numeric(.))
-    all_combos %>% 
-      mutate(
-        .linpred = preds, 
-        # fake bc it's not actually mean(posterior_predict(.))
-        .epred = plogis(preds)
-      )
-  })) %>% 
-  select(-data) %>% 
-  unnest(pi)
-```
-
-# Model
-
-TODO: Intercept only because (1) LOO is best, and (2) it makes most sense causally since all confounding arrows are deleted due to randomization
-
-# Method: Marginal means
-
-To find the causal effects defined in each of our estimands, we calculate estimated marginal means (EMMs) by finding the fitted values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (4 organizations × 4 issues × 2 transparency × 2 accountability × 3 funding × 3 government relationship = 576 rows).
-We transform these estimates to the probability scale in order to work directly with predicted probabilities rather than the link (logit) scale.
-We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.
-
-TODO: Simple example here to just to illustrate the process—show literal marginal means in the margins of a balanced reference grid, then subtract them for the difference in marginal means, or AMCEs
-
-Here's what the full grid of 576 options looks like, with posterior median predictions for each combination:
-
-```{r}
-#| column: screen-inset
-all_combos_means %>% 
-  group_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>% 
-  summarize(avg = mean(.epred)) %>% 
-  ungroup() %>% 
-  gt() %>% 
-  cols_align(align = "left") %>% 
-  cols_label(
-    feat_org = "Organization",
-    feat_issue = "Issue",
-    feat_transp = "Transparency",
-    feat_acc = "Accountability",
-    feat_funding = "Funding",
-    feat_govt = "Relationship",
-    avg = "Median probability"
-  ) %>% 
-  opts_theme() %>% 
-  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, use_filters = TRUE)
-```
-
-# H~1~: Branding
 
@@
 
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace.
-However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam.
-In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International.
-
-![](img/contrasts_hypothesis01.png)
-:::
-
 ```{r h1-calc-estimands}
-h1_mms <- all_combos_means %>% 
+h1_mms <- means_features_only %>% 
   group_by(feat_org, .draw) %>% 
@@
 ```{r plot-h1-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: body-outset
+#| column: page-inset-right
 p_h1_mms <- h1_mms %>% 
@@
   scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(1, 3, 5, 7)], guide = "none") +
+  scale_fill_manual(values = clrs$prism[c(1, 3, 5, 7)], guide = "none") +
   labs(
@@
   stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
+  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
   scale_x_continuous(labels = label_pp) +
   scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(1, 3, 5, 7)], guide = "none") +
+  scale_fill_manual(values = clrs$prism[c(1, 3, 5, 7)], guide = "none") +
   labs(
@@
 ```{r table-h1-mm-amce}
-#| column: body-outset
+#| column: page-inset-right
 h1_tbl_mm <- h1_mms %>% 
@@
 ```
-
-# H~2~: Government crackdown
-
-## H~2a~: Relationship with host government
-
-::: {.callout-tip}
-## H~2a~: Relationship with host government
-
-**Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism.**
-
-*Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively.
-This perception of efficacy leads to increased donations.*
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Under crackdown} \right) \bigr] - 
-\textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Friendly} \right) \bigr] \\[10pt]
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Criticized} \right) \bigr] - \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Friendly} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism.
-This decreased likelihood to donate is also greater for NGOs under crackdown compared to those under criticism.
-
-![](img/contrasts_hypothesis02a.png)
-:::
-
-```{r h2a-calc-estimands}
-h2a_mms <- all_combos_means %>% 
-  group_by(feat_govt, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h2a_amces <- h2a_mms %>% 
-  group_by(feat_govt) %>% 
-  compare_levels(variable = avg, by = feat_govt, comparison = "control")
-```
-
-```{r plot-h2a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: body-outset
-p_h2a_mms <- h2a_mms %>% 
-  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
-  stat_halfeye() +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    title = "Estimated marginal means"
-  )
-
-p_h2a_amces <- h2a_amces %>% 
-  ungroup() %>% 
-  separate_wider_delim(
-    feat_govt,
-    delim = " - ", 
-    names = c("feat_govt", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feat_govt = "Friendly") %>%
-  mutate(feat_govt = factor(feat_govt, levels = levels(h2a_mms$feat_govt))) %>% 
-  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Average marginal component effects (AMCEs)"
-  )
-
-p_h2a_mms | p_h2a_amces
-```
-
-```{r table-h2a-mm-amce}
-#| column: body-outset
-h2a_tbl_mm <- h2a_mms %>% 
-  group_by(feat_govt) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(feat_govt, nice)
-
-h2a_tbl_amces <- h2a_amces %>% 
-  group_by(feat_govt) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_govt = str_replace(feat_govt, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(contrast = feat_govt, amce_nice = nice, p_neq_0)
-
-bind_cols(
-  h2a_tbl_mm, 
-  add_row(h2a_tbl_amces, contrast = "*(Reference)*")
-) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_govt, contrast)) %>% 
-  cols_label(
-    feat_govt = "Relationship", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    amce_nice = "Posterior AMCE",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, amce_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-## H~2b~: Organization and relationship with host government
-
-::: {.callout-tip}
-## H~2b~: Organization and relationship with host government
-
-**Donors will show increased willingness to donate to Oxfam and Red Cross when they are facing government crackdown or criticism compared to when Amnesty or Greenpeace is facing crackdown.**
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Oxfam or Red Cross}  \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr] - \\
-&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Amnesty International or Greenpeace} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-These data don't support our hypothesis; the Red Cross brand has an insignificant impact on likelihood to donate compared to both Greenpeace and Amnesty.
-While the contrasts for Oxfam are closer to being statistically significant, the effect is working in the other direction--Greenpeace and Amnesty both induce increased likelihood to donate on behalf of donors.
-
-![](img/contrasts_hypothesis02b.png)
-
-![](img/contrasts_hypothesis02b_alt.png)
-:::
-
-```{r h2b-calc-estimands}
-h2b_mms <- all_combos_means %>% 
-  mutate(org_collapsed = fct_collapse(feat_org, 
-    `Oxfam & Red Cross` = c("Oxfam", "Red Cross"),
-    `Amnesty International & Greenpeace` = c("Amnesty International", "Greenpeace"))) %>% 
-  group_by(org_collapsed, feat_govt, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h2b_amces <- h2b_mms %>% 
-  group_by(feat_govt) %>% 
-  compare_levels(variable = avg, by = org_collapsed, comparison = "control")
-```
-
-```{r plot-h2b-mm-amce, fig.width=6.5, fig.height=7, out.width="70%"}
-#| column: body-outset
-p_h2b_mms <- h2b_mms %>% 
-  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
-  stat_halfeye(aes(slab_alpha = org_collapsed)) +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
-  scale_slab_alpha_discrete(
-    range = c(0.4, 1),
-    guide = guide_legend(
-      reverse = TRUE, override.aes = list(fill = "grey10"), 
-      keywidth = 0.8, keyheight = 0.8, nrow = 1
-    )
-  ) +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    slab_alpha = NULL,
-    title = "Estimated marginal means"
-  ) +
-  theme(
-    legend.position = "top",
-    legend.justification = "left",
-    legend.margin = margin(l = -7, t = 0)
-  )
-
-p_h2b_amces <- h2b_amces %>% 
-  ungroup() %>% 
-  separate_wider_delim(
-    org_collapsed,
-    delim = " - ", 
-    names = c("org_collapsed", "reference_level")
-  ) %>% 
-  mutate(feat_govt = factor(feat_govt, levels = levels(h2a_mms$feat_govt))) %>% 
-  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
-  facet_wrap(vars(paste(org_collapsed, "−", reference_level))) +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Difference in estimated marginal means",
-    subtitle = "Positive values indicate greater preference for Oxfam & Red Cross"
-  )
-
-(p_h2b_mms / plot_spacer() / p_h2b_amces) +
-  plot_layout(ncol = 1, heights = c(0.49, 0.02, 0.49))
-```
-
-```{r table-h2b-mm-amce}
-#| column: body-outset
-h2b_tbl_mm <- h2b_mms %>% 
-  group_by(feat_govt, org_collapsed) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_govt), desc(org_collapsed)) %>% 
-  select(org_collapsed, feat_govt, nice)
-
-h2b_tbl_amces <- h2b_amces %>% 
-  group_by(feat_govt, org_collapsed) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  ungroup() %>% 
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(org_collapsed = str_replace(org_collapsed, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(contrast = org_collapsed, diff_nice = nice, p_neq_0)
-
-bind_cols(
-  h2b_tbl_mm, 
-  h2b_tbl_amces %>% 
-    add_row(contrast = NA, .after = 1) %>% 
-    add_row(contrast = NA, .after = 3) %>% 
-    add_row(contrast = NA, .after = 5)
-) %>% 
-  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
-  group_by(feat_govt) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(org_collapsed, contrast)) %>% 
-  cols_label(
-    org_collapsed = "Organizations", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    diff_nice = "Posterior ∆",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_style(
-    style = cell_fill(color = "grey90"),
-    locations = cells_row_groups()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, diff_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-# H~3~: Issue Area
-
-## H~3a~: Issue area
-
-::: {.callout-tip}
-## H~3a~: Issue area
-
-**Donors will show increased willingness to donate to NGOs working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights).**
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{More contentious} \right) \bigr] -
-\textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{Less contentious} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors appear to be sensitive to NGO issue area when they are considering to donate.
-Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations.
-While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs, which was contrary to our expectations.
-It is worth noting that there is some overlap between the intervals of the issue areas, which would suggest that their effect isn't as significant as other factors.
-:::
-
-```{r h3a-calc-estimands}
-h3a_mms <- all_combos_means %>% 
-  group_by(feat_issue, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h3a_amces <- h3a_mms %>% 
-  group_by(feat_issue) %>% 
-  compare_levels(variable = avg, by = feat_issue, comparison = "control")
-```
-
-```{r plot-h3a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: body-outset
-p_h3a_mms <- h3a_mms %>% 
-  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
-  stat_halfeye() +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    title = "Estimated marginal means"
-  )
-
-p_h3a_amces <- h3a_amces %>% 
-  ungroup() %>% 
-  separate_wider_delim(
-    feat_issue,
-    delim = " - ", 
-    names = c("feat_issue", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feat_issue = "Emergency response") %>%
-  mutate(feat_issue = factor(feat_issue, levels = levels(h3a_mms$feat_issue))) %>% 
-  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Average marginal component effects (AMCEs)"
-  )
-
-p_h3a_mms | p_h3a_amces
-```
-
-```{r table-h3a-mm-amce}
-#| column: body-outset
-h3a_tbl_mm <- h3a_mms %>% 
-  group_by(feat_issue) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_issue)) %>% 
-  select(feat_issue, nice)
-
-h3a_tbl_amces <- h3a_amces %>% 
-  group_by(feat_issue) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_issue = str_replace(feat_issue, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_issue)) %>% 
-  select(contrast = feat_issue, amce_nice = nice, p_neq_0)
-
-bind_cols(
-  h3a_tbl_mm, 
-  add_row(h3a_tbl_amces, contrast = "*(Reference)*")
-) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_issue, contrast)) %>% 
-  cols_label(
-    feat_issue = "Issue area", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    amce_nice = "Posterior AMCE",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, amce_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-## H~3b~: Relationship with host government and issue area
-
-::: {.callout-tip}
-## H~3b~: Relationship with host government and issue area
-
-**Donors will show increased willingness to donate to NGOs facing government crackdown/criticism working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights)**
-
-*Mechanisms: Perceptions of deservingness of NGOs dealing with emergency response and refugee relief.
-Donors are also more likely to donate to programs that are compatible with government preferences and have easily measurable outputs, which environment and human rights programs often lack.
-NGOs working on more contentious issue areas may be expelled or shut down, which would be a waste of donor resources, make it less likely that they donate to these groups.*
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{More contentious}  \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr] - \\
-&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{Less contentnious} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-The generated contrasts don't provides results which are statistically significant. 0 is found within all intervals.
-
-![](img/contrasts_hypothesis03b.png)
-:::
-
-```{r h3b-calc-estimands}
-h3b_mms <- all_combos_means %>% 
-  group_by(feat_issue, feat_govt, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h3b_amces <- h3b_mms %>% 
-  group_by(feat_govt) %>% 
-  compare_levels(variable = avg, by = feat_issue, comparison = "control")
-```
-
-```{r plot-h3b-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
-#| column: body-outset
-p_h3b_mms <- h3b_mms %>% 
-  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
-  stat_halfeye() +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
-  facet_wrap(vars(feat_govt), ncol = 1) +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    title = "Estimated marginal means"
-  ) +
-  theme(
-    legend.position = "top",
-    legend.justification = "left",
-    legend.margin = margin(l = -7, t = 0)
-  )
-
-p_h3b_amces <- h3b_amces %>% 
-  ungroup() %>% 
-  separate_wider_delim(
-    feat_issue,
-    delim = " - ", 
-    names = c("feat_issue", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Friendly") %>%
-  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Criticized") %>%
-  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Under crackdown") %>%
-  mutate(feat_issue = factor(feat_issue, levels = levels(h3b_mms$feat_issue))) %>% 
-  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
-  facet_wrap(vars(feat_govt), ncol = 1) +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Difference in estimated marginal means"
-  )
-
-p_h3b_mms | p_h3b_amces
-```
-
-```{r table-h3b-mm-amce}
-#| column: body-outset
-h3b_tbl_mm <- h3b_mms %>% 
-  group_by(feat_govt, feat_issue) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_govt), desc(feat_issue)) %>% 
-  select(feat_issue, feat_govt, nice)
-
-h3b_tbl_amces <- h3b_amces %>% 
-  group_by(feat_govt, feat_issue) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  ungroup() %>% 
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_issue = str_replace(feat_issue, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(contrast = feat_issue, diff_nice = nice, p_neq_0)
-
-bind_cols(
-  h3b_tbl_mm, 
-  h3b_tbl_amces %>% 
-    add_row(contrast = NA, .after = 3) %>% 
-    add_row(contrast = NA, .after = 7) %>% 
-    add_row(contrast = NA, .after = 12)
-) %>% 
-  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
-  group_by(feat_govt) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_issue, contrast)) %>% 
-  cols_label(
-    feat_issue = "Issue", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    diff_nice = "Posterior ∆",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_style(
-    style = cell_fill(color = "grey90"),
-    locations = cells_row_groups()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, diff_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-# H~4~: Funding sources
-
-## H~4a~: Funding sources
-
-> Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealthy private donors and government grants [Mechanism: Perception of efficacy - your contribution matters as a small donor.
-Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.]
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-As stated in the hypothesis, donors show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants.
-
-![](img/contrasts_hypothesis04.png)
-:::
-
-## H~4b~: Relationship with host government and funding sources
-
-> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-The marginal posteriors for these contrasts are strange, but still tell us that the interaction between funding sources and government relationship produce no significant effects.
-
-![](img/contrasts_hypothesis04b.png)
-:::
-
-## H~4c~: Relationship with host government, funding sources, and issue area
-
-> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors and work in less contentious areas (emergency response and refugee relief)
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Once again, we see some interesting distributions, but no results significant enough to confirm our hypothesis.
-
-![](img/contrasts_hypothesis04c.png)
-:::
-
-# H~5~: Organizational practices
-
-## H~5a~: Organizational practices
-
-> Donors will show increased willingness to donate to NGOs that are financially transparent [Mechanism: Perception of efficacy]
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors show an increased likelihood to donate to NGOs that are financially transparent, as hypothesized.
-
-![](img/contrasts_hypothesis05.png)
-:::
-
-## H~5b~: Relationship with host government, organizational practices
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent.
-However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
-
-![](img/contrasts_hypothesis05b.png)
-:::
-
-## H~5c~: Relationship with host government, organizational practices, and funding sources
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and are funded primarily by numerous small private donors
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-These intervals are massive; 0 is well within them, leaving us with insufficient evidence to confirm the hypothesis.
-
-![](img/contrasts_hypothesis05c.png)
-:::
-
-## H~5d~: Relationship with host government, organizational practices, and issue area
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief)
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-The contrasts don't support the hypothesis, however, there is an interesting difference between emergency_environment_crackdown and emergency_environment_criticized.
-
-![](img/contrasts_hypothesis05d.png)
-:::
-
-## H~5e~: Relationship with host government, organizational practices, issue area, and funding sources
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-These marginal posteriors don't support our hypothesis, but again show an interesting difference between emergency_environment_criticized and emergency_environment_crackdown.
-
-![](img/contrasts_hypothesis05e.png)
-:::
-
-## H~5f~: Organizational practices
-
-> Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits [Mechanism: Donors don't necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks]
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent.
-However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
-
-![](img/contrasts_hypothesis05f.png)
-:::

### 2023-08-28 notebook/results-branding.qmd
Add H2 and H3

@@
 
+# H~1~: Branding
+
 ::: {.callout-tip}
@@
 
-### Estimand
+## Estimand
 
@@
 ```{r plot-h1-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: page-inset-right
+#| column: body-outset-right
 p_h1_mms <- h1_mms %>% 
@@
 ```{r table-h1-mm-amce}
-#| column: page-inset-right
+#| column: body-outset-right
 h1_tbl_mm <- h1_mms %>% 

### 2023-08-28 notebook/results-crackdown.qmd
Add H2 and H3

--- 2023-08-26 hypotheses.qmd
@@
 ---
-title: Hypotheses
+title: "H~2~: Government crackdown"
 format:
@@
 
-build_ci <- function(lower, upper) {
-  glue("[{fmt_decimal(lower)}, {fmt_decimal(upper)}]")
-}
+# Targets stuff
+tar_config_set(store = here('_targets'),
+               script = here('_targets.R'))
 
-theme_nice <- function() {
-  theme_minimal(base_family = "Clear Sans") +
-    theme(panel.grid.minor = element_blank(),
-      plot.title = element_text(family = "Clear Sans", face = "bold"),
-      axis.title.x = element_text(hjust = 0),
-      axis.title.y = element_text(hjust = 1),
-      strip.text = element_text(family = "Clear Sans", face = "bold",
-        size = rel(0.75), hjust = 0),
-      strip.background = element_rect(fill = "grey90", color = NA))
-}
+tar_load(c(means_features_only))
 
-opts_theme <- function(x) {
-  x %>% 
-    opt_table_font(font = "Inter") %>% 
-    tab_options(column_labels.font.weight = "bold",
-                row_group.font.weight = "bold")
-}
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
 
-theme_set(theme_nice())
-prism <- carto_pal(name = "Prism")
-peach <- carto_pal(name = "Peach")
+theme_set(theme_ngo())
 ```
 
-```{r create-ref-grid}
-all_combos <- expand_grid(
-  feat_org = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"), 
-  feat_issue = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-  feat_transp = c("No", "Yes"), 
-  feat_acc = c("No", "Yes"),
-  feat_funding = c("Many small donors", "Handful of wealthy private donors", "Government grants"),
-  feat_govt = c("Friendly", "Criticized", "Under crackdown")
-) %>% 
-  mutate(across(everything(), ~fct_inorder(.)))
-
-all_combos_design_grid <- sparse.model.matrix(
-  ~ 0 + feat_org + feat_issue + feat_transp + 
-    feat_acc + feat_funding + feat_govt, 
-  data = all_combos
-)
-```
-
-```{r create-all-combos-means}
-gammas_raw <- readRDS(here("data", "raw_data", "posterior_draws", "intercept.rds"))
-
-all_combos_means <- gammas_raw %>% 
-  pivot_wider(names_from = i, values_from = Gamma) %>% 
-  group_by(j, .chain, .iteration, .draw) %>% 
-  nest() %>% 
-  mutate(pi = map(data, ~{
-    preds <- as.numeric(all_combos_design_grid %*% as.numeric(.))
-    all_combos %>% 
-      mutate(
-        .linpred = preds, 
-        # fake bc it's not actually mean(posterior_predict(.))
-        .epred = plogis(preds)
-      )
-  })) %>% 
-  select(-data) %>% 
-  unnest(pi)
-```
-
-# Model
-
-TODO: Intercept only because (1) LOO is best, and (2) it makes most sense causally since all confounding arrows are deleted due to randomization
-
-# Method: Marginal means
-
-To find the causal effects defined in each of our estimands, we calculate estimated marginal means (EMMs) by finding the fitted values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (4 organizations × 4 issues × 2 transparency × 2 accountability × 3 funding × 3 government relationship = 576 rows).
-We transform these estimates to the probability scale in order to work directly with predicted probabilities rather than the link (logit) scale.
-We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.
-
-TODO: Simple example here to just to illustrate the process—show literal marginal means in the margins of a balanced reference grid, then subtract them for the difference in marginal means, or AMCEs
-
-Here's what the full grid of 576 options looks like, with posterior median predictions for each combination:
-
-```{r}
-#| column: screen-inset
-all_combos_means %>% 
-  group_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>% 
-  summarize(avg = mean(.epred)) %>% 
-  ungroup() %>% 
-  gt() %>% 
-  cols_align(align = "left") %>% 
-  cols_label(
-    feat_org = "Organization",
-    feat_issue = "Issue",
-    feat_transp = "Transparency",
-    feat_acc = "Accountability",
-    feat_funding = "Funding",
-    feat_govt = "Relationship",
-    avg = "Median probability"
-  ) %>% 
-  opts_theme() %>% 
-  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, use_filters = TRUE)
-```
-
-# H~1~: Branding
-
-::: {.callout-tip}
-## H~1~: Branding
-
-**Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace.**
-
-*Mechanism: awareness of need and contentiousness of issue area*
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Oxfam or Red Cross} \right) \bigr] - \\
-&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Amnesty International or Greenpeace} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace.
-However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam.
-In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International.
-
-![](img/contrasts_hypothesis01.png)
-:::
-
-```{r h1-calc-estimands}
-h1_mms <- all_combos_means %>% 
-  group_by(feat_org, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h1_amces <- h1_mms %>% 
-  group_by(feat_org) %>% 
-  compare_levels(variable = avg, by = feat_org, comparison = "control")
-```
-
-```{r plot-h1-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: body-outset
-p_h1_mms <- h1_mms %>% 
-  ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +
-  stat_halfeye() +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(1, 3, 5, 7)], guide = "none") +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    title = "Estimated marginal means"
-  )
-
-p_h1_amces <- h1_amces %>% 
-  ungroup() %>% 
-    separate_wider_delim(
-    feat_org,
-    delim = " - ", 
-    names = c("feat_org", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feat_org = "Amnesty International") %>% 
-  ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(1, 3, 5, 7)], guide = "none") +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Average marginal component effects (AMCEs)"
-  )
-
-p_h1_mms | p_h1_amces
-```
-
-```{r table-h1-mm-amce}
-#| column: body-outset
-h1_tbl_mm <- h1_mms %>% 
-  group_by(feat_org) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_org)) %>% 
-  select(feat_org, nice)
-
-h1_tbl_amces <- h1_amces %>% 
-  group_by(feat_org) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_org = str_replace(feat_org, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_org)) %>% 
-  select(contrast = feat_org, amce_nice = nice, p_neq_0)
-
-bind_cols(
-  h1_tbl_mm, 
-  add_row(h1_tbl_amces, contrast = "*(Reference)*")
-) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_org, contrast)) %>% 
-  cols_label(
-    feat_org = "Organization", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    amce_nice = "Posterior AMCE",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, amce_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-# H~2~: Government crackdown
-
-## H~2a~: Relationship with host government
+# H~2a~: Relationship with host government
 
@@
 
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism.
-This decreased likelihood to donate is also greater for NGOs under crackdown compared to those under criticism.
-
-![](img/contrasts_hypothesis02a.png)
-:::
-
 ```{r h2a-calc-estimands}
-h2a_mms <- all_combos_means %>% 
+h2a_mms <- means_features_only %>% 
   group_by(feat_govt, .draw) %>% 
@@
 ```{r plot-h2a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: body-outset
+#| column: body-outset-right
 p_h2a_mms <- h2a_mms %>% 
@@
   scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
+  scale_fill_manual(values = clrs$peach[c(2, 5, 7)], guide = "none") +
   labs(
@@
   stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
+  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
   scale_x_continuous(labels = label_pp) +
   scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
+  scale_fill_manual(values = clrs$peach[c(2, 5, 7)], guide = "none") +
   labs(
@@
 ```{r table-h2a-mm-amce}
-#| column: body-outset
+#| column: body-outset-right
 h2a_tbl_mm <- h2a_mms %>% 
@@
 
-## H~2b~: Organization and relationship with host government
+# H~2b~: Organization and relationship with host government
 
@@
 
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-These data don't support our hypothesis; the Red Cross brand has an insignificant impact on likelihood to donate compared to both Greenpeace and Amnesty.
-While the contrasts for Oxfam are closer to being statistically significant, the effect is working in the other direction--Greenpeace and Amnesty both induce increased likelihood to donate on behalf of donors.
-
-![](img/contrasts_hypothesis02b.png)
-
-![](img/contrasts_hypothesis02b_alt.png)
-:::
-
 ```{r h2b-calc-estimands}
-h2b_mms <- all_combos_means %>% 
+h2b_mms <- means_features_only %>% 
   mutate(org_collapsed = fct_collapse(feat_org, 
@@
 ```{r plot-h2b-mm-amce, fig.width=6.5, fig.height=7, out.width="70%"}
-#| column: body-outset
+#| column: body-outset-right
 p_h2b_mms <- h2b_mms %>% 
@@
   scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
+  scale_fill_manual(values = clrs$peach[c(2, 5, 7)], guide = "none") +
   scale_slab_alpha_discrete(
@@
   stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
+  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
   scale_x_continuous(labels = label_pp) +
   scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
+  scale_fill_manual(values = clrs$peach[c(2, 5, 7)], guide = "none") +
   facet_wrap(vars(paste(org_collapsed, "−", reference_level))) +
@@
 ```{r table-h2b-mm-amce}
-#| column: body-outset
+#| column: body-outset-right
 h2b_tbl_mm <- h2b_mms %>% 
@@
 ```
-
-# H~3~: Issue Area
-
-## H~3a~: Issue area
-
-::: {.callout-tip}
-## H~3a~: Issue area
-
-**Donors will show increased willingness to donate to NGOs working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights).**
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{More contentious} \right) \bigr] -
-\textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{Less contentious} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors appear to be sensitive to NGO issue area when they are considering to donate.
-Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations.
-While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs, which was contrary to our expectations.
-It is worth noting that there is some overlap between the intervals of the issue areas, which would suggest that their effect isn't as significant as other factors.
-:::
-
-```{r h3a-calc-estimands}
-h3a_mms <- all_combos_means %>% 
-  group_by(feat_issue, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h3a_amces <- h3a_mms %>% 
-  group_by(feat_issue) %>% 
-  compare_levels(variable = avg, by = feat_issue, comparison = "control")
-```
-
-```{r plot-h3a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: body-outset
-p_h3a_mms <- h3a_mms %>% 
-  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
-  stat_halfeye() +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    title = "Estimated marginal means"
-  )
-
-p_h3a_amces <- h3a_amces %>% 
-  ungroup() %>% 
-  separate_wider_delim(
-    feat_issue,
-    delim = " - ", 
-    names = c("feat_issue", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feat_issue = "Emergency response") %>%
-  mutate(feat_issue = factor(feat_issue, levels = levels(h3a_mms$feat_issue))) %>% 
-  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Average marginal component effects (AMCEs)"
-  )
-
-p_h3a_mms | p_h3a_amces
-```
-
-```{r table-h3a-mm-amce}
-#| column: body-outset
-h3a_tbl_mm <- h3a_mms %>% 
-  group_by(feat_issue) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_issue)) %>% 
-  select(feat_issue, nice)
-
-h3a_tbl_amces <- h3a_amces %>% 
-  group_by(feat_issue) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_issue = str_replace(feat_issue, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_issue)) %>% 
-  select(contrast = feat_issue, amce_nice = nice, p_neq_0)
-
-bind_cols(
-  h3a_tbl_mm, 
-  add_row(h3a_tbl_amces, contrast = "*(Reference)*")
-) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_issue, contrast)) %>% 
-  cols_label(
-    feat_issue = "Issue area", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    amce_nice = "Posterior AMCE",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, amce_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-## H~3b~: Relationship with host government and issue area
-
-::: {.callout-tip}
-## H~3b~: Relationship with host government and issue area
-
-**Donors will show increased willingness to donate to NGOs facing government crackdown/criticism working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights)**
-
-*Mechanisms: Perceptions of deservingness of NGOs dealing with emergency response and refugee relief.
-Donors are also more likely to donate to programs that are compatible with government preferences and have easily measurable outputs, which environment and human rights programs often lack.
-NGOs working on more contentious issue areas may be expelled or shut down, which would be a waste of donor resources, make it less likely that they donate to these groups.*
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{More contentious}  \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr] - \\
-&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{Less contentnious} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-The generated contrasts don't provides results which are statistically significant. 0 is found within all intervals.
-
-![](img/contrasts_hypothesis03b.png)
-:::
-
-```{r h3b-calc-estimands}
-h3b_mms <- all_combos_means %>% 
-  group_by(feat_issue, feat_govt, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h3b_amces <- h3b_mms %>% 
-  group_by(feat_govt) %>% 
-  compare_levels(variable = avg, by = feat_issue, comparison = "control")
-```
-
-```{r plot-h3b-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
-#| column: body-outset
-p_h3b_mms <- h3b_mms %>% 
-  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
-  stat_halfeye() +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
-  facet_wrap(vars(feat_govt), ncol = 1) +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    title = "Estimated marginal means"
-  ) +
-  theme(
-    legend.position = "top",
-    legend.justification = "left",
-    legend.margin = margin(l = -7, t = 0)
-  )
-
-p_h3b_amces <- h3b_amces %>% 
-  ungroup() %>% 
-  separate_wider_delim(
-    feat_issue,
-    delim = " - ", 
-    names = c("feat_issue", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Friendly") %>%
-  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Criticized") %>%
-  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Under crackdown") %>%
-  mutate(feat_issue = factor(feat_issue, levels = levels(h3b_mms$feat_issue))) %>% 
-  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
-  facet_wrap(vars(feat_govt), ncol = 1) +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Difference in estimated marginal means"
-  )
-
-p_h3b_mms | p_h3b_amces
-```
-
-```{r table-h3b-mm-amce}
-#| column: body-outset
-h3b_tbl_mm <- h3b_mms %>% 
-  group_by(feat_govt, feat_issue) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_govt), desc(feat_issue)) %>% 
-  select(feat_issue, feat_govt, nice)
-
-h3b_tbl_amces <- h3b_amces %>% 
-  group_by(feat_govt, feat_issue) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  ungroup() %>% 
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_issue = str_replace(feat_issue, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(contrast = feat_issue, diff_nice = nice, p_neq_0)
-
-bind_cols(
-  h3b_tbl_mm, 
-  h3b_tbl_amces %>% 
-    add_row(contrast = NA, .after = 3) %>% 
-    add_row(contrast = NA, .after = 7) %>% 
-    add_row(contrast = NA, .after = 12)
-) %>% 
-  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
-  group_by(feat_govt) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_issue, contrast)) %>% 
-  cols_label(
-    feat_issue = "Issue", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    diff_nice = "Posterior ∆",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_style(
-    style = cell_fill(color = "grey90"),
-    locations = cells_row_groups()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, diff_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-# H~4~: Funding sources
-
-## H~4a~: Funding sources
-
-> Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealthy private donors and government grants [Mechanism: Perception of efficacy - your contribution matters as a small donor.
-Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.]
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-As stated in the hypothesis, donors show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants.
-
-![](img/contrasts_hypothesis04.png)
-:::
-
-## H~4b~: Relationship with host government and funding sources
-
-> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-The marginal posteriors for these contrasts are strange, but still tell us that the interaction between funding sources and government relationship produce no significant effects.
-
-![](img/contrasts_hypothesis04b.png)
-:::
-
-## H~4c~: Relationship with host government, funding sources, and issue area
-
-> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors and work in less contentious areas (emergency response and refugee relief)
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Once again, we see some interesting distributions, but no results significant enough to confirm our hypothesis.
-
-![](img/contrasts_hypothesis04c.png)
-:::
-
-# H~5~: Organizational practices
-
-## H~5a~: Organizational practices
-
-> Donors will show increased willingness to donate to NGOs that are financially transparent [Mechanism: Perception of efficacy]
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors show an increased likelihood to donate to NGOs that are financially transparent, as hypothesized.
-
-![](img/contrasts_hypothesis05.png)
-:::
-
-## H~5b~: Relationship with host government, organizational practices
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent.
-However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
-
-![](img/contrasts_hypothesis05b.png)
-:::
-
-## H~5c~: Relationship with host government, organizational practices, and funding sources
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and are funded primarily by numerous small private donors
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-These intervals are massive; 0 is well within them, leaving us with insufficient evidence to confirm the hypothesis.
-
-![](img/contrasts_hypothesis05c.png)
-:::
-
-## H~5d~: Relationship with host government, organizational practices, and issue area
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief)
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-The contrasts don't support the hypothesis, however, there is an interesting difference between emergency_environment_crackdown and emergency_environment_criticized.
-
-![](img/contrasts_hypothesis05d.png)
-:::
-
-## H~5e~: Relationship with host government, organizational practices, issue area, and funding sources
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-These marginal posteriors don't support our hypothesis, but again show an interesting difference between emergency_environment_criticized and emergency_environment_crackdown.
-
-![](img/contrasts_hypothesis05e.png)
-:::
-
-## H~5f~: Organizational practices
-
-> Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits [Mechanism: Donors don't necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks]
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent.
-However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
-
-![](img/contrasts_hypothesis05f.png)
-:::

### 2023-08-28 notebook/results-issue.qmd
Add H2 and H3

--- 2023-08-26 hypotheses.qmd
@@
 ---
-title: Hypotheses
+title: "H~3~: Issue area"
 format:
@@
 
-build_ci <- function(lower, upper) {
-  glue("[{fmt_decimal(lower)}, {fmt_decimal(upper)}]")
-}
+# Targets stuff
+tar_config_set(store = here('_targets'),
+               script = here('_targets.R'))
 
-theme_nice <- function() {
-  theme_minimal(base_family = "Clear Sans") +
-    theme(panel.grid.minor = element_blank(),
-      plot.title = element_text(family = "Clear Sans", face = "bold"),
-      axis.title.x = element_text(hjust = 0),
-      axis.title.y = element_text(hjust = 1),
-      strip.text = element_text(family = "Clear Sans", face = "bold",
-        size = rel(0.75), hjust = 0),
-      strip.background = element_rect(fill = "grey90", color = NA))
-}
+tar_load(c(means_features_only))
 
-opts_theme <- function(x) {
-  x %>% 
-    opt_table_font(font = "Inter") %>% 
-    tab_options(column_labels.font.weight = "bold",
-                row_group.font.weight = "bold")
-}
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
 
-theme_set(theme_nice())
-prism <- carto_pal(name = "Prism")
-peach <- carto_pal(name = "Peach")
+theme_set(theme_ngo())
 ```
 
-```{r create-ref-grid}
-all_combos <- expand_grid(
-  feat_org = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"), 
-  feat_issue = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-  feat_transp = c("No", "Yes"), 
-  feat_acc = c("No", "Yes"),
-  feat_funding = c("Many small donors", "Handful of wealthy private donors", "Government grants"),
-  feat_govt = c("Friendly", "Criticized", "Under crackdown")
-) %>% 
-  mutate(across(everything(), ~fct_inorder(.)))
-
-all_combos_design_grid <- sparse.model.matrix(
-  ~ 0 + feat_org + feat_issue + feat_transp + 
-    feat_acc + feat_funding + feat_govt, 
-  data = all_combos
-)
-```
-
-```{r create-all-combos-means}
-gammas_raw <- readRDS(here("data", "raw_data", "posterior_draws", "intercept.rds"))
-
-all_combos_means <- gammas_raw %>% 
-  pivot_wider(names_from = i, values_from = Gamma) %>% 
-  group_by(j, .chain, .iteration, .draw) %>% 
-  nest() %>% 
-  mutate(pi = map(data, ~{
-    preds <- as.numeric(all_combos_design_grid %*% as.numeric(.))
-    all_combos %>% 
-      mutate(
-        .linpred = preds, 
-        # fake bc it's not actually mean(posterior_predict(.))
-        .epred = plogis(preds)
-      )
-  })) %>% 
-  select(-data) %>% 
-  unnest(pi)
-```
-
-# Model
-
-TODO: Intercept only because (1) LOO is best, and (2) it makes most sense causally since all confounding arrows are deleted due to randomization
-
-# Method: Marginal means
-
-To find the causal effects defined in each of our estimands, we calculate estimated marginal means (EMMs) by finding the fitted values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (4 organizations × 4 issues × 2 transparency × 2 accountability × 3 funding × 3 government relationship = 576 rows).
-We transform these estimates to the probability scale in order to work directly with predicted probabilities rather than the link (logit) scale.
-We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.
-
-TODO: Simple example here to just to illustrate the process—show literal marginal means in the margins of a balanced reference grid, then subtract them for the difference in marginal means, or AMCEs
-
-Here's what the full grid of 576 options looks like, with posterior median predictions for each combination:
-
-```{r}
-#| column: screen-inset
-all_combos_means %>% 
-  group_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>% 
-  summarize(avg = mean(.epred)) %>% 
-  ungroup() %>% 
-  gt() %>% 
-  cols_align(align = "left") %>% 
-  cols_label(
-    feat_org = "Organization",
-    feat_issue = "Issue",
-    feat_transp = "Transparency",
-    feat_acc = "Accountability",
-    feat_funding = "Funding",
-    feat_govt = "Relationship",
-    avg = "Median probability"
-  ) %>% 
-  opts_theme() %>% 
-  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, use_filters = TRUE)
-```
-
-# H~1~: Branding
-
-::: {.callout-tip}
-## H~1~: Branding
-
-**Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace.**
-
-*Mechanism: awareness of need and contentiousness of issue area*
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Oxfam or Red Cross} \right) \bigr] - \\
-&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Amnesty International or Greenpeace} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace.
-However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam.
-In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International.
-
-![](img/contrasts_hypothesis01.png)
-:::
-
-```{r h1-calc-estimands}
-h1_mms <- all_combos_means %>% 
-  group_by(feat_org, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h1_amces <- h1_mms %>% 
-  group_by(feat_org) %>% 
-  compare_levels(variable = avg, by = feat_org, comparison = "control")
-```
-
-```{r plot-h1-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: body-outset
-p_h1_mms <- h1_mms %>% 
-  ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +
-  stat_halfeye() +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(1, 3, 5, 7)], guide = "none") +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    title = "Estimated marginal means"
-  )
-
-p_h1_amces <- h1_amces %>% 
-  ungroup() %>% 
-    separate_wider_delim(
-    feat_org,
-    delim = " - ", 
-    names = c("feat_org", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feat_org = "Amnesty International") %>% 
-  ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(1, 3, 5, 7)], guide = "none") +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Average marginal component effects (AMCEs)"
-  )
-
-p_h1_mms | p_h1_amces
-```
-
-```{r table-h1-mm-amce}
-#| column: body-outset
-h1_tbl_mm <- h1_mms %>% 
-  group_by(feat_org) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_org)) %>% 
-  select(feat_org, nice)
-
-h1_tbl_amces <- h1_amces %>% 
-  group_by(feat_org) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_org = str_replace(feat_org, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_org)) %>% 
-  select(contrast = feat_org, amce_nice = nice, p_neq_0)
-
-bind_cols(
-  h1_tbl_mm, 
-  add_row(h1_tbl_amces, contrast = "*(Reference)*")
-) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_org, contrast)) %>% 
-  cols_label(
-    feat_org = "Organization", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    amce_nice = "Posterior AMCE",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, amce_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-# H~2~: Government crackdown
-
-## H~2a~: Relationship with host government
-
-::: {.callout-tip}
-## H~2a~: Relationship with host government
-
-**Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism.**
-
-*Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively.
-This perception of efficacy leads to increased donations.*
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Under crackdown} \right) \bigr] - 
-\textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Friendly} \right) \bigr] \\[10pt]
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Criticized} \right) \bigr] - \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Friendly} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism.
-This decreased likelihood to donate is also greater for NGOs under crackdown compared to those under criticism.
-
-![](img/contrasts_hypothesis02a.png)
-:::
-
-```{r h2a-calc-estimands}
-h2a_mms <- all_combos_means %>% 
-  group_by(feat_govt, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h2a_amces <- h2a_mms %>% 
-  group_by(feat_govt) %>% 
-  compare_levels(variable = avg, by = feat_govt, comparison = "control")
-```
-
-```{r plot-h2a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: body-outset
-p_h2a_mms <- h2a_mms %>% 
-  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
-  stat_halfeye() +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    title = "Estimated marginal means"
-  )
-
-p_h2a_amces <- h2a_amces %>% 
-  ungroup() %>% 
-  separate_wider_delim(
-    feat_govt,
-    delim = " - ", 
-    names = c("feat_govt", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feat_govt = "Friendly") %>%
-  mutate(feat_govt = factor(feat_govt, levels = levels(h2a_mms$feat_govt))) %>% 
-  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Average marginal component effects (AMCEs)"
-  )
-
-p_h2a_mms | p_h2a_amces
-```
-
-```{r table-h2a-mm-amce}
-#| column: body-outset
-h2a_tbl_mm <- h2a_mms %>% 
-  group_by(feat_govt) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(feat_govt, nice)
-
-h2a_tbl_amces <- h2a_amces %>% 
-  group_by(feat_govt) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_govt = str_replace(feat_govt, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(contrast = feat_govt, amce_nice = nice, p_neq_0)
-
-bind_cols(
-  h2a_tbl_mm, 
-  add_row(h2a_tbl_amces, contrast = "*(Reference)*")
-) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_govt, contrast)) %>% 
-  cols_label(
-    feat_govt = "Relationship", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    amce_nice = "Posterior AMCE",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, amce_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-## H~2b~: Organization and relationship with host government
-
-::: {.callout-tip}
-## H~2b~: Organization and relationship with host government
-
-**Donors will show increased willingness to donate to Oxfam and Red Cross when they are facing government crackdown or criticism compared to when Amnesty or Greenpeace is facing crackdown.**
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Oxfam or Red Cross}  \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr] - \\
-&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Amnesty International or Greenpeace} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-These data don't support our hypothesis; the Red Cross brand has an insignificant impact on likelihood to donate compared to both Greenpeace and Amnesty.
-While the contrasts for Oxfam are closer to being statistically significant, the effect is working in the other direction--Greenpeace and Amnesty both induce increased likelihood to donate on behalf of donors.
-
-![](img/contrasts_hypothesis02b.png)
-
-![](img/contrasts_hypothesis02b_alt.png)
-:::
-
-```{r h2b-calc-estimands}
-h2b_mms <- all_combos_means %>% 
-  mutate(org_collapsed = fct_collapse(feat_org, 
-    `Oxfam & Red Cross` = c("Oxfam", "Red Cross"),
-    `Amnesty International & Greenpeace` = c("Amnesty International", "Greenpeace"))) %>% 
-  group_by(org_collapsed, feat_govt, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h2b_amces <- h2b_mms %>% 
-  group_by(feat_govt) %>% 
-  compare_levels(variable = avg, by = org_collapsed, comparison = "control")
-```
-
-```{r plot-h2b-mm-amce, fig.width=6.5, fig.height=7, out.width="70%"}
-#| column: body-outset
-p_h2b_mms <- h2b_mms %>% 
-  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
-  stat_halfeye(aes(slab_alpha = org_collapsed)) +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
-  scale_slab_alpha_discrete(
-    range = c(0.4, 1),
-    guide = guide_legend(
-      reverse = TRUE, override.aes = list(fill = "grey10"), 
-      keywidth = 0.8, keyheight = 0.8, nrow = 1
-    )
-  ) +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    slab_alpha = NULL,
-    title = "Estimated marginal means"
-  ) +
-  theme(
-    legend.position = "top",
-    legend.justification = "left",
-    legend.margin = margin(l = -7, t = 0)
-  )
-
-p_h2b_amces <- h2b_amces %>% 
-  ungroup() %>% 
-  separate_wider_delim(
-    org_collapsed,
-    delim = " - ", 
-    names = c("org_collapsed", "reference_level")
-  ) %>% 
-  mutate(feat_govt = factor(feat_govt, levels = levels(h2a_mms$feat_govt))) %>% 
-  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
-  facet_wrap(vars(paste(org_collapsed, "−", reference_level))) +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Difference in estimated marginal means",
-    subtitle = "Positive values indicate greater preference for Oxfam & Red Cross"
-  )
-
-(p_h2b_mms / plot_spacer() / p_h2b_amces) +
-  plot_layout(ncol = 1, heights = c(0.49, 0.02, 0.49))
-```
-
-```{r table-h2b-mm-amce}
-#| column: body-outset
-h2b_tbl_mm <- h2b_mms %>% 
-  group_by(feat_govt, org_collapsed) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_govt), desc(org_collapsed)) %>% 
-  select(org_collapsed, feat_govt, nice)
-
-h2b_tbl_amces <- h2b_amces %>% 
-  group_by(feat_govt, org_collapsed) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  ungroup() %>% 
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(org_collapsed = str_replace(org_collapsed, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(contrast = org_collapsed, diff_nice = nice, p_neq_0)
-
-bind_cols(
-  h2b_tbl_mm, 
-  h2b_tbl_amces %>% 
-    add_row(contrast = NA, .after = 1) %>% 
-    add_row(contrast = NA, .after = 3) %>% 
-    add_row(contrast = NA, .after = 5)
-) %>% 
-  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
-  group_by(feat_govt) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(org_collapsed, contrast)) %>% 
-  cols_label(
-    org_collapsed = "Organizations", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    diff_nice = "Posterior ∆",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_style(
-    style = cell_fill(color = "grey90"),
-    locations = cells_row_groups()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, diff_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-# H~3~: Issue Area
-
-## H~3a~: Issue area
+# H~3a~: Issue area
 
@@
 
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors appear to be sensitive to NGO issue area when they are considering to donate.
-Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations.
-While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs, which was contrary to our expectations.
-It is worth noting that there is some overlap between the intervals of the issue areas, which would suggest that their effect isn't as significant as other factors.
-:::
-
 ```{r h3a-calc-estimands}
-h3a_mms <- all_combos_means %>% 
+h3a_mms <- means_features_only %>% 
   group_by(feat_issue, .draw) %>% 
@@
 ```{r plot-h3a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: body-outset
+#| column: body-outset-right
 p_h3a_mms <- h3a_mms %>% 
@@
   scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
+  scale_fill_manual(values = clrs$prism[c(2, 6, 8, 10)], guide = "none") +
   labs(
@@
   stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
+  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
   scale_x_continuous(labels = label_pp) +
   scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
+  scale_fill_manual(values = clrs$prism[c(2, 6, 8, 10)], guide = "none") +
   labs(
@@
 ```{r table-h3a-mm-amce}
-#| column: body-outset
+#| column: body-outset-right
 h3a_tbl_mm <- h3a_mms %>% 
@@
 
-## H~3b~: Relationship with host government and issue area
+# H~3b~: Relationship with host government and issue area
 
@@
 
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-The generated contrasts don't provides results which are statistically significant. 0 is found within all intervals.
-
-![](img/contrasts_hypothesis03b.png)
-:::
-
 ```{r h3b-calc-estimands}
-h3b_mms <- all_combos_means %>% 
+h3b_mms <- means_features_only %>% 
   group_by(feat_issue, feat_govt, .draw) %>% 
@@
 ```{r plot-h3b-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
-#| column: body-outset
+#| column: body-outset-right
 p_h3b_mms <- h3b_mms %>% 
@@
   scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
+  scale_fill_manual(values = clrs$prism[c(2, 6, 8, 10)], guide = "none") +
   facet_wrap(vars(feat_govt), ncol = 1) +
@@
   stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
+  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
   scale_x_continuous(labels = label_pp) +
   scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
+  scale_fill_manual(values = clrs$prism[c(2, 6, 8, 10)], guide = "none") +
   facet_wrap(vars(feat_govt), ncol = 1) +
@@
 ```{r table-h3b-mm-amce}
-#| column: body-outset
+#| column: body-outset-right
 h3b_tbl_mm <- h3b_mms %>% 
@@
 ```
-
-# H~4~: Funding sources
-
-## H~4a~: Funding sources
-
-> Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealthy private donors and government grants [Mechanism: Perception of efficacy - your contribution matters as a small donor.
-Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.]
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-As stated in the hypothesis, donors show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants.
-
-![](img/contrasts_hypothesis04.png)
-:::
-
-## H~4b~: Relationship with host government and funding sources
-
-> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-The marginal posteriors for these contrasts are strange, but still tell us that the interaction between funding sources and government relationship produce no significant effects.
-
-![](img/contrasts_hypothesis04b.png)
-:::
-
-## H~4c~: Relationship with host government, funding sources, and issue area
-
-> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors and work in less contentious areas (emergency response and refugee relief)
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Once again, we see some interesting distributions, but no results significant enough to confirm our hypothesis.
-
-![](img/contrasts_hypothesis04c.png)
-:::
-
-# H~5~: Organizational practices
-
-## H~5a~: Organizational practices
-
-> Donors will show increased willingness to donate to NGOs that are financially transparent [Mechanism: Perception of efficacy]
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors show an increased likelihood to donate to NGOs that are financially transparent, as hypothesized.
-
-![](img/contrasts_hypothesis05.png)
-:::
-
-## H~5b~: Relationship with host government, organizational practices
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent.
-However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
-
-![](img/contrasts_hypothesis05b.png)
-:::
-
-## H~5c~: Relationship with host government, organizational practices, and funding sources
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and are funded primarily by numerous small private donors
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-These intervals are massive; 0 is well within them, leaving us with insufficient evidence to confirm the hypothesis.
-
-![](img/contrasts_hypothesis05c.png)
-:::
-
-## H~5d~: Relationship with host government, organizational practices, and issue area
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief)
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-The contrasts don't support the hypothesis, however, there is an interesting difference between emergency_environment_crackdown and emergency_environment_criticized.
-
-![](img/contrasts_hypothesis05d.png)
-:::
-
-## H~5e~: Relationship with host government, organizational practices, issue area, and funding sources
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-These marginal posteriors don't support our hypothesis, but again show an interesting difference between emergency_environment_criticized and emergency_environment_crackdown.
-
-![](img/contrasts_hypothesis05e.png)
-:::
-
-## H~5f~: Organizational practices
-
-> Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits [Mechanism: Donors don't necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks]
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent.
-However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
-
-![](img/contrasts_hypothesis05f.png)
-:::

### 2023-08-29 R/funs_graphics.R
Move labeling functions to targets

@@ -28,3 +28,12 @@ set_annotation_fonts <- function() {
 build_ci <- function(lower, upper) {
   glue::glue("[{fmt_decimal(lower)}, {fmt_decimal(upper)}]")
 }
+
+# Put these scales things in functions so that they work like regular functions,
+# otherwise {targets} complains that "... may be used in an incorrect context"
+fmt_decimal <- \(x) scales::label_number(accuracy = 0.001, style_negative = "minus")(x)
+
+label_pp <- function(x) {
+  scales::label_number(accuracy = 1, scale = 100, 
+    suffix = " pp.", style_negative = "minus")(x)
+}

### 2023-08-29 _targets.R

@@ -46,7 +46,8 @@ list(
   
   ## Graphics and tables ----
   tar_target(graphic_functions, lst(
-    theme_ngo, set_annotation_fonts, clrs, build_ci
+    theme_ngo, set_annotation_fonts, clrs, 
+    build_ci, fmt_decimal, label_pp
   )),
   tar_target(table_functions, lst(opts_int, opts_theme)),
   

### 2023-08-29 notebook/results-crackdown.qmd
Move labeling functions to targets
Better hypothesis icons

@@
 
-# Helpful functions
-label_pp <- label_number(accuracy = 1, scale = 100, 
-  suffix = " pp.", style_negative = "minus")
-
-fmt_decimal <- label_number(accuracy = 0.001, style_negative = "minus")
-
 # Targets stuff
@@
 
-::: {.callout-tip}
-## H~2a~: Relationship with host government
+::: {.callout-tip icon=false}
+## {{< iconify fa6-solid flask-vial >}} Hypothesis 2~a~: Relationship with host government
 
@@
 
-::: {.callout-tip}
-## H~2b~: Organization and relationship with host government
+::: {.callout-tip icon=false}
+## {{< iconify fa6-solid flask-vial >}} Hypothesis 2~b~: Organization and relationship with host government
 

### 2023-08-29 notebook/results-issue.qmd
Move labeling functions to targets
Better hypothesis icons

@@
 
-::: {.callout-tip}
-## H~3a~: Issue area
+::: {.callout-tip icon=false}
+## {{< iconify fa6-solid flask-vial >}} Hypothesis 3~a~: Issue area
 
@@
 
-::: {.callout-tip}
-## H~3b~: Relationship with host government and issue area
+::: {.callout-tip icon=false}
+## {{< iconify fa6-solid flask-vial >}} Hypothesis 3~b~: Relationship with host government and issue area
 

### 2023-08-29 notebook/results.qmd
Add overall AMCEs

---
title: "All AMCEs"
format:
  html:
    code-fold: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "80%", collapse = TRUE,
  dev = "ragg_png"
)

options(
  digits = 3, width = 120,
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)
```

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(patchwork)
library(ggforce)
library(scales)
library(glue)
library(gt)
library(gtExtras)
library(here)

# Targets stuff
tar_config_set(store = here('_targets'),
               script = here('_targets.R'))

tar_load(c(means_features_only, ref_grid_features_only))

invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))

theme_set(theme_ngo())
```

```{r create-var-lookups}
var_levels <- tibble(
  variable = c("feat_org", "feat_issue", "feat_transp", "feat_acc", "feat_funding", "feat_govt")
) %>% 
  mutate(levels = map(variable, ~{
    x <- ref_grid_features_only$all_combos[[.x]]
    if (is.numeric(x)) {
      ""
    } else if (is.factor(x)) {
      levels(x)
    } else {
      sort(unique(x))
    }
  })) %>% 
  unnest(levels)

# Make a little lookup table for nicer feature labels
var_lookup <- tribble(
  ~variable,      ~variable_nice,
  "feat_org",     "Organizations",
  "feat_issue",   "Issue areas",
  "feat_transp",  "Transparency",
  "feat_acc",     "Accountability",
  "feat_funding", "Funding sources",
  "feat_govt",    "Relationship with host government"
) %>% 
  mutate(amce_var = str_replace(variable, "feat_", "amces_")) %>% 
  mutate(variable_nice = fct_inorder(variable_nice))
```

```{r calc-mms}
mms_org <- means_features_only %>% 
  group_by(feat_org, .draw) %>% 
  summarize(avg = mean(.epred))

mms_issue <- means_features_only %>% 
  group_by(feat_issue, .draw) %>% 
  summarize(avg = mean(.epred))

mms_transp <- means_features_only %>% 
  group_by(feat_transp, .draw) %>% 
  summarize(avg = mean(.epred))

mms_acc <- means_features_only %>% 
  group_by(feat_acc, .draw) %>% 
  summarize(avg = mean(.epred))

mms_funding <- means_features_only %>% 
  group_by(feat_funding, .draw) %>% 
  summarize(avg = mean(.epred))

mms_govt <- means_features_only %>% 
  group_by(feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))
```

```{r calc-amces}
amces_org <- mms_org %>% 
  group_by(feat_org) %>% 
  compare_levels(variable = avg, by = feat_org, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feat_org,
    delim = " - ", 
    names = c("value", "reference_level")
  ) %>% 
  add_row(avg = 0, value = "Amnesty International")

amces_issue <- mms_issue %>% 
  group_by(feat_issue) %>% 
  compare_levels(variable = avg, by = feat_issue, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feat_issue,
    delim = " - ", 
    names = c("value", "reference_level")
  ) %>% 
  add_row(avg = 0, value = "Emergency response")

amces_transp <- mms_transp %>% 
  group_by(feat_transp) %>% 
  compare_levels(variable = avg, by = feat_transp, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feat_transp,
    delim = " - ", 
    names = c("value", "reference_level")
  ) %>% 
  add_row(avg = 0, value = "No")

amces_acc <- mms_acc %>% 
  group_by(feat_acc) %>% 
  compare_levels(variable = avg, by = feat_acc, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feat_acc,
    delim = " - ", 
    names = c("value", "reference_level")
  ) %>% 
  add_row(avg = 0, value = "No")

amces_funding <- mms_funding %>% 
  group_by(feat_funding) %>% 
  compare_levels(variable = avg, by = feat_funding, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feat_funding,
    delim = " - ", 
    names = c("value", "reference_level")
  ) %>% 
  add_row(avg = 0, value = "Many small donors")

amces_govt <- mms_govt %>% 
  group_by(feat_govt) %>% 
  compare_levels(variable = avg, by = feat_govt, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feat_govt,
    delim = " - ", 
    names = c("value", "reference_level")
  ) %>% 
  add_row(avg = 0, value = "Friendly")

amces_all <- bind_rows(
  lst(amces_org, amces_issue, amces_transp, amces_acc, amces_funding, amces_govt),
  .id = "amce_var"
) %>%
  left_join(var_lookup, by = join_by(amce_var)) %>%
  mutate(value = factor(value, levels = unique(var_levels$levels)))
```

```{r plot-amces-all, fig.width=7, fig.height=6, out.width="100%"}
ggplot(
  amces_all,
  aes(x = avg, y = value, fill = variable_nice)
) +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  stat_halfeye(normalize = "groups") +  # Make the heights of the distributions equal within each facet
  guides(fill = "none") +
  facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
  scale_x_continuous(labels = label_pp) +
  scale_fill_manual(values = clrs$prism[1:6]) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    title = "Posterior AMCEs"
  )
```

### 2023-09-07 notebook/results.qmd
Add marginal means plot

@@
   mutate(amce_var = str_replace(variable, "feat_", "amces_")) %>% 
+  mutate(mm_var = str_replace(variable, "feat_", "mms_")) %>% 
   mutate(variable_nice = fct_inorder(variable_nice))
@@
 
+```{r plot-mms-all, fig.width=7, fig.height=6, out.width="100%"}
+mms_all <- bind_rows(
+  lst(
+    mms_org = rename(mms_org, value = feat_org), 
+    mms_issue = rename(mms_issue, value = feat_issue), 
+    mms_transp = rename(mms_transp, value = feat_transp), 
+    mms_acc = rename(mms_acc, value = feat_acc), 
+    mms_funding = rename(mms_funding, value = feat_funding), 
+    mms_govt = rename(mms_govt, value = feat_govt)
+  ),
+  .id = "mm_var"
+) %>%
+  left_join(var_lookup, by = join_by(mm_var)) %>%
+  mutate(value = factor(value, levels = unique(var_levels$levels)))
+
+ggplot(
+  mms_all,
+  aes(x = avg, y = value, fill = variable_nice)
+) +
+  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
+  stat_halfeye(normalize = "groups") +
+  guides(fill = "none") +
+  facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(values = clrs$prism[1:6]) +
+  labs(
+    x = "Marginal means of probabilities",
+    y = NULL,
+    title = "Posterior marginal means"
+  )
+```
+
 ```{r plot-amces-all, fig.width=7, fig.height=6, out.width="100%"}

### 2023-09-07 R/funs_means.R
Use .linpred for consistency

@@ -13,7 +13,7 @@ calculate_grid_means <- function(draws, ref_grid) {
         mutate(
           .linpred = preds, 
           # fake bc it's not actually mean(posterior_predict(.))
-          .epred = plogis(preds)
+          .epred = plogis(.linpred)
         )
     })) %>% 
     select(-data) %>% 

### 2023-09-07 basic-amces-mms.qmd
Create categorical column

@@
   mutate(choice_binary = ifelse(choice == alt, 1, 0)) %>%
+  mutate(choice_alt = factor(alt * choice_binary)) %>% 
   mutate(

### 2023-09-07 R/funs_data.R
targets-ize data cleaning

@@ -1,0 +1,736 @@
+make_clean_data <- function(path) {
+  # Load original pre-anonymized Qualtrics data
+  data_raw <- read_csv(path, guess_max = 1500, show_col_types = FALSE)
+  
+  # Keep only eligible respondents
+  data_eligible <- data_raw %>%
+    filter(V10 == 1) %>%          # Keep respondents who completed the entire survey
+    filter(Q1.1 == 1) %>%         # Keep respondents who gave consent
+    filter(Q2.5 %in% c(1:5)) %>%  # Keep respondents who passed the screener
+    filter(Q2.11 == 3)            # Keep respondents who passed the attention check
+  
+  # Get full data ready for cleaning and merging
+  data_pre_clean <- data_eligible %>% 
+    mutate(id = row_number()) %>% 
+    rename(version = vers_CBCONJOINT) %>% 
+    select(-contains("_TEXT")) %>% 
+    select(id, version, Q1.1:Q5.18)
+  
+  # MEGA CLEANING PIPELINE
+  data_clean <- data_pre_clean %>% 
+    mutate(
+      # *Q2.1*: How often do you follow national news? 
+      # 
+      # - Multiple times a day → At least once a day
+      # - Every day → At least once a day
+      # - Once a week → Once a week
+      # - Hardly ever → Rarely (base case)
+      # - Never → Rarely
+      Q2.1 = factor(
+        case_when(
+          Q2.1 == 1 ~ "At least once a day",
+          Q2.1 == 2 ~ "At least once a day",
+          Q2.1 == 3 ~ "Once a week",
+          Q2.1 == 4 ~ "Rarely",
+          Q2.1 == 5 ~ "Rarely"
+        ),
+        levels = c("Rarely", "Once a week", "At least once a day"),
+        labels = str_c(
+          "Follow national news: ",
+          c("Rarely", "Once a week", "At least once a day")
+        )
+      ),
+      # *Q2.2*: How often do you follow international news? 
+      # 
+      # - Always
+      # - Sometimes
+      # - Never
+      Q2.2 = fct_relevel(
+        factor(
+          Q2.2, 
+          labels = str_c(
+            "Follow international news: ", 
+            c("Always", "Sometimes", "Never")
+          ),
+        ),
+        str_c(
+          "Follow international news: ", 
+          c("Never", "Sometimes", "Always")
+        )
+      )
+    ) %>% 
+    mutate(
[…]

### 2023-09-07 _targets.R

@@ -38,6 +38,16 @@ lapply(list.files("R", full.names = TRUE, recursive = TRUE), source)
 # Actual pipeline ---------------------------------------------------------
 list(
   ## Data and draws ----
+  tar_target(
+    qualtrics_anonymized_file,
+    here_rel("data", "raw_data", "conjointqsf_final.csv"),
+    format = "file"
+  ),
+  
+  tar_target(data_processed, make_clean_data(qualtrics_anonymized_file)),
+  tar_target(data_sans_conjoint, data_processed[["data_clean"]]),
+  tar_target(data_full, data_processed[["data_final"]]),
+  
   tar_target(gammas_intercept_only,
     here_rel("data", "raw_data", "posterior_draws", "intercept.rds"),
     format = "file"

### 2023-09-07 R/funs_data.R
Fix missing factor levels for transparency and accountaiblity

@@ -699,12 +699,8 @@ make_clean_data <- function(path) {
       feat_issue = factor(feat_issue,
         levels = c("Emergency response", "Environment", "Human rights", "Refugee relief")
       ),
-      feat_transp = factor(feat_transp,
-        levels = c("Transparency: No", "Transparency: Yes")
-      ),
-      feat_acc = factor(feat_acc,
-        levels = c("Accountability: No", "Accountability: Yes")
-      ),
+      feat_transp = factor(feat_transp, levels = c("No", "Yes")),
+      feat_acc = factor(feat_acc, levels = c("No", "Yes")),
       feat_funding = factor(feat_funding,
         levels = c(
           "Funded primarily by many small private donations",
@@ -718,6 +714,15 @@ make_clean_data <- function(path) {
           "Criticized by government",
           "Under government crackdown"
         )
+      ),
+      # Make the levels for transparency and accountability unique
+      feat_transp = fct_recode(feat_transp,
+        "Transparency: No" = "No",
+        "Transparency: Yes" = "Yes"
+      ),
+      feat_acc = fct_recode(feat_acc,
+        "Accountability: No" = "No",
+        "Accountability: Yes" = "Yes"
       )
     ) %>% 
     

### 2023-09-07 R/funs_models.R
targets-ify modeling

@@ -1,0 +1,26 @@
+f_treatment_only <- function(dat) {
+  BAYES_SEED <- 706615  # From random.org
+
+  categorical_priors <- c(
+    prior(normal(0, 3), class = b, dpar = mu1),
+    prior(normal(0, 3), class = b, dpar = mu2),
+    prior(normal(0, 3), class = b, dpar = mu3),
+    prior(exponential(1), class = sd, dpar = mu1),
+    prior(exponential(1), class = sd, dpar = mu2),
+    prior(exponential(1), class = sd, dpar = mu3) # ,
+  )
+
+  model <- brm(
+    bf(choice_alt ~
+      # Conjoint attributes (treatment variables)
+      feat_org + feat_issue + feat_transp + feat_acc + feat_funding + feat_govt +
+      # Respondent-specific intercepts
+      (1 | id)),
+    data = dat,
+    family = categorical(refcat = "0"),
+    prior = categorical_priors,
+    chains = 4, warmup = 1000, iter = 5000, seed = BAYES_SEED, refresh = 10
+  )
+
+  return(model)
+}

### 2023-09-07 _targets.R

@@ -18,6 +18,14 @@ options(
   dplyr.summarise.inform = FALSE
 )
 
+# Bayes stuff
+suppressPackageStartupMessages(library(brms))
+options(
+  mc.cores = 4,
+  brms.backend = "cmdstanr",
+  brms.threads = 2
+)
+
 set.seed(265927) # From random.org
 
 tar_option_set(
@@ -61,6 +69,9 @@ list(
   )),
   tar_target(table_functions, lst(opts_int, opts_theme)),
   
+  
+  ## Models ----
+  tar_target(m_treatment_only, f_treatment_only(data_full)),
   
   ## Create reference grid(s) ----
   tar_target(ref_grid_features_only, create_ref_grid_features_only()),

### 2023-09-07 R/funs_grids.R
targets-ify grid and predictions

@@ -1,21 +1,24 @@
-create_ref_grid_features_only <- function() {
-  suppressPackageStartupMessages(library(Matrix))
-  
-  all_combos <- expand_grid(
-    feat_org = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"), 
-    feat_issue = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-    feat_transp = c("No", "Yes"), 
-    feat_acc = c("No", "Yes"),
-    feat_funding = c("Many small donors", "Handful of wealthy private donors", "Government grants"),
-    feat_govt = c("Friendly", "Criticized", "Under crackdown")
-  ) %>% 
-    mutate(across(everything(), ~fct_inorder(.)))
-  
-  all_combos_design_grid <- sparse.model.matrix(
-    ~ 0 + feat_org + feat_issue + feat_transp + 
-      feat_acc + feat_funding + feat_govt, 
-    data = all_combos
-  )
-  
-  return(lst(all_combos, matrix = all_combos_design_grid))
+create_grid_treatment_only <- function(dat) {
+  all_combos <- dat %>%
+    # Get all combinations of all feature levels
+    tidyr::expand(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>%
+    
+    # Make shorter versions of these levels for the sake of plotting/tables/etc.
+    mutate(
+      feat_transp_short = fct_relabel(feat_transp, ~ str_remove(.x, "Transparency: ")),
+      feat_acc_short = fct_relabel(feat_acc, ~ str_remove(.x, "Accountability: ")),
+      feat_funding_short = fct_recode(feat_funding,
+        "Many small donors" = "Funded primarily by many small private donations",
+        "Handful of wealthy private donors" = "Funded primarily by a handful of wealthy private donors",
+        "Government grants" = "Funded primarily by government grants"
+      ),
+      feat_govt_short = fct_recode(feat_govt,
+        "Friendly" = "Friendly relationship with government",
+        "Criticized" = "Criticized by government",
+        "Under crackdown" = "Under government crackdown"
+      )
+    ) %>%
+    mutate(across(everything(), ~ fct_inorder(.)))
+
+  return(all_combos)
 }

### 2023-09-07 R/funs_means.R

@@ -1,23 +1,0 @@
-calculate_grid_means <- function(draws, ref_grid) {
-  library(tidybayes)
-  
-  draws <- readRDS(draws)
-
-  grid_means <- draws %>% 
-    pivot_wider(names_from = i, values_from = Gamma) %>% 
-    group_by(j, .chain, .iteration, .draw) %>% 
-    nest() %>% 
-    mutate(pi = map(data, ~{
-      preds <- as.numeric(ref_grid$matrix %*% as.numeric(.))
-      ref_grid$all_combos %>% 
-        mutate(
-          .linpred = preds, 
-          # fake bc it's not actually mean(posterior_predict(.))
-          .epred = plogis(.linpred)
-        )
-    })) %>% 
-    select(-data) %>% 
-    unnest(pi)
-  
-  return(grid_means)
-}

### 2023-09-07 R/funs_preds.R

@@ -1,0 +1,21 @@
+suppressPackageStartupMessages(library(tidybayes))
+
+# Average respondent
+create_preds_conditional_treatment_only <- function(model, grid) {
+  preds <- model %>% 
+    epred_draws(
+      newdata = grid, 
+      re_formula = NA
+    )
+}
+
+# New respondent
+create_preds_new_treatment_only <- function(model, grid) {
+  preds <- model %>% 
+    epred_draws(
+      newdata = mutate(grid, id = -1), 
+      re_formula = NULL,
+      allow_new_levels = TRUE,
+      sample_new_levels = "uncertainty"
+    )
+}

### 2023-09-07 _targets.R

@@ -74,11 +74,17 @@ list(
   tar_target(m_treatment_only, f_treatment_only(data_full)),
   
   ## Create reference grid(s) ----
-  tar_target(ref_grid_features_only, create_ref_grid_features_only()),
+  tar_target(grid_treatment_only, create_grid_treatment_only(data_full)),
   
   ## Calculate predicted values for reference grids ----
-  tar_target(means_features_only, calculate_grid_means(gammas_intercept_only, ref_grid_features_only))#,
+  tar_target(preds_conditional_treatment_only, 
+    create_preds_conditional_treatment_only(m_treatment_only, grid_treatment_only)
+  ),
+  tar_target(preds_new_treatment_only, 
+    create_preds_new_treatment_only(m_treatment_only, grid_treatment_only)
+  ),
 
+  
   ## Analysis ----
   # tar_target(summary_activities, make_activities_summary(survey_orgs)),
   # tar_target(models_activities, make_activities_models(summary_activities))#,

### 2023-09-08 notebook/results.qmd
targets-ify predictions and plots

--- 2023-08-29 notebook/results.qmd
@@
 ---
-title: "All AMCEs"
+title: "All MMs and AMCEs"
 format:
@@
 
-tar_load(c(means_features_only, ref_grid_features_only))
+tar_load(c(preds_conditional_treatment_only, grid_treatment_only))
+tar_load(c(level_lookup, feature_lookup))
 
@@
 
-```{r create-var-lookups}
-var_levels <- tibble(
-  variable = c("feat_org", "feat_issue", "feat_transp", "feat_acc", "feat_funding", "feat_govt")
-) %>% 
-  mutate(levels = map(variable, ~{
-    x <- ref_grid_features_only$all_combos[[.x]]
-    if (is.numeric(x)) {
-      ""
-    } else if (is.factor(x)) {
-      levels(x)
-    } else {
-      sort(unique(x))
-    }
-  })) %>% 
-  unnest(levels)
+```{r calc-mms}
+preds_all <- preds_conditional_treatment_only %>% 
+  filter(.category == 0) %>% 
+  mutate(.epred = 1 - .epred)
 
-# Make a little lookup table for nicer feature labels
-var_lookup <- tribble(
-  ~variable,      ~variable_nice,
-  "feat_org",     "Organizations",
-  "feat_issue",   "Issue areas",
-  "feat_transp",  "Transparency",
-  "feat_acc",     "Accountability",
-  "feat_funding", "Funding sources",
-  "feat_govt",    "Relationship with host government"
-) %>% 
-  mutate(amce_var = str_replace(variable, "feat_", "amces_")) %>% 
-  mutate(variable_nice = fct_inorder(variable_nice))
-```
-
-```{r calc-mms}
-mms_org <- means_features_only %>% 
+mms_org <- preds_all %>% 
   group_by(feat_org, .draw) %>% 
@@
 
-mms_issue <- means_features_only %>% 
+mms_issue <- preds_all %>% 
   group_by(feat_issue, .draw) %>% 
@@
 
-mms_transp <- means_features_only %>% 
+mms_transp <- preds_all %>% 
   group_by(feat_transp, .draw) %>% 
@@
 
-mms_acc <- means_features_only %>% 
+mms_acc <- preds_all %>% 
   group_by(feat_acc, .draw) %>% 
@@
 
-mms_funding <- means_features_only %>% 
+mms_funding <- preds_all %>% 
   group_by(feat_funding, .draw) %>% 
@@
 
-mms_govt <- means_features_only %>% 
+mms_govt <- preds_all %>% 
   group_by(feat_govt, .draw) %>% 
@@
     delim = " - ", 
-    names = c("value", "reference_level")
+    names = c("feature_level", "reference_level")
   ) %>% 
-  add_row(avg = 0, value = "Amnesty International")
+  add_row(avg = 0, feature_level = unique(.$reference_level))
 
@@
     delim = " - ", 
-    names = c("value", "reference_level")
+    names = c("feature_level", "reference_level")
   ) %>% 
-  add_row(avg = 0, value = "Emergency response")
+  add_row(avg = 0, feature_level = unique(.$reference_level))
 
@@
     delim = " - ", 
-    names = c("value", "reference_level")
+    names = c("feature_level", "reference_level")
   ) %>% 
-  add_row(avg = 0, value = "No")
+  add_row(avg = 0, feature_level = unique(.$reference_level))
 
@@
     delim = " - ", 
-    names = c("value", "reference_level")
+    names = c("feature_level", "reference_level")
   ) %>% 
-  add_row(avg = 0, value = "Many small donors")
+  add_row(avg = 0, feature_level = unique(.$reference_level))
 
@@
     delim = " - ", 
-    names = c("value", "reference_level")
+    names = c("feature_level", "reference_level")
   ) %>% 
-  add_row(avg = 0, value = "Friendly")
+  add_row(avg = 0, feature_level = unique(.$reference_level))
 
@@
 ) %>%
-  left_join(var_lookup, by = join_by(amce_var)) %>%
-  mutate(value = factor(value, levels = unique(var_levels$levels)))
+  left_join(select(feature_lookup, amce_var, feature_nice), by = join_by(amce_var)) %>%
+  left_join(
+    select(level_lookup, contains("_level")), 
+    by = join_by(feature_level)
+  )
+```
+
+```{r plot-mms-all, fig.width=7, fig.height=6, out.width="100%"}
+mms_all <- bind_rows(
+  lst(
+    mms_org = rename(mms_org, feature_level = feat_org), 
+    mms_issue = rename(mms_issue, feature_level = feat_issue), 
+    mms_transp = rename(mms_transp, feature_level = feat_transp), 
+    mms_acc = rename(mms_acc, feature_level = feat_acc), 
+    mms_funding = rename(mms_funding, feature_level = feat_funding), 
+    mms_govt = rename(mms_govt, feature_level = feat_govt)
+  ),
+  .id = "mm_var"
+) %>%
+  left_join(select(feature_lookup, mm_var, feature_nice), by = join_by(mm_var)) %>%
+  left_join(
+    select(level_lookup, contains("_level")), 
+    by = join_by(feature_level)
+  )
+
+ggplot(
+  mms_all,
+  aes(x = avg, y = feature_short_level, fill = feature_nice)
+) +
+  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
+  stat_halfeye(normalize = "groups") +
+  guides(fill = "none") +
+  facet_col(facets = "feature_nice", scales = "free_y", space = "free") +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(values = clrs$prism[1:6]) +
+  labs(
+    x = "Marginal means of probabilities",
+    y = NULL,
+    title = "Posterior marginal means"
+  )
 ```
@@
   amces_all,
-  aes(x = avg, y = value, fill = variable_nice)
+  aes(x = avg, y = feature_short_level, fill = feature_nice)
 ) +
@@
   guides(fill = "none") +
-  facet_col(facets = "variable_nice", scales = "free_y", space = "free") +
+  facet_col(facets = "feature_nice", scales = "free_y", space = "free") +
   scale_x_continuous(labels = label_pp) +

### 2023-09-08 R/funs_preds.R

@@ -1,5 +1,55 @@
 suppressPackageStartupMessages(library(tidybayes))
 
+# Lookup tables
+# Little table of all feature level labels in the right order
+make_level_lookup <- function(grid) {
+  level_lookup <- tibble(
+    feature = c(
+      "feat_org", "feat_issue", "feat_transp", 
+      "feat_acc", "feat_funding", "feat_govt"
+    ),
+    feature_short = c(
+      "feat_org", "feat_issue", "feat_transp_short", 
+      "feat_acc_short", "feat_funding_short", "feat_govt_short"
+    )
+  ) %>%
+    mutate(across(
+      c(feature, feature_short),
+      list(level = ~ map(.x, ~ {
+        x <- grid[[.x]]
+        if (is.numeric(x)) {
+          ""
+        } else if (is.factor(x)) {
+          levels(x)
+        } else {
+          sort(unique(x))
+        }
+      }))
+    )) %>%
+    unnest(c(feature_level, feature_short_level)) %>%
+    mutate(across(c(feature_level, feature_short_level), ~ fct_inorder(.)))
+
+  return(level_lookup)
+}
+
+# Little table for all feature labels in the right order
+make_feature_lookup <- function() {
+  feature_lookup <- tribble(
+    ~feature,      ~feature_nice,
+    "feat_org",     "Organizations",
+    "feat_issue",   "Issue areas",
+    "feat_transp",  "Transparency",
+    "feat_acc",     "Accountability",
+    "feat_funding", "Funding sources",
+    "feat_govt",    "Relationship with host government"
+  ) %>% 
+    mutate(amce_var = str_replace(feature, "feat_", "amces_")) %>% 
+    mutate(mm_var = str_replace(feature, "feat_", "mms_")) %>% 
+    mutate(feature_nice = fct_inorder(feature_nice))
+  
+  return(feature_lookup)
+}
+
 # Average respondent
 create_preds_conditional_treatment_only <- function(model, grid) {
   preds <- model %>% 

### 2023-09-08 _targets.R

@@ -69,7 +69,6 @@ list(
   )),
   tar_target(table_functions, lst(opts_int, opts_theme)),
   
-  
   ## Models ----
   tar_target(m_treatment_only, f_treatment_only(data_full)),
   
@@ -84,6 +83,9 @@ list(
     create_preds_new_treatment_only(m_treatment_only, grid_treatment_only)
   ),
 
+  ## Helper objects like lookup tables
+  tar_target(level_lookup, make_level_lookup(grid_treatment_only)),
+  tar_target(feature_lookup, make_feature_lookup())
   
   ## Analysis ----
   # tar_target(summary_activities, make_activities_summary(survey_orgs)),

### 2023-09-08 notebook/basic-amces-mms.qmd
Reorganize and standardize notebook

--- 2023-08-26 basic-amces-mms.qmd
@@
 library(cregg)
+library(targets)
 
-results_long <- readRDS("original_data.rds") %>% 
-  mutate(choice_binary = ifelse(choice == alt, 1, 0)) %>% 
+# Targets stuff
+tar_config_set(store = here::here('_targets'),
+               script = here::here('_targets.R'))
+
+results_long <- tar_read(data_full) %>% 
   mutate(

### 2023-09-08 _targets.R
Remove raw stan draws as target

@@ -56,12 +56,6 @@ list(
   tar_target(data_sans_conjoint, data_processed[["data_clean"]]),
   tar_target(data_full, data_processed[["data_final"]]),
   
-  tar_target(gammas_intercept_only,
-    here_rel("data", "raw_data", "posterior_draws", "intercept.rds"),
-    format = "file"
-  ),
-  
-  
   ## Graphics and tables ----
   tar_target(graphic_functions, lst(
     theme_ngo, set_annotation_fonts, clrs, 

### 2023-09-08 notebook/results.qmd
Sum the epreds for categories 1-3 instead of inverting 0

@@
 
-tar_load(c(preds_conditional_treatment_only, grid_treatment_only))
-tar_load(c(level_lookup, feature_lookup))
+tar_load(c(grid_treatment_only, level_lookup, feature_lookup))
+preds_all <- tar_read(preds_conditional_treatment_only)
 
@@
 ```{r calc-mms}
-preds_all <- preds_conditional_treatment_only %>% 
-  filter(.category == 0) %>% 
-  mutate(.epred = 1 - .epred)
-
 mms_org <- preds_all %>% 

### 2023-09-08 R/funs_preds.R

@@ -50,6 +50,18 @@ make_feature_lookup <- function() {
   return(feature_lookup)
 }
 
+filter_responses_only <- function(preds) {
+  preds %>% 
+    # Get rid of all category 0 rows
+    filter(.category != 0) %>% 
+    # Stop grouping by category so we can add the three categories together
+    ungroup(.category) %>% 
+    # Add .draw as a group so that we collapse the epreds within each draw
+    group_by(.draw, .add = TRUE) %>% 
+    # Combine the three epreds
+    summarize(.epred = sum(.epred))
+}
+
 # Average respondent
 create_preds_conditional_treatment_only <- function(model, grid) {
   preds <- model %>% 

### 2023-09-08 _targets.R

@@ -70,11 +70,17 @@ list(
   tar_target(grid_treatment_only, create_grid_treatment_only(data_full)),
   
   ## Calculate predicted values for reference grids ----
-  tar_target(preds_conditional_treatment_only, 
+  tar_target(preds_conditional_treatment_only_full, 
     create_preds_conditional_treatment_only(m_treatment_only, grid_treatment_only)
   ),
-  tar_target(preds_new_treatment_only, 
+  tar_target(preds_conditional_treatment_only,
+    filter_responses_only(preds_conditional_treatment_only_full)
+  ),
+  tar_target(preds_new_treatment_only_full, 
     create_preds_new_treatment_only(m_treatment_only, grid_treatment_only)
+  ),
+  tar_target(preds_new_treatment_only,
+    filter_responses_only(preds_new_treatment_only_full)
   ),
 
   ## Helper objects like lookup tables

### 2023-09-08 notebook/results-branding.qmd
Move labeling functions to targets
Better hypothesis icons
Update H1, H2, and H3 with new brms models

@@
 library(gtExtras)
-library(here)
-
-# Helpful functions
-label_pp <- label_number(accuracy = 1, scale = 100, 
-  suffix = " pp.", style_negative = "minus")
-
-fmt_decimal <- label_number(accuracy = 0.001, style_negative = "minus")
 
 # Targets stuff
-tar_config_set(store = here('_targets'),
-               script = here('_targets.R'))
+tar_config_set(
+  store = here::here("_targets"),
+  script = here::here("_targets.R")
+)
 
-tar_load(c(means_features_only))
+preds_all <- tar_read(preds_conditional_treatment_only)
 
@@
 
-::: {.callout-tip}
-## H~1~: Branding
+::: {.callout-tip icon=false}
+## {{< iconify fa6-solid flask-vial >}} Hypothesis 1: Branding
 
@@
 ```{r h1-calc-estimands}
-h1_mms <- means_features_only %>% 
+h1_mms <- preds_all %>% 
   group_by(feat_org, .draw) %>% 
@@
   ) %>% 
-  add_row(avg = 0, feat_org = "Amnesty International") %>% 
+  add_row(avg = 0, feat_org = unique(.$reference_level)) %>% 
   ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +

### 2023-09-08 notebook/results-crackdown.qmd
Update H1, H2, and H3 with new brms models

@@
 library(gtExtras)
-library(here)
 
-# Targets stuff
-tar_config_set(store = here('_targets'),
-               script = here('_targets.R'))
+tar_config_set(
+  store = here::here("_targets"),
+  script = here::here("_targets.R")
+)
 
-tar_load(c(means_features_only))
+preds_all <- tar_read(preds_new_treatment_only)
 
@@
 ```{r h2a-calc-estimands}
-h2a_mms <- means_features_only %>% 
+h2a_mms <- preds_all %>% 
   group_by(feat_govt, .draw) %>% 
@@
   ) %>% 
-  add_row(avg = 0, feat_govt = "Friendly") %>%
+  add_row(avg = 0, feat_govt = unique(.$reference_level)) %>%
   mutate(feat_govt = factor(feat_govt, levels = levels(h2a_mms$feat_govt))) %>% 
@@
 ```{r h2b-calc-estimands}
-h2b_mms <- means_features_only %>% 
+h2b_mms <- preds_all %>% 
   mutate(org_collapsed = fct_collapse(feat_org, 

### 2023-09-08 notebook/results-issue.qmd
Update H1, H2, and H3 with new brms models

@@
 library(gtExtras)
-library(here)
 
-# Targets stuff
-tar_config_set(store = here('_targets'),
-               script = here('_targets.R'))
+tar_config_set(
+  store = here::here("_targets"),
+  script = here::here("_targets.R")
+)
 
-tar_load(c(means_features_only))
+preds_all <- tar_read(preds_conditional_treatment_only)
 
@@
 ```{r h3a-calc-estimands}
-h3a_mms <- means_features_only %>% 
+h3a_mms <- preds_all %>% 
   group_by(feat_issue, .draw) %>% 
@@
   ) %>% 
-  add_row(avg = 0, feat_issue = "Emergency response") %>%
+  add_row(avg = 0, feat_issue = unique(.$reference_level)) %>%
   mutate(feat_issue = factor(feat_issue, levels = levels(h3a_mms$feat_issue))) %>% 
@@
 ```{r h3b-calc-estimands}
-h3b_mms <- means_features_only %>% 
+h3b_mms <- preds_all %>% 
   group_by(feat_issue, feat_govt, .draw) %>% 
@@
   ) %>% 
-  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Friendly") %>%
-  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Criticized") %>%
-  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Under crackdown") %>%
+  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Friendly relationship with government") %>%
+  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Criticized by government") %>%
+  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Under government crackdown") %>%
   mutate(feat_issue = factor(feat_issue, levels = levels(h3b_mms$feat_issue))) %>% 

### 2023-09-08 notebook/hypotheses.qmd
Move marginal mean explanation out of hypotheses file

--- 2023-08-26 hypotheses.qmd
@@
   unnest(pi)
-```
-
-# Model
-
-TODO: Intercept only because (1) LOO is best, and (2) it makes most sense causally since all confounding arrows are deleted due to randomization
-
-# Method: Marginal means
-
-To find the causal effects defined in each of our estimands, we calculate estimated marginal means (EMMs) by finding the fitted values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (4 organizations × 4 issues × 2 transparency × 2 accountability × 3 funding × 3 government relationship = 576 rows).
-We transform these estimates to the probability scale in order to work directly with predicted probabilities rather than the link (logit) scale.
-We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.
-
-TODO: Simple example here to just to illustrate the process—show literal marginal means in the margins of a balanced reference grid, then subtract them for the difference in marginal means, or AMCEs
-
-Here's what the full grid of 576 options looks like, with posterior median predictions for each combination:
-
-```{r}
-#| column: screen-inset
-all_combos_means %>% 
-  group_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>% 
-  summarize(avg = mean(.epred)) %>% 
-  ungroup() %>% 
-  gt() %>% 
-  cols_align(align = "left") %>% 
-  cols_label(
-    feat_org = "Organization",
-    feat_issue = "Issue",
-    feat_transp = "Transparency",
-    feat_acc = "Accountability",
-    feat_funding = "Funding",
-    feat_govt = "Relationship",
-    avg = "Median probability"
-  ) %>% 
-  opts_theme() %>% 
-  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, use_filters = TRUE)
 ```

### 2023-09-08 notebook/methods.qmd
Move marginal mean explanation out of hypotheses file

--- 2023-08-26 hypotheses.qmd
@@
 ---
-title: Hypotheses
-format:
-  html:
-    code-fold: true
+title: "Methods"
 ---
@@
 
-```{r libraries-functions, warning=FALSE, message=FALSE}
+```{r libraries-data, warning=FALSE, message=FALSE}
 library(tidyverse)
-library(scales)
-library(glue)
-library(here)
-library(patchwork)
-library(tidybayes)
+library(targets)
 library(gt)
 library(gtExtras)
-library(rcartocolor)
-library(Matrix)
 
-label_pp <- label_number(accuracy = 1, scale = 100, 
-  suffix = " pp.", style_negative = "minus")
+tar_config_set(
+  store = here::here("_targets"),
+  script = here::here("_targets.R")
+)
 
-fmt_decimal <- label_number(accuracy = 0.001, style_negative = "minus")
+preds_all <- tar_read(preds_conditional_treatment_only)
 
-build_ci <- function(lower, upper) {
-  glue("[{fmt_decimal(lower)}, {fmt_decimal(upper)}]")
-}
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
 
-theme_nice <- function() {
-  theme_minimal(base_family = "Clear Sans") +
-    theme(panel.grid.minor = element_blank(),
-      plot.title = element_text(family = "Clear Sans", face = "bold"),
-      axis.title.x = element_text(hjust = 0),
-      axis.title.y = element_text(hjust = 1),
-      strip.text = element_text(family = "Clear Sans", face = "bold",
-        size = rel(0.75), hjust = 0),
-      strip.background = element_rect(fill = "grey90", color = NA))
-}
-
-opts_theme <- function(x) {
-  x %>% 
-    opt_table_font(font = "Inter") %>% 
-    tab_options(column_labels.font.weight = "bold",
-                row_group.font.weight = "bold")
-}
-
-theme_set(theme_nice())
-prism <- carto_pal(name = "Prism")
-peach <- carto_pal(name = "Peach")
-```
-
-```{r create-ref-grid}
-all_combos <- expand_grid(
-  feat_org = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"), 
-  feat_issue = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
-  feat_transp = c("No", "Yes"), 
-  feat_acc = c("No", "Yes"),
-  feat_funding = c("Many small donors", "Handful of wealthy private donors", "Government grants"),
-  feat_govt = c("Friendly", "Criticized", "Under crackdown")
-) %>% 
-  mutate(across(everything(), ~fct_inorder(.)))
-
-all_combos_design_grid <- sparse.model.matrix(
-  ~ 0 + feat_org + feat_issue + feat_transp + 
-    feat_acc + feat_funding + feat_govt, 
-  data = all_combos
-)
-```
-
-```{r create-all-combos-means}
-gammas_raw <- readRDS(here("data", "raw_data", "posterior_draws", "intercept.rds"))
-
-all_combos_means <- gammas_raw %>% 
-  pivot_wider(names_from = i, values_from = Gamma) %>% 
-  group_by(j, .chain, .iteration, .draw) %>% 
-  nest() %>% 
-  mutate(pi = map(data, ~{
-    preds <- as.numeric(all_combos_design_grid %*% as.numeric(.))
-    all_combos %>% 
-      mutate(
-        .linpred = preds, 
-        # fake bc it's not actually mean(posterior_predict(.))
-        .epred = plogis(preds)
-      )
-  })) %>% 
-  select(-data) %>% 
-  unnest(pi)
+theme_set(theme_ngo())
 ```
@@
 #| column: screen-inset
-all_combos_means %>% 
+preds_all %>% 
   group_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>% 
@@
 ```
-
-# H~1~: Branding
-
-::: {.callout-tip}
-## H~1~: Branding
-
-**Donors will be more likely to donate to Oxfam and Red Cross compared to Amnesty International and Greenpeace.**
-
-*Mechanism: awareness of need and contentiousness of issue area*
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Oxfam or Red Cross} \right) \bigr] - \\
-&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Amnesty International or Greenpeace} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace.
-However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam.
-In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International.
-
-![](img/contrasts_hypothesis01.png)
-:::
-
-```{r h1-calc-estimands}
-h1_mms <- all_combos_means %>% 
-  group_by(feat_org, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h1_amces <- h1_mms %>% 
-  group_by(feat_org) %>% 
-  compare_levels(variable = avg, by = feat_org, comparison = "control")
-```
-
-```{r plot-h1-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: body-outset
-p_h1_mms <- h1_mms %>% 
-  ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +
-  stat_halfeye() +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(1, 3, 5, 7)], guide = "none") +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    title = "Estimated marginal means"
-  )
-
-p_h1_amces <- h1_amces %>% 
-  ungroup() %>% 
-    separate_wider_delim(
-    feat_org,
-    delim = " - ", 
-    names = c("feat_org", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feat_org = "Amnesty International") %>% 
-  ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(1, 3, 5, 7)], guide = "none") +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Average marginal component effects (AMCEs)"
-  )
-
-p_h1_mms | p_h1_amces
-```
-
-```{r table-h1-mm-amce}
-#| column: body-outset
-h1_tbl_mm <- h1_mms %>% 
-  group_by(feat_org) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_org)) %>% 
-  select(feat_org, nice)
-
-h1_tbl_amces <- h1_amces %>% 
-  group_by(feat_org) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_org = str_replace(feat_org, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_org)) %>% 
-  select(contrast = feat_org, amce_nice = nice, p_neq_0)
-
-bind_cols(
-  h1_tbl_mm, 
-  add_row(h1_tbl_amces, contrast = "*(Reference)*")
-) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_org, contrast)) %>% 
-  cols_label(
-    feat_org = "Organization", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    amce_nice = "Posterior AMCE",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, amce_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-# H~2~: Government crackdown
-
-## H~2a~: Relationship with host government
-
-::: {.callout-tip}
-## H~2a~: Relationship with host government
-
-**Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism.**
-
-*Mechanism: Governments wouldn't be cracking down on them if they didn't perceive a threat from them which means organizations implementing their missions effectively.
-This perception of efficacy leads to increased donations.*
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Under crackdown} \right) \bigr] - 
-\textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Friendly} \right) \bigr] \\[10pt]
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Criticized} \right) \bigr] - \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Relationship} = \text{Friendly} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism.
-This decreased likelihood to donate is also greater for NGOs under crackdown compared to those under criticism.
-
-![](img/contrasts_hypothesis02a.png)
-:::
-
-```{r h2a-calc-estimands}
-h2a_mms <- all_combos_means %>% 
-  group_by(feat_govt, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h2a_amces <- h2a_mms %>% 
-  group_by(feat_govt) %>% 
-  compare_levels(variable = avg, by = feat_govt, comparison = "control")
-```
-
-```{r plot-h2a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: body-outset
-p_h2a_mms <- h2a_mms %>% 
-  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
-  stat_halfeye() +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    title = "Estimated marginal means"
-  )
-
-p_h2a_amces <- h2a_amces %>% 
-  ungroup() %>% 
-  separate_wider_delim(
-    feat_govt,
-    delim = " - ", 
-    names = c("feat_govt", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feat_govt = "Friendly") %>%
-  mutate(feat_govt = factor(feat_govt, levels = levels(h2a_mms$feat_govt))) %>% 
-  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Average marginal component effects (AMCEs)"
-  )
-
-p_h2a_mms | p_h2a_amces
-```
-
-```{r table-h2a-mm-amce}
-#| column: body-outset
-h2a_tbl_mm <- h2a_mms %>% 
-  group_by(feat_govt) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(feat_govt, nice)
-
-h2a_tbl_amces <- h2a_amces %>% 
-  group_by(feat_govt) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_govt = str_replace(feat_govt, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(contrast = feat_govt, amce_nice = nice, p_neq_0)
-
-bind_cols(
-  h2a_tbl_mm, 
-  add_row(h2a_tbl_amces, contrast = "*(Reference)*")
-) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_govt, contrast)) %>% 
-  cols_label(
-    feat_govt = "Relationship", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    amce_nice = "Posterior AMCE",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, amce_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-## H~2b~: Organization and relationship with host government
-
-::: {.callout-tip}
-## H~2b~: Organization and relationship with host government
-
-**Donors will show increased willingness to donate to Oxfam and Red Cross when they are facing government crackdown or criticism compared to when Amnesty or Greenpeace is facing crackdown.**
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Oxfam or Red Cross}  \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr] - \\
-&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Organization} = \text{Amnesty International or Greenpeace} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-These data don't support our hypothesis; the Red Cross brand has an insignificant impact on likelihood to donate compared to both Greenpeace and Amnesty.
-While the contrasts for Oxfam are closer to being statistically significant, the effect is working in the other direction--Greenpeace and Amnesty both induce increased likelihood to donate on behalf of donors.
-
-![](img/contrasts_hypothesis02b.png)
-
-![](img/contrasts_hypothesis02b_alt.png)
-:::
-
-```{r h2b-calc-estimands}
-h2b_mms <- all_combos_means %>% 
-  mutate(org_collapsed = fct_collapse(feat_org, 
-    `Oxfam & Red Cross` = c("Oxfam", "Red Cross"),
-    `Amnesty International & Greenpeace` = c("Amnesty International", "Greenpeace"))) %>% 
-  group_by(org_collapsed, feat_govt, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h2b_amces <- h2b_mms %>% 
-  group_by(feat_govt) %>% 
-  compare_levels(variable = avg, by = org_collapsed, comparison = "control")
-```
-
-```{r plot-h2b-mm-amce, fig.width=6.5, fig.height=7, out.width="70%"}
-#| column: body-outset
-p_h2b_mms <- h2b_mms %>% 
-  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
-  stat_halfeye(aes(slab_alpha = org_collapsed)) +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
-  scale_slab_alpha_discrete(
-    range = c(0.4, 1),
-    guide = guide_legend(
-      reverse = TRUE, override.aes = list(fill = "grey10"), 
-      keywidth = 0.8, keyheight = 0.8, nrow = 1
-    )
-  ) +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    slab_alpha = NULL,
-    title = "Estimated marginal means"
-  ) +
-  theme(
-    legend.position = "top",
-    legend.justification = "left",
-    legend.margin = margin(l = -7, t = 0)
-  )
-
-p_h2b_amces <- h2b_amces %>% 
-  ungroup() %>% 
-  separate_wider_delim(
-    org_collapsed,
-    delim = " - ", 
-    names = c("org_collapsed", "reference_level")
-  ) %>% 
-  mutate(feat_govt = factor(feat_govt, levels = levels(h2a_mms$feat_govt))) %>% 
-  ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = peach[c(2, 5, 7)], guide = "none") +
-  facet_wrap(vars(paste(org_collapsed, "−", reference_level))) +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Difference in estimated marginal means",
-    subtitle = "Positive values indicate greater preference for Oxfam & Red Cross"
-  )
-
-(p_h2b_mms / plot_spacer() / p_h2b_amces) +
-  plot_layout(ncol = 1, heights = c(0.49, 0.02, 0.49))
-```
-
-```{r table-h2b-mm-amce}
-#| column: body-outset
-h2b_tbl_mm <- h2b_mms %>% 
-  group_by(feat_govt, org_collapsed) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_govt), desc(org_collapsed)) %>% 
-  select(org_collapsed, feat_govt, nice)
-
-h2b_tbl_amces <- h2b_amces %>% 
-  group_by(feat_govt, org_collapsed) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  ungroup() %>% 
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(org_collapsed = str_replace(org_collapsed, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(contrast = org_collapsed, diff_nice = nice, p_neq_0)
-
-bind_cols(
-  h2b_tbl_mm, 
-  h2b_tbl_amces %>% 
-    add_row(contrast = NA, .after = 1) %>% 
-    add_row(contrast = NA, .after = 3) %>% 
-    add_row(contrast = NA, .after = 5)
-) %>% 
-  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
-  group_by(feat_govt) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(org_collapsed, contrast)) %>% 
-  cols_label(
-    org_collapsed = "Organizations", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    diff_nice = "Posterior ∆",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_style(
-    style = cell_fill(color = "grey90"),
-    locations = cells_row_groups()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, diff_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-# H~3~: Issue Area
-
-## H~3a~: Issue area
-
-::: {.callout-tip}
-## H~3a~: Issue area
-
-**Donors will show increased willingness to donate to NGOs working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights).**
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{More contentious} \right) \bigr] -
-\textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{Less contentious} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors appear to be sensitive to NGO issue area when they are considering to donate.
-Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations.
-While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs, which was contrary to our expectations.
-It is worth noting that there is some overlap between the intervals of the issue areas, which would suggest that their effect isn't as significant as other factors.
-:::
-
-```{r h3a-calc-estimands}
-h3a_mms <- all_combos_means %>% 
-  group_by(feat_issue, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h3a_amces <- h3a_mms %>% 
-  group_by(feat_issue) %>% 
-  compare_levels(variable = avg, by = feat_issue, comparison = "control")
-```
-
-```{r plot-h3a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
-#| column: body-outset
-p_h3a_mms <- h3a_mms %>% 
-  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
-  stat_halfeye() +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    title = "Estimated marginal means"
-  )
-
-p_h3a_amces <- h3a_amces %>% 
-  ungroup() %>% 
-  separate_wider_delim(
-    feat_issue,
-    delim = " - ", 
-    names = c("feat_issue", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feat_issue = "Emergency response") %>%
-  mutate(feat_issue = factor(feat_issue, levels = levels(h3a_mms$feat_issue))) %>% 
-  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Average marginal component effects (AMCEs)"
-  )
-
-p_h3a_mms | p_h3a_amces
-```
-
-```{r table-h3a-mm-amce}
-#| column: body-outset
-h3a_tbl_mm <- h3a_mms %>% 
-  group_by(feat_issue) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_issue)) %>% 
-  select(feat_issue, nice)
-
-h3a_tbl_amces <- h3a_amces %>% 
-  group_by(feat_issue) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_issue = str_replace(feat_issue, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_issue)) %>% 
-  select(contrast = feat_issue, amce_nice = nice, p_neq_0)
-
-bind_cols(
-  h3a_tbl_mm, 
-  add_row(h3a_tbl_amces, contrast = "*(Reference)*")
-) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_issue, contrast)) %>% 
-  cols_label(
-    feat_issue = "Issue area", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    amce_nice = "Posterior AMCE",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, amce_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-## H~3b~: Relationship with host government and issue area
-
-::: {.callout-tip}
-## H~3b~: Relationship with host government and issue area
-
-**Donors will show increased willingness to donate to NGOs facing government crackdown/criticism working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights)**
-
-*Mechanisms: Perceptions of deservingness of NGOs dealing with emergency response and refugee relief.
-Donors are also more likely to donate to programs that are compatible with government preferences and have easily measurable outputs, which environment and human rights programs often lack.
-NGOs working on more contentious issue areas may be expelled or shut down, which would be a waste of donor resources, make it less likely that they donate to these groups.*
-:::
-
-### Estimand
-
-$$
-\begin{aligned}
-\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{More contentious}  \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr] - \\
-&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Issue} = \text{Less contentnious} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr]
-\end{aligned}
-$$
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-The generated contrasts don't provides results which are statistically significant. 0 is found within all intervals.
-
-![](img/contrasts_hypothesis03b.png)
-:::
-
-```{r h3b-calc-estimands}
-h3b_mms <- all_combos_means %>% 
-  group_by(feat_issue, feat_govt, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-h3b_amces <- h3b_mms %>% 
-  group_by(feat_govt) %>% 
-  compare_levels(variable = avg, by = feat_issue, comparison = "control")
-```
-
-```{r plot-h3b-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
-#| column: body-outset
-p_h3b_mms <- h3b_mms %>% 
-  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
-  stat_halfeye() +
-  scale_x_continuous(labels = label_percent()) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
-  facet_wrap(vars(feat_govt), ncol = 1) +
-  labs(
-    x = "Overall average predicted probability",
-    y = NULL,
-    fill = NULL,
-    title = "Estimated marginal means"
-  ) +
-  theme(
-    legend.position = "top",
-    legend.justification = "left",
-    legend.margin = margin(l = -7, t = 0)
-  )
-
-p_h3b_amces <- h3b_amces %>% 
-  ungroup() %>% 
-  separate_wider_delim(
-    feat_issue,
-    delim = " - ", 
-    names = c("feat_issue", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Friendly") %>%
-  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Criticized") %>%
-  add_row(avg = 0, feat_issue = "Emergency response", feat_govt = "Under crackdown") %>%
-  mutate(feat_issue = factor(feat_issue, levels = levels(h3b_mms$feat_issue))) %>% 
-  ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +
-  stat_halfeye() +
-  geom_vline(xintercept = 0, color = prism[8], linetype = "dashed", linewidth = 0.25) +
-  scale_x_continuous(labels = label_pp) +
-  scale_y_discrete(labels = label_wrap(10)) +
-  scale_fill_manual(values = prism[c(2, 6, 8, 10)], guide = "none") +
-  facet_wrap(vars(feat_govt), ncol = 1) +
-  labs(
-    x = "Percentage point change in probability of choice selection",
-    y = NULL,
-    fill = NULL,
-    title = "Difference in estimated marginal means"
-  )
-
-p_h3b_mms | p_h3b_amces
-```
-
-```{r table-h3b-mm-amce}
-#| column: body-outset
-h3b_tbl_mm <- h3b_mms %>% 
-  group_by(feat_govt, feat_issue) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
-  arrange(desc(feat_govt), desc(feat_issue)) %>% 
-  select(feat_issue, feat_govt, nice)
-
-h3b_tbl_amces <- h3b_amces %>% 
-  group_by(feat_govt, feat_issue) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>%
-  ungroup() %>% 
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_issue = str_replace(feat_issue, " - ", "−<br>")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(contrast = feat_issue, diff_nice = nice, p_neq_0)
-
-bind_cols(
-  h3b_tbl_mm, 
-  h3b_tbl_amces %>% 
-    add_row(contrast = NA, .after = 3) %>% 
-    add_row(contrast = NA, .after = 7) %>% 
-    add_row(contrast = NA, .after = 12)
-) %>% 
-  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
-  group_by(feat_govt) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_issue, contrast)) %>% 
-  cols_label(
-    feat_issue = "Issue", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    diff_nice = "Posterior ∆",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_style(
-    style = cell_fill(color = "grey90"),
-    locations = cells_row_groups()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, diff_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme()
-```
-
-# H~4~: Funding sources
-
-## H~4a~: Funding sources
-
-> Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealthy private donors and government grants [Mechanism: Perception of efficacy - your contribution matters as a small donor.
-Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.]
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-As stated in the hypothesis, donors show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants.
-
-![](img/contrasts_hypothesis04.png)
-:::
-
-## H~4b~: Relationship with host government and funding sources
-
-> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-The marginal posteriors for these contrasts are strange, but still tell us that the interaction between funding sources and government relationship produce no significant effects.
-
-![](img/contrasts_hypothesis04b.png)
-:::
-
-## H~4c~: Relationship with host government, funding sources, and issue area
-
-> Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors and work in less contentious areas (emergency response and refugee relief)
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Once again, we see some interesting distributions, but no results significant enough to confirm our hypothesis.
-
-![](img/contrasts_hypothesis04c.png)
-:::
-
-# H~5~: Organizational practices
-
-## H~5a~: Organizational practices
-
-> Donors will show increased willingness to donate to NGOs that are financially transparent [Mechanism: Perception of efficacy]
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors show an increased likelihood to donate to NGOs that are financially transparent, as hypothesized.
-
-![](img/contrasts_hypothesis05.png)
-:::
-
-## H~5b~: Relationship with host government, organizational practices
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent.
-However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
-
-![](img/contrasts_hypothesis05b.png)
-:::
-
-## H~5c~: Relationship with host government, organizational practices, and funding sources
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and are funded primarily by numerous small private donors
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-These intervals are massive; 0 is well within them, leaving us with insufficient evidence to confirm the hypothesis.
-
-![](img/contrasts_hypothesis05c.png)
-:::
-
-## H~5d~: Relationship with host government, organizational practices, and issue area
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief)
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-The contrasts don't support the hypothesis, however, there is an interesting difference between emergency_environment_crackdown and emergency_environment_criticized.
-
-![](img/contrasts_hypothesis05d.png)
-:::
-
-## H~5e~: Relationship with host government, organizational practices, issue area, and funding sources
-
-> Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-These marginal posteriors don't support our hypothesis, but again show an interesting difference between emergency_environment_criticized and emergency_environment_crackdown.
-
-![](img/contrasts_hypothesis05e.png)
-:::
-
-## H~5f~: Organizational practices
-
-> Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits [Mechanism: Donors don't necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks]
-
-::: {.callout-note collapse="true"}
-## Show results from `contrasts` branch
-
-Donors show a similar increase in willingness to donate to accountable NGOs in comparison to NGOs that are financially transparent.
-However, this is contrary to what was hypothesized--we predicted that donor's willingness to donate wouldn't be affected by accountability practices.
-
-![](img/contrasts_hypothesis05f.png)
-:::

### 2023-09-08 notebook/survey-design.qmd
Add IRB, preregistration, and survey

---
title: "Experimental design"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "80%", collapse = TRUE,
  dev = "ragg_png",
  echo = FALSE
)

options(
  digits = 3, width = 120,
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)
```

```{r libraries-functions, warning=FALSE, message=FALSE}
library(tidyverse)
library(gt)
library(targets)

set.seed(12345)

# Targets stuff
tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

tar_load(data_sans_conjoint)

invisible(list2env(tar_read(table_functions), .GlobalEnv))
```

We use a partial fractional factorial design using the following organizational attributes:

```{css, echo=FALSE}
/* Remove padding on lists in tables */
.gt_table ul, .gt_table ol {
  padding-left: 1rem;
}
```

```{r design-table}
orgs <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
issues <- c("Emergency response", "Environment", "Human rights", "Refugee relief")
transparency <- c("Doesn't engage in transparency", "Engages in transparency")
accountability <- c("Doesn't engage in accountability", "Engages in accountability")
funding <- c("Funded primarily by many small private donations", "Funded primarily by a handful of wealthy private donors", "Funded primarily by government grants")
govt <- c("Friendly relationship with government", "Criticized by government", "Under government crackdown")

tribble(
  ~feature, ~levels,
  "Organization", paste0(paste0("- ", orgs), collapse = "\n"),
  "Issue area", paste0(paste0("- ", issues), collapse = "\n"),
  "Financial transparency", paste0(paste0("- ", transparency), collapse = "\n"),
  "Accountability", paste0(paste0("- ", accountability), collapse = "\n"),
  "Funding source", paste0(paste0("- ", funding), collapse = "\n"),
  "Relationship with host government", paste0(paste0("- ", govt), collapse = "\n")
) %>% 
  gt() %>% 
  cols_label(feature = "Feature/Attribute", levels = "Levels") %>% 
  fmt_markdown(columns = levels) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  opts_theme()
```

Participants were then presented with random combinations of these attributes and asked to select which hypothetical organization they'd be willing to donate to. Participants see 12 iterations of a question that looks like this:

::: {.callout-tip icon=false}
### {{< iconify fa6-solid check-to-slot >}}&emsp; Example conjoint survey question

***Q4.x*: For each of the next 12 questions, imagine you are selecting an organization you will donate to and that each of the listed organizations exists. Which of the following organizations would you donate to?**

```{r conjoint-table, echo=FALSE, warning=FALSE, message=FALSE}
tribble(
  ~Attribute, ~`Option 1`, ~`Option 2`, ~`Option 3`, ~None,
  "Organization", sample(orgs, 1), sample(orgs, 1), sample(orgs, 1), "—",
  "Issue area", sample(issues, 1), sample(issues, 1), sample(issues, 1), "—",
  "Transparency", sample(transparency, 1), sample(transparency, 1), sample(transparency, 1), "—",
  "Accountability", sample(accountability, 1), sample(accountability, 1), sample(accountability, 1), "—",
  "Funding sources", sample(funding, 1), sample(funding, 1), sample(funding, 1), "—",
  "Relationship with host government", sample(govt, 1), sample(govt, 1), sample(govt, 1), "—"
) %>% 
  gt() %>% 
  cols_align(align = "center", columns = everything()) %>% 
  cols_align(align = "left", columns = Attribute) %>% 
  cols_width(everything() ~ pct(20)) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_style(
    style = cell_text(weight = "bold"),
    location = cells_body(columns = Attribute)
  ) %>% 
  opts_theme()
```

:::

Our target sample size was 1,000 (and we ended up with `r scales::label_comma()(nrow(data_sans_conjoint))` valid responses), which constitutes a sufficient size for model estimation. A sample size of at least 500 respondents is typical for estimating a hierarchical Bayesian model based on conjoint data. We double this amount because we are interested in analyzing subpopulations of respondents, which requires a larger sample. We present respondents with 4 hypothetical organizations that have 4 randomly assigned features. Respondents will be shown 12 sets of hypothetical organizations. This partial fractional factorial design results in 288 (4 × 4 × 2 × 3 × 3) possible combinations of organization features, and no single respondent will be offered every combination. To provide better coverage and arrive at better individual-level estimates, we use a larger sample size.

### 2023-09-08 notebook/survey-irb.qmd
Add IRB, preregistration, and survey

---
title: "Human subjects and IRB approval"
---

This project has received IRB approval from the human subjects research committees at BYU, Christopher Newport, and Georgia State. We have included a generic version of our protocol below.

<p class="text-center">
<a href="files/byu-irb-approval.pdf" class="btn btn-success btn-md" target="_blank" role="button">
{{< iconify fa6-solid circle-check >}} &nbsp; BYU IRB approval
</a> 
&nbsp;
<a href="files/cnu-irb-approval.pdf" class="btn btn-md btn-success" target="_blank" role="button">
{{< iconify fa6-solid circle-check >}} &nbsp; Christopher Newport IRB approval
</a>
&nbsp;
<a href="files/gsu-irb-approval.pdf" class="btn btn-success btn-md" target="_blank" role="button">
{{< iconify fa6-solid circle-check >}} &nbsp; Georgia State IRB approval
</a>
</p>

---

{{< include survey/irb.md >}}

### 2023-09-08 notebook/manuscript.qmd
Add manuscript link

---
title: "Manuscript"
---

Manuscript iframe stuff goes here.

### 2023-09-09 notebook/methods.qmd
Use a chunk name

@@
 
-```{r}
+```{r show-full-grid-preds}
 #| column: screen-inset

### 2023-09-09 notebook/results-funding.qmd
Add initial H4 stuff

---
title: "H~4~: Funding sources"
format:
  html:
    code-fold: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "80%", collapse = TRUE,
  dev = "ragg_png"
)

options(
  digits = 3, width = 120,
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)
```

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(patchwork)
library(scales)
library(ggh4x)
library(glue)
library(gt)
library(gtExtras)

tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

preds_all <- tar_read(preds_conditional_treatment_only)

invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))

theme_set(theme_ngo())
```

# H~4a~: Funding sources

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 4~a~: Funding sources

**Donors will show increased willingness to donate to NGOs that are funded primarily by numerous small private donors compared to NGOs that are funded by a handful of wealthy private donors and government grants**

*Mechanisms: Perception of efficacy - your contribution matters as a small donor. Government funding may also imply lack of independence of government which can reduce the efficiency of an organization.*
:::

## Estimand

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Funding} = \text{Few wealthy donors or Government} \right) \bigr] - \\
&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Funding} = \text{Many small donors} \right) \bigr]
\end{aligned}
$$

```{r h4a-calc-estimands}
h4a_mms <- preds_all %>% 
  group_by(feat_funding_short, .draw) %>% 
  summarize(avg = mean(.epred))

h4a_amces <- h4a_mms %>% 
  group_by(feat_funding_short) %>% 
  compare_levels(variable = avg, by = feat_funding_short, comparison = "control")
```

```{r plot-h4a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
#| column: body-outset-right
p_h4a_mms <- h4a_mms %>% 
  ggplot(aes(x = avg, y = feat_funding_short, fill = feat_funding_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(3, 6, 5)], guide = "none") +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  )

p_h4a_amces <- h4a_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_funding_short,
    delim = " - ", 
    names = c("feat_funding_short", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_funding_short = unique(.$reference_level)) %>%
  mutate(feat_funding_short = factor(feat_funding_short, levels = levels(h4a_mms$feat_funding_short))) %>% 
  ggplot(aes(x = avg, y = feat_funding_short, fill = feat_funding_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(3, 6, 5)], guide = "none") +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Average marginal component effects (AMCEs)"
  )

p_h4a_mms | p_h4a_amces
```

```{r table-h4a-mm-amce}
#| column: body-outset-right
h4a_tbl_mm <- h4a_mms %>% 
  group_by(feat_funding_short) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_funding_short)) %>% 
  select(feat_funding_short, nice)

h4a_tbl_amces <- h4a_amces %>% 
  group_by(feat_funding_short) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>%
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
  mutate(feat_funding_short = str_replace(feat_funding_short, " - ", "−<br>")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
  arrange(desc(feat_funding_short)) %>% 
  select(contrast = feat_funding_short, amce_nice = nice, p_neq_0)

bind_cols(
  h4a_tbl_mm, 
  add_row(h4a_tbl_amces, contrast = "*(Reference)*")
) %>% 
  gt() %>% 
  sub_missing(columns = everything(), missing_text = "—") %>% 
  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
  cols_align(align = "center", columns = everything()) %>% 
  cols_align(align = "left", columns = c(feat_funding_short, contrast)) %>% 
  cols_label(
    feat_funding_short = "Funding source", 
    nice = "Posterior EMM",
    contrast = "Contrast",
    amce_nice = "Posterior AMCE",
    p_neq_0 = "*p*~direction~",
    .fn = md
  ) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_footnote(
    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
    locations = cells_column_labels(columns = c(nice, amce_nice))
  ) %>% 
  tab_footnote(
    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
    locations = cells_column_labels(columns = p_neq_0)
  ) %>% 
  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
  opt_footnote_marks(marks = "standard") %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

# H~4b~: Relationship with host government and funding sources

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 4~b~: Relationship with host government and funding sources

**Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors**
:::

## Estimand

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Funding} = \text{Few wealthy donors or Government} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr] - \\
&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Funding} = \text{Many small donors} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr]
\end{aligned}
$$

```{r h4b-calc-estimands}
h4b_mms <- preds_all %>% 
  group_by(feat_funding_short, feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

h4b_amces <- h4b_mms %>% 
  group_by(feat_govt) %>% 
  compare_levels(variable = avg, by = feat_funding_short, comparison = "control")
```

```{r plot-h4b-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset-right
p_h4b_mms <- h4b_mms %>% 
  ggplot(aes(x = avg, y = feat_funding_short, fill = feat_funding_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(3, 6, 5)], guide = "none") +
  facet_wrap(vars(feat_govt), ncol = 1) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )

p_h4b_amces <- h4b_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_funding_short,
    delim = " - ", 
    names = c("feat_funding_short", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_funding_short = "Many small donors", feat_govt = "Friendly relationship with government") %>%
  add_row(avg = 0, feat_funding_short = "Many small donors", feat_govt = "Criticized by government") %>%
  add_row(avg = 0, feat_funding_short = "Many small donors", feat_govt = "Under government crackdown") %>%
  mutate(feat_funding_short = factor(feat_funding_short, levels = levels(h4b_mms$feat_funding_short))) %>% 
  ggplot(aes(x = avg, y = feat_funding_short, fill = feat_funding_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(3, 6, 5)], guide = "none") +
  facet_wrap(vars(feat_govt), ncol = 1) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

p_h4b_mms | p_h4b_amces
```

```{r table-h4b-mm-amce}
#| column: body-outset-right
h4b_tbl_mm <- h4b_mms %>% 
  group_by(feat_govt, feat_funding_short) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_govt), desc(feat_funding_short)) %>% 
  select(feat_funding_short, feat_govt, nice)

h4b_tbl_amces <- h4b_amces %>% 
  group_by(feat_govt, feat_funding_short) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>%
  ungroup() %>% 
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
  mutate(feat_funding_short = str_replace(feat_funding_short, " - ", "−<br>")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
  arrange(desc(feat_govt)) %>% 
  select(contrast = feat_funding_short, diff_nice = nice, p_neq_0)

bind_cols(
  h4b_tbl_mm, 
  h4b_tbl_amces %>% 
    add_row(contrast = NA, .after = 2) %>% 
    add_row(contrast = NA, .after = 5) %>% 
    add_row(contrast = NA, .after = 8)
) %>% 
  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
  group_by(feat_govt) %>% 
  gt() %>% 
  sub_missing(columns = everything(), missing_text = "—") %>% 
  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
  cols_align(align = "center", columns = everything()) %>% 
  cols_align(align = "left", columns = c(feat_funding_short, contrast)) %>% 
  cols_label(
    feat_funding_short = "Funding source", 
    nice = "Posterior EMM",
    contrast = "Contrast",
    diff_nice = "Posterior ∆",
    p_neq_0 = "*p*~direction~",
    .fn = md
  ) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_style(
    style = cell_fill(color = "grey90"),
    locations = cells_row_groups()
  ) %>% 
  tab_footnote(
    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
    locations = cells_column_labels(columns = c(nice, diff_nice))
  ) %>% 
  tab_footnote(
    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
    locations = cells_column_labels(columns = p_neq_0)
  ) %>% 
  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
  opt_footnote_marks(marks = "standard") %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

## H~4c~: Relationship with host government, funding sources, and issue area

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 4~c~: Relationship with host government, funding sources, and issue area

**Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors and work in less contentious areas (emergency response and refugee relief)**
:::

## Estimand

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Funding} = \text{Few wealthy donors or Government} \mid \text{(Relationship = Under crackdown or Criticized) and (Issue = less contentious)} \right) \bigr] - \\
&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Funding} = \text{Many small donors} \mid \text{(Relationship = Under crackdown or Criticized) and (Issue = less contentious)} \right) \bigr]
\end{aligned}
$$

```{r h4c-calc-estimands}
h4c_mms <- preds_all %>% 
  group_by(feat_funding_short, feat_govt, feat_issue, .draw) %>% 
  summarize(avg = mean(.epred))

h4c_amces <- h4c_mms %>% 
  group_by(feat_govt, feat_issue) %>% 
  compare_levels(variable = avg, by = feat_funding_short, comparison = "control")
```

```{r plot-h4c-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset-right
p_h4c_mms <- h4c_mms %>%
  ggplot(aes(x = avg, y = feat_funding_short, fill = feat_funding_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(3, 6, 5)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_issue),
    ncol = 4,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )

baselines <- expand_grid(
  avg = 0,
  feat_funding_short = "Many small donors",
  feat_govt = levels(h4c_mms$feat_govt),
  feat_issue = levels(h4c_mms$feat_issue)
)
p_h4c_mms

p_h4c_amces <- h4c_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_funding_short,
    delim = " - ", 
    names = c("feat_funding_short", "reference_level")
  ) %>% 
  bind_rows(baselines) %>% 
  mutate(feat_funding_short = factor(feat_funding_short, levels = levels(h4c_mms$feat_funding_short))) %>% 
  ggplot(aes(x = avg, y = feat_funding_short, fill = feat_funding_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(3, 6, 5)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_issue),
    ncol = 4,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

p_h4c_amces
```

### 2023-09-09 notebook/results-practices.qmd
Finish initial H5 stuff

---
title: "H~5~: Organizational practices"
format:
  html:
    code-fold: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "80%", collapse = TRUE,
  dev = "ragg_png"
)

options(
  digits = 3, width = 120,
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)
```

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(patchwork)
library(scales)
library(ggh4x)
library(glue)
library(gt)
library(gtExtras)

tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

preds_all <- tar_read(preds_conditional_treatment_only)

invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))

theme_set(theme_ngo())
```

# H~5a~: Financial transparency

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~a~: Financial transparency

**Donors will show increased willingness to donate to NGOs that are financially transparent**

*Mechanism: Perception of efficacy*
:::

## Estimand

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Transparency} = \text{Yes} \right) \bigr]
\end{aligned}
$$
```{r h5a-calc-estimands}
h5a_mms <- preds_all %>% 
  group_by(feat_transp_short, .draw) %>% 
  summarize(avg = mean(.epred))

h5a_amces <- h5a_mms %>% 
  group_by(feat_transp_short) %>% 
  compare_levels(variable = avg, by = feat_transp_short, comparison = "control")
```

```{r plot-h5a-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
#| column: body-outset-right
p_h5a_mms <- h5a_mms %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  )

p_h5a_amces <- h5a_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_transp_short,
    delim = " - ", 
    names = c("feat_transp_short", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_transp_short = unique(.$reference_level)) %>%
  mutate(feat_transp_short = factor(feat_transp_short, levels = levels(h5a_mms$feat_transp_short))) %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Average marginal component effects (AMCEs)"
  )

p_h5a_mms | p_h5a_amces
```

```{r table-h5a-mm-amce}
#| column: body-outset-right
h5a_tbl_mm <- h5a_mms %>% 
  group_by(feat_transp_short) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_transp_short)) %>% 
  select(feat_transp_short, nice)

h5a_tbl_amces <- h5a_amces %>% 
  group_by(feat_transp_short) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>%
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
  mutate(feat_transp_short = str_replace(feat_transp_short, " - ", "−<br>")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
  arrange(desc(feat_transp_short)) %>% 
  select(contrast = feat_transp_short, amce_nice = nice, p_neq_0)

bind_cols(
  h5a_tbl_mm, 
  add_row(h5a_tbl_amces, contrast = "*(Reference)*")
) %>% 
  gt() %>% 
  sub_missing(columns = everything(), missing_text = "—") %>% 
  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
  cols_align(align = "center", columns = everything()) %>% 
  cols_align(align = "left", columns = c(feat_transp_short, contrast)) %>% 
  cols_label(
    feat_transp_short = "Transparency", 
    nice = "Posterior EMM",
    contrast = "Contrast",
    amce_nice = "Posterior AMCE",
    p_neq_0 = "*p*~direction~",
    .fn = md
  ) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_footnote(
    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
    locations = cells_column_labels(columns = c(nice, amce_nice))
  ) %>% 
  tab_footnote(
    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
    locations = cells_column_labels(columns = p_neq_0)
  ) %>% 
  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
  opt_footnote_marks(marks = "standard") %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

# H~5b~: Relationship with host government, organizational practices

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~b~: Relationship with host government, organizational practices

**Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent**
:::

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Transparency} = \text{Yes} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr] - \\
&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Transparency} = \text{Yes} \mid \text{Relationship = Friendly} \right) \bigr]
\end{aligned}
$$

```{r h5b-calc-estimands}
h5b_mms <- preds_all %>% 
  group_by(feat_transp_short, feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

h5b_amces <- h5b_mms %>% 
  group_by(feat_govt) %>% 
  compare_levels(variable = avg, by = feat_transp_short, comparison = "control")
```

```{r plot-h5b-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset-right
p_h5b_mms <- h5b_mms %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_wrap(vars(feat_govt), ncol = 1) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )

p_h5b_amces <- h5b_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_transp_short,
    delim = " - ", 
    names = c("feat_transp_short", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_transp_short = "No", feat_govt = "Friendly relationship with government") %>%
  add_row(avg = 0, feat_transp_short = "No", feat_govt = "Criticized by government") %>%
  add_row(avg = 0, feat_transp_short = "No", feat_govt = "Under government crackdown") %>%
  mutate(feat_transp_short = factor(feat_transp_short, levels = levels(h5b_mms$feat_transp_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h5b_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_wrap(vars(feat_govt), ncol = 1) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

p_h5b_mms | p_h5b_amces
```

```{r table-h5b-mm-amce}
#| column: body-outset-right
h5b_tbl_mm <- h5b_mms %>% 
  group_by(feat_govt, feat_transp_short) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_govt), desc(feat_transp_short)) %>% 
  select(feat_transp_short, feat_govt, nice)

h5b_tbl_amces <- h5b_amces %>% 
  group_by(feat_govt, feat_transp_short) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>%
  ungroup() %>% 
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
  mutate(feat_transp_short = str_replace(feat_transp_short, " - ", "−<br>")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
  arrange(desc(feat_govt)) %>% 
  select(contrast = feat_transp_short, diff_nice = nice, p_neq_0)

bind_cols(
  h5b_tbl_mm, 
  h5b_tbl_amces %>% 
    add_row(contrast = NA, .after = 1) %>% 
    add_row(contrast = NA, .after = 3) %>% 
    add_row(contrast = NA, .after = 5)
) %>% 
  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
  group_by(feat_govt) %>% 
  gt() %>% 
  sub_missing(columns = everything(), missing_text = "—") %>% 
  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
  cols_align(align = "center", columns = everything()) %>% 
  cols_align(align = "left", columns = c(feat_transp_short, contrast)) %>% 
  cols_label(
    feat_transp_short = "Transparency", 
    nice = "Posterior EMM",
    contrast = "Contrast",
    diff_nice = "Posterior ∆",
    p_neq_0 = "*p*~direction~",
    .fn = md
  ) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_style(
    style = cell_fill(color = "grey90"),
    locations = cells_row_groups()
  ) %>% 
  tab_footnote(
    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
    locations = cells_column_labels(columns = c(nice, diff_nice))
  ) %>% 
  tab_footnote(
    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
    locations = cells_column_labels(columns = p_neq_0)
  ) %>% 
  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
  opt_footnote_marks(marks = "standard") %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

## H~5c~: Relationship with host government, organizational practices, and funding sources

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~c~: Relationship with host government, organizational practices, and funding sources

**Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and are funded primarily by numerous small private donors**
:::

## Estimand

TODO

```{r h5c-calc-estimands}
h5c_mms <- preds_all %>% 
  group_by(feat_transp_short, feat_govt, feat_funding_short, .draw) %>% 
  summarize(avg = mean(.epred))

h5c_amces <- h5c_mms %>% 
  group_by(feat_govt, feat_funding_short) %>% 
  compare_levels(variable = avg, by = feat_transp_short, comparison = "control")
```

```{r plot-h5c-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset-right
p_h5c_mms <- h5c_mms %>%
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_funding_short),
    ncol = 3,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )
p_h5c_mms

baselines <- expand_grid(
  avg = 0,
  feat_transp_short = "No",
  feat_govt = levels(h5c_mms$feat_govt),
  feat_funding_short = levels(h5c_mms$feat_funding_short)
)

p_h5c_amces <- h5c_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_transp_short,
    delim = " - ", 
    names = c("feat_transp_short", "reference_level")
  ) %>% 
  bind_rows(baselines) %>% 
  mutate(feat_transp_short = factor(feat_transp_short, levels = levels(h5c_mms$feat_transp_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h5c_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_funding_short),
    ncol = 3,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

p_h5c_amces
```

# H~5d~: Relationship with host government, organizational practices, and issue area

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~d~: Relationship with host government, organizational practices, and issue area

**Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief)**
:::

## Estimand

TODO

```{r h5d-calc-estimands}
h5d_mms <- preds_all %>% 
  group_by(feat_transp_short, feat_govt, feat_issue, .draw) %>% 
  summarize(avg = mean(.epred))

h5d_amces <- h5d_mms %>% 
  group_by(feat_govt, feat_issue) %>% 
  compare_levels(variable = avg, by = feat_transp_short, comparison = "control")
```

```{r plot-h5d-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset-right
p_h5d_mms <- h5d_mms %>%
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_issue),
    ncol = 4,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )
p_h5d_mms

baselines <- expand_grid(
  avg = 0,
  feat_transp_short = "No",
  feat_govt = levels(h5d_mms$feat_govt),
  feat_issue = levels(h5d_mms$feat_issue)
)

p_h5d_amces <- h5d_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_transp_short,
    delim = " - ", 
    names = c("feat_transp_short", "reference_level")
  ) %>% 
  bind_rows(baselines) %>% 
  mutate(feat_transp_short = factor(feat_transp_short, levels = levels(h5d_mms$feat_transp_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h5d_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_issue),
    ncol = 4,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

p_h5d_amces
```

# H~5e~: Relationship with host government, organizational practices, issue area, and funding sources

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~e~: Relationship with host government, organizational practices, issue area, and funding sources

**Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors**
:::

TODO

```{r h5e-calc-estimands}
h5e_mms <- preds_all %>% 
  group_by(feat_transp_short, feat_govt, feat_funding_short, feat_issue, .draw) %>% 
  summarize(avg = mean(.epred))

h5e_amces <- h5e_mms %>% 
  group_by(feat_govt, feat_funding_short, feat_issue) %>% 
  compare_levels(variable = avg, by = feat_transp_short, comparison = "control")
```

```{r plot-h5e-mm-amce, fig.width=14, fig.height=6.5, out.width="100%"}
#| column: page
p_h5e_mms <- h5e_mms %>%
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_funding_short, feat_issue),
    ncol = 12,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )
p_h5e_mms

baselines <- expand_grid(
  avg = 0,
  feat_transp_short = "No",
  feat_govt = levels(h5e_mms$feat_govt),
  feat_funding_short = levels(h5e_mms$feat_funding_short),
  feat_issue = levels(h5e_mms$feat_issue)
)

p_h5e_amces <- h5e_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_transp_short,
    delim = " - ", 
    names = c("feat_transp_short", "reference_level")
  ) %>% 
  bind_rows(baselines) %>% 
  mutate(feat_transp_short = factor(feat_transp_short, levels = levels(h5e_mms$feat_transp_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h5e_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_funding_short, feat_issue),
    ncol = 12,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

p_h5e_amces
```

# H~5f~: Accountability

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~f~: Accountability

**Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits**

*Mechanism: Donors don't necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks*
:::

## Estimand

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Accountability} = \text{Yes} \right) \bigr]
\end{aligned}
$$

```{r h5f-calc-estimands}
h5f_mms <- preds_all %>% 
  group_by(feat_acc_short, .draw) %>% 
  summarize(avg = mean(.epred))

h5f_amces <- h5f_mms %>% 
  group_by(feat_acc_short) %>% 
  compare_levels(variable = avg, by = feat_acc_short, comparison = "control")
```

```{r plot-h5f-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
#| column: body-outset-right
p_h5f_mms <- h5f_mms %>% 
  ggplot(aes(x = avg, y = feat_acc_short, fill = feat_acc_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(9, 4)], guide = "none") +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  )

p_h5f_amces <- h5f_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_acc_short,
    delim = " - ", 
    names = c("feat_acc_short", "reference_level")
  ) %>% 
  add_row(avg = 0, feat_acc_short = unique(.$reference_level)) %>%
  mutate(feat_acc_short = factor(feat_acc_short, levels = levels(h5f_mms$feat_acc_short))) %>% 
  ggplot(aes(x = avg, y = feat_acc_short, fill = feat_acc_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(9, 4)], guide = "none") +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Average marginal component effects (AMCEs)"
  )

p_h5f_mms | p_h5f_amces
```

```{r table-h5f-mm-amce}
#| column: body-outset-right
h5f_tbl_mm <- h5f_mms %>% 
  group_by(feat_acc_short) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_acc_short)) %>% 
  select(feat_acc_short, nice)

h5f_tbl_amces <- h5f_amces %>% 
  group_by(feat_acc_short) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>%
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
  mutate(feat_acc_short = str_replace(feat_acc_short, " - ", "−<br>")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
  arrange(desc(feat_acc_short)) %>% 
  select(contrast = feat_acc_short, amce_nice = nice, p_neq_0)

bind_cols(
  h5f_tbl_mm, 
  add_row(h5f_tbl_amces, contrast = "*(Reference)*")
) %>% 
  gt() %>% 
  sub_missing(columns = everything(), missing_text = "—") %>% 
  fmt_markdown(columns = c(nice, amce_nice, contrast)) %>%
  cols_align(align = "center", columns = everything()) %>% 
  cols_align(align = "left", columns = c(feat_acc_short, contrast)) %>% 
  cols_label(
    feat_acc_short = "Accountability", 
    nice = "Posterior EMM",
    contrast = "Contrast",
    amce_nice = "Posterior AMCE",
    p_neq_0 = "*p*~direction~",
    .fn = md
  ) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_footnote(
    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
    locations = cells_column_labels(columns = c(nice, amce_nice))
  ) %>% 
  tab_footnote(
    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
    locations = cells_column_labels(columns = p_neq_0)
  ) %>% 
  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
  opt_footnote_marks(marks = "standard") %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

### 2023-09-09 notebook/results-branding.qmd
Add MM line; fix facet ordering

@@
   stat_halfeye() +
+  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
   scale_x_continuous(labels = label_percent()) +

### 2023-09-09 notebook/results-crackdown.qmd
Use conditional estimates
Add MM line; fix facet ordering

@@
 
-preds_all <- tar_read(preds_new_treatment_only)
+preds_all <- tar_read(preds_conditional_treatment_only)
 
@@
   stat_halfeye(aes(slab_alpha = org_collapsed)) +
+  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
   scale_x_continuous(labels = label_percent()) +
@@
   ) %>% 
-  mutate(feat_govt = factor(feat_govt, levels = levels(h2a_mms$feat_govt))) %>% 
+  mutate(feat_govt = factor(feat_govt, levels = levels(h2b_mms$feat_govt))) %>% 
   ggplot(aes(x = avg, y = feat_govt, fill = feat_govt)) +

### 2023-09-09 notebook/results-funding.qmd
Add MM line; fix facet ordering

@@
   mutate(feat_funding_short = factor(feat_funding_short, levels = levels(h4b_mms$feat_funding_short))) %>% 
+  mutate(feat_govt = factor(feat_govt, levels = levels(h4b_mms$feat_govt))) %>% 
   ggplot(aes(x = avg, y = feat_funding_short, fill = feat_funding_short)) +
@@
   )
+p_h4c_mms
 
@@
 )
-p_h4c_mms
 
@@
   mutate(feat_funding_short = factor(feat_funding_short, levels = levels(h4c_mms$feat_funding_short))) %>% 
+  mutate(feat_govt = factor(feat_govt, levels = levels(h4c_mms$feat_govt))) %>% 
   ggplot(aes(x = avg, y = feat_funding_short, fill = feat_funding_short)) +

### 2023-09-09 notebook/results-issue.qmd
Add MM line; fix facet ordering

@@
   mutate(feat_issue = factor(feat_issue, levels = levels(h3b_mms$feat_issue))) %>% 
+  mutate(feat_govt = factor(feat_govt, levels = levels(h3b_mms$feat_govt))) %>% 
   ggplot(aes(x = avg, y = feat_issue, fill = feat_issue)) +

### 2023-09-09 notebook/results.qmd
Add TODO

@@
 ```
+
+TODO: Hypotheses
+
+- General basic ones, like only each lever, one at a time
+- More specific ones that we preregistered.
+These conditional ones are tricky because there are so many different possible questions we could explore (at least 576 of them!).
+To avoid selective p-hacking, we pre-registered a handful that we're most interested in, and we only explore those.
 

### 2023-09-09 notebook/model-details.qmd
Add model details and diagnostics

---
title: "Model details"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "80%", collapse = TRUE,
  dev = "ragg_png"
)

options(
  digits = 3, width = 120,
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)
```

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(glue)
library(gt)
library(gtExtras)

tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

tar_load(m_treatment_only)

invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))

theme_set(theme_ngo())
```

```{r calculate-model-times}
models <- tribble(
  ~model_name, ~nesting, ~model,
  "Treatment variables only", "Respondent-specific intercepts", m_treatment_only#,
  # "Treatment variables only", "Respondent-specific intercepts and slopes", NA
) %>% 
  mutate(duration = map(model, ~{
    .$fit %>% 
      rstan::get_elapsed_time() %>% 
      as_tibble() %>% 
      summarize(total = as.duration(max(warmup + sample)))
  })) %>% 
  select(-model) %>% 
  unnest(duration)

dur <- as.period(as.duration(sum(models$total)))

total_run_time <- glue(
  "{hours} hours, {minutes} minutes, and {seconds} seconds",
  hours = hour(dur), minutes = minute(dur), seconds = round(second(dur), 0)
)
```

We ran these models on a 2021 M1 MacBook Pro with 32 GB of RAM, with 4 MCMC chains spread across 8 cores, with two CPU threads per chain, using Stan through brms through cmdstanr.

In total, it took `r total_run_time` to run everything.

```{r mcmc-duration-table}
models %>% 
  gt() %>% 
  tab_footnote(
    footnote = "Duration of the longest-running MCMC chain",
    locations = cells_column_labels(columns = total)
  ) %>% 
  cols_label(
    model_name = "Model variation",
    nesting =  "Nesting structure",
    total = "Total time"
  ) %>% 
  cols_align(
    align = "left",
    columns = everything()
  ) %>%
  grand_summary_rows(
    columns = c(total),
    fns = list(`Overall total` = ~as.duration(sum(.)))
  ) %>% 
  opt_footnote_marks(marks = "standard") %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

### 2023-09-09 R/funs_plots.R

@@ -1,0 +1,30 @@
+# Diagnostic plots
+
+plot_trace <- function(model, params) {
+  model %>% 
+    tidybayes::gather_draws(!!!syms(params)) %>% 
+    ggplot(aes(x = .iteration, y = .value, color = factor(.chain))) +
+    geom_line(linewidth = 0.1) +
+    scale_color_viridis_d(option = "rocket", end = 0.85) +
+    labs(color = "Chain") +
+    facet_wrap(vars(.variable), scales = "free_y") +
+    theme_ngo()
+}
+
+plot_trank <- function(model, params) {
+  model %>% 
+    tidybayes::gather_draws(!!!syms(params)) %>% 
+    group_by(.variable) %>% 
+    mutate(draw_rank = rank(.value)) %>% 
+    ggplot(aes(x = draw_rank, color = factor(.chain))) +
+    stat_bin(geom = "step", binwidth = 200, position = position_identity(), boundary = 0) +
+    scale_color_viridis_d(option = "rocket", end = 0.85) +
+    labs(color = "Chain") +
+    facet_wrap(vars(.variable), scales = "free_y") +
+    theme_ngo()
+}
+
+plot_pp <- function(model) {
+  bayesplot::pp_check(model, ndraws = 100, type = "bars") +
+    theme_ngo()
+}

### 2023-09-09 _targets.R

@@ -62,6 +62,7 @@ list(
     build_ci, fmt_decimal, label_pp
   )),
   tar_target(table_functions, lst(opts_int, opts_theme)),
+  tar_target(diagnostic_functions, lst(plot_trace, plot_trank, plot_pp)),
   
   ## Models ----
   tar_target(m_treatment_only, f_treatment_only(data_full)),

### 2023-09-09 notebook/style-guide.qmd
Add initial style guide

---
title: "Visual style guide"
resources: 
  - "html/linux-libertine-woff/*"
format: 
  html: 
    toc-depth: 4
---

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(scales)

tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

# Load graphics functions from targets
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))

show_nice_pal <- function(pal, nrow = 1, show_text = TRUE) {
  out <- tibble(x = 1:length(pal),
                color = pal) %>% 
    mutate(x_nice = glue::glue("[{x}]")) %>% 
    mutate(across(c(color, x_nice), ~fct_inorder(.))) %>% 
    ggplot(aes(x = color, y = 1, fill = color)) +
    geom_tile() +
    scale_x_discrete(expand = c(0, 0)) +
    scale_fill_identity() +
    facet_wrap(vars(x_nice), scales = "free_x", nrow = nrow) +
    theme_void(base_family = "Inconsolata") +
    theme(panel.spacing.x = unit(-1, units = "pt"),
          panel.spacing.y = unit(-0.5, units = "lines"),
          strip.text = element_blank())

  if (show_text) {
    out <- out + 
      theme(axis.text.x = element_text(margin = margin(b = 5)),
            strip.text = element_text(size = rel(1.1), margin = margin(t = 5)),
            panel.spacing.y = unit(0, units = "lines"))
  }

  return(out)
}
```

# Fonts

```{scss echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Inter&display=swap');

@font-face {
  font-family: 'Linux Libertine O';
  font-style: normal;
  font-weight: normal;
  src: local('Linux Libertine O Regular'), url('/notebook/html/linux-libertine-woff/LinLibertine_R.woff') format('woff');
}

@font-face {
  font-family: 'Linux Libertine O';
  font-style: italic;
  font-weight: normal;
  src: local('Linux Libertine O Italic'), url('/notebook/html/linux-libertine-woff/LinLibertine_RI.woff') format('woff');
}

@font-face {
  font-family: 'Linux Libertine O';
  font-style: normal;
  font-weight: bold;
  src: local('Linux Libertine O Bold'), url('/notebook/html/linux-libertine-woff/LinLibertine_RB.woff') format('woff');
}

@font-face {
  font-family: 'Linux Libertine O Bold';
  font-style: italic;
  font-weight: bold;
  src: local('Linux Libertine O Bold Italic'), url('LinLibertine_RBI.woff') format('woff');
}

.font-example {
  background: #ffffff;
  padding: 1.5em 1.5em 0.75em 1.5em;
  margin-bottom: 1rem;
  border-left: 10px solid #68abb8;
  border-top: 1px solid #68abb8;
  border-right: 1px solid #68abb8;
  border-bottom: 1px solid #68abb8;
  font-size: 1.1em;
}

.inter {
  font-family: "Inter";
}

.libertine {
  font-family: "Linux Libertine O Regular";
  font-size: 1.2em;
}
```

We use [Inter](https://rsms.me/inter/) (accessible for free from [Google Fonts](https://fonts.google.com/specimen/Inter)) as the main font in all our plots.

::: {.font-example .inter}
**Inter**

Whereas recognition of the *inherent dignity* and of the ***equal and inalienable*** rights of all members of the human family is the foundation of freedom, justice and peace in the world…
:::

In the fancy preprint version of our manuscript we use [Linux Libertine](https://en.wikipedia.org/wiki/Linux_Libertine) for the main body font, since it fits with [Libertinus Math](https://github.com/alerque/libertinus) for fancier math typesetting.

::: {.font-example .libertine}
**Linux Libertine**

Whereas recognition of the *inherent dignity* and of the ***equal and inalienable*** rights of all members of the human family is the foundation of freedom, justice and peace in the world…
:::

# Colors

## Palettes

### Prism (`clrs$prism`)

```{r show-prism-short, fig.width=8, fig.height=0.2}
#| out-width: 100%
#| echo: false
clrs$prism %>% show_nice_pal(show_text = FALSE, nrow = 1)
```

Our main palette is the [qualitative Prism palette from CARTOColors](https://carto.com/carto-colors/). CARTOColors palettes were designed for data-focused map visualizations,but can be used in any kind of visualization, similar to [ColorBrewer](http://colorbrewer2.org/).

Access the palette using `clrs$prism`, and access specific colors with indexes like `clrs$prism[8]`:

```{r show-prism, fig.width=8, fig.height=2}
#| out-width: 100%
#| echo: false
clrs$prism %>% show_nice_pal(show_text = TRUE, nrow = 2)
```

```{r hex-prism}
#| code-fold: show
clrs$prism %>% set_names(1:length(.))
```

\

### Single-ish-color sequential palettes

In some cases, like with plots that use `geom_lineribbon()`, we use a range of sequential colors. For these, we use several different [sequential palettes from CARTOColors](https://carto.com/carto-colors/) since they tend to match the color scheme from `clrs$prism`.

### Peach (`clrs$peach`)

```{r show-peach, fig.width=8, fig.height=1}
#| out-width: 100%
#| echo: false
clrs$peach %>% show_nice_pal(show_text = TRUE)
```

```{r hex-peach}
#| code-fold: show
clrs$peach %>% set_names(1:length(.))
```

## Color mappings

TODO: Color sets for specific features/levels/contrasts

### 2023-09-09 R/funs_plots.R
Wider histogram bins

@@ -17,7 +17,7 @@ plot_trank <- function(model, params) {
     group_by(.variable) %>% 
     mutate(draw_rank = rank(.value)) %>% 
     ggplot(aes(x = draw_rank, color = factor(.chain))) +
-    stat_bin(geom = "step", binwidth = 200, position = position_identity(), boundary = 0) +
+    stat_bin(geom = "step", binwidth = 400, position = position_identity(), boundary = 0) +
     scale_color_viridis_d(option = "rocket", end = 0.85) +
     labs(color = "Chain") +
     facet_wrap(vars(.variable), scales = "free_y") +

### 2023-09-09 manuscript/manuscript.qmd
Add manuscript infrastructure

---
title: "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy"
short-title: "Why Donors Donate"
date: "2023-09-09"
author:
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
  orcid: 0000-0003-3506-7590
- name: Marc Dotson
  affiliation: Brigham Young University
  url: https://marriottschool.byu.edu/directory/details?id=50683
  email: marc_dotson@byu.edu
- name: Andrew Heiss
  affiliation: Georgia State University
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
abstract: |
  As space for civil society has closed around the world, transnational NGOs have faced a crisis of funding. We explore how NGOs have shifted from traditionally Northern funding sources toward grassroots private philanthropic money. How do individual donors in the US feel about donating to legally besieged NGOs abroad? Do legal restrictions on NGOs influence donors’ decision to donate? We use a conjoint survey experiment to argue that domestic political environments of NGO host countries influence preferences of private donors and that legal crackdowns on NGOs serve as a heuristic of organizational deservingness.
keywords:
  - philanthropy
  - civil society
  - conjoint experiments
  - donor heuristics
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/silent-skywalk>"
bibliography: references.bib
link-citations: true
---

```{r setup, include=FALSE}
if (is.null(knitr::pandoc_to())) {
  fmt_out <- "interactive"
} else {
  fmt_out <- knitr::pandoc_to()
}

knitr::opts_chunk$set(echo = FALSE, include = FALSE, 
                      warning = FALSE, message = FALSE)

knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
                      fig.width = 6, fig.height = (6 * 0.618),
                      out.width = "100%", collapse = TRUE)

options(digits = 3, width = 120,
        dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

Over the last three decades, states have increasingly sought to crack down on civil society organizations. In Human Rights Watch's 2016 Annual Report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory. Policymakers have referred to this phenomenon as the "closing of civic space" and data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in nearly 60% of countries—111 in total [@CIVICUS:2017]. These attacks—most of which have occurred through restrictive legislation targeted against nongovernmental organizations (NGOs)—have adversely affected the ability of both domestic and international NGOs to operate and raise funds. Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official aid donors channel fewer funds to contentious issues and instead choose to fund "tame" causes [@ChaudhryHeiss:2018; @Bush:2015].

In response to this dramatic shift in the NGO funding landscape, international NGOs (INGOs) have increasingly turned to foreign individual donors to offset the loss of funding from government and foundation sources [@BanksHulmeEdwards:2015]. The amount of this private foreign aid is not insignificant—from 2000–2010, private giving by U.S. entities towards international causes doubled in real terms [@desaikharas, 505]. In 2016, U.S. private philanthropy towards international NGOs amounted to \$22.06 billion [@givingusa:2017].

This turn to private donors opens INGOs up to new dynamics in seeking out aid. Many organizations that had previously relied on governments and foundations had optimized their fundraising strategies for those kinds of organizations, but now need to tailor their fundraising attempts to private individuals, who behave differently from governments and foundations. Individuals have different preferences and rely on signals of effectiveness that differ from the benchmarks that large donor agencies rely on, including ratios of administrative overhead spending, financial transparency, accountability, and efficiency. These signals are are organizational characteristics that INGOs have direct control over. However, the political environment in the countries INGOs work in—including the global crackdown on civil society that is causing many organizations to seek out private funding in the first place—is a structural factor that INGOs can rarely influence on their own. How do organizational elements of private donor decision-making interact with broader structural limits on INGO fundraising?

Given the growing crackdown on INGOs across the world, how do individual donors in the U.S. feel about donating to legally besieged NGOs abroad? How do organizational-level factors such as financial transparency and accountability; funding sources, including private donations and government grants; and various different issue areas compare with more structural-level factors such as host country politics when deciding to donate?

While recent research on private foreign aid has examined funding decisions of donor NGOs themselves, we know less about the funding choices of the individuals responsible for much of these private aid flows [@desaikharas]. We argue that NGO-level organizational factors and domestic political environments of NGO host countries can influence preferences of foreign private donors by serving as heuristics to potential donors. Using a conjoint survey experiment, we find that private donors favor NGOs that voluntarily engage in transparency and accountability, prefer organizations that receive funding from many private individuals, rather than government or foundation grants, and that work on issues related to humanitarian and disaster relief rather than human rights and environmental advocacy. Importantly, we also find that structural factors play an important role in the private decision to donate—donors are significantly less likely to donate to INGOs that face government criticism or crackdown. Our results have important implications for international NGOs facing increased antagonism by government abroad and point to possible methods of adapting to these new regulations alienating their newfound donor base.

# Private foreign aid

Substantial research on nonprofit studies has looked at the motivation of individual donors, including altruism, reputational benefits and alignments with personal values [@BilodeauSlivinski:1997; @Wiepking:2010; @BekkersWiepking:2011]. However, this research has overwhelmingly looked at individual donor behavior and motivation for giving to local—rather than international—causes. On the other hand, the systematic study of private foreign aid is still in its infancy—there is an absence of expansive and high quality data [@greenhill2013], and most research has been restricted to elite, high net-worth donors [@USTrust2014].

We argue that understanding funding decisions of private citizens is important for two main reasons. Examining the organizational-level factors in a group that make the average donor increase their charitable-giving towards these groups can help NGOs better target their programming towards these donors. It can also help organizations market their activities more saliently. More broadly, understanding motivations of private citizens can help organizations and governments better assess claims about the benefits of privatizing foreign aid. Previous research has argued that private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the grounds [@easterlywilliamson].

While recent research on private foreign aid has examined funding decisions of donor NGOs and foundations[^1], we know less about the funding choices of the individuals responsible for much of these private aid flows [@desaikharas]. While we do investigate the impact of individual-level factors on such private philanthropy targeted towards international causes in our larger project, in this paper we seek to understand the impact of organizational features of nongovernmental organizations and the structural factors in target countries in which they operate on donors’ decisions to engage in philanthropy.

[^1]: On aid from world's largest NGOs, see @koch2009, on private aid flows from NGOs based in the US, see @buthe2012.

## Organizational heuristics: The impact of NGO organizational decisions on individual philanthropy

Existing research has found that donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking out complete information about an organization's deservingness and efficiency is costly and time-consuming. One common signal for donors is organizational efficacy or the belief that an individual's donation will make a real difference. This can manifest itself through multiple mechanisms such as the amount an organization spends on overhead costs, whether an organization makes its finances public, or whether an organization participates in voluntary accountability practices, such as listing organizational details on websites like GuideStar and Charity Navigator.

Financial transparency, defined as the degree of completeness of information, provided by organizations to the public concerning its business activities is one such important organizational practice that can enhance donor trust and confidence in organizations [@Vacarro:2006; @vaccaromadsen]. Previous research has found that media exposés about charity mismanagement can generate negative reputational spillovers for the charitable sector [@gibelmangelman]. Therefore, being financially transparent and engaging in activities that further transparency can reduce actual or perceived information asymmetries between donors and charities, and increase donor perception of organizational efficacy.

> **H~1a~**:  If NGOs are financially transparent, then individual private donors will be more likely to donate to them.

In addition to financial transparency, researchers and organizations, especially those auditing accountability practices, argue that accountability is another factor that can impact donor willingness to donate. While transparency is an organization's willingness to make critical data about the organization public, accountability is the willingness of the organization to explain its action to shareholders.

Explaining actions to stakeholders can be important because many NGOs, even when well-intentioned, can devote excessive resources towards marketing and overheads [@bowman:2006]. Private donors, subsequently, may be more likely to dislike NGOs that spend a large share of their revenues for unproductive purposes [@rose1982], or rather, a large share of resources on administration, management and fundraising. As @Tremblay-BoirePrakash:2017 point out, while individuals would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead, donors do not necessarily have the time to research charities thoroughly. Based on a survey experiment, they find that membership in a voluntary program ultimately does not influence people's willingness to donate. Thus, while seeking out explanations about NGO actions can be important to individual donors, they do not necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks.

> **H~1b~**: If NGOs are accountable and hold regular third-party audits, then individual private donors will be more likely to donate to them.

Another heuristic for deservingness is the *issue area* an NGO engages in. Donors can have very different preferences regarding the nature of NGO activities that they would like to support [@AndreoniPayne:2003]. Organizations that address humanitarian issues such as relief and development have broader appeal to donors who might shy away from NGOs dealing with more political causes like human rights. Organizations focusing on the former may also be able to frame their activities as in need of greater support.

Perception of need, whether from personal experiences or acquired through media framing, can strongly influence the decisions of individuals to donate to relief efforts [@BekkersWiepking:2010, 6-8; @wiepkingleeuwen, 227-29]. This is especially the case when donors are faced with beneficiaries that fit the commonly accepted stereotypes of "victims" [@breezedean, 134]. Indeed, previous research has found that emergency funding, at least in the form of bilateral aid NGO, is more likely to be directed towards the senders of asylum-seekers and refugees [@czaikamayer; @bermeoleblang]. Therefore, donors may be more willing to donate to NGOs working on emergency response or relief focusing on victimized groups such as refugees or women and children in war.

On the other hand, donors may be less willing to support NGOs focusing on contentious issue areas or programs that are not compatible with host government preferences. While NGOs working on issues like health, education and humanitarian relief rarely challenge the government [@Bush:2015; @Kiai:2017], those working on more contentious areas such as human rights, environmental advocacy, or election monitoring can pose political and economic challenges to regimes [@Chaudhry:2016]. These organizations are often viewed as politically motivated outsiders and run a higher risk of getting expelled [@DPR2015], increasing the possibility of wasting donor resources. Further, unlike the former causes, their programmatic output is harder to measure and quantify, which is another factor that is important to donors [@Bush:2015].

>**H~2~**: If NGOs work in less contentious issue areas (emergency response and refugee relief), then individual private donors will be more likely to donate to them over more contentious issue areas (environment and human rights).

The *source of NGO funding* can also influence donor behavior. Government grants to NGOs can often crowd out private funding [@AndreoniPayne:2003]. Donors are less likely to contribute to NGOs that rely heavily on government grants since their donation might feel more impersonal and less needed, while donors are more likely to give to organizations that rely primarily on private donations given that they may feel personally invested in the organization and perceive their contribution mattering. Government grants may also imply lack of independence from government which can reduce the efficiency of an organization [@Stroup:2012].

>**H~3~**: If NGOs are funded primarily by numerous small private donors, then individual private donors will be more likely to donate to them compared to NGOs that are funded by a handful of wealthy private donors and government grants.

Each of these signals is *organizational*. NGOs typically have direct control over their organizational practices, mission and issue area, and funding sources. We theorize that organizational characteristics like managerial practices, issue area, and funding sources all influence the decision to donate to an NGO (see @fig:big-dag). At the same time, however, we propose that structural characteristics like an NGO's host-country political and legal environment can also serve as donor heuristics.

## Structural heuristics: The impact of anti-NGO crackdowns on individual philanthropy

NGOs have less control over *structural* issues, and the role of political and legal institutions in donor decision making has been understudied. However, over the past decade international NGOs have become increasingly politicized and legally restricted around the world. NGO registration is not inherently restrictive, as governments frequently use regulations to streamline NGO-state relationships. Restrictive NGO laws, on the other hand, are designed to limit organizational programming by imposing barriers to entry, funding, and advocacy. These anti-NGO laws may signal to donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and crack down on them. Therefore, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization.

>**H~4~**: If NGOs face legal crackdowns abroad, then individual donors will be more likely to donate to them.

## Examining the joint impact of organizational and structural factors

```
![Causal diagram showing causes of donor behavior. D = donation to NGO (outcome); G = NGO-government relationship, I = NGO issue area, F = NGO funding source, O = NGO organizational and managerial practices.](output/figures/causal-path.pdf){#fig:big-dag}
```

Identifying the causal link between structural factors and donor behavior is more difficult than measuring the link between organizational factors and donor behavior, however, because (1) NGOs have less direct control over their political environments, and (2) organizational characteristics like issue area and funding can sour the NGO-government relationship (as we explain in further detail below, governments are more likely to crack down on NGOs that address human rights and that receive government funding). @fig:big-dag helps disentangle this complex relationship. Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**). Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both funding and issue area. As such, legal crackdowns do not occur in isolation. Countries are more likely to repress NGOs when organizational missions are in tension with government preferences and when organizations receive substantial funding from abroad [@DPR2015]. Therefore, the same organizational characteristic that can increase the likelihood of crackdown can also simultaneously serve as a donor heuristic and influence perceptions of NGO deservingness.

Donors therefore may show increased willingness to donate to NGOs facing government crackdown/criticism working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights). Those working on contentious issues may be expelled or shut down, which would waste donor resources and make it less likely that they donate to these organizations. Similarly, the combination of legal crackdown and funding may reshape donor perceptions of deservingness. Private donors may be more likely to punish government-funded NGOs that face restrictions. This is because legal trouble with the group's main funder could fuel private donor mistrust.

Finally, the combination of financial transparency and government crackdown may increase donor willingness to support besieged NGOs. While concerns about NGO mismanagement and lack of financial transparency may signal concerns about an NGO's operations and its ability to abide by the host country's regulatory environment, the presence of such transparency may instead convince donors that government targeting of NGOs may be ill-intentioned rather than simply a manifestation of financial oversight. Donors may view NGO legislation as a sign of governments looking to crack down on groups that seek to keep governments accountable, rather than merely auditing and punishing groups that violate routine regulations.

> **H~5a~**: Donors will show increased willingness to donate to NGOs facing government crackdown/criticism working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights).
>
> **H~5b~**: Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors.
>
>**H~5c~**: Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors and work in less contentious areas (emergency response and refugee relief).
>
>**H~5d~**: Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors.

# Methods

## Conjoint analysis

It is possible to study the effects of both organizational and structural heuristics on donor decision making individually, but disentangling the interaction of the two heuristics from individual donor characteristics adds complex dimensionality and makes more standard experimental work difficult, costly, and statistically fraught. To address this, we use conjoint analysis to simultaneously test individual donor preferences in the face of both organizational and structural heuristics. Conjoint analysis is a staple in marketing research for evaluating which product attributes are most important to consumers. It has been extensively used in new product development and product line optimization. Conjoint analysis is generally applicable whenever individuals face complex, multi-dimensional tradeoffs that make it difficult (or even impossible) to explicitly elicit preferences. In the context of this project, we use conjoint techniques to evaluate donor rather than consumer preferences as they choose NGOs which to donate to based on both organizational and structural heuristics.

Conjoint analysis has been widely used within social sciences to explain causality and has recently begun to be used in political and public policy fields. @Helfer:2016 and @Mummolo:2016 both used conjoint analysis to assess perceptions of political communications. @KnudsenJohannesson:2019 argue that political communication research requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility. Because we also want to capture the complexity of a respondent's judgment of which NGO they should donate to, if any, we saw potential to expand the application of conjoint analysis within public policy.

## Sample

After collecting baseline information on respondent demographics and attitudes toward charity and voluntarism, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.^[See the appendix for a copy of the survey.] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross. We then displayed various combinations of features, including one of four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), one of two organizational practices (financial transparency and third-party accountability audits), one of three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and one of three relationships with host governments (friendly, criticized by the government, and under government crackdown). We presented twelve sets of four hypothetical combinations of organizational features, and because our partial fractional factorial design resulted in 288 (4 × 4 × 2 × 3 × 3) possible combinations of organizations and features, no single respondent was offered every combination.

Survey participants were recruited through Centiment, a commercial online provider of high quality non-probability opt-in survey panels. Centiment ensures panel quality by actively recruiting representative samples of the US population and provides monetary incentives and rewards to participants. To see how varying NGO characteristics influence the decision to donate, our sample was representative of the population of people who are likely to donate to charity. We asked potential participants a screening question early in the survey ("Q2.5: How often do you donate to charity?"). If a participant responded that they give once every few years or never, they were disqualified from the study. We received 1,016 viable responses, which is a sufficient size for model estimation. A sample size of at least 500 respondents is typical for estimating a hierarchical Bayesian model based on conjoint data. We doubled this amount because we are interested in analyzing subpopulations of respondents, which requires a larger sample.

```
output/tables/tbl-sample-details.md
```

@tbl:sample-details provides a detailed breakdown of the individual characteristics of our sample. In general, respondents were well balanced across genders and tended to be older than the national median age of 36—less than 20% of respondents were under 36 years old. The majority of respondents (45%) had never been married, while nearly 40% were married, with 10% divorced. A quarter of the sample had a high school degree, with the remainder attending some level of college or university. The majority (58%) earned less than the national median income (\$61,372).

Since we limited the sample to people who frequently donate to charities, most respondents have a favorable opinion of nonprofits and charities, with more than half reporting a 5 or greater (on a 7-point scale) of trust in charities. Nearly 90% of respondents indicated that it is important to trust charities, rating importance of trust at least a 3 on a 7-point scale. The majority of respondents volunteer at least once a year, donate to charity at least once a year, and give between \$1–\$999 annually. Most rarely attend church, but feel that religion is important. Respondents are also engaged civically (three quarters voted in the last election) and follow national news closely (70% follow the news daily). Respondents are fairly balanced ideologically, with the majority reporting a 3, 4, or 5 on a 7-point scale of liberal–conservative political ideology.

## Modeling

We analyze the effect of the various combinations of organizational features and donor characteristics with the following hierarchical Bayesian multinomial logit model:

$$
\begin{aligned}
\beta &\sim \operatorname{Multivariate} \mathcal{N}(Z \Gamma, \xi) \\
y &\sim \operatorname{Multinomial\ logit}(X \beta, \varepsilon)
\end{aligned}
$$

where $y$ = which alternative the respondent chooses to donate to, $X$ = design matrix of attribute levels (i.e. organizations, issue areas, organizational practices, funding sources, and government relations), $\beta$ = latent individual preferences for the attribute levels, $Z$ = matrix of individual-level covariates (i.e. demographics, political knowledge, attitudes towards charity, etc.), $\Gamma$ = matrix of coefficients mapping individual-level covariates onto the latent individual-level preferences, and $\varepsilon$ and $\xi$ = errors. Simply put, the first level of the model predicts individual donor preferences for various combinations of features (e.g. the combination of human rights issues, financial transparency, government funding, and government crackdown), while the second level of the model uses these fitted preferences to predict the ultimate choice of donation.

We use median values from the posterior distributions of the model as point estimates and calculate credible intervals using the 95% highest posterior density. We report the results primarily through density plots that show both the posterior distributions and 95% credible intervals. Inference based on Bayesian analysis differs from more common frequentist null hypothesis testing—as such, we declare an effect statistically significant if the posterior probability of being different from zero (or from other comparison values) exceeds 0.95.

# Results

## Effect of organizational and structural features on the likelihood of selection

We hypothesized that the interaction of structural, organizational, and individual donor characteristics would have varying significant effects on donor behavior, and our results bear this out. @fig:probs-org shows the baseline probabilities of selecting an organization to donate to based on organization. Even without varying issue area, organizational practices, funding sources, and government relationships, respondents were most likely to donate to the Red Cross, with an 86% probability of being selected when given the choice. Oxfam had the lowest probability of being selected (65%), likely because it has less name recognition in the United States. Amnesty International and Greenpeace were slightly more probable (69% and 72%, respectively).

```
![Baseline probability of selecting an organization for donation](output/figures/probs-org.pdf){#fig:probs-org}
```

@fig:first-hypotheses presents the results for our first four hypotheses, which deal with the effect of organizational and structural factors on individual decisions to donate. The main coefficient parameter $\theta$ is shown as an odds ratio ($e^\theta$) to demonstrate changes in likelihood. Each conjoint feature omits one level as the base case.

```
![Changes in the likelihood of selecting an organization for donation across different levels within conjoint features. Values shown as odds ratios; red line at 1 shows point of no change in likelihood](output/figures/results-h1-4.pdf){#fig:first-hypotheses}
```

In our first set of hypotheses, we predicted that donors would be more likely to donate to organizations that engage in organizational practices that highlight transparency and accountability. As seen in the top left panel of @fig:first-hypotheses, donors were roughly three times more likely to select an organization that either voluntarily undergoes external audits for the sake of accountability or voluntarily discloses financial details. There is no significant difference between these two practices. Based on this evidence, donors rely heavily on heuristics of managerial best practices and reward INGOs for being transparent and accountable.

According to our second hypothesis, donors should be more likely to donate to organizations working on less contentious issues like emergency response and refugee relief. A heuristic of deservingness should drive donor decisions, with donors leaning more towards causes that alleviate human suffering. The results from the experiment provide mixed results for this hypothesis. As seen in the top right panel of @fig:first-hypotheses, an emergency response frame has the most positive influence on donor decisions—since it is the reference group, all other issues decrease the likelihood of donation. Interestingly, human rights advocacy is the next most influential issue—respondents were 15% less likely to donate (compared to emergency response) when presented with human rights issues. Respondents are 36% less likely to donate when presented with an organization working on environmental issues, and a surprising 44% less likely when shown an organization working on refugee relief. There is no significant difference between refugee relief and environmental issues; both are significantly different from human rights, and human rights is significantly different from 1. While the preeminence of refugee relief follows our hypothesis, the other issues diverge markedly from our expectations. Human rights and environmental issues do decrease the likelihood of donation compared to emergency relief, as expected, but refugee issues see the most negative change in likelihood, contrary to the idea that tamer NGOs working on issues of human suffering will receive more attention from donors.

The bottom left panel of @fig:first-hypotheses shows the results for our third hypothesis that an NGO's funding sources matter for donors. We posited that donors use the fact that an INGO receives many small donations as a heuristic of deservingness, providing individual donors with a greater chance that their money will have a positive impact on an NGO's programs. Our results confirm this: compared to the reference level of an INGO that receives many small donations, donors are 22% less likely to donate to an organization that receives its funding primarily from government donors, and 31% less likely to donate to one that receives the bulk of its funding from a handful of wealthy donors. There is no significant difference between the change in likelihood across government grants and wealthy donors, but both are significantly different from 1.

These first three hypotheses all deal with organizational heuristics, or practices and attributes that an NGO has more direct control over. INGOs have less control over structural factors, such as the political environments of their host countries, but donors will likely still use these factors as signals of deservingness. The bottom right panel of @fig:first-hypotheses demonstrates that donors likely punish organizations that fall afoul of their host countries. Compared to an INGO with a friendly relationship with its host government, donors are 49% less likely to choose to donate to an organization that is criticized by its host government, and a sizable 64% less likely if the organization is under government crackdown (there is a significant difference between criticized by government and under government crackdown, and both are significantly different from 1). Contrary to expectations, donors appear to punish INGOs that face legal difficulties abroad.

## Interaction between organizational and structural features and individual characteristics

In our final set of hypotheses, we are interested in how individual-level donor characteristics interact with structural and organizational heuristics. In particular, we are interested in finding which kinds of donors are more or less likely to consider an INGO's managerial practices, issue area, funding sources, and host country politics when deciding to donate.

**NOTE**: This section is still in progress—disentangling all the effects here is complex, which is good! Looking at the different interactions between conjoint features and attributes and individual-level covariates is one of the most powerful contributions of conjoint analysis, but isolating the most important effects (given that there are nearly 300 different combinations of just the organizational attributes, which then combine with dozens of possible covariate combinations), is difficult. We're still working on finding the best way to communicate this complexity graphically.

In the meantime, @fig:second-level shows one attempt at this, displaying a heatmap of the significance of individual-level characteristics in the second level of a model that uses covariates related to attitudes toward charity and voluntarism. We find that personal experiences with and attitudes toward charity influence have heterogenous effects on the salience of different organizational and structural characteristics. For instance, believing that it is important to trust charities makes individuals less likely that government grants and rich donors play a role in the decision to donate, perhaps due to the perception that an organization receiving many small donations (the reference level) is more trustworthy. Similarly, the importance of trusting charities makes it more likely that accountability and transparency will influence the decision to donate. Notably, few of the covariates related to charity and voluntarism interact with structural attributes in any consistent way, other than personal involvement in activism—those with a history of activism are more likely to select an organization that is either facing government criticism or government crackdown.

```
![Heatmap showing significance of various covariates across conjoint attributes and levels](output/figures/q2-heatmap.pdf){#fig:second-level}
```

# Discussion and conclusion

In general we find support for our hypotheses. With the turn towards private philanthropy in the face of the global crackdown on civil society, INGOs need to be aware of the dynamics of individual donor preferences and how those preferences interact with their managerial and organizational decision. Additionally, structural factors like political trends in INGO host countries influence donor decision-making. In aggregate, donors are less likely to give to organizations that face government criticism and crackdown, which could be a worrying sign for INGOs working on contentious issues that are more likely to elicit negative government responses. However, for the subgroup of respondents with personal involvement in advocacy, government crackdown serves as a positive heuristic instead, likely because those involved in advocacy understand how the relationship between governments and charities can be fraught.

### 2023-09-09 notebook/manuscript.qmd
Add manuscript infrastructure

@@
 ---
-title: "Manuscript"
+title: Manuscript
+toc: false
+page-layout: full
 ---
 
-Manuscript iframe stuff goes here.
+```{r include=FALSE}
+# Add the manuscript target as a dependency to the overall website
+# targets::tar_load(c(manuscript_nice, manuscript_manuscripty))
+```
+
+```{=html}
+<p class="text-center">
+  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/manuscript.html" target="manuscript">
+  <iconify-icon inline="" icon="fa6-solid:file-lines"></iconify-icon> &ensp;HTML
+  </a>
+
+  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/manuscript.html" target="_blank">
+  <iconify-icon inline="" icon="fa6-solid:arrow-up-right-from-square"></iconify-icon> &ensp;HTML <small>(new window)</small>
+  </a>
+
+  <a class="btn btn-danger btn-sm mb-1" href="/manuscript/output/manuscript.pdf" target="manuscript">
+  <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;PDF
+  </a>
+
+  <a class="btn btn-danger btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript.pdf">
+  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;PDF <small>(download)</small>
+  </a>
+
+  <a class="btn btn-warning btn-sm mb-1" href="/manuscript/output-ms/manuscript-ms.pdf" target="manuscript">
+  <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;Manuscripty PDF
+  </a>
+
+  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output-ms/manuscript-ms.pdf">
+  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;Manuscripty PDF <small>(download)</small>
+  </a>
+</p>
+
+<iframe src="/manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:90%;width:100%;border:2px solid #ccc;" height="90%" width="100%" name="manuscript"></iframe>
+```

### 2023-09-09 notebook/results-funding.qmd
Use Libre Franklin

@@
       text_x = list(element_text(
-        family = "Clear Sans",
+        family = "Libre Franklin",
         face = "bold"

### 2023-09-09 notebook/style-guide.qmd
Use Libre Franklin

@@
 ```{scss echo=FALSE}
-@import url('https://fonts.googleapis.com/css2?family=Inter&display=swap');
+@import url('https://fonts.googleapis.com/css2?family=Libre+Franklin&display=swap');
 
@@
 
-.inter {
-  font-family: "Inter";
+.libre-franklin {
+  font-family: "Libre Franklin";
 }
@@
 
-We use [Inter](https://rsms.me/inter/) (accessible for free from [Google Fonts](https://fonts.google.com/specimen/Inter)) as the main font in all our plots.
+We use [Libre Franklin](https://github.com/impallari/Libre-Franklin) (accessible for free from [Google Fonts](https://fonts.google.com/specimen/Libre+Franklin)) as the main font in all our plots.
 
-::: {.font-example .inter}
-**Inter**
+::: {.font-example .libre-franklin}
+**Libre Franklin**
 

### 2023-09-09 R/funs_graphics.R

@@ -8,19 +8,19 @@ clrs <- list(
 
 # Theme stuff
 theme_ngo <- function() {
-  theme_minimal(base_family = "Clear Sans") +
+  theme_minimal(base_family = "Libre Franklin") +
     theme(panel.grid.minor = element_blank(),
-      plot.title = element_text(family = "Clear Sans", face = "bold"),
+      plot.title = element_text(family = "Libre Franklin", face = "bold"),
       axis.title.x = element_text(hjust = 0),
       axis.title.y = element_text(hjust = 1),
-      strip.text = element_text(family = "Clear Sans", face = "bold",
+      strip.text = element_text(family = "Libre Franklin", face = "bold",
         size = rel(0.75), hjust = 0),
       strip.background = element_rect(fill = "grey90", color = NA))
 }
 
 set_annotation_fonts <- function() {
-  ggplot2::update_geom_defaults("label", list(family = "Clear Sans", face = "plain"))
-  ggplot2::update_geom_defaults("text", list(family = "Clear Sans", face = "plain"))
+  ggplot2::update_geom_defaults("label", list(family = "Libre Franklin", face = "plain"))
+  ggplot2::update_geom_defaults("text", list(family = "Libre Franklin", face = "plain"))
 }
 
 

### 2023-09-09 R/funs_plots.R
Slightly wider bins

@@ -17,7 +17,7 @@ plot_trank <- function(model, params) {
     group_by(.variable) %>% 
     mutate(draw_rank = rank(.value)) %>% 
     ggplot(aes(x = draw_rank, color = factor(.chain))) +
-    stat_bin(geom = "step", binwidth = 400, position = position_identity(), boundary = 0) +
+    stat_bin(geom = "step", binwidth = 500, position = position_identity(), boundary = 0) +
     scale_color_viridis_d(option = "rocket", end = 0.85) +
     labs(color = "Chain") +
     facet_wrap(vars(.variable), scales = "free_y") +

### 2023-09-09 sandbox.R
Remove sandbox

@@ -1,811 +1,0 @@
-library(tidyverse)
-library(here)
-
-data <- read_csv(
-  here::here("data", "raw_data", "conjointqsf_final.csv"),
-  guess_max = 1500
-)
-
-data_clean <- data %>%
-  filter(V10 == 1) %>%         # Keep respondents who completed the entire survey
-  filter(Q1.1 == 1) %>%        # Keep respondents who gave consent
-  filter(Q2.5 %in% c(1:5)) %>% # Keep respondents who passed the screener
-  filter(Q2.11 == 3)           # Keep respondents who passed the attention check
-
-data_clean %>%
-  select(Q4.1:Q4.12) %>%
-  gather(key = "task", value = "choice") %>%
-  count(choice)
-
-design_orig <- read_csv(here("data", "derived_data", "design.csv")) %>% 
-  rename(
-    version = question_set,
-    task = question,
-    alt = choice
-  ) %>% 
-  gather(key = "atts", value = "levels", -c(version:alt))
-
-design_surv <- data_clean %>% 
-  select(contains("CBCONJOINT"), -revision_CBCONJOINT) %>% 
-  gather(key = "temp", value = "level_names", -vers_CBCONJOINT) %>% 
-  separate(temp, into = c("atts", "task", "alt"), sep = "\\.") %>% 
-  separate(alt, into = c("alt", "temp")) %>% 
-  select(vers_CBCONJOINT, task, alt, atts, level_names) %>% 
-  rename(version = vers_CBCONJOINT) %>% 
-  mutate(
-    task = as.numeric(task),
-    alt = as.numeric(alt),
-    atts = recode(
-      atts,
-      "732d72a6-25a3-4194-8416-461acae30837" = "Organization",
-      "bd54b90a-efb3-4ac8-b65a-1ebeefcaf703" = "Issue area",
-      "a6836e28-fd7a-4b71-b65e-f6269e5c883f" = "Financial transparency",
-      "c2249c1a-11fa-4395-a0a3-61d9648a2e55" = "Accountability",
-      "db44c406-390e-4fc4-875b-65796aa95ffa" = "Funding sources",
-      "85f14c50-61cc-461c-8e77-19453b83d76d" = "Relationship with host government"
-    )
-  ) %>%
-  distinct() %>% 
-  arrange(version, task, alt) %>% 
-  pivot_wider(names_from = atts, values_from = level_names)
-
-design_surv %>% 
[…]

### 2023-09-09 _targets.R
targets-ify manuscript, website, and readme

@@ -86,21 +86,20 @@ list(
 
   ## Helper objects like lookup tables
   tar_target(level_lookup, make_level_lookup(grid_treatment_only)),
-  tar_target(feature_lookup, make_feature_lookup())
+  tar_target(feature_lookup, make_feature_lookup()),
   
-  ## Analysis ----
-  # tar_target(summary_activities, make_activities_summary(survey_orgs)),
-  # tar_target(models_activities, make_activities_models(summary_activities))#,
-  # 
-  # Manuscript and analysis notebook ----
-  # tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),
-  # tar_quarto(output_ms, path = "manuscript", quiet = FALSE, profile = "ms"),
-  # tar_quarto(website, path = ".", quiet = FALSE),
-  # tar_target(deploy_script, here_rel("deploy.sh"), format = "file"),
-  # tar_target(deploy, {
-  #   # Force a dependency
-  #   website
-  #   # Run the deploy script
-  #   if (Sys.getenv("UPLOAD_WEBSITES") == "TRUE") processx::run(paste0("./", deploy_script))
-  # })
+  ## Manuscript and notebook ----
+  tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),
+  tar_quarto(output_ms, path = "manuscript", quiet = FALSE, profile = "ms"),
+  tar_quarto(website, path = ".", quiet = FALSE),
+  tar_target(deploy_script, here_rel("deploy.sh"), format = "file"),
+  tar_target(deploy, {
+    # Force a dependency
+    website
+    # Run the deploy script
+    if (Sys.getenv("UPLOAD_WEBSITES") == "TRUE") processx::run(paste0("./", deploy_script))
+  }),
+  
+  ## Render the README ----
+  tar_quarto(readme, here_rel("README.qmd"))
 )

### 2023-09-09 _dependencies.R
renv-ification

@@ -1,0 +1,6 @@
+# Things that need to be installed but didn't get installed automatically as 
+# dependencies for whatever reason
+library(quarto)
+library(collapse)
+library(cmdstanr)
+library(yaml)

### 2023-09-09 _targets.R

@@ -29,7 +29,7 @@ options(
 set.seed(265927) # From random.org
 
 tar_option_set(
-  packages = c("tidyverse", "Matrix"),
+  packages = c("tidyverse"),
   format = "qs"
 )
 

### 2023-09-10 notebook/model-definitions.qmd
Add empty model definitions page

---
title: "Model definitions"
---

TODO: Formal math for the models

### 2023-09-12 notebook/marginal-means.qmd
Explain/illustrate marginal means as coefs

---
title: "Why marginal means"
format:
  html:
    code-fold: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "80%", collapse = TRUE,
  dev = "ragg_png"
)

options(
  digits = 3, width = 120,
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)
```

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(gt)
library(gtExtras)

tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

preds_all <- tar_read(preds_conditional_treatment_only)
conjoint_model <- tar_read(m_treatment_only)

invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))

theme_set(theme_ngo())
```

To find the causal effects defined in each of our estimands, we calculate estimated marginal means (EMMs) by finding the fitted values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (4 organizations × 4 issues × 2 transparency × 2 accountability × 3 funding × 3 government relationship = 576 rows). We transform these estimates to the probability scale in order to work directly with predicted probabilities rather than the link (logit) scale. We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.

This is a little more complicated than just looking at the model coefficients, but it is a valid way of thinking about marginal contrasts and it is a common approach in fields like epidemiology, and the complex multinomial models we're using require it.

## Marginal means, differences in marginal means, marginal effects, and regression coefficients

At its core, a "marginal mean" refers to the literal mean in the margins in a contingency table of model predictions. To illustrate, we'll make a model that predicts penguin weight based on species and sex and then make predictions for a balanced grid of covariates (i.e. male Adelie, female Adelie, male Chinstrap, female Chinstrap, male Gentoo, female Gentoo):

```{r make example model}
#| code-fold: show
library(marginaleffects)
library(palmerpenguins)
penguins <- penguins %>% drop_na(sex)

model <- lm(body_mass_g ~ species + sex, data = penguins)

preds <- model %>% 
  predictions(datagrid(species = unique, sex = unique))
```

```{r basic-contingency-table}
preds %>% 
  select(estimate, species, sex) %>% 
  pivot_wider(names_from = sex, values_from = estimate) %>% 
  ungroup() %>% 
  gt() %>% 
  cols_label(female = "Female", male = "Male", species = "Species") %>% 
  cols_align(align = "center", columns = c(female, male)) %>% 
  cols_align(align = "left", columns = species) %>% 
  tab_spanner(label = "Sex", columns = c(female, male)) %>% 
  tab_source_note(source_note = md("Predicted penguin weights (g) from model `lm(body_mass_g ~ species + sex)`")) %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

We can add a column and row in the margins to show the species-specific and sex-specific average predicted weights. For the sex-specific averages, all the between-species variation is "marginalized out" or accounted for. For the species-specific averages, all the between-sex variation is similarly marginalized out:

```{r fancy-mm-contingency-table}
mean_species <- preds %>% 
  group_by(species) %>% 
  summarize(avg_estimate = mean(estimate))

mean_sex <- preds %>% 
  group_by(sex) %>% 
  mutate(avg_estimate = mean(estimate)) %>% 
  select(species, sex, estimate, avg_estimate) %>% 
  pivot_wider(names_from = species, values_from = estimate) %>% 
  mutate(avg_explanation = glue::glue(
    "{round(avg_estimate, 0)}<br><span style='font-size:70%'>({round(Adelie, 0)} + {round(Chinstrap, 0)} + {round(Gentoo, 0)}) / 3</span>"
  )) %>% 
  select(sex, avg_explanation) %>% 
  mutate(species = "**Marginal mean**") %>% 
  pivot_wider(names_from = sex, values_from = avg_explanation)

preds %>% 
  ungroup() %>% 
  select(estimate, species, sex) %>% 
  pivot_wider(names_from = sex, values_from = estimate) %>% 
  left_join(mean_species, by = join_by(species)) %>% 
  arrange(species) %>% 
  mutate(avg_explanation = glue::glue(
    "{round(avg_estimate, 0)}<br><span style='font-size:70%'>({round(female, 0)} + {round(male, 0)}) / 2</span>"
  )) %>% 
  mutate(across(c(female, male), ~as.character(round(., 0)))) %>% 
  select(-avg_estimate) %>% 
  bind_rows(mean_sex) %>% 
  gt() %>% 
  sub_missing(columns = everything(), missing_text = "") %>% 
  fmt_markdown(columns = everything()) %>% 
  cols_label(
    female = "Female", male = "Male", 
    species = "Species", avg_explanation = "Marginal mean"
  ) %>% 
  cols_align(align = "center", columns = c(female, male, avg_explanation)) %>% 
  cols_align(align = "left", columns = species) %>% 
  tab_spanner(label = "Sex", columns = c(female, male)) %>% 
  gt_add_divider(columns = avg_explanation, style = "dashed", weight = px(1), sides = "left") %>% 
  tab_style(
    style = cell_borders(sides = "top", style = "dashed", weight = px(1)),
    locations = cells_body(rows = 4)
  ) %>% 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>% 
  tab_source_note(source_note = md("Predicted penguin weights (g) from model `lm(body_mass_g ~ species + sex)`")) %>% 
  opt_horizontal_padding(3) %>% 
  opts_theme()
```

```{r extract-sex-means, include=FALSE}
mean_sex_small <- preds %>% 
  group_by(sex) %>% 
  summarize(avg_estimate = mean(estimate)) %>% 
  split(~sex)
```

Because regression is just fancy averages, the differences in marginal means here are actually identical to the coefficients in regression model. For instance, here are the results from the model:

```{r show-model-results}
#| code-fold: show
model %>% broom::tidy()
```

The `sexmale` coefficient of `r round(filter(broom::tidy(model), term == "sexmale")$estimate, 2)` represents the effect of moving from male to female when species is held constant.

The marginal means table shows the same thing. Marginalizing over species (i.e. holding species constant), the average predicted weight for female penguins is `r round(mean_sex_small$female$avg_estimate, 1)` and for male penguins is `r round(mean_sex_small$male$avg_estimate, 1)`. The difference in those marginal means is `r round(mean_sex_small$male$avg_estimate - mean_sex_small$female$avg_estimate, 2)`—identical to the `sexmale` coefficient!

**Differences in marginal means are equivalent to marginal effects or regression coefficients.**

## AMCEs from multinomial models

The idea that differences in marginal means can be the same as marginal effects/regression coefficients is crucial for calculating average marginal component effects (AMCEs) with our multinomial conjoint model. With multinomial regression, we actually get three sets of coefficients: one set per conjoint option. Each coefficient shows the shift in probability that someone will choose an organization from column 1, column 2, or column 3, so we get a coefficient for each of those outcomes (or µ1, µ2, and µ3). For instance, here are the posterior median coefficients from our main model for just the funding feature. There are two coefficients (wealthy donors and government grants), but repeated three times (for `mu1`, `mu2`, and `mu3`):

```{r show-funding-mus}
#| code-fold: show
conjoint_model %>% 
  gather_draws(`^b_mu\\d_feat_funding.*`, regex = TRUE) %>% 
  group_by(.variable) %>% 
  median_qi(.value)
```

Under experimental conditions where cells in the contingency table are randomly assigned, it's safe to assume that the cell proportions are equal and then marginalize (i.e. find the average) across the rows or columns. That means we can safely and legally take the average of each set of three coefficients to create a single value per term, like so:

```{r show-funding-mus-collapsed}
#| code-fold: show
conjoint_model %>% 
  gather_draws(`^b_mu\\d_feat_funding.*`, regex = TRUE) %>% 
  mutate(.variable = str_remove(.variable, "_mu\\d")) %>% 
  group_by(.variable) %>% 
  median_qi(.value)
```

However, these values are on an uninterpretable log odds scale scale and to unlogit them and backtransform them to the probability scale, we need to do all sorts of fancy math involving the intercept terms and omitted levels. That's tricky and I don't know how to do it.

So instead, we can take advantage of the fact that regression coefficients are also differences in marginal means. We can create a complete balanced grid of all 576 combinations of feature levels (4 organizations × 4 issues × 2 transparency × 2 accountability × 3 funding × 3 government relationship = 576 rows), calculate predicted probabilities for each row, and then

Here's what the full grid of 576 options looks like, with posterior median predictions for each combination. Because of the magic of {brms}, these predictions automatically incorporate information from the `mu1`, `mu2`, and `mu3` versions of the coefficients.

```{r show-full-grid-preds}
#| column: screen
preds_all %>% 
  group_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>% 
  summarize(avg = mean(.epred)) %>% 
  ungroup() %>% 
  gt() %>% 
  cols_align(align = "left") %>% 
  cols_label(
    feat_org = "Organization",
    feat_issue = "Issue",
    feat_transp = "Transparency",
    feat_acc = "Accountability",
    feat_funding = "Funding",
    feat_govt = "Relationship",
    avg = "Median probability"
  ) %>% 
  opts_theme() %>% 
  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, use_filters = TRUE)
```

\

If we want the AMCE of one of the features, like funding, we can calculate the marginal means by grouping by `feat_funding` and finding the average across each MCMC draw within each type of funding.

```{r calc-mms-funding}
#| code-fold: show
mms_funding <- preds_all %>% 
  group_by(feat_funding, .draw) %>% 
  summarize(avg = mean(.epred))
mms_funding
```

We can then use `compare_levels()` to find the difference in marginal means, which, as we saw with the penguins example, is the equivalent of looking at a regression coefficient where all other variables in the contingency table (i.e. organization, transparency, accountability, and government relations) are held constant. This gives us the average marginal component effect for funding *on the probability scale*:

```{r show-amces-funding}
#| code-fold: show
amces_funding <- mms_funding %>% 
  group_by(feat_funding) %>% 
  compare_levels(variable = avg, by = feat_funding, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feat_funding,
    delim = " - ", 
    names = c("feature_level", "reference_level")
  ) %>% 
  add_row(avg = 0, feature_level = unique(.$reference_level))

amces_funding %>% 
  group_by(feature_level) %>% 
  median_qi(avg)

amces_funding %>% 
  mutate(feature_level = fct_rev(fct_inorder(feature_level))) %>% 
  ggplot(aes(x = avg, y = feature_level)) +
  stat_halfeye() +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = scales::label_wrap(30)) +
  labs(x = "AMCE", y = NULL)
```

## AMCEs with covariates

By relying on marginal means, we can also incorporate information about individual-level covariates by creating larger reference grids. For instance, if we want to know how the AMCE for funding varies across different levels of respondent education, we can repeat the 576-row reference grid for each level of education, then group and summarize across funding and education. See [the AMCEs section in part 3 of this blog post](https://www.andrewheiss.com/blog/2023/08/12/conjoint-multilevel-multinomial-guide/#amces-2) for more about that.

### 2023-09-12 notebook/marginal-means.qmd
Fix wording

@@
 
-To find the causal effects defined in each of our estimands, we calculate estimated marginal means (EMMs) by finding the fitted values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (4 organizations × 4 issues × 2 transparency × 2 accountability × 3 funding × 3 government relationship = 576 rows).
-We transform these estimates to the probability scale in order to work directly with predicted probabilities rather than the link (logit) scale.
+To find the causal effects defined in each of our estimands, we calculate estimated marginal means (EMMs) by finding the fitted probability-scale values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (4 organizations × 4 issues × 2 transparency × 2 accountability × 3 funding × 3 government relationship = 576 rows).
 We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.

### 2023-09-12 R/funs_graphics.R
Better axis title formatting

@@ -11,8 +11,14 @@ theme_ngo <- function() {
   theme_minimal(base_family = "Libre Franklin") +
     theme(panel.grid.minor = element_blank(),
       plot.title = element_text(family = "Libre Franklin", face = "bold"),
-      axis.title.x = element_text(hjust = 0),
-      axis.title.y = element_text(hjust = 1),
+      axis.title.x = element_text(
+        family = "Libre Franklin SemiBold", face = "plain",
+        hjust = 0, size = rel(0.9), 
+        margin = margin(t = 10)),
+      axis.title.y = element_text(
+        family = "Libre Franklin SemiBold", face = "plain",
+        hjust = 1, size = rel(0.9), 
+        margin = margin(r = 10)),
       strip.text = element_text(family = "Libre Franklin", face = "bold",
         size = rel(0.75), hjust = 0),
       strip.background = element_rect(fill = "grey90", color = NA))

### 2023-10-26 manuscript/manuscript.qmd
targets-ify manuscript, website, and readme
Suparna mega edits/updates

@@
 abstract: |
-  As space for civil society has closed around the world, transnational NGOs have faced a crisis of funding.
-We explore how NGOs have shifted from traditionally Northern funding sources toward grassroots private philanthropic money.
-How do individual donors in the US feel about donating to legally besieged NGOs abroad?
-Do legal restrictions on NGOs influence donors’ decision to donate?
-We use a conjoint survey experiment to argue that domestic political environments of NGO host countries influence preferences of private donors and that legal crackdowns on NGOs serve as a heuristic of organizational deservingness.
+  Prior research on nonprofit fundraising has primarily examined how financial transparency and organizational accountability influence individual donor behavior.
+Over the past two decades, however, an increasing number of host governments have cracked down on non-governmental organizations (NGOs).
+QUESTION.
+We test these questions by administering a series of conjoint experiments in the US that examine...We find....
+This suggests...
 keywords:
@@
 
-Over the last three decades, states have increasingly sought to crack down on civil society organizations.
-In Human Rights Watch's 2016 Annual Report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory.
-Policymakers have referred to this phenomenon as the "closing of civic space" and data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in nearly 60% of countries—111 in total [@CIVICUS:2017].
-These attacks—most of which have occurred through restrictive legislation targeted against nongovernmental organizations (NGOs)—have adversely affected the ability of both domestic and international NGOs to operate and raise funds.
-Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official aid donors channel fewer funds to contentious issues and instead choose to fund "tame" causes [@ChaudhryHeiss:2018; @Bush:2015].
+```{r libraries-data}
+library(tidyverse)
+library(targets)
 
+# Targets stuff
+tar_config_set(store = here::here('_targets'),
+               script = here::here('_targets.R'))
+
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+```
+
+Over the last three decades, governments globally have increasingly sought to crack down on NGOs (CITE).
+Repressive governments have repressed these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs.
+(CITE) Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" (CITE) and data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in nearly 60% of countries—111 in total (UPDATE FROM NEW CIVICUS DATA).
+These attacks—most of which have been implemented through anti-NGO laws—have adversely affected the ability of both domestic and international NGOs to operate and raise funds.
+Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official aid donors channel fewer funds to contentious issues and instead choose to fund "tame" causes [@ChaudhryHeiss:2018; @Bush:2015, HERROLD, SPRINGMAN].
 In response to this dramatic shift in the NGO funding landscape, international NGOs (INGOs) have increasingly turned to foreign individual donors to offset the loss of funding from government and foundation sources [@BanksHulmeEdwards:2015].
-The amount of this private foreign aid is not insignificant—from 2000–2010, private giving by U.S.
+
+The amount of private foreign aid is not insignificant—from 2000–2010, private giving by U.S.
 entities towards international causes doubled in real terms [@desaikharas, 505].
@@
 private philanthropy towards international NGOs amounted to \$22.06 billion [@givingusa:2017].
+Most notably, a large portion of this growth was driven by individuals making small-scale donations.
+In 2017, individuals gave US\$286.7 billion or approximately 70% of total giving to international affairs.
+This further increased to US\$427.71 billion in 2018, 85.7% of which was through individuals (Giving USA, 2019).
+This turn to private donors opens INGOs up to new dynamics in seeking out aid.
+Many organizations that had previously relied on governments and foundations had optimized their fundraising strategies for those donors, but now need to tailor their fundraising strategies to private individuals, who behave differently from governments and foundations.
 
-This turn to private donors opens INGOs up to new dynamics in seeking out aid.
-Many organizations that had previously relied on governments and foundations had optimized their fundraising strategies for those kinds of organizations, but now need to tailor their fundraising attempts to private individuals, who behave differently from governments and foundations.
-Individuals have different preferences and rely on signals of effectiveness that differ from the benchmarks that large donor agencies rely on, including ratios of administrative overhead spending, financial transparency, accountability, and efficiency.
-These signals are are organizational characteristics that INGOs have direct control over.
-However, the political environment in the countries INGOs work in—including the global crackdown on civil society that is causing many organizations to seek out private funding in the first place—is a structural factor that INGOs can rarely influence on their own.
+Individuals have different preferences and rely on signals of effectiveness that differ from the benchmarks that large donor agencies rely on, including financial transparency and accountability.
+While INGOs have control over these organizational-level factors that motivate donations, the political environment in the host countries INGOs work in—including the global crackdown on civil society that is causing many organizations to seek out private funding in the first place—is a structural factor that INGOs can rarely influence on their own.
 How do organizational elements of private donor decision-making interact with broader structural limits on INGO fundraising?
+How do individual donors in the U.S.
+feel about donating to legally besieged NGOs abroad?
+How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country politics when deciding to donate?
 
-Given the growing crackdown on INGOs across the world, how do individual donors in the U.S.
-feel about donating to legally besieged NGOs abroad?
-How do organizational-level factors such as financial transparency and accountability; funding sources, including private donations and government grants; and various different issue areas compare with more structural-level factors such as host country politics when deciding to donate?
+Although a robust body of work on NGOs and donor behavior examines the motivation of public donors, private foundations and elite donors (CITE), we are yet to examine the impact of closing civic space, especially individual private donors, who are likely to be important funders in the face of increased government repression.
+Existing research shows that organizational accountability and financial transparency play an important role in motivating individual donors to donate to NGOs (CITE).
+In this article, we extend this literature by evaluating how these organization-level characteristics influence private donor behavior in an era of shrinking civic space.
+In considering this question, we engage with a growing body of research on the consequences of closing civic space on NGOs and donors (CITE).
+We argue that NGO-level organizational factors and domestic political environments of NGO host countries serve as heuristics and can influence foreign private donors' preferences.
+We fielded a conjoint experiment to a nationally representative sample of X adults in the US.
+A conjoint design allows us to directly compare the relative impact of host government repression of NGOs vis-a-vis an organization's financial transparency and accountability on individual donor preferences.
+The result of these experiments show both financial transparency and accountability increases individuals' willingness to donate NGOs.
+Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability protect against this dampening effect.
+INSERT LINE ABOUT EFFECT SIZE.
 
-While recent research on private foreign aid has examined funding decisions of donor NGOs themselves, we know less about the funding choices of the individuals responsible for much of these private aid flows [@desaikharas].
-We argue that NGO-level organizational factors and domestic political environments of NGO host countries can influence preferences of foreign private donors by serving as heuristics to potential donors.
-Using a conjoint survey experiment, we find that private donors favor NGOs that voluntarily engage in transparency and accountability, prefer organizations that receive funding from many private individuals, rather than government or foundation grants, and that work on issues related to humanitarian and disaster relief rather than human rights and environmental advocacy.
-Importantly, we also find that structural factors play an important role in the private decision to donate—donors are significantly less likely to donate to INGOs that face government criticism or crackdown.
-Our results have important implications for international NGOs facing increased antagonism by government abroad and point to possible methods of adapting to these new regulations alienating their newfound donor base.
+These findings make two main contributions.
+While recent research on private foreign aid has examined funding decisions of donor NGOs and foundations[^1], we know less about the funding choices of the individuals responsible for much of these private aid flows [@desaikharas].
+The systematic study of private foreign aid is still in its infancy—there is an absence of expansive and high quality data [@greenhill2013], and most research has been restricted to elite, high net-worth donors [@USTrust2014].
+Our research makes a significant contribution to research on individual giving and indicates the promise and limits of different framing appeals on individual donor preferences.
 
-# Private foreign aid
+Second, research shows that NGO leades often have difficulty in attracting new donors and also find it challenging to moviate current donors (Cao 2015).
+Examining the organizational-level factors in a group that make the average donor increase their charitable-giving towards these groups, especially when facing restricted civic space abroad, can help NGOs better target their programming and frame their funding appeals towards these donors.
+Our results thus have important implications for international NGOs facing increased antagonism by government abroad and point to possible methods of adapting to worsening or shrinking civic environments.
 
-Substantial research on nonprofit studies has looked at the motivation of individual donors, including altruism, reputational benefits and alignments with personal values [@BilodeauSlivinski:1997; @Wiepking:2010; @BekkersWiepking:2011].
-However, this research has overwhelmingly looked at individual donor behavior and motivation for giving to local—rather than international—causes.
-On the other hand, the systematic study of private foreign aid is still in its infancy—there is an absence of expansive and high quality data [@greenhill2013], and most research has been restricted to elite, high net-worth donors [@USTrust2014].
-
-We argue that understanding funding decisions of private citizens is important for two main reasons.
-Examining the organizational-level factors in a group that make the average donor increase their charitable-giving towards these groups can help NGOs better target their programming towards these donors.
-It can also help organizations market their activities more saliently.
-More broadly, understanding motivations of private citizens can help organizations and governments better assess claims about the benefits of privatizing foreign aid.
-Previous research has argued that private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the grounds [@easterlywilliamson].
-
-While recent research on private foreign aid has examined funding decisions of donor NGOs and foundations[^1], we know less about the funding choices of the individuals responsible for much of these private aid flows [@desaikharas].
-While we do investigate the impact of individual-level factors on such private philanthropy targeted towards international causes in our larger project, in this paper we seek to understand the impact of organizational features of nongovernmental organizations and the structural factors in target countries in which they operate on donors’ decisions to engage in philanthropy.
+Below, we summarize existing research on determinants of individual giving to foreign NGOs, laying out our expectations regarding how financial transparency, accountability shape individuals' philanthropic preferences in an environment of closing civic space.
+We then describe our conjoint experiment and and present the results.
+We conclude with implications for NGOs working in repressive countries.
 
@@
 
-## Organizational heuristics: The impact of NGO organizational decisions on individual philanthropy
+# What determines individual donor behvior?
 
-Existing research has found that donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking out complete information about an organization's deservingness and efficiency is costly and time-consuming.
+Substantial research on NGOs has looked at the motivation of individual donors, including altruism, reputational benefits and alignments with personal values [@BilodeauSlivinski:1997; @Wiepking:2010; @BekkersWiepking:2011].
+However, this research has overwhelmingly looked at individual donor behavior and motivation for giving to local—rather than international—causes (CITE -2).
+Understanding the latter is important as philanthropy to international causes can be harder to motivate because the number of recipients is larger and further removed from the donor (Casale & Baumann, 2015, 100).
+Further, as Micklewright and Schnepf (2009) point out, motivations for donating to ongoing international causes differ from donating money to natural disasters or emergency international causes.
+Under ordinary circumstances, “donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad” (Tremblay-Boire & Prakash, 2017, p.
+644).
+However, we lack adequate data and theory regarding philanthropy towards INGOs.
+
+The third wave of democratization, the collapse of the Soviet Union, and the spread of a "pro-NGO norm" led to an increased role and visibility for NGOs.
+Globally, a large amount of resources were channeled to NGOs focused on service provision or development because many public and private donors perceived them as more efficient than states with weak institutions and poor governance; there was a high risk that such states would use aid transfers inefficiently (Dietrich 2013).
+
+But as INGOs became increasingly powerful actors in global policy circles, they faced a number of criticisms.
+Many organizations struggle with the conflicting imperatives of being large organizations that can operate efficiently at scale, while maintaining the grassroots contacts and consensus building that contributed to their early successes.\footnote{\cite{mitchell2020between}, 2; \cite{jalali2013, bano2012, rahman2006}.} Many nonprofit scandals involve some form of financial wrongdoing (Prakash and Gugerty 2010).
+Globally, around 5\% of revenue is lost annually due to fraud (Lamothe et al 2022).
+Misappropriation of assets and embezzlement schemes are among the most common forms of financial fraud (Lamthoe).
+These criticisms and concerns, in turn, have led donors to demand greater NGO responsiveness, especially in terms of financial transparency and accountability.
+
+Donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking out complete information about an organization's deservingness and efficiency is costly and time-consuming (Croson & Shang, 2011; Tremblay-Boire & Prakash, 2017).
+Nonprofits fundraising internationally may therefore rely on framing to control perceptions.
+Below, we theorize the effect of different frames surrounding a country’s legal environment and nonprofit organizational characteristics on individual donor preferences.
+
+## Organizational heuristics: The impact of NGO organizational practices on individual philanthropy
+
+In theory, donors should scrutinize each aspect of an NGO’s organizational structure and programmatic performance prior to donation, but this rarely happens in practice (Tremblay-Boire & Prakash, 2017).
+Instead, individuals rely on heuristics to simplify their decision-making.
+
 One common signal for donors is organizational efficacy or the belief that an individual's donation will make a real difference.
 This can manifest itself through multiple mechanisms such as the amount an organization spends on overhead costs, whether an organization makes its finances public, or whether an organization participates in voluntary accountability practices, such as listing organizational details on websites like GuideStar and Charity Navigator.
+An NGO's financial transparency, defined as the degree of completeness of information, provided by organizations to the public concerning its business activities, is one tangible heuristics that donors use to make their decisions.
+NGOs can engage in financial transparency in a variety of ways such as distribution of audiented financial statements, third party intermediaries.
+Reserach shows that transparency is associated with greater donations, lower debt and better governance (Harris and Neely 2021, Saxton et al 2012).
+It can also enhance donor trust and confidence in organizations [@Vacarro:2006; @vaccaromadsen].
 
-Financial transparency, defined as the degree of completeness of information, provided by organizations to the public concerning its business activities is one such important organizational practice that can enhance donor trust and confidence in organizations [@Vacarro:2006; @vaccaromadsen].
 Previous research has found that media exposés about charity mismanagement can generate negative reputational spillovers for the charitable sector [@gibelmangelman].
-Therefore, being financially transparent and engaging in activities that further transparency can reduce actual or perceived information asymmetries between donors and charities, and increase donor perception of organizational efficacy.
+Diversions, or the unauthorized use of an organization's assets, including embezzlement and theft can result in a decrease in donatons.
+This effect becomes even stronger with media coverage of diversion (Harris et al 2023).
+Organizational financial transparent can reduce actual or perceived information asymmetries between donors and charities, this potentially increasing donor likelihood of donating to an INGO.
 
@@
 
-In addition to financial transparency, researchers and organizations, especially those auditing accountability practices, argue that accountability is another factor that can impact donor willingness to donate.
+Accountability is another factor that can impact donor willingness to donate.
+Accountability is necessary to promote public trust in NGOs.
 While transparency is an organization's willingness to make critical data about the organization public, accountability is the willingness of the organization to explain its action to shareholders.
+It also encompasses how well an organization's mission is aligned with its reources and how it manages resources to optimize performance (Sloan 2009).
 
-Explaining actions to stakeholders can be important because many NGOs, even when well-intentioned, can devote excessive resources towards marketing and overheads [@bowman:2006].
+Explaining actions to stakeholders can be important because many NGOs, even when well-intentioned ones, can devote excessive resources towards marketing and overheads [@bowman:2006].
 Private donors, subsequently, may be more likely to dislike NGOs that spend a large share of their revenues for unproductive purposes [@rose1982], or rather, a large share of resources on administration, management and fundraising.
 As @Tremblay-BoirePrakash:2017 point out, while individuals would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead, donors do not necessarily have the time to research charities thoroughly.
-Based on a survey experiment, they find that membership in a voluntary program ultimately does not influence people's willingness to donate.
-Thus, while seeking out explanations about NGO actions can be important to individual donors, they do not necessarily seek assurance through third-party programs/audits and charity watchdogs, but rather through word of mouth, personal scrutiny and local networks.
+Lack of accountability is associated with lesser public trust, reputation, perceived quality and donation behavior (Becker 2018).
+
+To judge organizational accountabiltiy, donors may use ratings by watchdog organizations like Charity Navigator and GuideStar as heuristics to guide their decisions.
+Research shows that initiatives to address accountability gaps by these organizations can affect donations to organizations in a significant manner (Sloan 2009, Gordon, Knock and Neely).
 
@@
 
-Another heuristic for deservingness is the *issue area* an NGO engages in.
-Donors can have very different preferences regarding the nature of NGO activities that they would like to support [@AndreoniPayne:2003].
-Organizations that address humanitarian issues such as relief and development have broader appeal to donors who might shy away from NGOs dealing with more political causes like human rights.
-Organizations focusing on the former may also be able to frame their activities as in need of greater support.
+## Structural heuristics: Host country conditions
 
-Perception of need, whether from personal experiences or acquired through media framing, can strongly influence the decisions of individuals to donate to relief efforts [@BekkersWiepking:2010, 6-8; @wiepkingleeuwen, 227-29].
-This is especially the case when donors are faced with beneficiaries that fit the commonly accepted stereotypes of "victims" [@breezedean, 134].
-Indeed, previous research has found that emergency funding, at least in the form of bilateral aid NGO, is more likely to be directed towards the senders of asylum-seekers and refugees [@czaikamayer; @bermeoleblang].
-Therefore, donors may be more willing to donate to NGOs working on emergency response or relief focusing on victimized groups such as refugees or women and children in war.
+In addition to organizational factors discussed above, political contexts in NGO host countries, especially their environments for civil society organizations, can also influence donor preferences for donating to foreign NGOs.
+A global cascade of anti-NGO laws in recent decades has created barriers to entry, funding, and advocacy for civic organizations (Glasius et al, Schmidt et al, Chaudhry, Heiss, DPR).
+As a result, NGOs must spend more time, effort, and resources to ensure their survival -- at the expense of pursuing their missions.
+Some NGOs have adapted to their repressive environments by recreating their organizations and changing their mission to avoid directly confronting the government.
+Analyzing the impact of anti-NGO laws in Bangladesh and Zambia, scholars have similarly found that NGOs with a broad mission ended up restricting themselves to service work and giving up on their advocacy work.
+Those that continued to engage in transnational advocacy changed the targets of their advocacy, the issues they focused on, and the language they used.
+For instance, many NGOs stopped lobbying the central government and focused their advocacy efforts on lower levels of government.\footnote{\cite{fransen2021tempering}.} Similarly, in Russia, many NGOs working with foreign partners and lobbying the central government no longer consider it an effective strategy.\footnote{\cite{sundstrom2022evolution}.} Overall, fewer groups may end up focusing on contentious causes, instead focusing on regime-compatible causes.
 
-On the other hand, donors may be less willing to support NGOs focusing on contentious issue areas or programs that are not compatible with host government preferences.
-While NGOs working on issues like health, education and humanitarian relief rarely challenge the government [@Bush:2015; @Kiai:2017], those working on more contentious areas such as human rights, environmental advocacy, or election monitoring can pose political and economic challenges to regimes [@Chaudhry:2016].
-These organizations are often viewed as politically motivated outsiders and run a higher risk of getting expelled [@DPR2015], increasing the possibility of wasting donor resources.
-Further, unlike the former causes, their programmatic output is harder to measure and quantify, which is another factor that is important to donors [@Bush:2015].
-
->**H~2~**: If NGOs work in less contentious issue areas (emergency response and refugee relief), then individual private donors will be more likely to donate to them over more contentious issue areas (environment and human rights).
-
-The *source of NGO funding* can also influence donor behavior.
-Government grants to NGOs can often crowd out private funding [@AndreoniPayne:2003].
-Donors are less likely to contribute to NGOs that rely heavily on government grants since their donation might feel more impersonal and less needed, while donors are more likely to give to organizations that rely primarily on private donations given that they may feel personally invested in the organization and perceive their contribution mattering.
-Government grants may also imply lack of independence from government which can reduce the efficiency of an organization [@Stroup:2012].
-
->**H~3~**: If NGOs are funded primarily by numerous small private donors, then individual private donors will be more likely to donate to them compared to NGOs that are funded by a handful of wealthy private donors and government grants.
-
-Each of these signals is *organizational*.
-NGOs typically have direct control over their organizational practices, mission and issue area, and funding sources.
-We theorize that organizational characteristics like managerial practices, issue area, and funding sources all influence the decision to donate to an NGO (see @fig:big-dag).
-At the same time, however, we propose that structural characteristics like an NGO's host-country political and legal environment can also serve as donor heuristics.
-
-## Structural heuristics: The impact of anti-NGO crackdowns on individual philanthropy
-
-NGOs have less control over *structural* issues, and the role of political and legal institutions in donor decision making has been understudied.
-However, over the past decade international NGOs have become increasingly politicized and legally restricted around the world.
-NGO registration is not inherently restrictive, as governments frequently use regulations to streamline NGO-state relationships.
-Restrictive NGO laws, on the other hand, are designed to limit organizational programming by imposing barriers to entry, funding, and advocacy.
-These anti-NGO laws may signal to donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and crack down on them.
+The changes in civic environments impacting NGO activity have also influenced official donor responses.
+In response to the passage of these laws, scholars have found that while multilateral donors do not reduce aid following the passage of anti-NGO laws, they are associated with a 32\% decline in bilateral aid inflows.\footnote{\cite{DupuyPrakash:2018}.} Further, advocacy-oriented donors -- i.e., those that fund democracy and civil society promotion activities -- reduced their spending by 74\%, but did not cut their spending on development projects such as education, health, water, and sanitation.\footnote{\cite{right2022advocacy}.
+However, previous literature has established that individual private donors may not necessarily use the same metrics as official donors (CITE).
+Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the grounds [@easterlywilliamson].
+These anti-NGO laws may signal to private donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and crack down on them.
 Therefore, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization.
 
->**H~4~**: If NGOs face legal crackdowns abroad, then individual donors will be more likely to donate to them.
+>**H~2~**: If NGOs face legal crackdowns abroad, then individual donors will be more likely to donate to them.
 
@@
 
-Identifying the causal link between structural factors and donor behavior is more difficult than measuring the link between organizational factors and donor behavior, however, because (1) NGOs have less direct control over their political environments, and (2) organizational characteristics like issue area and funding can sour the NGO-government relationship (as we explain in further detail below, governments are more likely to crack down on NGOs that address human rights and that receive government funding).
+Identifying the causal link between structural factors and donor behavior is more difficult than measuring the link between organizational factors and donor behavior, however, because (1) NGOs have less direct control over their political environments, and (2) organizational characteristics like financial transparency and accountability can sour the NGO-government relationship -- governments may be more likely to target NGOs that lack financial transparency and accountability.
 @fig:big-dag helps disentangle this complex relationship.
 Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**).
-Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both funding and issue area.
+Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both transparency and accountability.
 As such, legal crackdowns do not occur in isolation.
-Countries are more likely to repress NGOs when organizational missions are in tension with government preferences and when organizations receive substantial funding from abroad [@DPR2015].
+Countries are more likely to repress NGOs when organizational features are in tension with government preferences and when organizations receive substantial funding from abroad [@DPR2015].
 Therefore, the same organizational characteristic that can increase the likelihood of crackdown can also simultaneously serve as a donor heuristic and influence perceptions of NGO deservingness.
 
-Donors therefore may show increased willingness to donate to NGOs facing government crackdown/criticism working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights).
-Those working on contentious issues may be expelled or shut down, which would waste donor resources and make it less likely that they donate to these organizations.
-Similarly, the combination of legal crackdown and funding may reshape donor perceptions of deservingness.
-Private donors may be more likely to punish government-funded NGOs that face restrictions.
-This is because legal trouble with the group's main funder could fuel private donor mistrust.
+Donors therefore may show increased willingness to donate to NGOs facing government crackdown/criticism while being financial transparent and accountable.
+While concerns about NGO mismanagement and lack of financial transparency may signal concerns about an NGO's operations and its ability to abide by the host country's regulatory environment, the presence of such transparency and accountability may instead convince donors that government targeting of NGOs may be ill-intentioned rather than simply a manifestation of financial oversight.
+Donors may view anti-NGO laws and inhospitable civic environments as a sign of governments looking to crack down on groups that seek to keep governments accountable, rather than merely auditing and punishing groups that violate routine regulations.
 
-Finally, the combination of financial transparency and government crackdown may increase donor willingness to support besieged NGOs.
-While concerns about NGO mismanagement and lack of financial transparency may signal concerns about an NGO's operations and its ability to abide by the host country's regulatory environment, the presence of such transparency may instead convince donors that government targeting of NGOs may be ill-intentioned rather than simply a manifestation of financial oversight.
-Donors may view NGO legislation as a sign of governments looking to crack down on groups that seek to keep governments accountable, rather than merely auditing and punishing groups that violate routine regulations.
-
-> **H~5a~**: Donors will show increased willingness to donate to NGOs facing government crackdown/criticism working in less contentious issue areas (emergency response and refugee relief) over more contentious issue areas (environment and human rights).
->
-> **H~5b~**: Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors.
->
->**H~5c~**: Donors will show increased willingness to donate to NGOs that are facing government crackdown and are funded primarily by numerous small private donors and work in less contentious areas (emergency response and refugee relief).
->
->**H~5d~**: Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent and work in less contentious areas (emergency response and refugee relief) and are funded by numerous small donors.
+Since we are running a conjoint experiment, the interactions between the main treatment variables described above is simply an exploratory analysis.
+Importantly, when testing these hypotheses, we do not assume that individual donors have perfect knowledge about an NGO or the country an NGO operates in.
+Moreover, the average donor will not know exactly what “crackdown” entails for any given organization (i.e., does it mean an NGO was expelled, or that its assets were frozen, or that it received a fine?).
+For the sake of this experiment, this ambiguity is not a central concern as the heuristics we explore here are explicitly simplified short- cuts to donor information-gathering.
+Knowing that an organization is financially transparent (even if donors are not familiar with specific kinds of requirements regarding transparency) or knowing that an NGO faces legal trouble abroad should be enough to trigger the effect of these frames on donor preferences.
+Moreover, although many NGOs make information about their operations accessible through annual reports, it is time-consuming to track down that information.
+In each of these hypotheses, we assume that donors will not spend additional effort to research the exact details concerning crackdown, transparency and accountability.
+Instead, donors rely on signals and heuristics about the organiza- tion to shape their preferences and behavior (Szper & Prakash, 2011).
 
@@
 After collecting baseline information on respondent demographics and attitudes toward charity and voluntarism, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.^[See the appendix for a copy of the survey.] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross.
+We chose these 4 organizations as the represent the core sectors of activity according to Charity Navigator (Environment, Human Rights, Humanitarian Relief, and Development).
 We then displayed various combinations of features, including one of four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), one of two organizational practices (financial transparency and third-party accountability audits), one of three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and one of three relationships with host governments (friendly, criticized by the government, and under government crackdown).
@@
 
-# Discussion and conclusion
+# Conclusion
+Over the last two decades, governments globally have systematically controlled and repressed NGOs using both violent tactics and administrative means over the last three decades -- a phenomenon known as `closing' or `shrinking' civic space.
+This trend of closing civic space has important implications for local and international NGOs as well as donors.
+Recent research has analyzed the impact of this crackdown on public or official aid donors.
+However, we know relatively little about how state repression of NGOs affects the preferences of foreign private donors.
+The responses of elite donors and foundations to government crackdown on civil society organizations remains a ripe area for research.
+Unlike state donors, individual and elite donors may not necessarily withdraw or reduce support for NGOs facing harassment abroad.
+This is important because private philanthropy towards organizations working in international affairs continues to grow despite inflation -- from 2021 to 2022, individual giving to nonprofits in international affairs grew by over 10.9% in the US (https://philanthropy.iupui.edu/news-events/news-item/giving-usa:-total-u.s.-charitable-giving-declined-in-2022-to-$499.33-billion-following-two-years-of-record-generosity.html?id=422).
 
-In general we find support for our hypotheses.
-With the turn towards private philanthropy in the face of the global crackdown on civil society, INGOs need to be aware of the dynamics of individual donor preferences and how those preferences interact with their managerial and organizational decision.
-Additionally, structural factors like political trends in INGO host countries influence donor decision-making.
-In aggregate, donors are less likely to give to organizations that face government criticism and crackdown, which could be a worrying sign for INGOs working on contentious issues that are more likely to elicit negative government responses.
-However, for the subgroup of respondents with personal involvement in advocacy, government crackdown serves as a positive heuristic instead, likely because those involved in advocacy understand how the relationship between governments and charities can be fraught.
+Given the increasing hurdles faced by these nonprofits, how do individual donors in the U.S.
+feel about donating to legally besieged NGOs abroad?
+How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country politics when deciding to donate?
+Using a conjoint experiment with a nationally representative sample of the U.S.
+population, we find COMPLETE.
+
+These results have important implications for NGO operations, fundraising and survivability at a time when a number of INGOs are dealing with hostile host governments.
+The crackdown is even more challenging for local NGOs in Global South countries, where much government and public support is channeled via service delivery organizations.
+Local groups tackling contentious issues may not be able to raise funds domestically, as publics may prefer donating to service organizations focusing on health, education, and poverty.\footnote{\cite{absar2017will}.} Even local philanthropists may be deterred from giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to poor tax incentives or a fear of retribution.\footnote{\cite{Brechenmacher:2017}; \cite{DPR2015}; \cite{Baoumi:2016}.} Our results highlight the importance of organizational characteristics like transparency and accountability even in an era of closing civic space.
+By finding new ways to communicate about organizational transparency and accountability to potential donors, NGOs can help overcome individual donors' concerns about host governments' criticisms of and crackdown on these groups.
+
+Future research should test how well these results map on to elite individual donors, not just the average private donor, as well as determine the extent to which these preferences translate into behavior.

### 2023-10-26 notebook/results-practices.qmd
Add accountability across government relationship

@@
 h5a_mms <- preds_all %>% 
-  group_by(feat_transp_short, .draw) %>% 
+  group_by(feat_acc, .draw) %>% 
   summarize(avg = mean(.epred))
@@
 h5a_amces <- h5a_mms %>% 
-  group_by(feat_transp_short) %>% 
-  compare_levels(variable = avg, by = feat_transp_short, comparison = "control")
+  group_by(feat_transp) %>% 
+  compare_levels(variable = avg, by = feat_transp, comparison = "control")
 ```
@@
 p_h5a_mms <- h5a_mms %>% 
-  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
+  ggplot(aes(x = avg, y = feat_acc, fill = feat_acc)) +
   stat_halfeye() +
@@
 
-# H~5b~: Relationship with host government, organizational practices
+# H~5b~: Relationship with host government and organizational practices
+
+## Transparency
 
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~b~: Relationship with host government, organizational practices
+### {{< iconify fa6-solid flask-vial >}} Hypothesis 5~b~: Relationship with host government, organizational practices
 
@@
     feat_transp_short = "Transparency", 
+    nice = "Posterior EMM",
+    contrast = "Contrast",
+    diff_nice = "Posterior ∆",
+    p_neq_0 = "*p*~direction~",
+    .fn = md
+  ) %>% 
+  tab_style(
+    style = cell_text(v_align = "top"),
+    locations = cells_body()
+  ) %>% 
+  tab_style(
+    style = cell_fill(color = "grey90"),
+    locations = cells_row_groups()
+  ) %>% 
+  tab_footnote(
+    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
+    locations = cells_column_labels(columns = c(nice, diff_nice))
+  ) %>% 
+  tab_footnote(
+    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
+    locations = cells_column_labels(columns = p_neq_0)
+  ) %>% 
+  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
+  opt_footnote_marks(marks = "standard") %>% 
+  opt_horizontal_padding(3) %>% 
+  opts_theme()
+```
+
+## Accountability
+
+::: {.callout-tip icon=false}
+### {{< iconify fa6-solid flask-vial >}} Hypothesis 5~b2~: Relationship with host government, organizational practices
+
+**Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are accountable and hold regular third party audits**
+:::
+
+$$
+\begin{aligned}
+\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Accountability} = \text{Yes} \mid \text{Relationship = Under crackdown or Criticized} \right) \bigr] - \\
+&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Accountability} = \text{Yes} \mid \text{Relationship = Friendly} \right) \bigr]
+\end{aligned}
+$$
+
+```{r h5b2-calc-estimands}
+h5b2_mms <- preds_all %>% 
+  group_by(feat_acc_short, feat_govt, .draw) %>% 
+  summarize(avg = mean(.epred))
+
+h5b2_amces <- h5b2_mms %>% 
+  group_by(feat_govt) %>% 
+  compare_levels(variable = avg, by = feat_acc_short, comparison = "control")
+```
+
+```{r plot-h5b2-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
+#| column: body-outset-right
+p_h5b2_mms <- h5b2_mms %>% 
+  ggplot(aes(x = avg, y = feat_acc_short, fill = feat_acc_short)) +
+  stat_halfeye() +
+  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
+  scale_x_continuous(labels = label_percent()) +
+  scale_y_discrete(labels = label_wrap(11)) +
+  scale_fill_manual(values = clrs$prism[c(9, 4)], guide = "none") +
+  facet_wrap(vars(feat_govt), ncol = 1) +
+  labs(
+    x = "Overall average predicted probability",
+    y = NULL,
+    fill = NULL,
+    title = "Estimated marginal means"
+  ) +
+  theme(
+    legend.position = "top",
+    legend.justification = "left",
+    legend.margin = margin(l = -7, t = 0)
+  )
+
+p_h5b2_amces <- h5b2_amces %>% 
+  ungroup() %>% 
+  separate_wider_delim(
+    feat_acc_short,
+    delim = " - ", 
+    names = c("feat_acc_short", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feat_acc_short = "No", feat_govt = "Friendly relationship with government") %>%
+  add_row(avg = 0, feat_acc_short = "No", feat_govt = "Criticized by government") %>%
+  add_row(avg = 0, feat_acc_short = "No", feat_govt = "Under government crackdown") %>%
+  mutate(feat_acc_short = factor(feat_acc_short, levels = levels(h5b2_mms$feat_acc_short))) %>% 
+  mutate(feat_govt = factor(feat_govt, levels = levels(h5b2_mms$feat_govt))) %>% 
+  ggplot(aes(x = avg, y = feat_acc_short, fill = feat_acc_short)) +
+  stat_halfeye() +
+  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
+  scale_x_continuous(labels = label_pp) +
+  scale_y_discrete(labels = label_wrap(11)) +
+  scale_fill_manual(values = clrs$prism[c(9, 4)], guide = "none") +
+  facet_wrap(vars(feat_govt), ncol = 1) +
+  labs(
+    x = "Percentage point change in probability of choice selection",
+    y = NULL,
+    fill = NULL,
+    title = "Difference in estimated marginal means"
+  )
+
+p_h5b2_mms | p_h5b2_amces
+```
+
+```{r table-h5b2-mm-amce}
+#| column: body-outset-right
+h5b2_tbl_mm <- h5b2_mms %>% 
+  group_by(feat_govt, feat_acc_short) %>% 
+  median_qi() %>% 
+  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
+  arrange(desc(feat_govt), desc(feat_acc_short)) %>% 
+  select(feat_acc_short, feat_govt, nice)
+
+h5b2_tbl_amces <- h5b2_amces %>% 
+  group_by(feat_govt, feat_acc_short) %>% 
+  summarize(
+    median_qi(avg),
+    p_gt_0 = sum(avg > 0) / n()
+  ) %>%
+  ungroup() %>% 
+  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
+  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
+  mutate(feat_acc_short = str_replace(feat_acc_short, " - ", "−<br>")) %>% 
+  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
+  arrange(desc(feat_govt)) %>% 
+  select(contrast = feat_acc_short, diff_nice = nice, p_neq_0)
+
+bind_cols(
+  h5b2_tbl_mm, 
+  h5b2_tbl_amces %>% 
+    add_row(contrast = NA, .after = 1) %>% 
+    add_row(contrast = NA, .after = 3) %>% 
+    add_row(contrast = NA, .after = 5)
+) %>% 
+  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
+  group_by(feat_govt) %>% 
+  gt() %>% 
+  sub_missing(columns = everything(), missing_text = "—") %>% 
+  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
+  cols_align(align = "center", columns = everything()) %>% 
+  cols_align(align = "left", columns = c(feat_acc_short, contrast)) %>% 
+  cols_label(
+    feat_acc_short = "Accountability", 
     nice = "Posterior EMM",

### 2023-10-26 manuscript/manuscript.qmd
Use Zotero + update all possible references

@@
 These attacks—most of which have been implemented through anti-NGO laws—have adversely affected the ability of both domestic and international NGOs to operate and raise funds.
-Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official aid donors channel fewer funds to contentious issues and instead choose to fund "tame" causes [@ChaudhryHeiss:2018; @Bush:2015, HERROLD, SPRINGMAN].
+Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official aid donors channel fewer funds to contentious issues and instead choose to fund "tame" causes [@ChaudhryHeiss:2018; @Bush:2015; @HERROLD; @SPRINGMAN].
 In response to this dramatic shift in the NGO funding landscape, international NGOs (INGOs) have increasingly turned to foreign individual donors to offset the loss of funding from government and foundation sources [@BanksHulmeEdwards:2015].
@@
 The amount of private foreign aid is not insignificant—from 2000–2010, private giving by U.S.
-entities towards international causes doubled in real terms [@desaikharas, 505].
+entities towards international causes doubled in real terms [@DesaiKharas:2018, 505].
 In 2016, U.S.
-private philanthropy towards international NGOs amounted to \$22.06 billion [@givingusa:2017].
+private philanthropy towards international NGOs amounted to \$22.06 billion [@GivingUSA:2017].
 Most notably, a large portion of this growth was driven by individuals making small-scale donations.
 In 2017, individuals gave US\$286.7 billion or approximately 70% of total giving to international affairs.
-This further increased to US\$427.71 billion in 2018, 85.7% of which was through individuals (Giving USA, 2019).
+This further increased to US\$427.71 billion in 2018, 85.7% of which was through individuals [@GivingUSA:2019].
 This turn to private donors opens INGOs up to new dynamics in seeking out aid.
@@
 These findings make two main contributions.
-While recent research on private foreign aid has examined funding decisions of donor NGOs and foundations[^1], we know less about the funding choices of the individuals responsible for much of these private aid flows [@desaikharas].
-The systematic study of private foreign aid is still in its infancy—there is an absence of expansive and high quality data [@greenhill2013], and most research has been restricted to elite, high net-worth donors [@USTrust2014].
+While recent research on private foreign aid has examined funding decisions of donor NGOs and foundations[^1], we know less about the funding choices of the individuals responsible for much of these private aid flows [@DesaiKharas:2018].
+The systematic study of private foreign aid is still in its infancy—there is an absence of expansive and high quality data [@GreenhillPrizzonRogerson:2013], and most research has been restricted to elite, high net-worth donors [@USTrust2014].
 Our research makes a significant contribution to research on individual giving and indicates the promise and limits of different framing appeals on individual donor preferences.
 
-Second, research shows that NGO leades often have difficulty in attracting new donors and also find it challenging to moviate current donors (Cao 2015).
+Second, research shows that NGO leaders often have difficulty in attracting new donors and also find it challenging to motivate current donors [@GaudreauCao:2015].
 Examining the organizational-level factors in a group that make the average donor increase their charitable-giving towards these groups, especially when facing restricted civic space abroad, can help NGOs better target their programming and frame their funding appeals towards these donors.
@@
 
-[^1]: On aid from world's largest NGOs, see @koch2009, on private aid flows from NGOs based in the US, see @buthe2012.
+[^1]: On aid from world's largest NGOs, see @Koch:2009, on private aid flows from NGOs based in the US, see @ButheMajorMello-e-Souza:2012.
 
-# What determines individual donor behvior?
+# What determines individual donor behavior?
 
-Substantial research on NGOs has looked at the motivation of individual donors, including altruism, reputational benefits and alignments with personal values [@BilodeauSlivinski:1997; @Wiepking:2010; @BekkersWiepking:2011].
+Substantial research on NGOs has looked at the motivation of individual donors, including altruism, reputational benefits, and alignment with personal values [@BilodeauSlivinski:1997; @Wiepking:2010; @BekkersWiepking:2011].
 However, this research has overwhelmingly looked at individual donor behavior and motivation for giving to local—rather than international—causes (CITE -2).
-Understanding the latter is important as philanthropy to international causes can be harder to motivate because the number of recipients is larger and further removed from the donor (Casale & Baumann, 2015, 100).
-Further, as Micklewright and Schnepf (2009) point out, motivations for donating to ongoing international causes differ from donating money to natural disasters or emergency international causes.
-Under ordinary circumstances, “donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad” (Tremblay-Boire & Prakash, 2017, p.
-644).
+Understanding the latter is important as philanthropy to international causes can be harder to motivate because the number of recipients is larger and further removed from the donor [@CasaleBaumann:2015, 100].
+Further, as @MicklewrightSchnepf:2009 point out, motivations for donating to ongoing international causes differ from donating money to natural disasters or emergency international causes.
+Under ordinary circumstances, “donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad” [@Tremblay-BoirePrakash:2017, 644].
 However, we lack adequate data and theory regarding philanthropy towards INGOs.
@@
 The third wave of democratization, the collapse of the Soviet Union, and the spread of a "pro-NGO norm" led to an increased role and visibility for NGOs.
-Globally, a large amount of resources were channeled to NGOs focused on service provision or development because many public and private donors perceived them as more efficient than states with weak institutions and poor governance; there was a high risk that such states would use aid transfers inefficiently (Dietrich 2013).
+Globally, a large amount of resources were channeled to NGOs focused on service provision or development because many public and private donors perceived them as more efficient than states with weak institutions and poor governance; there was a high risk that such states would use aid transfers inefficiently [@Dietrich:2013].
 
 But as INGOs became increasingly powerful actors in global policy circles, they faced a number of criticisms.
-Many organizations struggle with the conflicting imperatives of being large organizations that can operate efficiently at scale, while maintaining the grassroots contacts and consensus building that contributed to their early successes.\footnote{\cite{mitchell2020between}, 2; \cite{jalali2013, bano2012, rahman2006}.} Many nonprofit scandals involve some form of financial wrongdoing (Prakash and Gugerty 2010).
-Globally, around 5\% of revenue is lost annually due to fraud (Lamothe et al 2022).
-Misappropriation of assets and embezzlement schemes are among the most common forms of financial fraud (Lamthoe).
+Many organizations struggle with the conflicting imperatives of being large organizations that can operate efficiently at scale, while maintaining the grassroots contacts and consensus building that contributed to their early successes [@MitchellSchmitzBruno-vanVijfeijken:2020; @Jalali:2008; @Bano:2012; @Rahman:2006].
+Many nonprofit scandals involve some form of financial wrongdoing [@PrakashGugerty:2010b].
+Globally, around 5% of revenue is lost annually due to fraud [@ACFE:2021].
+Misappropriation of assets and embezzlement schemes are among the most common forms of financial fraud [@LamotheTer-MkrtchyanRuddle:2023].
 These criticisms and concerns, in turn, have led donors to demand greater NGO responsiveness, especially in terms of financial transparency and accountability.
 
-Donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking out complete information about an organization's deservingness and efficiency is costly and time-consuming (Croson & Shang, 2011; Tremblay-Boire & Prakash, 2017).
+Donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking out complete information about an organization's deservingness and efficiency is costly and time-consuming [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
 Nonprofits fundraising internationally may therefore rely on framing to control perceptions.
@@
 
-In theory, donors should scrutinize each aspect of an NGO’s organizational structure and programmatic performance prior to donation, but this rarely happens in practice (Tremblay-Boire & Prakash, 2017).
+In theory, donors should scrutinize each aspect of an NGO’s organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017].
 Instead, individuals rely on heuristics to simplify their decision-making.
@@
 An NGO's financial transparency, defined as the degree of completeness of information, provided by organizations to the public concerning its business activities, is one tangible heuristics that donors use to make their decisions.
-NGOs can engage in financial transparency in a variety of ways such as distribution of audiented financial statements, third party intermediaries.
-Reserach shows that transparency is associated with greater donations, lower debt and better governance (Harris and Neely 2021, Saxton et al 2012).
-It can also enhance donor trust and confidence in organizations [@Vacarro:2006; @vaccaromadsen].
+NGOs can engage in financial transparency in a variety of ways such as distribution of audited financial statements, third party intermediaries.
+Research shows that transparency is associated with greater donations, lower debt and better governance [@HarrisNeely:2021; @SaxtonKuoHo:2012].
+It can also enhance donor trust and confidence in organizations [@Vaccaro:2006; @VaccaroMadsen:2006].
 
-Previous research has found that media exposés about charity mismanagement can generate negative reputational spillovers for the charitable sector [@gibelmangelman].
-Diversions, or the unauthorized use of an organization's assets, including embezzlement and theft can result in a decrease in donatons.
-This effect becomes even stronger with media coverage of diversion (Harris et al 2023).
+Previous research has found that media exposés about charity mismanagement can generate negative reputational spillovers for the charitable sector [@GibelmanGelman:2004].
+Diversions, or the unauthorized use of an organization's assets, including embezzlement and theft can result in a decrease in donations.
+This effect becomes even stronger with media coverage of diversion [@HarrisPetrovitsYetman:2023].
 Organizational financial transparent can reduce actual or perceived information asymmetries between donors and charities, this potentially increasing donor likelihood of donating to an INGO.
@@
 While transparency is an organization's willingness to make critical data about the organization public, accountability is the willingness of the organization to explain its action to shareholders.
-It also encompasses how well an organization's mission is aligned with its reources and how it manages resources to optimize performance (Sloan 2009).
+It also encompasses how well an organization's mission is aligned with its resources and how it manages resources to optimize performance [@Sloan:2009].
 
-Explaining actions to stakeholders can be important because many NGOs, even when well-intentioned ones, can devote excessive resources towards marketing and overheads [@bowman:2006].
-Private donors, subsequently, may be more likely to dislike NGOs that spend a large share of their revenues for unproductive purposes [@rose1982], or rather, a large share of resources on administration, management and fundraising.
+Explaining actions to stakeholders can be important because many NGOs, even when well-intentioned ones, can devote excessive resources towards marketing and overheads [@Bowman:2006].
+Private donors, subsequently, may be more likely to dislike NGOs that spend a large share of their revenues for unproductive purposes [@Rose-Ackerman:1982], or rather, a large share of resources on administration, management and fundraising.
 As @Tremblay-BoirePrakash:2017 point out, while individuals would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead, donors do not necessarily have the time to research charities thoroughly.
-Lack of accountability is associated with lesser public trust, reputation, perceived quality and donation behavior (Becker 2018).
+Lack of accountability is associated with lesser public trust, reputation, perceived quality and donation behavior [@Becker:2018].
 
-To judge organizational accountabiltiy, donors may use ratings by watchdog organizations like Charity Navigator and GuideStar as heuristics to guide their decisions.
-Research shows that initiatives to address accountability gaps by these organizations can affect donations to organizations in a significant manner (Sloan 2009, Gordon, Knock and Neely).
+To judge organizational accountability, donors may use ratings by watchdog organizations like Charity Navigator and GuideStar as heuristics to guide their decisions.
+Research shows that initiatives to address accountability gaps by these organizations can affect donations to organizations in a significant manner [@Sloan:2009; @GordonKnockNeely:2009]
 
@@
 In addition to organizational factors discussed above, political contexts in NGO host countries, especially their environments for civil society organizations, can also influence donor preferences for donating to foreign NGOs.
-A global cascade of anti-NGO laws in recent decades has created barriers to entry, funding, and advocacy for civic organizations (Glasius et al, Schmidt et al, Chaudhry, Heiss, DPR).
+A global cascade of anti-NGO laws in recent decades has created barriers to entry, funding, and advocacy for civic organizations [@GlasiusSchalkDeLange:2020; @Schmidt-et-al; @Chaudhry:2022; @Heiss:2017; @DupuyRonPrakash:2015].
 As a result, NGOs must spend more time, effort, and resources to ensure their survival -- at the expense of pursuing their missions.
@@
 Those that continued to engage in transnational advocacy changed the targets of their advocacy, the issues they focused on, and the language they used.
-For instance, many NGOs stopped lobbying the central government and focused their advocacy efforts on lower levels of government.\footnote{\cite{fransen2021tempering}.} Similarly, in Russia, many NGOs working with foreign partners and lobbying the central government no longer consider it an effective strategy.\footnote{\cite{sundstrom2022evolution}.} Overall, fewer groups may end up focusing on contentious causes, instead focusing on regime-compatible causes.
+For instance, many NGOs stopped lobbying the central government and focused their advocacy efforts on lower levels of government [@FransenDupuyHinfelaar:2021].
+Similarly, in Russia, many NGOs working with foreign partners and lobbying the central government no longer consider it an effective strategy [@SundstromHenrySperling:2022].
+Overall, fewer groups may end up focusing on contentious causes, instead focusing on regime-compatible causes.
 
 The changes in civic environments impacting NGO activity have also influenced official donor responses.
-In response to the passage of these laws, scholars have found that while multilateral donors do not reduce aid following the passage of anti-NGO laws, they are associated with a 32\% decline in bilateral aid inflows.\footnote{\cite{DupuyPrakash:2018}.} Further, advocacy-oriented donors -- i.e., those that fund democracy and civil society promotion activities -- reduced their spending by 74\%, but did not cut their spending on development projects such as education, health, water, and sanitation.\footnote{\cite{right2022advocacy}.
+In response to the passage of these laws, scholars have found that while multilateral donors do not reduce aid following the passage of anti-NGO laws, they are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018].
+Further, advocacy-oriented donors -- i.e., those that fund democracy and civil society promotion activities -- reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022].
 However, previous literature has established that individual private donors may not necessarily use the same metrics as official donors (CITE).
-Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the grounds [@easterlywilliamson].
+Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the grounds [@EasterlyWilliamson:2011].
 These anti-NGO laws may signal to private donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and crack down on them.
@@
 As such, legal crackdowns do not occur in isolation.
-Countries are more likely to repress NGOs when organizational features are in tension with government preferences and when organizations receive substantial funding from abroad [@DPR2015].
+Countries are more likely to repress NGOs when organizational features are in tension with government preferences and when organizations receive substantial funding from abroad [@DupuyRonPrakash:2015].
 Therefore, the same organizational characteristic that can increase the likelihood of crackdown can also simultaneously serve as a donor heuristic and influence perceptions of NGO deservingness.
@@
 In each of these hypotheses, we assume that donors will not spend additional effort to research the exact details concerning crackdown, transparency and accountability.
-Instead, donors rely on signals and heuristics about the organiza- tion to shape their preferences and behavior (Szper & Prakash, 2011).
+Instead, donors rely on signals and heuristics about the organization to shape their preferences and behavior [@SzperPrakash:2011].
 
@@
 Unlike state donors, individual and elite donors may not necessarily withdraw or reduce support for NGOs facing harassment abroad.
-This is important because private philanthropy towards organizations working in international affairs continues to grow despite inflation -- from 2021 to 2022, individual giving to nonprofits in international affairs grew by over 10.9% in the US (https://philanthropy.iupui.edu/news-events/news-item/giving-usa:-total-u.s.-charitable-giving-declined-in-2022-to-$499.33-billion-following-two-years-of-record-generosity.html?id=422).
+This is important because private philanthropy towards organizations working in international affairs continues to grow despite inflation -- from 2021 to 2022, individual giving to nonprofits in international affairs grew by over 10.9% in the US [@GivingUSA:2023].
 
@@
 The crackdown is even more challenging for local NGOs in Global South countries, where much government and public support is channeled via service delivery organizations.
-Local groups tackling contentious issues may not be able to raise funds domestically, as publics may prefer donating to service organizations focusing on health, education, and poverty.\footnote{\cite{absar2017will}.} Even local philanthropists may be deterred from giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to poor tax incentives or a fear of retribution.\footnote{\cite{Brechenmacher:2017}; \cite{DPR2015}; \cite{Baoumi:2016}.} Our results highlight the importance of organizational characteristics like transparency and accountability even in an era of closing civic space.
+Local groups tackling contentious issues may not be able to raise funds domestically, as publics may prefer donating to service organizations focusing on health, education, and poverty [@absar2017will].
+Even local philanthropists may be deterred from giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to poor tax incentives or a fear of retribution [@Brechenmacher:2017; @DupuyRonPrakash:2015; @Baoumi:2016].
+Our results highlight the importance of organizational characteristics like transparency and accountability even in an era of closing civic space.
 By finding new ways to communicate about organizational transparency and accountability to potential donors, NGOs can help overcome individual donors' concerns about host governments' criticisms of and crackdown on these groups.

### 2023-10-27 manuscript/manuscript.qmd
Add a few placeholders

@@
 
-# Methods
+# Research design
 
-## Conjoint analysis
+TODO: Cite @ChaudhryHeiss:2022
+
+We use an experiment...
+
+## Conjoint research design
 
@@
 Because we also want to capture the complexity of a respondent's judgment of which NGO they should donate to, if any, we saw potential to expand the application of conjoint analysis within public policy.
+
+TODO: More on conjoint stuff
+
+Before launching the survey experiment, in an effort to avoid issues with p-hacking and cherry-picking results, we preregistered a series of confirmatory hypotehses at the Open Science Framework, and our preregistration protocol is available at URL.
+Appendix contains blah.
+Analysis fully reproducible using code and data available at BLAH
 
@@
 
-## Modeling
+## Modeling and estimation
 
@@
 the combination of human rights issues, financial transparency, government funding, and government crackdown), while the second level of the model uses these fitted preferences to predict the ultimate choice of donation.
+
+Marginal means and marginalization across a balanced reference grid
 
@@
 # Conclusion
+
 Over the last two decades, governments globally have systematically controlled and repressed NGOs using both violent tactics and administrative means over the last three decades -- a phenomenon known as `closing' or `shrinking' civic space.

### 2023-10-30 R/funs_preds.R
Add paper order of features

@@ -35,18 +35,34 @@ make_level_lookup <- function(grid) {
 # Little table for all feature labels in the right order
 make_feature_lookup <- function() {
   feature_lookup <- tribble(
-    ~feature,      ~feature_nice,
-    "feat_org",     "Organizations",
-    "feat_issue",   "Issue areas",
-    "feat_transp",  "Transparency",
-    "feat_acc",     "Accountability",
-    "feat_funding", "Funding sources",
-    "feat_govt",    "Relationship with host government"
-  ) %>% 
-    mutate(amce_var = str_replace(feature, "feat_", "amces_")) %>% 
-    mutate(mm_var = str_replace(feature, "feat_", "mms_")) %>% 
-    mutate(feature_nice = fct_inorder(feature_nice))
-  
+    ~category, ~feature, ~feature_nice,
+    "Comparison", "feat_org", "Organizations",
+    "Comparison", "feat_issue", "Issue areas",
+    "Organizational", "feat_transp", "Transparency",
+    "Organizational", "feat_acc", "Accountability",
+    "Comparison", "feat_funding", "Funding sources",
+    "Structural", "feat_govt", "Relationship with host government"
+  ) %>%
+    mutate(amce_var = str_replace(feature, "feat_", "amces_")) %>%
+    mutate(mm_var = str_replace(feature, "feat_", "mms_")) %>%
+    mutate(
+      feature_nice = fct_inorder(feature_nice),
+      feature_nice_paper = factor(feature_nice,
+        levels = c(
+          # H1a and b
+          "Transparency", "Accountability",
+          # H2
+          "Relationship with host government",
+          # Other things
+          "Organizations", "Issue areas", "Funding sources"
+        )
+      ),
+      category_nice = factor(
+        category,
+        levels = c("Organizational", "Structural", "Comparison")
+      )
+    )
+
   return(feature_lookup)
 }
 

### 2023-10-30 notebook/results-practices.qmd
oops fix this

@@
 h5a_mms <- preds_all %>% 
-  group_by(feat_acc, .draw) %>% 
+  group_by(feat_transp_short, .draw) %>% 
   summarize(avg = mean(.epred))
@@
 h5a_amces <- h5a_mms %>% 
-  group_by(feat_transp) %>% 
-  compare_levels(variable = avg, by = feat_transp, comparison = "control")
+  group_by(feat_transp_short) %>% 
+  compare_levels(variable = avg, by = feat_transp_short, comparison = "control")
 ```
@@
 p_h5a_mms <- h5a_mms %>% 
-  ggplot(aes(x = avg, y = feat_acc, fill = feat_acc)) +
+  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
   stat_halfeye() +

### 2023-10-30 manuscript/manuscript.qmd
Mega updates to results section

--- 2023-10-26 manuscript/manuscript.qmd
@@
 short-title: "Why Donors Donate"
-date: "2023-09-09"
+date: "2023-10-29"
 author:
@@
 library(targets)
+library(tidybayes)
+library(patchwork)
+library(ggforce)
+library(scales)
+library(glue)
+library(gt)
+library(gtExtras)
+library(here)
 
 # Targets stuff
-tar_config_set(store = here::here('_targets'),
-               script = here::here('_targets.R'))
+tar_config_set(
+  store = here("_targets"),
+  script = here("_targets.R")
+)
+
+tar_load(c(grid_treatment_only, level_lookup, feature_lookup))
+preds_all <- tar_read(preds_conditional_treatment_only)
 
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
+
+theme_set(theme_ngo())
 ```
@@
 Repressive governments have repressed these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs.
-(CITE) Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" (CITE) and data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in nearly 60% of countries—111 in total (UPDATE FROM NEW CIVICUS DATA).
-These attacks—most of which have been implemented through anti-NGO laws—have adversely affected the ability of both domestic and international NGOs to operate and raise funds.
-Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official aid donors channel fewer funds to contentious issues and instead choose to fund "tame" causes [@ChaudhryHeiss:2018; @Bush:2015; @HERROLD; @SPRINGMAN].
+(CITE) Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" (CITE) and data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in nearly 60% of countries---111 in total (UPDATE FROM NEW CIVICUS DATA).
+These attacks---most of which have been implemented through anti-NGO laws---have adversely affected the ability of both domestic and international NGOs to operate and raise funds.
+Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official aid donors channel fewer funds to contentious issues and instead choose to fund "tame" causes [@ChaudhryHeiss:2018; @Bush:2015; @Herrold:2020; @RightSpringmanWibbels:2022].
 In response to this dramatic shift in the NGO funding landscape, international NGOs (INGOs) have increasingly turned to foreign individual donors to offset the loss of funding from government and foundation sources [@BanksHulmeEdwards:2015].
 
-The amount of private foreign aid is not insignificant—from 2000–2010, private giving by U.S.
+The amount of private foreign aid is not insignificant---from 2000--2010, private giving by U.S.
 entities towards international causes doubled in real terms [@DesaiKharas:2018, 505].
@@
 Individuals have different preferences and rely on signals of effectiveness that differ from the benchmarks that large donor agencies rely on, including financial transparency and accountability.
-While INGOs have control over these organizational-level factors that motivate donations, the political environment in the host countries INGOs work in—including the global crackdown on civil society that is causing many organizations to seek out private funding in the first place—is a structural factor that INGOs can rarely influence on their own.
+While INGOs have control over these organizational-level factors that motivate donations, the political environment in the host countries INGOs work in---including the global crackdown on civil society that is causing many organizations to seek out private funding in the first place---is a structural factor that INGOs can rarely influence on their own.
 How do organizational elements of private donor decision-making interact with broader structural limits on INGO fundraising?
@@
 While recent research on private foreign aid has examined funding decisions of donor NGOs and foundations[^1], we know less about the funding choices of the individuals responsible for much of these private aid flows [@DesaiKharas:2018].
-The systematic study of private foreign aid is still in its infancy—there is an absence of expansive and high quality data [@GreenhillPrizzonRogerson:2013], and most research has been restricted to elite, high net-worth donors [@USTrust2014].
+The systematic study of private foreign aid is still in its infancy---there is an absence of expansive and high quality data [@GreenhillPrizzonRogerson:2013], and most research has been restricted to elite, high net-worth donors [@USTrust2014].
 Our research makes a significant contribution to research on individual giving and indicates the promise and limits of different framing appeals on individual donor preferences.
+
+[^1]: On aid from world's largest NGOs, see @Koch:2009, on private aid flows from NGOs based in the US, see @ButheMajorMello-e-Souza:2012.
 
@@
 
-[^1]: On aid from world's largest NGOs, see @Koch:2009, on private aid flows from NGOs based in the US, see @ButheMajorMello-e-Souza:2012.
-
 # What determines individual donor behavior?
@@
 Substantial research on NGOs has looked at the motivation of individual donors, including altruism, reputational benefits, and alignment with personal values [@BilodeauSlivinski:1997; @Wiepking:2010; @BekkersWiepking:2011].
-However, this research has overwhelmingly looked at individual donor behavior and motivation for giving to local—rather than international—causes (CITE -2).
+However, this research has overwhelmingly looked at individual donor behavior and motivation for giving to local---rather than international---causes (CITE -2).
 Understanding the latter is important as philanthropy to international causes can be harder to motivate because the number of recipients is larger and further removed from the donor [@CasaleBaumann:2015, 100].
 Further, as @MicklewrightSchnepf:2009 point out, motivations for donating to ongoing international causes differ from donating money to natural disasters or emergency international causes.
-Under ordinary circumstances, “donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad” [@Tremblay-BoirePrakash:2017, 644].
+Under ordinary circumstances, "donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad" [@Tremblay-BoirePrakash:2017, 644].
 However, we lack adequate data and theory regarding philanthropy towards INGOs.
@@
 Nonprofits fundraising internationally may therefore rely on framing to control perceptions.
-Below, we theorize the effect of different frames surrounding a country’s legal environment and nonprofit organizational characteristics on individual donor preferences.
+Below, we theorize the effect of different frames surrounding a country's legal environment and nonprofit organizational characteristics on individual donor preferences.
+
+TODO: Cite @ChaudhryHeiss:2021 somewhere
 
@@
 
-In theory, donors should scrutinize each aspect of an NGO’s organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017].
+In theory, donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017].
 Instead, individuals rely on heuristics to simplify their decision-making.
@@
 In addition to organizational factors discussed above, political contexts in NGO host countries, especially their environments for civil society organizations, can also influence donor preferences for donating to foreign NGOs.
-A global cascade of anti-NGO laws in recent decades has created barriers to entry, funding, and advocacy for civic organizations [@GlasiusSchalkDeLange:2020; @Schmidt-et-al; @Chaudhry:2022; @Heiss:2017; @DupuyRonPrakash:2015].
-As a result, NGOs must spend more time, effort, and resources to ensure their survival -- at the expense of pursuing their missions.
+A global cascade of anti-NGO laws in recent decades has created barriers to entry, funding, and advocacy for civic organizations [@GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022; @Heiss:2017; @DupuyRonPrakash:2015].
+As a result, NGOs must spend more time, effort, and resources to ensure their survival—at the expense of pursuing their missions.
 Some NGOs have adapted to their repressive environments by recreating their organizations and changing their mission to avoid directly confronting the government.
@@
 In response to the passage of these laws, scholars have found that while multilateral donors do not reduce aid following the passage of anti-NGO laws, they are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018].
-Further, advocacy-oriented donors -- i.e., those that fund democracy and civil society promotion activities -- reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022].
+Further, advocacy-oriented donors---i.e., those that fund democracy and civil society promotion activities---reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022].
 However, previous literature has established that individual private donors may not necessarily use the same metrics as official donors (CITE).
@@
 
->**H~2~**: If NGOs face legal crackdowns abroad, then individual donors will be more likely to donate to them.
+> **H~2~**: If NGOs face legal crackdowns abroad, then individual donors will be more likely to donate to them.
 
@@
 
-```
-![Causal diagram showing causes of donor behavior.
-D = donation to NGO (outcome); G = NGO-government relationship, I = NGO issue area, F = NGO funding source, O = NGO organizational and managerial practices.](output/figures/causal-path.pdf){#fig:big-dag}
-```
-
-Identifying the causal link between structural factors and donor behavior is more difficult than measuring the link between organizational factors and donor behavior, however, because (1) NGOs have less direct control over their political environments, and (2) organizational characteristics like financial transparency and accountability can sour the NGO-government relationship -- governments may be more likely to target NGOs that lack financial transparency and accountability.
-@fig:big-dag helps disentangle this complex relationship.
-Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**).
-Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both transparency and accountability.
-As such, legal crackdowns do not occur in isolation.
+Identifying the causal link between structural factors and donor behavior is more difficult than measuring the link between organizational factors and donor behavior, however, because (1) NGOs have less direct control over their political environments, and (2) organizational characteristics like financial transparency and accountability can sour the NGO-government relationship---governments may be more likely to target NGOs that lack financial transparency and accountability.
+Legal restrictions do not occur in isolation.
 Countries are more likely to repress NGOs when organizational features are in tension with government preferences and when organizations receive substantial funding from abroad [@DupuyRonPrakash:2015].
@@
 
-Since we are running a conjoint experiment, the interactions between the main treatment variables described above is simply an exploratory analysis.
+As a result, we are uncertain about the interaction between transparency, accountability, and host country legal environment.
+We suspect that there is a relationship, but we are uncertain about the exact direction or magnitude.
+Accordingly, we do not propose any confirmatory hypothesis testing, but instead explore the interaction between our primary treatment variables to inform future research on the interplay between organizational and structural dynamics.
+
 Importantly, when testing these hypotheses, we do not assume that individual donors have perfect knowledge about an NGO or the country an NGO operates in.
-Moreover, the average donor will not know exactly what “crackdown” entails for any given organization (i.e., does it mean an NGO was expelled, or that its assets were frozen, or that it received a fine?).
+Moreover, the average donor will not know exactly what "crackdown" entails for any given organization (i.e., does it mean an NGO was expelled, or that its assets were frozen, or that it received a fine?).
 For the sake of this experiment, this ambiguity is not a central concern as the heuristics we explore here are explicitly simplified short- cuts to donor information-gathering.
@@
 
-# Methods
-
-## Conjoint analysis
+# Research design
 
@@
 To address this, we use conjoint analysis to simultaneously test individual donor preferences in the face of both organizational and structural heuristics.
-Conjoint analysis is a staple in marketing research for evaluating which product attributes are most important to consumers.
-It has been extensively used in new product development and product line optimization.
 Conjoint analysis is generally applicable whenever individuals face complex, multi-dimensional tradeoffs that make it difficult (or even impossible) to explicitly elicit preferences.
-In the context of this project, we use conjoint techniques to evaluate donor rather than consumer preferences as they choose NGOs which to donate to based on both organizational and structural heuristics.
+Conjoint designs have been used extensively in political science to study complex preferences for elections, laws, public policy, and public opinion [@HainmuellerHopkinsYamamoto:2014; @Mummolo:2016; @KertzerRenshonYarhi-Milo:2021; @BansakHainmuellerHopkins:2021].
+@KnudsenJohannesson:2019 argue that research related to respondent opinions requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility.
+Because we also want to capture the complexity of a respondent's judgment of philanthropic preferences, we use a conjoint design to evaluate the effect of organizational and structural heuristics on philanthropic preferences.
 
-Conjoint analysis has been widely used within social sciences to explain causality and has recently begun to be used in political and public policy fields.
-@Helfer:2016 and @Mummolo:2016 both used conjoint analysis to assess perceptions of political communications.
-@KnudsenJohannesson:2019 argue that political communication research requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility.
-Because we also want to capture the complexity of a respondent's judgment of which NGO they should donate to, if any, we saw potential to expand the application of conjoint analysis within public policy.
+A conjoint research design also allows us to calculate treatment effects even if respondents do not see every combination of organization attributes, and correspondingly provides a substantial increase in statistical power.
+In standard factorial experimental designs, every combination of treatment attributes would need to be shown to some number of participants would ordinarily need to be shown all possible combinations of experimental attributes.
+In our experiment, we presented respondents with six possible treatments with varying counts of attributes for each treatment, yielding 576 possible unique combinations of features.
+Even with respondents answering twelve iterations of the experiment, not every combination was seen.
+However, as long as all the possible organizational attributes are well randomized and there are no systematic biases toward specific options (i.e.
+more respondents select the first option because it is the first) or toward earlier iterations of attribute choices (i.e.
+respondents are more careful and attentive for the first hypothetical organization than the last), we can pool all observations together for specific attributes of interest while marginalizing across all other attributes [@KertzerRenshonYarhi-Milo:2021].
+This allows us to (1) estimate the effect of each experimental treatment even if some unique combinations of attributes were unseen, and (2) use a much smaller sample size than would be required in a more traditional factorial design.
+
+While the ability to select key attributes and marginalize over others provides us with analytic flexibility, it also raises possible issues with multiple comparisons, *p*-hacking, and selective cherry-picking [@BansakHainmuellerHopkins:2021].
+As such, before launching the survey experiment, we preregistered a set of confirmatory and exploratory hypotheses at the Open Science Framework.
+Our preregistration protocol is available at `ANONYMIZED_URL` and in Appendix TODO, and our data and reproducible code is available at `ANONYMIZED_URL`.
 
@@
 
-After collecting baseline information on respondent demographics and attitudes toward charity and voluntarism, we presented respondents with four randomly selected international nonprofit organizations with four randomly assigned features.^[See the appendix for a copy of the survey.] We included organizations that are associated with a range of contentious and noncontentious issues: Amnesty International, Greenpeace, Oxfam, and the International Committee of the Red Cross.
-We chose these 4 organizations as the represent the core sectors of activity according to Charity Navigator (Environment, Human Rights, Humanitarian Relief, and Development).
-We then displayed various combinations of features, including one of four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), one of two organizational practices (financial transparency and third-party accountability audits), one of three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and one of three relationships with host governments (friendly, criticized by the government, and under government crackdown).
-We presented twelve sets of four hypothetical combinations of organizational features, and because our partial fractional factorial design resulted in 288 (4 × 4 × 2 × 3 × 3) possible combinations of organizations and features, no single respondent was offered every combination.
-
-Survey participants were recruited through Centiment, a commercial online provider of high quality non-probability opt-in survey panels.
+We recruited survey participants through Centiment, a commercial online provider of high quality non-probability opt-in survey panels.
 Centiment ensures panel quality by actively recruiting representative samples of the US population and provides monetary incentives and rewards to participants.
@@
 If a participant responded that they give once every few years or never, they were disqualified from the study.
-We received 1,016 viable responses, which is a sufficient size for model estimation.
-A sample size of at least 500 respondents is typical for estimating a hierarchical Bayesian model based on conjoint data.
-We doubled this amount because we are interested in analyzing subpopulations of respondents, which requires a larger sample.
+We also included an attention check question early in the survey and removed respondents who failed the question.
+Importantly, these screening questions were presented *prior to* the experimental manipulation to avoid post-treatment bias [@MontgomeryNyhanTorres:2018].
 
-```
-output/tables/tbl-sample-details.md
-```
-
+Following screening, we received 1,016 viable responses.
 @tbl:sample-details provides a detailed breakdown of the individual characteristics of our sample.
-In general, respondents were well balanced across genders and tended to be older than the national median age of 36—less than 20% of respondents were under 36 years old.
+In general, respondents were well balanced across genders and tended to be older than the national median age of 36---less than 20% of respondents were under 36 years old.
 The majority of respondents (45%) had never been married, while nearly 40% were married, with 10% divorced.
@@
 The majority (58%) earned less than the national median income (\$61,372).
-
 Since we limited the sample to people who frequently donate to charities, most respondents have a favorable opinion of nonprofits and charities, with more than half reporting a 5 or greater (on a 7-point scale) of trust in charities.
 Nearly 90% of respondents indicated that it is important to trust charities, rating importance of trust at least a 3 on a 7-point scale.
-The majority of respondents volunteer at least once a year, donate to charity at least once a year, and give between \$1–\$999 annually.
+The majority of respondents volunteer at least once a year, donate to charity at least once a year, and give between \$1--\$999 annually.
 Most rarely attend church, but feel that religion is important.
 Respondents are also engaged civically (three quarters voted in the last election) and follow national news closely (70% follow the news daily).
-Respondents are fairly balanced ideologically, with the majority reporting a 3, 4, or 5 on a 7-point scale of liberal–conservative political ideology.
+Respondents are fairly balanced ideologically, with the majority reporting a 3, 4, or 5 on a 7-point scale of liberal--conservative political ideology.
 
-## Modeling
+## Experimental design
+
+After collecting baseline information on respondent demographics and attitudes toward charity and voluntarism, we presented respondents with three randomly generated hypothetical international nonprofit organizations with six randomly assigned features.
+In this paper, we hypothesize and empirically test the effect of financial transparency, accountability, and host country relationship on the likelihood of donations.
+In our experiment, we included a few additional treatments to aid with the interpretation and comparison of effect sizes for our treatments of interest.
+In total, we varied six different organizational and structural attributes that might have an effect on donor behavior: (1) organization name and branding, (2) organization issue area, (3) financial transparency practices, (4) accountability practices, (5) funding sources, and (6) relationship with host government (see @tbl-design).
+
+```{css, echo=FALSE}
+/* Remove padding on lists in tables */
+.gt_table ul, .gt_table ol {
+  padding-left: 1rem;
+}
+```
+
+```{r tbl-design, include=TRUE}
+#| tbl-cap: "All experimental features and levels included in the conjoint experiment"
+transparency <- c("Doesn't engage in transparency", "Engages in transparency")
+accountability <- c("Doesn't engage in accountability", "Engages in accountability")
+govt <- c("Friendly relationship with government", "Criticized by government", "Under government crackdown")
+orgs <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
+issues <- c("Emergency response", "Environment", "Human rights", "Refugee relief")
+funding <- c("Funded primarily by many small private donations", "Funded primarily by a handful of wealthy private donors", "Funded primarily by government grants")
+
+tribble(
+  ~type, ~feature, ~levels,
+  "H~1a~", "Financial transparency", paste0(paste0("- ", transparency), collapse = "\n"),
+  "H~1b~", "Accountability", paste0(paste0("- ", accountability), collapse = "\n"),
+  "H~2~", "Relationship with host government", paste0(paste0("- ", govt), collapse = "\n"),
+  "Comparison", "Organization", paste0(paste0("- ", orgs), collapse = "\n"),
+  "Comparison", "Issue area", paste0(paste0("- ", issues), collapse = "\n"),
+  "Comparison", "Funding source", paste0(paste0("- ", funding), collapse = "\n")
+) %>% 
+  gt() %>% 
+  cols_label(feature = "Feature/Attribute", levels = "Levels", type = "Purpose") %>% 
+  fmt_markdown(columns = c(type, levels)) %>% 
+  tab_style(
+    style = cell_text(v_align = "top"),
+    locations = cells_body()
+  ) %>% 
+  opts_theme()
+```
+
+Charity Navigator—a large database of U.S.
+nonprofit financial information—categorizes its nonprofit organizations into four core sectors: humanitarian relief, human rights, development, and the environment.
+Accordingly, we used four nonprofits that are stereotypical for each issue: the International Committee of the Red Cross (humanitarian relief), Amnesty International (human rights), Oxfam (development), and Greenpeace (environment).
+We also varied several other features, including four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), two organizational practices (financial transparency and third-party accountability audits), three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and three relationships with host governments (friendly, criticized by the government, and under government crackdown).
+
+After presenting respondents with three organizations, we asked them which of the three they would be willing to donate to, along with an option for no selection (see @tbl-example for an example).
+We then repeated the process eleven more times for a total of twelve randomized iterations of hypothetical combinations of attributes, resulting in 12,192 completed experimental tasks (12 iterations × 1,016 respondents).
+
+```{r tbl-example, include=TRUE}
+#| tbl-cap: "Example possible experimental task, with three randomized combinations of organizational attributes"
+withr::with_seed(12345, {
+  tribble(
+    ~Attribute, ~`Option 1`, ~`Option 2`, ~`Option 3`, ~None,
+    "Organization", sample(orgs, 1), sample(orgs, 1), sample(orgs, 1), "—",
+    "Issue area", sample(issues, 1), sample(issues, 1), sample(issues, 1), "—",
+    "Transparency", sample(transparency, 1), sample(transparency, 1), sample(transparency, 1), "—",
+    "Accountability", sample(accountability, 1), sample(accountability, 1), sample(accountability, 1), "—",
+    "Funding sources", sample(funding, 1), sample(funding, 1), sample(funding, 1), "—",
+    "Relationship with host government", sample(govt, 1), sample(govt, 1), sample(govt, 1), "—"
+  ) %>%
+    gt() %>%
+    cols_align(align = "center", columns = everything()) %>%
+    cols_align(align = "left", columns = Attribute) %>%
+    cols_width(everything() ~ pct(20)) %>%
+    tab_style(
+      style = cell_text(v_align = "top"),
+      locations = cells_body()
+    ) %>%
+    tab_style(
+      style = cell_text(weight = "bold"),
+      location = cells_body(columns = Attribute)
+    ) %>%
+    opts_theme()
+})
+```
+
+## Modeling and estimands
+
+We analyze the results using a multilevel Bayesian multinomial model.
+Our experimental data has a natural hierarchical structure, with 3 questions nested inside 12 separate experimental tasks, nested inside each of the 1,016 respondents, which lends itself to multilevel modeling.
+Relying on standard OLS regression can discard useful information about (1) the relationships and covariance between the different combinations of feature levels offered to respondents, and (2) individual-specific differences in how respondents react to different feature levels [@JensenMarbleScheve:2021].
+Since it was impossible for every respondent to see every possible all 12,000 experimental tasks, multilevel modeling allows us to pool together information about respondents with similar characteristics facing similar sets of choices.
+Moreover, using random respondent effects provides natural regularization and shrinkage for our estimates—experimental tasks that happened to appear more often due to chance will be accounted for and not influence the overall causal effect.
 
@@
 \begin{aligned}
-\beta &\sim \operatorname{Multivariate} \mathcal{N}(Z \Gamma, \xi) \\
-y &\sim \operatorname{Multinomial\ logit}(X \beta, \varepsilon)
+&\ \mathrlap{\textbf{Multinomial probability of selection of choice}_i \textbf{ in respondent}_j} \\
+\text{Choice}_{i_j} \sim&\ \mathrlap{\operatorname{Categorical}(\{\mu_{1,i_j}, \mu_{2,i_j}, \mu_{3,i_j}\})} \\[10pt]
+&\ \mathrlap{\textbf{Model for probability of each option}} \\
+\{\mu_{1,i_j}, \mu_{2,i_j}, \mu_{3,i_j}\} =&\ 
+  \mathrlap{\begin{aligned}[t]
+  & (\beta_0 + b_{0_j}) + \beta_{1, 2, 3} \text{Organization}_{i_j} + \beta_{4, 5, 6} \text{Issue area}_{i_j} + \\
+  &\ \beta_7 \text{Transparency}_{i_j} + \beta_8 \text{Accountability}_{i_j} + \\
+  &\ \beta_{9, 10} \text{Funding source}_{i_j} + \beta_{11, 12} \text{Government relationship}_{i_j}
+  \end{aligned}}\\[5pt]
+b_{0_j} \sim&\ \mathcal{N}(0, \sigma_0) && \text{Respondent-specific offsets from global probability}\\[10pt]
+&\ \textbf{Priors} \\
+\beta_{0 \dots 12} \sim&\ \mathcal{N} (0, 3) && \text{Prior for choice-level intercept and coefficients} \\
+\sigma_0 \sim&\ \operatorname{Exponential}(1) && \text{Prior for between-respondent variability}
 \end{aligned}
@@
 
-where $y$ = which alternative the respondent chooses to donate to, $X$ = design matrix of attribute levels (i.e.
-organizations, issue areas, organizational practices, funding sources, and government relations), $\beta$ = latent individual preferences for the attribute levels, $Z$ = matrix of individual-level covariates (i.e.
-demographics, political knowledge, attitudes towards charity, etc.), $\Gamma$ = matrix of coefficients mapping individual-level covariates onto the latent individual-level preferences, and $\varepsilon$ and $\xi$ = errors.
-Simply put, the first level of the model predicts individual donor preferences for various combinations of features (e.g.
-the combination of human rights issues, financial transparency, government funding, and government crackdown), while the second level of the model uses these fitted preferences to predict the ultimate choice of donation.
+Importantly, we do not include any respondent-level covariates beyond the treatment variables.
+Because this is an experimental design, any statistical confounding is accounted for during the process of randomization and covariates should have no systematic effect on treatment effects.
+We do not work with the raw results of the model directly (though a complete table of results is included in Appendix TODO).
+Given the conjoint design, we instead create a complete balanced grid of all 576 combinations of feature levels (4 organizations × 4 issues × 2 transparency × 2 accountability × 3 funding × 3 government relationships) and use the model to calculate predicted probabilities of choice selection for each row of possible treatment values.
+We then collapse this set of predicted probabilities into estimated marginal means (EMMs) for specific features of interested while marginalizing or averaging over all other predicted variables.
+To calculate the causal effect of a treatment, we find the average marginal component effect (AMCE), which is equivalent to the difference in estimated marginal means for specific feature levels.
+For example, when estimating the marginal means of the transparency treatment, we find the average predicted probability across the 288 rows of the reference grid where transparency is true and across the 288 rows where transparency is false—the difference between these two estimated marginal means is the AMCE, or the causal effect of the treatment, on the probability scale.
 
-We use median values from the posterior distributions of the model as point estimates and calculate credible intervals using the 95% highest posterior density.
-We report the results primarily through density plots that show both the posterior distributions and 95% credible intervals.
-Inference based on Bayesian analysis differs from more common frequentist null hypothesis testing—as such, we declare an effect statistically significant if the posterior probability of being different from zero (or from other comparison values) exceeds 0.95.
+# Results and discussion
 
-# Results
+We present the posterior distributions of the marginal means and AMCEs for each of our experimental conditions in @fig-all-results and provide posterior medians and credible intervals in @tbl-all-results in the appendix.
+Because AMCEs are relative statements (i.e.
+contrasts between one feature level and a reference level), we try to use logical reference levels: for binary treatments like transparency and accountability, we calculate the difference between false and true levels; for ordered treatments like host country relationship, we calculate the differences between different levels of crackdown compared to no crackdown.
+To avoid imposing an artificial order on other unordered treatment variables, we report both marginal means and AMCEs [@LeeperHoboltTilley:2020].
 
-## Effect of organizational and structural features on the likelihood of selection
+```{r calc-mms}
+mms_org <- preds_all %>% 
+  group_by(feat_org, .draw) %>% 
+  summarize(avg = mean(.epred))
 
-We hypothesized that the interaction of structural, organizational, and individual donor characteristics would have varying significant effects on donor behavior, and our results bear this out.
-@fig:probs-org shows the baseline probabilities of selecting an organization to donate to based on organization.
-Even without varying issue area, organizational practices, funding sources, and government relationships, respondents were most likely to donate to the Red Cross, with an 86% probability of being selected when given the choice.
-Oxfam had the lowest probability of being selected (65%), likely because it has less name recognition in the United States.
-Amnesty International and Greenpeace were slightly more probable (69% and 72%, respectively).
+mms_issue <- preds_all %>% 
+  group_by(feat_issue, .draw) %>% 
+  summarize(avg = mean(.epred))
 
-```
-![Baseline probability of selecting an organization for donation](output/figures/probs-org.pdf){#fig:probs-org}
+mms_transp <- preds_all %>% 
+  group_by(feat_transp, .draw) %>% 
+  summarize(avg = mean(.epred))
+
+mms_acc <- preds_all %>% 
+  group_by(feat_acc, .draw) %>% 
+  summarize(avg = mean(.epred))
+
+mms_funding <- preds_all %>% 
+  group_by(feat_funding, .draw) %>% 
+  summarize(avg = mean(.epred))
+
+mms_govt <- preds_all %>% 
+  group_by(feat_govt, .draw) %>% 
+  summarize(avg = mean(.epred))
 ```
 
-@fig:first-hypotheses presents the results for our first four hypotheses, which deal with the effect of organizational and structural factors on individual decisions to donate.
-The main coefficient parameter $\theta$ is shown as an odds ratio ($e^\theta$) to demonstrate changes in likelihood.
-Each conjoint feature omits one level as the base case.
+```{r calc-amces}
+amces_org <- mms_org %>% 
+  group_by(feat_org) %>% 
+  compare_levels(variable = avg, by = feat_org, comparison = "control") %>% 
+  ungroup() %>% 
+    separate_wider_delim(
+    feat_org,
+    delim = " - ", 
+    names = c("feature_level", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feature_level = unique(.$reference_level))
 
-```
-![Changes in the likelihood of selecting an organization for donation across different levels within conjoint features.
-Values shown as odds ratios; red line at 1 shows point of no change in likelihood](output/figures/results-h1-4.pdf){#fig:first-hypotheses}
+amces_issue <- mms_issue %>% 
+  group_by(feat_issue) %>% 
+  compare_levels(variable = avg, by = feat_issue, comparison = "control") %>% 
+  ungroup() %>% 
+    separate_wider_delim(
+    feat_issue,
+    delim = " - ", 
+    names = c("feature_level", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feature_level = unique(.$reference_level))
+
+amces_transp <- mms_transp %>% 
+  group_by(feat_transp) %>% 
+  compare_levels(variable = avg, by = feat_transp, comparison = "control") %>% 
+  ungroup() %>% 
+    separate_wider_delim(
+    feat_transp,
+    delim = " - ", 
+    names = c("feature_level", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feature_level = unique(.$reference_level))
+
+amces_acc <- mms_acc %>% 
+  group_by(feat_acc) %>% 
+  compare_levels(variable = avg, by = feat_acc, comparison = "control") %>% 
+  ungroup() %>% 
+    separate_wider_delim(
+    feat_acc,
+    delim = " - ", 
+    names = c("feature_level", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feature_level = unique(.$reference_level))
+
+amces_funding <- mms_funding %>% 
+  group_by(feat_funding) %>% 
+  compare_levels(variable = avg, by = feat_funding, comparison = "control") %>% 
+  ungroup() %>% 
+    separate_wider_delim(
+    feat_funding,
+    delim = " - ", 
+    names = c("feature_level", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feature_level = unique(.$reference_level))
+
+amces_govt <- mms_govt %>% 
+  group_by(feat_govt) %>% 
+  compare_levels(variable = avg, by = feat_govt, comparison = "control") %>% 
+  ungroup() %>% 
+    separate_wider_delim(
+    feat_govt,
+    delim = " - ", 
+    names = c("feature_level", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feature_level = unique(.$reference_level))
+
+amces_all <- bind_rows(
+  lst(amces_org, amces_issue, amces_transp, amces_acc, amces_funding, amces_govt),
+  .id = "amce_var"
+) %>%
+  left_join(select(feature_lookup, amce_var, feature_nice_paper), by = join_by(amce_var)) %>%
+  left_join(
+    select(level_lookup, contains("_level")), 
+    by = join_by(feature_level)
+  )
 ```
 
-In our first set of hypotheses, we predicted that donors would be more likely to donate to organizations that engage in organizational practices that highlight transparency and accountability.
-As seen in the top left panel of @fig:first-hypotheses, donors were roughly three times more likely to select an organization that either voluntarily undergoes external audits for the sake of accountability or voluntarily discloses financial details.
-There is no significant difference between these two practices.
-Based on this evidence, donors rely heavily on heuristics of managerial best practices and reward INGOs for being transparent and accountable.
+```{r fig-all-results, include=TRUE}
+#| fig-width: 12
+#| fig-height: 6
+#| out-width: "100%"
+#| fig-cap: "Estimated marginal means and average marginal component effects for conjoint experiment results"
+#| column: page
+mms_all <- bind_rows(
+  lst(
+    mms_org = rename(mms_org, feature_level = feat_org), 
+    mms_issue = rename(mms_issue, feature_level = feat_issue), 
+    mms_transp = rename(mms_transp, feature_level = feat_transp), 
+    mms_acc = rename(mms_acc, feature_level = feat_acc), 
+    mms_funding = rename(mms_funding, feature_level = feat_funding), 
+    mms_govt = rename(mms_govt, feature_level = feat_govt)
+  ),
+  .id = "mm_var"
+) %>%
+  left_join(select(feature_lookup, mm_var, feature_nice_paper), by = join_by(mm_var)) %>%
+  left_join(
+    select(level_lookup, contains("_level")), 
+    by = join_by(feature_level)
+  )
 
-According to our second hypothesis, donors should be more likely to donate to organizations working on less contentious issues like emergency response and refugee relief.
-A heuristic of deservingness should drive donor decisions, with donors leaning more towards causes that alleviate human suffering.
-The results from the experiment provide mixed results for this hypothesis.
-As seen in the top right panel of @fig:first-hypotheses, an emergency response frame has the most positive influence on donor decisions—since it is the reference group, all other issues decrease the likelihood of donation.
-Interestingly, human rights advocacy is the next most influential issue—respondents were 15% less likely to donate (compared to emergency response) when presented with human rights issues.
-Respondents are 36% less likely to donate when presented with an organization working on environmental issues, and a surprising 44% less likely when shown an organization working on refugee relief.
-There is no significant difference between refugee relief and environmental issues; both are significantly different from human rights, and human rights is significantly different from 1.
-While the preeminence of refugee relief follows our hypothesis, the other issues diverge markedly from our expectations.
-Human rights and environmental issues do decrease the likelihood of donation compared to emergency relief, as expected, but refugee issues see the most negative change in likelihood, contrary to the idea that tamer NGOs working on issues of human suffering will receive more attention from donors.
+p1 <- ggplot(
+  mms_all,
+  aes(x = avg, y = feature_short_level, fill = feature_nice_paper)
+) +
+  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
+  stat_halfeye(normalize = "groups") +
+  guides(fill = "none") +
+  facet_col(facets = "feature_nice_paper", scales = "free_y", space = "free") +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(values = clrs$prism[1:6]) +
+  labs(
+    x = "Marginal means of probabilities",
+    y = NULL,
+    title = "Posterior marginal means"
+  )
 
-The bottom left panel of @fig:first-hypotheses shows the results for our third hypothesis that an NGO's funding sources matter for donors.
-We posited that donors use the fact that an INGO receives many small donations as a heuristic of deservingness, providing individual donors with a greater chance that their money will have a positive impact on an NGO's programs.
-Our results confirm this: compared to the reference level of an INGO that receives many small donations, donors are 22% less likely to donate to an organization that receives its funding primarily from government donors, and 31% less likely to donate to one that receives the bulk of its funding from a handful of wealthy donors.
-There is no significant difference between the change in likelihood across government grants and wealthy donors, but both are significantly different from 1.
+p2 <- ggplot(
+  amces_all,
+  aes(x = avg, y = feature_short_level, fill = feature_nice_paper)
+) +
+  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
+  stat_halfeye(normalize = "groups") +  # Make the heights of the distributions equal within each facet
+  guides(fill = "none") +
+  facet_col(facets = "feature_nice_paper", scales = "free_y", space = "free") +
+  scale_x_continuous(labels = label_pp) +
+  scale_fill_manual(values = clrs$prism[1:6]) +
+  labs(
+    x = "Percentage point change in probability of choice selection",
+    y = NULL,
+    title = "Posterior AMCEs"
+  )
 
-These first three hypotheses all deal with organizational heuristics, or practices and attributes that an NGO has more direct control over.
-INGOs have less control over structural factors, such as the political environments of their host countries, but donors will likely still use these factors as signals of deservingness.
-The bottom right panel of @fig:first-hypotheses demonstrates that donors likely punish organizations that fall afoul of their host countries.
-Compared to an INGO with a friendly relationship with its host government, donors are 49% less likely to choose to donate to an organization that is criticized by its host government, and a sizable 64% less likely if the organization is under government crackdown (there is a significant difference between criticized by government and under government crackdown, and both are significantly different from 1).
-Contrary to expectations, donors appear to punish INGOs that face legal difficulties abroad.
-
-## Interaction between organizational and structural features and individual characteristics
-
-In our final set of hypotheses, we are interested in how individual-level donor characteristics interact with structural and organizational heuristics.
-In particular, we are interested in finding which kinds of donors are more or less likely to consider an INGO's managerial practices, issue area, funding sources, and host country politics when deciding to donate.
-
-**NOTE**: This section is still in progress—disentangling all the effects here is complex, which is good!
-Looking at the different interactions between conjoint features and attributes and individual-level covariates is one of the most powerful contributions of conjoint analysis, but isolating the most important effects (given that there are nearly 300 different combinations of just the organizational attributes, which then combine with dozens of possible covariate combinations), is difficult.
-We're still working on finding the best way to communicate this complexity graphically.
-
-In the meantime, @fig:second-level shows one attempt at this, displaying a heatmap of the significance of individual-level characteristics in the second level of a model that uses covariates related to attitudes toward charity and voluntarism.
-We find that personal experiences with and attitudes toward charity influence have heterogenous effects on the salience of different organizational and structural characteristics.
-For instance, believing that it is important to trust charities makes individuals less likely that government grants and rich donors play a role in the decision to donate, perhaps due to the perception that an organization receiving many small donations (the reference level) is more trustworthy.
-Similarly, the importance of trusting charities makes it more likely that accountability and transparency will influence the decision to donate.
-Notably, few of the covariates related to charity and voluntarism interact with structural attributes in any consistent way, other than personal involvement in activism—those with a history of activism are more likely to select an organization that is either facing government criticism or government crackdown.
-
-```
-![Heatmap showing significance of various covariates across conjoint attributes and levels](output/figures/q2-heatmap.pdf){#fig:second-level}
+p1 | p2
 ```
 
+We use median values of the posterior marginal means and AMCEs as point estimates and calculate credible intervals using a 95% equal-tailed quantile interval.
+However, we are generally less concerned with the exact point estimates of our causal effects and instead focus on the direction and relative magnitude of their posterior distributions.
+For inference, we calculate the probability of direction ($p_d$), or the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median.
+
+## Effect of general things (lol needs better heading)
+
+To contextualize the magnitude of the causal effects for our hypotheses of interest, we begin our analysis with a brief overview of the effects of organizational characteristics that nonprofits have less direct control over: their brand name, their issue area, and their funding sources.
+Name brand recognition appears to be a powerful heuristic for donor decision making.
+Respondents were substantially more likely to prefer an organization when it was identified as the Red Cross, with an average marginal mean of 35%—ten percentage points higher than the 25% probability that would be expected if respondents selected an organization at random.
+When using Amnesty International as the reference category, the AMCE for the Red Cross is 12 percentage points ($p_d$ = 1).
+Other organizations see much smaller marginal means and AMCEs.
+Compared to Amnesty International, Greenpeace causes a small 2.x percentage point increase ($p_d$ = X) and Oxfam causes a small 3.x percentage point decrease ($p_d$ = X) in the probability of selecting an organization.
+The Red Cross brand name heuristic is actually the strongest of all the experimental treatments and features, signifying the organization's brand power and goodwill among potential donors.
+
+The issue area an organization works on also serves as a heuristic for donors.
+As seen in the marginal means in @fig-all-results, organizations focused on human rights and emergency response are more popular than those working on issues related to the environment or refugee relief.
+When using emergency response (the most popular issue) as the reference category for AMCEs, working with human rights causes a 3 percentage point decrease ($p_d$ = X), while environmental and refugee relief issues see a 4 and 6 percentage point decrease, respectively ($p_d$).
+To put these effects in context, these effects are smaller than the the Red Cross effect and a little larger than the Oxfam and Greenpeace effects.
+
+Finally, organization funding source also serves as a reliable donor heuristic.
+Organizations that are funded by many small donors are substantially more popular than those funded by government grants or a a small group of wealthy donors—when compared to many small donors, both government and wealthy individual funding cause a 4 percentage point decrease in the probability of selection ($p_d$ = X).
+TODO: SHORT SPECULATION ABOUT DONOR EFFICACY AND WHY THIS IS EXPECTED?
+
+## Effect of transparency and accountability
+
+Having explored the effects of general organizational characteristics on the propensity to donate, we can test our first hypotheses and examine the effects of our treatments of interest.
+As seen in the marginal means in @fig-all-results, both transparency and accountability are surprisingly strong signals of organizational deservingness.
+Respondents strongly prefer organizations that engage in either transparency or accountability—both treatments have a marginal mean of 30% compared to a baseline equally-at-random probability of 25%.
+The AMCEs for each treatment show a roughly 10 percentage point increase in the probability of selection compared to organizations that do not engage in transparency or accountability ($p_d$ = X).
+This effect is nearly the same order of magnitude as the Red Cross effect—an NGO that chooses to be more transparent or that takes steps to demonstrate greater accountability can expect to see an increase in the probability of selection equivalent to the boost that the brand name boost associated with the Red Cross.
+
+We thus find strong evidence for both H~1a~ and H~1b~: if NGOs are financially transparent or engage in accountability practices, then individual private donors are roughly 10 percentage points more likely to donate to them.
+TODO: MORE DISCUSSION ABOUT THAT HERE
+
+MAYBE: Something about how the two effects are the same and maybe interchangeable?
+Or that donors don't care about which one specifically—they just want some sort of indication that the organization is trying to be a good citizen.
+TODO: This might need some different statistical test to see the differences in marginal means - like maybe 4 conditions (T/T, T/F, F/T, F/F for transparency and accountability)?
+
+## Effect of crackdown
+
+To test our second hypothesis regarding structural heuristics, we explore the effect of an NGO's host country conditions on the propensity to donate.
+Contrary to our expectations, respondents appear to prefer donating to NGOs that have friendly relationships with their host governments, with a marginal mean of 32% (compared to a baseline of 25%).
+Respondents are less likely to donate when an organization is criticized by its host government, and far less likely when an organization is under legal crackdown.
+Compared to other treatments, an organization facing legal crackdown has roughly the same negative preference as an organization without transparency or accountability measures, while having a friendly relationship is generally equivalent to engaging in transparency or accountability.
+
+In addition to these overall trends in preferences, we can measure the causal effect of moving from friendly relations to something more restrictive.
+Using friendly relationship as the reference category, facing criticism by the host government is causes a 7 percentage point reduction in the probability of selection ($p_d$ = 1).
+Participants respond more strongly as the relationship becomes more conflictual and restricted—an NGO facing crackdown sees a 10 percentage point reduction ($p_d$ = 1) in support.
+We thus find strong evidence against H~2~: if NGOs face legal crackdown abroad, individual donors are *less* likely to donate to them.
+For context, the causal effect of facing crackdown is the same magnitude as the Red Cross branding effect, but in the opposite direction---donors appear to punish NGOs facing criticism to an inverse degree as they reward the Red Cross.
+TODO: Speculation about why this is the case?
+
+## The interaction between transparency, accountability, and crackdown
+
+TODO: I still need to finish this section, based on H~5b~ here: <https://stats.andrewheiss.com/silent-skywalk/notebook/results-practices.html#h5b-relationship-with-host-government-organizational-practices>.
+Main gist = the transparency and accountability effects decrease as relationship with host country gets worse—it's 12 pp when friendly, 8 pp when not.
+
+TODO: Speculation about why that's the case
+
 # Conclusion
-Over the last two decades, governments globally have systematically controlled and repressed NGOs using both violent tactics and administrative means over the last three decades -- a phenomenon known as `closing' or `shrinking' civic space.
+
+Over the last two decades, governments globally have systematically controlled and repressed NGOs using both violent tactics and administrative means over the last three decades---a phenomenon known as "closing" or "shrinking" civic space.
 This trend of closing civic space has important implications for local and international NGOs as well as donors.
@@
 Unlike state donors, individual and elite donors may not necessarily withdraw or reduce support for NGOs facing harassment abroad.
-This is important because private philanthropy towards organizations working in international affairs continues to grow despite inflation -- from 2021 to 2022, individual giving to nonprofits in international affairs grew by over 10.9% in the US [@GivingUSA:2023].
+This is important because private philanthropy towards organizations working in international affairs continues to grow despite inflation---from 2021 to 2022, individual giving to nonprofits in international affairs grew by over 10.9% in the US [@GivingUSA:2023].
 
@@
 The crackdown is even more challenging for local NGOs in Global South countries, where much government and public support is channeled via service delivery organizations.
-Local groups tackling contentious issues may not be able to raise funds domestically, as publics may prefer donating to service organizations focusing on health, education, and poverty [@absar2017will].
+Local groups tackling contentious issues may not be able to raise funds domestically, as publics may prefer donating to service organizations focusing on health, education, and poverty [@AbsarCrowRon:2017].
 Even local philanthropists may be deterred from giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to poor tax incentives or a fear of retribution [@Brechenmacher:2017; @DupuyRonPrakash:2015; @Baoumi:2016].
@@
 Future research should test how well these results map on to elite individual donors, not just the average private donor, as well as determine the extent to which these preferences translate into behavior.
+
+# References

### 2023-11-04 manuscript/manuscript.qmd
Use BJPS style

@@
 bibliography: references.bib
+csl: csl/british-journal-of-political-science.csl
 link-citations: true

### 2023-11-04 manuscript/manuscript.qmd
More Suparna edits

@@
 
-Over the last three decades, governments globally have increasingly sought to crack down on NGOs (CITE).
-Repressive governments have repressed these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs.
-(CITE) Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" (CITE) and data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in nearly 60% of countries---111 in total (UPDATE FROM NEW CIVICUS DATA).
+Over the last three decades, governments globally have increasingly sought to crack down on NGOs [@ChristensenWeinstein:2013; @DupuyRonPrakash:2016, @Heiss:2017; @GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022].
+Repressive governments have cracked down on these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs [@DupuyRonPrakash:2016; Chaudhry 2022].
+Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" [@CarothersBrechenmacher:2014; @Rutzen:2015] and data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in more than 60% of countries---117 in total (https://monitor.civicus.org/globalfindings/).
 These attacks---most of which have been implemented through anti-NGO laws---have adversely affected the ability of both domestic and international NGOs to operate and raise funds.
@@
 
-Although a robust body of work on NGOs and donor behavior examines the motivation of public donors, private foundations and elite donors (CITE), we are yet to examine the impact of closing civic space, especially individual private donors, who are likely to be important funders in the face of increased government repression.
-Existing research shows that organizational accountability and financial transparency play an important role in motivating individual donors to donate to NGOs (CITE).
+Existing research shows that organizational accountability and financial transparency play an important role in motivating individual donors to donate to NGOs [@HarrisNeely:2021; @SaxtonKuoHo:2012; @Vaccaro:2006; @VaccaroMadsen:2006; @Tremblay-BoirePrakash:2017; @Becker:2018].
 In this article, we extend this literature by evaluating how these organization-level characteristics influence private donor behavior in an era of shrinking civic space.
-In considering this question, we engage with a growing body of research on the consequences of closing civic space on NGOs and donors (CITE).
+In considering this question, we engage with a growing body of research on the consequences of closing civic space on NGOs and donors [@DupuyPrakash:2018; @RightSpringmanWibbels:2022; @FransenDupuyHinfelaar:2021; @SundstromHenrySperling:2022; @Herrold:2020; @ChaudhryHeiss:2021].
 We argue that NGO-level organizational factors and domestic political environments of NGO host countries serve as heuristics and can influence foreign private donors' preferences.
-We fielded a conjoint experiment to a nationally representative sample of X adults in the US.
+We fielded a conjoint experiment to a nationally representative sample of X [HOW MANY] adults in the US.
 A conjoint design allows us to directly compare the relative impact of host government repression of NGOs vis-a-vis an organization's financial transparency and accountability on individual donor preferences.
@@
 Substantial research on NGOs has looked at the motivation of individual donors, including altruism, reputational benefits, and alignment with personal values [@BilodeauSlivinski:1997; @Wiepking:2010; @BekkersWiepking:2011].
-However, this research has overwhelmingly looked at individual donor behavior and motivation for giving to local---rather than international---causes (CITE -2).
+However, this research has overwhelmingly looked at individual donor behavior and motivation for giving to local---rather than international---causes [@BekkersWiepking:2011; @Tremblay-BoirePrakash:2017].
 Understanding the latter is important as philanthropy to international causes can be harder to motivate because the number of recipients is larger and further removed from the donor [@CasaleBaumann:2015, 100].
@@
 Under ordinary circumstances, "donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad" [@Tremblay-BoirePrakash:2017, 644].
-However, we lack adequate data and theory regarding philanthropy towards INGOs.
+However, we lack adequate data and theory regarding the conditions under which private donors engage in increased philanthropy towards INGOs.
+This gap also exists because conventionally, public donors or official aid donors have been among the main funders of INGOs.
 
 The third wave of democratization, the collapse of the Soviet Union, and the spread of a "pro-NGO norm" led to an increased role and visibility for NGOs.
-Globally, a large amount of resources were channeled to NGOs focused on service provision or development because many public and private donors perceived them as more efficient than states with weak institutions and poor governance; there was a high risk that such states would use aid transfers inefficiently [@Dietrich:2013].
+Globally, a large amount of official aid resources were channeled to NGOs focusing on service provision and development.
+public and private donors perceived them as more efficient than states with weak institutions and poor governance; there was a high risk that such states would use aid transfers inefficiently [@Dietrich:2013].
+Less bureaucratic and more nimble than state institutions, NGOs were seen as key agents of development and democratization [@Herrold:2020, 142--43].
 
@@
 
-Donors respond to a host of heuristics and signals when deciding whether to donate to an NGO, since seeking out complete information about an organization's deservingness and efficiency is costly and time-consuming [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
-Nonprofits fundraising internationally may therefore rely on framing to control perceptions.
+Private donors, however, do not necessarily seek out complete information about an organization's deservingness and efficiency, since this is a costly and time-consuming process [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
+As such, these donors respond to a host of heuristics and signals when deciding whether to donate to an NGO.
+Nonprofits fundraising internationally may therefore rely on framing to control perceptions [@ChaudhryHeiss:2021].
 Below, we theorize the effect of different frames surrounding a country's legal environment and nonprofit organizational characteristics on individual donor preferences.
-
-TODO: Cite @ChaudhryHeiss:2021 somewhere
 
@@
 This can manifest itself through multiple mechanisms such as the amount an organization spends on overhead costs, whether an organization makes its finances public, or whether an organization participates in voluntary accountability practices, such as listing organizational details on websites like GuideStar and Charity Navigator.
+
 An NGO's financial transparency, defined as the degree of completeness of information, provided by organizations to the public concerning its business activities, is one tangible heuristics that donors use to make their decisions.
@@
 
-In addition to organizational factors discussed above, political contexts in NGO host countries, especially their environments for civil society organizations, can also influence donor preferences for donating to foreign NGOs.
-A global cascade of anti-NGO laws in recent decades has created barriers to entry, funding, and advocacy for civic organizations [@GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022; @Heiss:2017; @DupuyRonPrakash:2015].
+While NGOs have control over organizational factors such as transparency and accountability, and can work to improve these characteristics and public perception of them, these NGOs may have little to no control over structural factors that can also influence philanthropy.
+These structural factors include political contexts in NGO host countries, especially their environments for civil society organizations.
+A global cascade of anti-NGO laws in recent decades has created barriers to entry, funding, and advocacy for civic organizations [@GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022; @Heiss:2017; @DupuyRonPrakash:2016].
 As a result, NGOs must spend more time, effort, and resources to ensure their survival—at the expense of pursuing their missions.
+
 Some NGOs have adapted to their repressive environments by recreating their organizations and changing their mission to avoid directly confronting the government.
@@
 Further, advocacy-oriented donors---i.e., those that fund democracy and civil society promotion activities---reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022].
-However, previous literature has established that individual private donors may not necessarily use the same metrics as official donors (CITE).
+However, previous literature has established that individual private donors may not necessarily use the same metrics as official donors [@DesaiKharas:2018; @ChaudhryHeiss:2021].
 Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the grounds [@EasterlyWilliamson:2011].
@@
 
-Identifying the causal link between structural factors and donor behavior is more difficult than measuring the link between organizational factors and donor behavior, however, because (1) NGOs have less direct control over their political environments, and (2) organizational characteristics like financial transparency and accountability can sour the NGO-government relationship---governments may be more likely to target NGOs that lack financial transparency and accountability.
-Legal restrictions do not occur in isolation.
+Identifying the causal link between structural factors and donor behavior is more difficult than measuring the link between organizational factors and donor behavior because (1) NGOs have less direct control over their political environments, and (2) organizational characteristics like financial transparency and accountability can sour the NGO-government relationship---governments may be more likely to target NGOs that lack financial transparency and accountability.
+Governments do not enact anti-NGO laws in isolation.
 Countries are more likely to repress NGOs when organizational features are in tension with government preferences and when organizations receive substantial funding from abroad [@DupuyRonPrakash:2015].
-Therefore, the same organizational characteristic that can increase the likelihood of crackdown can also simultaneously serve as a donor heuristic and influence perceptions of NGO deservingness.
+Therefore, the same organizational characteristic that can increase the likelihood of government crackdown can also simultaneously serve as a donor heuristic and influence perceptions of NGO deservingness.
 
@@
 In standard factorial experimental designs, every combination of treatment attributes would need to be shown to some number of participants would ordinarily need to be shown all possible combinations of experimental attributes.
-In our experiment, we presented respondents with six possible treatments with varying counts of attributes for each treatment, yielding 576 possible unique combinations of features.
+In our experiment, we presented respondents with six possible treatments with varying counts of attributes for each treatment, yielding 576 possible unique combinations of features [EXPLAIN HERE THAT WE HAVE ALL THE IVS BUT WE LOOK AT JUST THESE].
 Even with respondents answering twelve iterations of the experiment, not every combination was seen.
@@
 
-# Results and discussion
+# Results
 
@@
 
-## Effect of general things (lol needs better heading)
+## Discussion
 
@@
 This trend of closing civic space has important implications for local and international NGOs as well as donors.
-Recent research has analyzed the impact of this crackdown on public or official aid donors.
-However, we know relatively little about how state repression of NGOs affects the preferences of foreign private donors.
+Recent research has analyzed the impact of this crackdown on public or official aid donors [@DupuyPrakash:2018; @Herrold:2020; @RightSpringmanWibbels:2022].
+However, we know relatively little about how state repression of NGOs affects the preferences of foreign private donors [@ChaudhryHeiss:2021].
 The responses of elite donors and foundations to government crackdown on civil society organizations remains a ripe area for research.
@@
 How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country politics when deciding to donate?
+We argue that informational heuristics about NGOs’ legal and political environments and organizational-level attributes can influence donor preferences for international giving.
 Using a conjoint experiment with a nationally representative sample of the U.S.
-population, we find COMPLETE.
+population, we find that both financial transparency and accountability increases individuals' willingness to donate NGOs.
+Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability protect against this dampening effect.
+INSERT LINE/MAKE MORE SPECIFIC.
 
 These results have important implications for NGO operations, fundraising and survivability at a time when a number of INGOs are dealing with hostile host governments.
-The crackdown is even more challenging for local NGOs in Global South countries, where much government and public support is channeled via service delivery organizations.
+A comparison of the effects of these organizational and structural factors is critical to NGO fundraising---while NGOs have control over transparency and accountability, as well as public perception of these organizational characteristics, they may little to no control over host government crackdowns over their organizations.
+As a result, they may need to rely entirely on improving individual donor perception of the causes of such crackdown, its impact on NGO operations and the need for private donor funds.
+This article provides an insight into the importance of different framing or informational heuristics that can motivate such individual donor giving.
+
+Government crackdown on civil society organizations is even more challenging for local NGOs in Global South countries, where much government and public support is channeled via service delivery organizations.
 Local groups tackling contentious issues may not be able to raise funds domestically, as publics may prefer donating to service organizations focusing on health, education, and poverty [@AbsarCrowRon:2017].
@@
 Our results highlight the importance of organizational characteristics like transparency and accountability even in an era of closing civic space.
-By finding new ways to communicate about organizational transparency and accountability to potential donors, NGOs can help overcome individual donors' concerns about host governments' criticisms of and crackdown on these groups.
+By finding new ways to communicate about organizational transparency and accountability to potential donors, as well as the causes of government crackdowns on even transparent organizations, NGOs can help overcome individual donors' concerns about host governments' criticisms of and crackdown on these groups.
 
 Future research should test how well these results map on to elite individual donors, not just the average private donor, as well as determine the extent to which these preferences translate into behavior.
+Future research should also test the generalizability of these findings to non-American populations.
+Donors in European countries may have different preferences when choosing to donate to NGOs, as nonprofits in the European sector typically do not rely as much on government funding, and already receive more support from private donors compared to the American context.
 

### 2023-11-15 manuscript/manuscript.qmd
MEGA update and revisions

@@
 short-title: "Why Donors Donate"
-date: "2023-10-29"
+date: "2023-11-14"
 author:
@@
 link-citations: true
+word-count: 9324
+
+crossref:
+  custom:
+    - kind: float
+      prefix: Table A
+      space-before-numbering: false
+      name: Table A
+      ref-type: apptbl
+      latex-env: apptbl
+      latex-list-of-file-extension: lost
+      latex-list-of-description: Appendix Table
+apptbl-cap-location: top
 ---
@@
 library(ggforce)
+library(ggh4x)
 library(scales)
@@
 library(gtExtras)
+library(kableExtra)
+library(modelsummary)
 library(here)
@@
 
-tar_load(c(grid_treatment_only, level_lookup, feature_lookup))
+tar_load(c(
+  grid_treatment_only, level_lookup, feature_lookup,
+  participant_summary, model_summary_table
+))
+
 preds_all <- tar_read(preds_conditional_treatment_only)
@@
 
+```{r calc-mms}
+mms_org <- preds_all %>% 
+  group_by(feature_level = feat_org, .draw) %>% 
+  summarize(avg = mean(.epred)) %>% 
+  ungroup()
+
+mms_issue <- preds_all %>% 
+  group_by(feature_level = feat_issue, .draw) %>% 
+  summarize(avg = mean(.epred)) %>% 
+  ungroup()
+
+mms_transp <- preds_all %>% 
+  group_by(feature_level = feat_transp, .draw) %>% 
+  summarize(avg = mean(.epred)) %>% 
+  ungroup()
+
+mms_acc <- preds_all %>% 
+  group_by(feature_level = feat_acc, .draw) %>% 
+  summarize(avg = mean(.epred)) %>% 
+  ungroup()
+
+mms_funding <- preds_all %>% 
+  group_by(feature_level = feat_funding, .draw) %>% 
+  summarize(avg = mean(.epred)) %>% 
+  ungroup()
+
+mms_govt <- preds_all %>% 
+  group_by(feature_level = feat_govt, .draw) %>% 
+  summarize(avg = mean(.epred)) %>% 
+  ungroup()
+
+mms_all <- bind_rows(
+  lst(mms_org, mms_issue, mms_transp, mms_acc, mms_funding, mms_govt),
+  .id = "mm_var"
+) %>%
+  left_join(select(feature_lookup, mm_var, feature_nice_paper), by = join_by(mm_var))
+
+mms_all_medians <- mms_all %>% 
+  group_by(feature_nice_paper, feature_level) %>% 
+  summarize(
+    median_qi(avg),
+    p_gt_25 = sum(avg > 0.25) / n()
+  ) %>% 
+  mutate(p_neq_25 = ifelse(y >= 0.25, p_gt_25, 1 - p_gt_25))
+
+# Make a bunch of differently-formatted numbers
+mms <- mms_all_medians %>% 
+  mutate(level = janitor::make_clean_names(feature_level)) %>% 
+  mutate(
+    pd = fmt_decimal2(p_neq_25),
+    pct = label_percent(accuracy = 0.1)(y),
+    nice_full = glue("{fmt_decimal(y)}; {build_ci(ymin, ymax)}; $p_d$ = {pd}"),
+    nice_simple = glue("{fmt_decimal(y)}; {build_ci(ymin, ymax)}"),
+    nice_ci = glue("{build_ci(ymin, ymax)}"),
+    nice_ci_pd = glue("{build_ci(ymin, ymax)}; $p_d$ = {pd}"),
+    nice_ci_pd_prefix = glue("95% cred. int. = {build_ci(ymin, ymax)}; $p_d$ = {pd}"),
+    nice_full_prefix = glue("{fmt_decimal(y)}; 95% cred. int. = {build_ci(ymin, ymax)}; $p_d$ = {pd}"),
+    nice_br = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")
+  ) %>% 
+  split(~level)
+
+# Marginal means for transparency and accountability together
+mms_transp_acc <- preds_all %>% 
+  group_by(feat_transp, feat_acc, .draw) %>% 
+  summarize(avg = mean(.epred)) %>% 
+  ungroup()
+
+mms_ta <- mms_transp_acc %>% 
+  group_by(feat_transp, feat_acc) %>% 
+  median_qi(avg) %>% 
+  mutate(combined = janitor::make_clean_names(paste0(feat_transp, feat_acc))) %>% 
+  mutate(
+    pct = label_percent(accuracy = 0.1)(avg),
+    nice_ci = glue("{build_ci(.lower, .upper)}")
+  ) %>% 
+  split(~combined)
+
+# Marginal means for transparency/accountability and crackdown together
+mms_transp_crackdown <- preds_all %>% 
+  group_by(feat_transp_short, feat_govt, .draw) %>% 
+  summarize(avg = mean(.epred))
+
+mms_acc_crackdown <- preds_all %>% 
+  group_by(feat_acc_short, feat_govt, .draw) %>% 
+  summarize(avg = mean(.epred))
+
+mms_tc <- mms_transp_crackdown %>% 
+  group_by(feat_transp_short, feat_govt) %>% 
+  median_qi(avg) %>% 
+  mutate(combined = janitor::make_clean_names(paste0(feat_transp_short, feat_govt))) %>% 
+  mutate(
+    pct = label_percent(accuracy = 0.1)(avg),
+    nice_ci = glue("{build_ci(.lower, .upper)}")
+  ) %>% 
+  split(~combined)
+```
+
+```{r calc-amces}
+amces_org <- mms_org %>% 
+  group_by(feature_level) %>% 
+  compare_levels(variable = avg, by = feature_level, comparison = "control") %>% 
+  ungroup() %>% 
+    separate_wider_delim(
+    feature_level,
+    delim = " - ", 
+    names = c("feature_level", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feature_level = unique(.$reference_level))
+
+amces_issue <- mms_issue %>% 
+  group_by(feature_level) %>% 
+  compare_levels(variable = avg, by = feature_level, comparison = "control") %>% 
+  ungroup() %>% 
+    separate_wider_delim(
+    feature_level,
+    delim = " - ", 
+    names = c("feature_level", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feature_level = unique(.$reference_level))
+
+amces_transp <- mms_transp %>% 
+  group_by(feature_level) %>% 
+  compare_levels(variable = avg, by = feature_level, comparison = "control") %>% 
+  ungroup() %>% 
+    separate_wider_delim(
+    feature_level,
+    delim = " - ", 
+    names = c("feature_level", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feature_level = unique(.$reference_level))
+
+amces_acc <- mms_acc %>% 
+  group_by(feature_level) %>% 
+  compare_levels(variable = avg, by = feature_level, comparison = "control") %>% 
+  ungroup() %>% 
+    separate_wider_delim(
+    feature_level,
+    delim = " - ", 
+    names = c("feature_level", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feature_level = unique(.$reference_level))
+
+amces_funding <- mms_funding %>% 
+  group_by(feature_level) %>% 
+  compare_levels(variable = avg, by = feature_level, comparison = "control") %>% 
+  ungroup() %>% 
+    separate_wider_delim(
+    feature_level,
+    delim = " - ", 
+    names = c("feature_level", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feature_level = unique(.$reference_level))
+
+amces_govt <- mms_govt %>% 
+  group_by(feature_level) %>% 
+  compare_levels(variable = avg, by = feature_level, comparison = "control") %>% 
+  ungroup() %>% 
+    separate_wider_delim(
+    feature_level,
+    delim = " - ", 
+    names = c("feature_level", "reference_level")
+  ) %>% 
+  add_row(avg = 0, feature_level = unique(.$reference_level))
+
+amces_all <- bind_rows(
+  lst(amces_org, amces_issue, amces_transp, amces_acc, amces_funding, amces_govt),
+  .id = "amce_var"
+) %>%
+  left_join(select(feature_lookup, amce_var, feature_nice_paper), by = join_by(amce_var)) %>%
+  left_join(
+    select(level_lookup, contains("_level")), 
+    by = join_by(feature_level)
+  )
+
+amces_all_medians <- amces_all %>% 
+  group_by(feature_nice_paper, feature_level) %>% 
+  summarize(
+    median_qi(avg),
+    p_gt_0 = sum(avg > 0) / n()
+  ) %>% 
+  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0))
+
+# Make a bunch of differently-formatted numbers
+amce <- amces_all_medians %>% 
+  mutate(level = janitor::make_clean_names(feature_level)) %>% 
+  mutate(
+    pd = fmt_decimal2(p_neq_0),
+    pp = fmt_pp_int(y),
+    pp_abs = fmt_pp_int(abs(y)),
+    nice_full = glue("{fmt_decimal(y)}; {build_ci(ymin, ymax)}; $p_d$ = {pd}"),
+    nice_ci_pd = glue("{build_ci(ymin, ymax)}; $p_d$ = {pd}"),
+    nice_ci_pd_prefix = glue("95% cred. int. = {build_ci(ymin, ymax)}; $p_d$ = {pd}"),
+    nice_full_prefix = glue("{fmt_decimal(y)}; 95% cred. int. = {build_ci(ymin, ymax)}; $p_d$ = {pd}"),
+    nice_br = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")
+  ) %>% 
+  split(~level)
+
+amces_transp_crackdown <- mms_transp_crackdown %>% 
+  group_by(feat_govt) %>% 
+  compare_levels(variable = avg, by = feat_transp_short, comparison = "control")
+
+amces_transp_crackdown_medians <- amces_transp_crackdown %>% 
+  group_by(feat_govt, feat_transp_short) %>% 
+  summarize(
+    median_qi(avg),
+    p_gt_0 = sum(avg > 0) / n()
+  ) %>% 
+  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0))
+
+amce_tc <- amces_transp_crackdown_medians %>% 
+  mutate(level = janitor::make_clean_names(feat_govt)) %>% 
+  mutate(
+    pd = fmt_decimal2(p_neq_0),
+    pp = fmt_pp_int(y),
+    pp_abs = fmt_pp_int(abs(y)),
+    nice_full = glue("{fmt_decimal(y)}; {build_ci(ymin, ymax)}; $p_d$ = {pd}"),
+    nice_ci_pd = glue("{build_ci(ymin, ymax)}; $p_d$ = {pd}"),
+    nice_ci_pd_prefix = glue("95% cred. int. = {build_ci(ymin, ymax)}; $p_d$ = {pd}"),
+    nice_full_prefix = glue("{fmt_decimal(y)}; 95% cred. int. = {build_ci(ymin, ymax)}; $p_d$ = {pd}"),
+    nice_br = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")
+  ) %>% 
+  split(~level)
+
+amces_acc_crackdown_medians <- mms_acc_crackdown %>% 
+  group_by(feat_govt) %>% 
+  compare_levels(variable = avg, by = feat_acc_short, comparison = "control") %>% 
+  group_by(feat_govt, feat_acc_short) %>% 
+  summarize(
+    median_qi(avg),
+    p_gt_0 = sum(avg > 0) / n()
+  ) %>% 
+  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0))
+```
+
+::: {.content-visible when-format="html"}
+# Introduction {.hide}
+:::
+
 Over the last three decades, governments globally have increasingly sought to crack down on NGOs [@ChristensenWeinstein:2013; @DupuyRonPrakash:2016, @Heiss:2017; @GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022].
-Repressive governments have cracked down on these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs [@DupuyRonPrakash:2016; Chaudhry 2022].
-Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" [@CarothersBrechenmacher:2014; @Rutzen:2015] and data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in more than 60% of countries---117 in total (https://monitor.civicus.org/globalfindings/).
+Repressive governments have cracked down on these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs [@DupuyRonPrakash:2016; @Chaudhry:2022].
+Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" [@CarothersBrechenmacher:2014; @Rutzen:2015] and data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in more than 60% of countries---117 in total [@CIVICUSMonitor].
 These attacks---most of which have been implemented through anti-NGO laws---have adversely affected the ability of both domestic and international NGOs to operate and raise funds.
@@
 Most notably, a large portion of this growth was driven by individuals making small-scale donations.
-In 2017, individuals gave US\$286.7 billion or approximately 70% of total giving to international affairs.
-This further increased to US\$427.71 billion in 2018, 85.7% of which was through individuals [@GivingUSA:2019].
+In 2017, individuals gave \$286.7 billion or approximately 70% of total giving to international affairs.
+This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [@GivingUSA:2019].
 This turn to private donors opens INGOs up to new dynamics in seeking out aid.
@@
 We argue that NGO-level organizational factors and domestic political environments of NGO host countries serve as heuristics and can influence foreign private donors' preferences.
-We fielded a conjoint experiment to a nationally representative sample of X [HOW MANY] adults in the US.
-A conjoint design allows us to directly compare the relative impact of host government repression of NGOs vis-a-vis an organization's financial transparency and accountability on individual donor preferences.
-The result of these experiments show both financial transparency and accountability increases individuals' willingness to donate NGOs.
-Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability protect against this dampening effect.
-INSERT LINE ABOUT EFFECT SIZE.
+We fielded a conjoint experiment to a nationally representative sample of 1,016 adults in the US, which allows us to directly compare the relative impact of host government repression of NGOs and organizational financial transparency and accountability on individual donor preferences.
+The result of this experiment shows that both financial transparency and accountability increase individuals' willingness to donate to NGOs.
+Conversely, learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability can protect against this dampening effect.
+These effect sizes are substantial: ten percentage point increases and decreases in the predicted probability of choosing to donate to an NGO.
 
-These findings make two main contributions.
+Our findings make two main contributions.
 While recent research on private foreign aid has examined funding decisions of donor NGOs and foundations[^1], we know less about the funding choices of the individuals responsible for much of these private aid flows [@DesaiKharas:2018].
@@
 Instead, individuals rely on heuristics to simplify their decision-making.
-
-One common signal for donors is organizational efficacy or the belief that an individual's donation will make a real difference.
+One common signal for donors is organizational efficacy or the belief that an individual's donation will make a real difference [@ChaudhryHeiss:2021].
 This can manifest itself through multiple mechanisms such as the amount an organization spends on overhead costs, whether an organization makes its finances public, or whether an organization participates in voluntary accountability practices, such as listing organizational details on websites like GuideStar and Charity Navigator.
@@
 A global cascade of anti-NGO laws in recent decades has created barriers to entry, funding, and advocacy for civic organizations [@GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022; @Heiss:2017; @DupuyRonPrakash:2016].
-As a result, NGOs must spend more time, effort, and resources to ensure their survival—at the expense of pursuing their missions.
+As a result, NGOs must spend more time, effort, and resources to ensure their survival---at the expense of pursuing their missions.
 
@@
 In standard factorial experimental designs, every combination of treatment attributes would need to be shown to some number of participants would ordinarily need to be shown all possible combinations of experimental attributes.
-In our experiment, we presented respondents with six possible treatments with varying counts of attributes for each treatment, yielding 576 possible unique combinations of features [EXPLAIN HERE THAT WE HAVE ALL THE IVS BUT WE LOOK AT JUST THESE].
+In our experiment, we presented respondents with six possible treatments with varying counts of attributes for each treatment, yielding 576 possible unique combinations of features.
 Even with respondents answering twelve iterations of the experiment, not every combination was seen.
@@
 
-While the ability to select key attributes and marginalize over others provides us with analytic flexibility, it also raises possible issues with multiple comparisons, *p*-hacking, and selective cherry-picking [@BansakHainmuellerHopkins:2021].
-As such, before launching the survey experiment, we preregistered a set of confirmatory and exploratory hypotheses at the Open Science Framework.
-Our preregistration protocol is available at `ANONYMIZED_URL` and in Appendix TODO, and our data and reproducible code is available at `ANONYMIZED_URL`.
+While the ability to select key attributes and marginalize over others provides us with analytic flexibility, it also raises possible issues with multiple comparisons, *p*-hacking, and selective cherry-picking [@BansakHainmuellerHopkins:2021], especially given the fact that we have 576 possible combinations of independent variables to explore.
+As such, before launching the survey experiment, we preregistered a subset of confirmatory and exploratory hypotheses at the Open Science Framework.
+These hypotheses deal specifically with our key research questions about the effect of transparency, accountability, and crackdown on the propensity to donate, along with comparison treatment effects for organization brand name, issue area, and funding sources.
+We also examine the interaction between transparency, accountability, and host-country relationships.
+Our preregistration protocol is available at `ANONYMIZED_URL` and in the appendix, and our data and reproducible code is available at `ANONYMIZED_URL`.[^prereg]
+
+[^prereg]: For narrative purposes, we do not explore all our preregistered hypotheses in this study—many of them are nested inside each other (e.g., the effect of branding and issue area and transparency and crackdown simultaneously).
+We instead focus here on the simplest, non-nested hypotheses.
+H~1a~ and H~1b~ correspond to preregistration question #5; H~2~ corresponds to preregistration question #2; our comparison treatments correspond to preregistration questions #1, #3, and #4.
+Our exploration of the interaction between transparency, accountability, and crackdown corresponds to part 2 of preregistration question #5.
 
@@
 To see how varying NGO characteristics influence the decision to donate, our sample was representative of the population of people who are likely to donate to charity.
-We asked potential participants a screening question early in the survey ("Q2.5: How often do you donate to charity?").
-If a participant responded that they give once every few years or never, they were disqualified from the study.
+We asked potential participants a screening question about their philanthropic behavior early in the survey---if a participant responded that they give once every few years or never, they were disqualified from the study.
+Our reported causal effects are therefore not representative of the entire population and instead are only valid for people interested in charitable giving.
 We also included an attention check question early in the survey and removed respondents who failed the question.
@@
 Following screening, we received 1,016 viable responses.
-@tbl:sample-details provides a detailed breakdown of the individual characteristics of our sample.
+@apptbl-sample-details provides a detailed breakdown of the individual characteristics of our sample.
 In general, respondents were well balanced across genders and tended to be older than the national median age of 36---less than 20% of respondents were under 36 years old.
@@
 
-```{css, echo=FALSE}
-/* Remove padding on lists in tables */
-.gt_table ul, .gt_table ol {
-  padding-left: 1rem;
-}
-```
-
-```{r tbl-design, include=TRUE}
+```{r}
+#| label: tbl-design
 #| tbl-cap: "All experimental features and levels included in the conjoint experiment"
+#| include: true
 transparency <- c("Doesn't engage in transparency", "Engages in transparency")
@@
   ~type, ~feature, ~levels,
-  "H~1a~", "Financial transparency", paste0(paste0("- ", transparency), collapse = "\n"),
-  "H~1b~", "Accountability", paste0(paste0("- ", accountability), collapse = "\n"),
-  "H~2~", "Relationship with host government", paste0(paste0("- ", govt), collapse = "\n"),
-  "Comparison", "Organization", paste0(paste0("- ", orgs), collapse = "\n"),
-  "Comparison", "Issue area", paste0(paste0("- ", issues), collapse = "\n"),
-  "Comparison", "Funding source", paste0(paste0("- ", funding), collapse = "\n")
+  "H~1a~", "Financial transparency", inline_listify(transparency),
+  "H~1b~", "Accountability", inline_listify(accountability),
+  "H~2~", "Relationship with host government", inline_listify(govt),
+  "Comparison", "Organization", inline_listify(orgs),
+  "Comparison", "Issue area", inline_listify(issues),
+  "Comparison", "Funding source", inline_listify(funding)
 ) %>% 
@@
   cols_label(feature = "Feature/Attribute", levels = "Levels", type = "Purpose") %>% 
-  fmt_markdown(columns = c(type, levels)) %>% 
+  fmt_markdown(columns = c(type)) %>% 
   tab_style(
@@
   ) %>% 
-  opts_theme()
+  opts_theme() |>
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
 ```
 
-Charity Navigator—a large database of U.S.
-nonprofit financial information—categorizes its nonprofit organizations into four core sectors: humanitarian relief, human rights, development, and the environment.
+Charity Navigator---a large database of U.S.
+nonprofit financial information---categorizes its nonprofit organizations into four core sectors: humanitarian relief, human rights, development, and the environment.
 Accordingly, we used four nonprofits that are stereotypical for each issue: the International Committee of the Red Cross (humanitarian relief), Amnesty International (human rights), Oxfam (development), and Greenpeace (environment).
@@
 
-```{r tbl-example, include=TRUE}
+```{r}
+#| label: tbl-example
 #| tbl-cap: "Example possible experimental task, with three randomized combinations of organizational attributes"
+#| include: true
 withr::with_seed(12345, {
@@
 Our experimental data has a natural hierarchical structure, with 3 questions nested inside 12 separate experimental tasks, nested inside each of the 1,016 respondents, which lends itself to multilevel modeling.
-Relying on standard OLS regression can discard useful information about (1) the relationships and covariance between the different combinations of feature levels offered to respondents, and (2) individual-specific differences in how respondents react to different feature levels [@JensenMarbleScheve:2021].
+Relying on standard OLS regression can discard valuable information about (1) the relationships and covariance between the different combinations of feature levels offered to respondents, and (2) individual-specific differences in how respondents react to different feature levels [@JensenMarbleScheve:2021].
 Since it was impossible for every respondent to see every possible all 12,000 experimental tasks, multilevel modeling allows us to pool together information about respondents with similar characteristics facing similar sets of choices.
-Moreover, using random respondent effects provides natural regularization and shrinkage for our estimates—experimental tasks that happened to appear more often due to chance will be accounted for and not influence the overall causal effect.
+Moreover, using random respondent effects provides natural regularization and shrinkage for our estimates---experimental tasks that happened to appear more often due to chance will be accounted for and their frequency will not bias the overall causal effect.
 
-We analyze the effect of the various combinations of organizational features and donor characteristics with the following hierarchical Bayesian multinomial logit model:
+We analyze the effect of the various combinations of organizational features and donor characteristics with the following Bayesian multinomial logit model and priors:
 
@@
 
-Importantly, we do not include any respondent-level covariates beyond the treatment variables.
+We do not include any respondent-level covariates beyond the treatment variables.
 Because this is an experimental design, any statistical confounding is accounted for during the process of randomization and covariates should have no systematic effect on treatment effects.
-We do not work with the raw results of the model directly (though a complete table of results is included in Appendix TODO).
+We do not work with the raw results of the model directly (though a complete table of results is included in @apptbl-coefs-orig).
 Given the conjoint design, we instead create a complete balanced grid of all 576 combinations of feature levels (4 organizations × 4 issues × 2 transparency × 2 accountability × 3 funding × 3 government relationships) and use the model to calculate predicted probabilities of choice selection for each row of possible treatment values.
@@
 To calculate the causal effect of a treatment, we find the average marginal component effect (AMCE), which is equivalent to the difference in estimated marginal means for specific feature levels.
-For example, when estimating the marginal means of the transparency treatment, we find the average predicted probability across the 288 rows of the reference grid where transparency is true and across the 288 rows where transparency is false—the difference between these two estimated marginal means is the AMCE, or the causal effect of the treatment, on the probability scale.
+For example, when estimating the marginal means of the transparency treatment, we find the average predicted probability across the 288 rows of the reference grid where transparency is true and across the 288 rows where transparency is false---the difference between these two estimated marginal means is the AMCE, or the causal effect of the treatment holding all other values constant, on the probability scale.
 
@@
 
-We present the posterior distributions of the marginal means and AMCEs for each of our experimental conditions in @fig-all-results and provide posterior medians and credible intervals in @tbl-all-results in the appendix.
+We present the posterior distributions of the marginal means and AMCEs for each of our experimental conditions in @fig-all-results and provide posterior medians, credible intervals, and other model diagnostics in @apptbl-all-results and @apptbl-coefs-orig.
 Because AMCEs are relative statements (i.e.
@@
 
-```{r calc-mms}
-mms_org <- preds_all %>% 
-  group_by(feat_org, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-mms_issue <- preds_all %>% 
-  group_by(feat_issue, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-mms_transp <- preds_all %>% 
-  group_by(feat_transp, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-mms_acc <- preds_all %>% 
-  group_by(feat_acc, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-mms_funding <- preds_all %>% 
-  group_by(feat_funding, .draw) %>% 
-  summarize(avg = mean(.epred))
-
-mms_govt <- preds_all %>% 
-  group_by(feat_govt, .draw) %>% 
-  summarize(avg = mean(.epred))
-```
-
-```{r calc-amces}
-amces_org <- mms_org %>% 
-  group_by(feat_org) %>% 
-  compare_levels(variable = avg, by = feat_org, comparison = "control") %>% 
-  ungroup() %>% 
-    separate_wider_delim(
-    feat_org,
-    delim = " - ", 
-    names = c("feature_level", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feature_level = unique(.$reference_level))
-
-amces_issue <- mms_issue %>% 
-  group_by(feat_issue) %>% 
-  compare_levels(variable = avg, by = feat_issue, comparison = "control") %>% 
-  ungroup() %>% 
-    separate_wider_delim(
-    feat_issue,
-    delim = " - ", 
-    names = c("feature_level", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feature_level = unique(.$reference_level))
-
-amces_transp <- mms_transp %>% 
-  group_by(feat_transp) %>% 
-  compare_levels(variable = avg, by = feat_transp, comparison = "control") %>% 
-  ungroup() %>% 
-    separate_wider_delim(
-    feat_transp,
-    delim = " - ", 
-    names = c("feature_level", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feature_level = unique(.$reference_level))
-
-amces_acc <- mms_acc %>% 
-  group_by(feat_acc) %>% 
-  compare_levels(variable = avg, by = feat_acc, comparison = "control") %>% 
-  ungroup() %>% 
-    separate_wider_delim(
-    feat_acc,
-    delim = " - ", 
-    names = c("feature_level", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feature_level = unique(.$reference_level))
-
-amces_funding <- mms_funding %>% 
-  group_by(feat_funding) %>% 
-  compare_levels(variable = avg, by = feat_funding, comparison = "control") %>% 
-  ungroup() %>% 
-    separate_wider_delim(
-    feat_funding,
-    delim = " - ", 
-    names = c("feature_level", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feature_level = unique(.$reference_level))
-
-amces_govt <- mms_govt %>% 
-  group_by(feat_govt) %>% 
-  compare_levels(variable = avg, by = feat_govt, comparison = "control") %>% 
-  ungroup() %>% 
-    separate_wider_delim(
-    feat_govt,
-    delim = " - ", 
-    names = c("feature_level", "reference_level")
-  ) %>% 
-  add_row(avg = 0, feature_level = unique(.$reference_level))
-
-amces_all <- bind_rows(
-  lst(amces_org, amces_issue, amces_transp, amces_acc, amces_funding, amces_govt),
-  .id = "amce_var"
-) %>%
-  left_join(select(feature_lookup, amce_var, feature_nice_paper), by = join_by(amce_var)) %>%
-  left_join(
-    select(level_lookup, contains("_level")), 
-    by = join_by(feature_level)
-  )
-```
-
-```{r fig-all-results, include=TRUE}
+```{r}
+#| label: fig-all-results
 #| fig-width: 12
@@
 #| column: page
+#| include: true
 mms_all <- bind_rows(
-  lst(
-    mms_org = rename(mms_org, feature_level = feat_org), 
-    mms_issue = rename(mms_issue, feature_level = feat_issue), 
-    mms_transp = rename(mms_transp, feature_level = feat_transp), 
-    mms_acc = rename(mms_acc, feature_level = feat_acc), 
-    mms_funding = rename(mms_funding, feature_level = feat_funding), 
-    mms_govt = rename(mms_govt, feature_level = feat_govt)
-  ),
+  lst(mms_org, mms_issue, mms_transp, mms_acc, mms_funding, mms_govt),
   .id = "mm_var"
@@
 ) +
+  stat_halfeye(normalize = "groups") +
   geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
-  stat_halfeye(normalize = "groups") +
   guides(fill = "none") +
@@
 ) +
+  stat_halfeye(normalize = "groups") +  # Make the heights of the distributions equal within each facet
   geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
-  stat_halfeye(normalize = "groups") +  # Make the heights of the distributions equal within each facet
   guides(fill = "none") +
@@
 However, we are generally less concerned with the exact point estimates of our causal effects and instead focus on the direction and relative magnitude of their posterior distributions.
-For inference, we calculate the probability of direction ($p_d$), or the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median.
+For inference, we calculate the probability of direction ($p_d$), or the probability that the posterior AMCE is strictly positive or negative---it is the proportion of the posterior AMCE that is the sign of the median.
 
-## Discussion
+## Effect of comparison treatments
 
 To contextualize the magnitude of the causal effects for our hypotheses of interest, we begin our analysis with a brief overview of the effects of organizational characteristics that nonprofits have less direct control over: their brand name, their issue area, and their funding sources.
-Name brand recognition appears to be a powerful heuristic for donor decision making.
-Respondents were substantially more likely to prefer an organization when it was identified as the Red Cross, with an average marginal mean of 35%—ten percentage points higher than the 25% probability that would be expected if respondents selected an organization at random.
-When using Amnesty International as the reference category, the AMCE for the Red Cross is 12 percentage points ($p_d$ = 1).
+Brand recognition appears to be a powerful heuristic for donor decision making.
+Respondents were substantially more likely to prefer an organization when it was identified as the Red Cross, with an median posterior marginal mean of `r mms$red_cross$pct` (95% cred.
+int.
+= `r mms$red_cross$nice_ci`)---ten percentage points higher than the 25% probability that would be expected if respondents selected an organization at random.
+When using Amnesty International as the reference category, the AMCE for the Red Cross is `r amce$red_cross$pp` percentage points (`r amce$red_cross$nice_ci_pd_prefix`).
 Other organizations see much smaller marginal means and AMCEs.
-Compared to Amnesty International, Greenpeace causes a small 2.x percentage point increase ($p_d$ = X) and Oxfam causes a small 3.x percentage point decrease ($p_d$ = X) in the probability of selecting an organization.
+Compared to Amnesty International, Greenpeace causes a small `r amce$greenpeace$pp` percentage point increase (`r amce$greenpeace$nice_ci_pd`) and Oxfam causes a small `r amce$oxfam$pp_abs` percentage point decrease (`r amce$oxfam$nice_ci_pd`) in the probability of selecting an organization.
 The Red Cross brand name heuristic is actually the strongest of all the experimental treatments and features, signifying the organization's brand power and goodwill among potential donors.
@@
 As seen in the marginal means in @fig-all-results, organizations focused on human rights and emergency response are more popular than those working on issues related to the environment or refugee relief.
-When using emergency response (the most popular issue) as the reference category for AMCEs, working with human rights causes a 3 percentage point decrease ($p_d$ = X), while environmental and refugee relief issues see a 4 and 6 percentage point decrease, respectively ($p_d$).
+When using emergency response (the most popular issue) as the reference category for AMCEs, working with human rights causes a `r amce$human_rights$pp_abs` percentage point decrease (`r amce$human_rights$nice_ci_pd`), while environmental and refugee relief issues see `r amce$environment$pp_abs` (`r amce$environment$nice_ci_pd`) and `r amce$refugee_relief$pp_abs` (`r amce$refugee_relief$nice_ci_pd`) percentage point decreases, respectively.
 To put these effects in context, these effects are smaller than the the Red Cross effect and a little larger than the Oxfam and Greenpeace effects.
@@
 Finally, organization funding source also serves as a reliable donor heuristic.
-Organizations that are funded by many small donors are substantially more popular than those funded by government grants or a a small group of wealthy donors—when compared to many small donors, both government and wealthy individual funding cause a 4 percentage point decrease in the probability of selection ($p_d$ = X).
-TODO: SHORT SPECULATION ABOUT DONOR EFFICACY AND WHY THIS IS EXPECTED?
+Organizations that are funded by many small donors are substantially more popular than those funded by government grants or a a small group of wealthy donors---when compared to many small donors, both government and wealthy individual funding cause `r amce$funded_primarily_by_government_grants$pp_abs` and `r amce$funded_primarily_by_a_handful_of_wealthy_private_donors$pp_abs` percentage point decreases in the probability of selection (`r amce$funded_primarily_by_government_grants$nice_ci_pd` and `r amce$funded_primarily_by_a_handful_of_wealthy_private_donors$nice_ci_pd`).
+These effects follow existing research on donor efficacy [@ChaudhryHeiss:2021]---when donors know that an organization is funded by others like themselves and that the marginal benefit of their individual donation is important, they are more likely to donate.
+In contrast, when donors know that an organization's funding does not come from the public and instead comes from a few wealthy donors or large government grants, the marginal benefit they receive from donating decreases and they are less likely to donate.
+Donors therefore appear to be motivated by some degree of personal efficacy.
 
@@
 As seen in the marginal means in @fig-all-results, both transparency and accountability are surprisingly strong signals of organizational deservingness.
-Respondents strongly prefer organizations that engage in either transparency or accountability—both treatments have a marginal mean of 30% compared to a baseline equally-at-random probability of 25%.
-The AMCEs for each treatment show a roughly 10 percentage point increase in the probability of selection compared to organizations that do not engage in transparency or accountability ($p_d$ = X).
-This effect is nearly the same order of magnitude as the Red Cross effect—an NGO that chooses to be more transparent or that takes steps to demonstrate greater accountability can expect to see an increase in the probability of selection equivalent to the boost that the brand name boost associated with the Red Cross.
+Respondents strongly prefer organizations that engage in either transparency or accountability---both treatments have a posterior marginal mean of roughly 30% compared to a baseline equally-at-random probability of 25% (transparency: `r mms$transparency_yes$nice_simple`; accountability: `r mms$accountability_yes$nice_simple`).
+The AMCEs for each treatment show a roughly 10 percentage point increase in the probability of selection compared to organizations that do not engage in transparency or accountability (transparency: `r amce$transparency_yes$nice_full`; accountability: `r amce$accountability_yes$nice_full`).
+This effect is nearly the same order of magnitude as the Red Cross effect---an NGO that chooses to be more transparent or that takes steps to demonstrate greater accountability can expect to see an increase in the probability of selection equivalent to the boost of the brand name effect associated with the Red Cross.
+As predicted, we thus find strong support for both H~1a~ and H~1b~: if NGOs are financially transparent or engage in accountability practices, then individual private donors are roughly 10 percentage points more likely to donate to them.
+Donors appear to reward NGOs for their efforts to disclose their funding and be more transparent.
 
-We thus find strong evidence for both H~1a~ and H~1b~: if NGOs are financially transparent or engage in accountability practices, then individual private donors are roughly 10 percentage points more likely to donate to them.
-TODO: MORE DISCUSSION ABOUT THAT HERE
+There is also some evidence that these two effects are equivalent and perhaps interchangeable.
+@fig-transp-acc (and @apptbl-mms-trans-acc) shows the posterior marginal means for all four combinations of possible levels of transparency and accountability.
+When respondents see both as "no" simultaneously, the estimated marginal mean is lower than any of the individual treatments in @fig-all-results, at `r mms_ta$transparency_no_accountability_no$pct` (`r mms_ta$transparency_no_accountability_no$nice_ci`), or 9 percentage points lower than the baseline probability of 25%.
+When either transparency or accountability is set to "yes", the estimated marginal mean is essentially identical at `r mms$transparency_yes$pct` and `r mms$accountability_yes$pct`, respectively.
+When both treatments are set to "yes", the estimated marginal mean is `r mms_ta$transparency_yes_accountability_yes$pct` (`r mms_ta$transparency_yes_accountability_yes$nice_ci`), which is roughly the same as the overall estimated marginal mean for the Red Cross.
+Holding all other treatments constant, the effect of transparency and accountability practices on their own are generally the same, and when combined, the overall favorability of the organization increases substantially.
+This could indicate that donors do not care about which specific type of organizational practice an NGO engages in and that instead they are looking for some sort of signal that the organization is following best practices in transparency or accountability.
 
-MAYBE: Something about how the two effects are the same and maybe interchangeable?
-Or that donors don't care about which one specifically—they just want some sort of indication that the organization is trying to be a good citizen.
-TODO: This might need some different statistical test to see the differences in marginal means - like maybe 4 conditions (T/T, T/F, F/T, F/F for transparency and accountability)?
+```{r}
+#| label: fig-transp-acc
+#| fig-width: 6
+#| fig-height: 2.5
+#| out-width: "80%"
+#| fig-cap: "Estimated marginal means for the four combinations of transparency and accountability"
+#| include: true
+mms_trans_acc_all <- mms_transp_acc %>% 
+  filter(
+    (feat_transp == "Transparency: Yes" & feat_acc == "Accountability: Yes") | 
+      (feat_transp == "Transparency: No" & feat_acc == "Accountability: No")) %>% 
+  bind_rows(
+    mms_transp %>% 
+      filter(feature_level == "Transparency: Yes") %>% 
+      rename(feat_transp = feature_level) %>% 
+      mutate(feat_acc = "Accountability: No"),
+    mms_acc %>% 
+      filter(feature_level == "Accountability: Yes") %>% 
+      rename(feat_acc = feature_level) %>% 
+      mutate(feat_transp = "Transparency: No")
+  )
+
+mms_trans_acc_all %>% 
+  mutate(
+    across(c(feat_transp, feat_acc), 
+      list(
+        grp = ~str_remove(.x, ": .*"),
+        short = ~str_remove(.x, ".*: "))
+    )) %>% 
+  mutate(combined = paste(feat_transp, feat_acc)) %>% 
+  ggplot(aes(x = avg, y = feat_transp, fill = combined)) +
+  stat_halfeye(normalize = "panels") +
+  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
+  facet_nested(
+    rows = vars(feat_transp_grp, feat_transp_short),
+    cols = vars(feat_acc_grp, feat_acc_short),
+    switch = "y", scales = "free_y",
+    strip = strip_nested(
+      background_x = list(element_rect(fill = "grey90"), element_blank()),
+      text_x = list(NULL, element_text(hjust = 0.5)),
+      by_layer_x = TRUE,
+      background_y = list(element_rect(fill = "grey90"), element_blank()),
+      text_y = list(NULL, element_text(hjust = 0.5)),
+      by_layer_y = TRUE
+    )
+  ) +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(values = clrs$prism[c(12, 2, 1, 7)], guide = "none") +
+  labs(
+    x = "Marginal means of probabilities",
+    y = NULL
+  ) +
+  theme_ngo() +
+  theme(
+    axis.text.y = element_blank(),
+    strip.text.y.left = element_text(hjust = 1)
+  )
+```
 
@@
 To test our second hypothesis regarding structural heuristics, we explore the effect of an NGO's host country conditions on the propensity to donate.
-Contrary to our expectations, respondents appear to prefer donating to NGOs that have friendly relationships with their host governments, with a marginal mean of 32% (compared to a baseline of 25%).
+Contrary to our expectations, respondents appear to prefer donating to NGOs that have friendly relationships with their host governments, with a marginal mean of `r mms$friendly_relationship_with_government$pct` (compared to a baseline of 25%; `r mms$friendly_relationship_with_government$nice_ci`).
 Respondents are less likely to donate when an organization is criticized by its host government, and far less likely when an organization is under legal crackdown.
@@
 In addition to these overall trends in preferences, we can measure the causal effect of moving from friendly relations to something more restrictive.
-Using friendly relationship as the reference category, facing criticism by the host government is causes a 7 percentage point reduction in the probability of selection ($p_d$ = 1).
-Participants respond more strongly as the relationship becomes more conflictual and restricted—an NGO facing crackdown sees a 10 percentage point reduction ($p_d$ = 1) in support.
+Using friendly relationship as the reference category, facing criticism by the host government causes a `r amce$criticized_by_government$pp_abs` percentage point reduction in the probability of selection (`r amce$criticized_by_government$nice_ci_pd`).
+Participants respond more strongly as the relationship becomes more conflictual and restricted---an NGO facing crackdown sees a `r amce$under_government_crackdown$pp_abs` percentage point reduction (`r amce$under_government_crackdown$nice_ci_pd`) in support.
 We thus find strong evidence against H~2~: if NGOs face legal crackdown abroad, individual donors are *less* likely to donate to them.
-For context, the causal effect of facing crackdown is the same magnitude as the Red Cross branding effect, but in the opposite direction---donors appear to punish NGOs facing criticism to an inverse degree as they reward the Red Cross.
-TODO: Speculation about why this is the case?
+For context, the causal effect of facing crackdown is the same magnitude as the Red Cross branding effect, but in the opposite direction---donors seem to penalize NGOs facing criticism to the same extent that they reward the Red Cross.
+This result is surprising, but clarifies findings in previous research.
+In a similar vignette-based experiment, @ChaudhryHeiss:2021 find no substantial effect of legal crackdown on the likelihood of donation, and any substantive crackdown-related effects are moderated by other treatments like NGO issue area or funding source.
+This negative effect might also be related to the notion of donor efficacy.
+When deciding how to maximize the impact or marginal benefit of their individual donation, donors look for signals that their money will make a difference.
+Transparency and accountability practices, in addition to knowing that other individuals regularly support the organization, all act as heuristics of efficacy.
+An NGO facing criticism or crackdown abroad, on the other hand, may signal that potential donations could be used for legal fees, or signal that the NGO had perhaps done something to deserve the legal limitations it faces.
+Legal crackdown thus serves as a negative heuristic, signaling that donations might not be used as effectively as donors might hope.
 
@@
 
-TODO: I still need to finish this section, based on H~5b~ here: <https://stats.andrewheiss.com/silent-skywalk/notebook/results-practices.html#h5b-relationship-with-host-government-organizational-practices>.
-Main gist = the transparency and accountability effects decrease as relationship with host country gets worse—it's 12 pp when friendly, 8 pp when not.
+Financial transparency and accountability practices both have a positive (and likely interchangeable) effect on NGO favorability, while government criticism and crackdown have a negative effect and discourage potential donors from donating.
+As seen in @fig-transp-crackdown (and @apptbl-transp-crackdown), these heuristics also interact with each other.[^transp-only] The estimated posterior marginal means for different relationships with host governments move in the same direction regardless of whether an organization engages in transparency practices: organizations with friendly relationships with their host governments are most preferred, while organizations under government crackdown are least preferred.
+Transparency practices in the presence of crackdown seem to have two general effects.
+First, engaging in transparency offsets most of the negative effect of facing crackdown.
+The estimated marginal mean for an organization with friendly host government relationships and no transparency is `r mms_tc$no_friendly_relationship_with_government$pct`, which is equivalent to the estimated marginal mean for an organization under government crackdown that does engage in transparency.
+On average, donors are indifferent to both of these situations---again, a marginal mean of 25% represents the probability of selecting an organization at random---but the presence of transparency shifts NGOs facing crackdown from negatively preferred to indifferent, while the absence of transparency shifts NGOs with friendly relationships from positively preferred to indifferent.
+From a practical perspective, this suggests that NGOs under crackdown can engage in specific organizational practices to offset the negative signals that accompany their legal difficulties.
 
-TODO: Speculation about why that's the case
+Second, worsening host government relationships weaken the positive effect of transparency.
+On its own, as seen in @fig-all-results, engaging in transparency causes a `r amce$transparency_yes$pp_abs` percentage point increase in the probability of a respondent selecting an organization.
+The right panel of @fig-transp-crackdown (and @apptbl-transp-crackdown) shows how the causal effect of transparency changes across different types of government relationships.
+These AMCEs represent the difference in the estimated posterior marginal means of the two levels of transparency in the left panel.
+The effect shrinks as relationships become more negative: under friendly conditions, the median posterior AMCE of transparency is `r amce_tc$friendly_relationship_with_government$pp` percentage points (`r amce_tc$friendly_relationship_with_government$nice_ci_pd`); when an NGO is criticized, the transparency effect is `r amce_tc$criticized_by_government$pp` percentage points (`r amce_tc$criticized_by_government$nice_ci_pd`); when an NGO faces crackdown, the effect drops to `r amce_tc$under_government_crackdown$pp` percentage points (`r amce_tc$under_government_crackdown$nice_ci_pd`).
+The causal effect remains substantially positive regardless of the relationship---even under the worst conditions, engaging in transparency causes a 9 percentage point boost---suggesting that NGOs facing crackdown can still increase their favorability with donors by signalling their commitment to transparency and accountability.
+
+[^transp-only]: We only show the interaction of transparency and crackdown in @fig-transp-crackdown.
+Given the near interchangeability of the two treatments, the interaction between accountability and crackdown is nearly identical.
+We include both transparency and accountability in @apptbl-transp-crackdown.
+
+```{r}
+#| label: fig-transp-crackdown
+#| fig-width: 7.5
+#| fig-height: 3
+#| out-width: "100%"
+#| fig-cap: "Estimated marginal means and average marginal component effects for the interaction between transparency and crackdown"
+#| include: true
+p1 <- mms_transp_crackdown %>% 
+  ggplot(aes(x = avg, y = feat_govt, fill = feat_transp_short)) +
+  stat_halfeye() +
+  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
+  scale_x_continuous(labels = label_percent()) +
+  scale_y_discrete(labels = label_wrap(20)) +
+  scale_fill_manual(values = c(colorspace::lighten(clrs$prism[1], 0.6), clrs$prism[1])) +
+  labs(
+    x = "Marginal means of probabilities",
+    y = NULL,
+    title = "Posterior marginal means",
+    fill = "Transparency"
+  ) +
+  theme_ngo()
+
+p2 <- amces_transp_crackdown %>% 
+  ungroup() %>% 
+  separate_wider_delim(
+    feat_transp_short,
+    delim = " - ", 
+    names = c("feat_transp_short", "reference_level")
+  ) %>% 
+  mutate(feat_transp_short = factor(feat_transp_short, levels = levels(mms_transp_crackdown$feat_transp_short))) %>% 
+  mutate(feat_govt = factor(feat_govt, levels = levels(mms_transp_crackdown$feat_govt))) %>% 
+  ggplot(aes(x = avg, y = feat_govt, fill = "AMCE for transparency")) +
+  stat_halfeye() +
+  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) + 
+  scale_x_continuous(labels = label_pp) +
+  scale_y_discrete(labels = label_wrap(20)) +
+  scale_fill_manual(values = clrs$prism[7]) +
+  labs(
+    x = "Percentage point change in\nprobability of choice selection",
+    y = NULL,
+    title = "Posterior AMCEs",
+    fill = NULL
+  ) +
+  theme_ngo()
+
+p1 | p2
+```
 
@@
 population, we find that both financial transparency and accountability increases individuals' willingness to donate NGOs.
-Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability protect against this dampening effect.
-INSERT LINE/MAKE MORE SPECIFIC.
+Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability protect against this dampening effect, increasing the probability of support by nine percentage points under the worst conditions of legal crackdown.
 
-These results have important implications for NGO operations, fundraising and survivability at a time when a number of INGOs are dealing with hostile host governments.
+These results have important implications for NGO operations, fundraising, and survivability at a time when a number of INGOs are dealing with hostile host governments.
 A comparison of the effects of these organizational and structural factors is critical to NGO fundraising---while NGOs have control over transparency and accountability, as well as public perception of these organizational characteristics, they may little to no control over host government crackdowns over their organizations.
 As a result, they may need to rely entirely on improving individual donor perception of the causes of such crackdown, its impact on NGO operations and the need for private donor funds.
-This article provides an insight into the importance of different framing or informational heuristics that can motivate such individual donor giving.
+This article provides insight into the importance of different framing or informational heuristics that can motivate such individual donor giving.
 
 Government crackdown on civil society organizations is even more challenging for local NGOs in Global South countries, where much government and public support is channeled via service delivery organizations.
-Local groups tackling contentious issues may not be able to raise funds domestically, as publics may prefer donating to service organizations focusing on health, education, and poverty [@AbsarCrowRon:2017].
+Local groups tackling contentious issues may not be able to raise funds domestically, as individuals may prefer donating to service organizations focusing on health, education, and poverty [@AbsarCrowRon:2017].
 Even local philanthropists may be deterred from giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to poor tax incentives or a fear of retribution [@Brechenmacher:2017; @DupuyRonPrakash:2015; @Baoumi:2016].
@@
 # References
+
+::: {#refs}
+:::
+
+\newpage
+
+:::: {#appendix-count}
+
+# Appendix
+
+## Sample details
+
+::: {#apptbl-sample-details}
+
+```{r}
+#| label: table-sample-details
+#| include: true
+tbl_participant_summary <- participant_summary %>% 
+  select(
+    category, 
+    Question = clean_name,
+    Response = level,
+    N = count,
+    `%` = nice_prop
+  )
+
+base_table <- tbl_participant_summary %>% 
+  group_by(category) %>% 
+  gt()
+
+base_table$`_data` <- base_table$`_data` %>% 
+  mutate(Question = ifelse(!duplicated(Question), as.character(Question), ""))
+
+base_table %>% 
+  tab_style(
+    style = cell_fill(color = "grey90"),
+    locations = cells_row_groups()
+  ) %>% 
+  opts_theme() |>
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
+# tbl_participant_summary %>%
+#   kbl(
+#     align = c("l", "l", "c", "c"),
+#     longtable = TRUE, booktabs = TRUE, linesep = ""
+#   ) %>%
+#   pack_rows(
+#     index = table(fct_inorder(participant_summary$category)),
+#     latex_gap_space = "1.5em", indent = FALSE
+#   ) %>%
+#   collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>% 
+#   kable_styling(latex_options = c("repeat_header"))
+```
+
+Summary of individual respondent characteristics
+
+:::
+
+## All marginal means and AMCEs
+
+::: {#apptbl-all-results}
+
+```{r}
+#| label: table-all-results
+#| include: true
+mms_all_tbl <- mms_all %>% 
+  drop_na(feature_level) %>% 
+  group_by(feature_nice_paper, feature_level = fct_rev(feature_level)) %>% 
+  median_qi(avg) %>% 
+  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
+  select(feature_nice_paper, feature_level, mm_nice = nice)
+
+amces_all_tbl <- amces_all %>% 
+  mutate(feature_level = factor(feature_level, levels = levels(mms_all$feature_level))) %>% 
+  mutate(contrast = glue("{feature_level}−{reference_level}")) %>% 
+  group_by(feature_nice_paper, feature_level = fct_rev(feature_level), contrast) %>% 
+  summarize(
+    median_qi(avg),
+    p_gt_0 = sum(avg > 0) / n()
+  ) %>% 
+  ungroup() %>% 
+  mutate(is_reference = str_detect(contrast, "−NA")) %>% 
+  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
+  mutate(contrast = ifelse(is_reference, "*(Reference)*", contrast)) %>% 
+  mutate(nice = ifelse(is_reference, NA, glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}"))) %>% 
+  mutate(pd = ifelse(is_reference, NA, fmt_decimal2(p_neq_0))) %>% 
+  select(feature_nice_paper, feature_level, contrast, amce_nice = nice, pd)
+
+left_join(
+  mms_all_tbl, amces_all_tbl, 
+  by = join_by(feature_nice_paper, feature_level)
+) %>% 
+  mutate(across(c(feature_level, contrast), ~{
+    .x %>% 
+      str_replace_all("Transparency: ", "") %>% 
+      str_replace_all("Accountability: ", "")
+  })) %>% 
+  # mutate(contrast = str_replace_all(contrast, "[Transparency: |Accountability: ]", "")) %>% 
+  group_by(feature_nice_paper) %>% 
+  gt() %>% 
+  sub_missing(columns = everything(), missing_text = "—") %>% 
+  fmt_markdown(columns = c(mm_nice, amce_nice, contrast)) %>%
+  cols_align(align = "center", columns = everything()) %>% 
+  cols_align(align = "left", columns = c(feature_level, contrast)) %>% 
+  cols_label(
+    feature_level = "Feature", 
+    mm_nice = "Posterior EMM",
+    contrast = "Contrast",
+    amce_nice = "Posterior AMCE",
+    pd = "*p*~direction~",
+    .fn = md
+  ) %>% 
+  tab_style(
+    style = cell_text(v_align = "top"),
+    locations = cells_body()
+  ) %>% 
+  tab_style(
+    style = cell_fill(color = "grey90"),
+    locations = cells_row_groups()
+  ) %>% 
+  tab_footnote(
+    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
+    locations = cells_column_labels(columns = c(mm_nice, amce_nice))
+  ) %>% 
+  tab_footnote(
+    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
+    locations = cells_column_labels(columns = pd)
+  ) %>% 
+  gt_add_divider(columns = mm_nice, style = "dashed", weight = px(1)) %>% 
+  opt_footnote_marks(marks = "standard") %>% 
+  opt_horizontal_padding(3) %>% 
+  opts_theme() %>% 
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
+```
+
+Complete results
+
+:::
+
+## Additional marginal means and AMCEs
+
+::: {#apptbl-mms-trans-acc}
+
+```{r}
+#| label: table-mms-trans-acc
+#| include: true
+mms_trans_acc_all %>% 
+  group_by(feat_transp, feat_acc) %>% 
+  median_qi() %>% 
+  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
+  select(feat_transp, feat_acc, nice) %>% 
+  group_by(feat_transp) %>% 
+  gt() %>% 
+  fmt_markdown(columns = c(nice)) %>%
+  cols_align(align = "center", columns = c(nice)) %>% 
+  cols_align(align = "left", columns = c(feat_transp, feat_acc)) %>% 
+  cols_label(
+    feat_acc = "Features", 
+    nice = "Posterior EMM",
+  ) %>% 
+  tab_style(
+    style = cell_text(v_align = "top"),
+    locations = cells_body()
+  ) %>% 
+  tab_style(
+    style = cell_fill(color = "grey90"),
+    locations = cells_row_groups()
+  ) %>% 
+  tab_footnote(
+    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
+    locations = cells_column_labels(columns = c(nice))
+  ) %>% 
+  opt_footnote_marks(marks = "standard") %>% 
+  opt_horizontal_padding(3) %>% 
+  opts_theme() %>% 
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
+```
+
+Marginal means for all combinations of transparency and accountability
+
+:::
+
+::: {#apptbl-transp-crackdown}
+
+```{r}
+#| label: table-transp-crackdown
+#| include: true
+
+mms_transp_crackdown_tbl <- mms_transp_crackdown %>% 
+  group_by(feat_transp_short, feat_govt) %>% 
+  median_qi() %>% 
+  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
+  ungroup() %>% 
+  arrange(desc(feat_govt), desc(feat_transp_short)) %>% 
+  select(feat_transp_short, feat_govt, nice)
+
+amces_transp_crackdown_tbl <- amces_transp_crackdown_medians %>% 
+  ungroup() %>% 
+  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
+  mutate(feat_transp_short = str_replace(feat_transp_short, " - ", "−<br>")) %>% 
+  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
+  arrange(desc(feat_govt)) %>% 
+  select(contrast = feat_transp_short, diff_nice = nice, p_neq_0)
+
+mms_acc_crackdown_tbl <- mms_acc_crackdown %>% 
+  group_by(feat_acc_short, feat_govt) %>% 
+  median_qi() %>% 
+  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
+  ungroup() %>% 
+  arrange(desc(feat_govt), desc(feat_acc_short)) %>% 
+  select(feat_acc_short, feat_govt, nice)
+
+amces_acc_crackdown_tbl <- amces_acc_crackdown_medians %>% 
+  ungroup() %>% 
+  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
+  mutate(feat_acc_short = str_replace(feat_acc_short, " - ", "−<br>")) %>% 
+  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
+  arrange(desc(feat_govt)) %>% 
+  select(contrast = feat_acc_short, diff_nice = nice, p_neq_0)
+
+bind_rows(
+  bind_cols(
+    mms_transp_crackdown_tbl, 
+    amces_transp_crackdown_tbl %>% 
+      add_row(contrast = NA, .after = 1) %>% 
+      add_row(contrast = NA, .after = 3) %>% 
+      add_row(contrast = NA, .after = 5)
+  ) %>% 
+    mutate(feat_level = paste("Transparency:", feat_transp_short)) %>% 
+    select(-feat_transp_short),
+  bind_cols(
+    mms_acc_crackdown_tbl, 
+    amces_acc_crackdown_tbl %>% 
+      add_row(contrast = NA, .after = 1) %>% 
+      add_row(contrast = NA, .after = 3) %>% 
+      add_row(contrast = NA, .after = 5)
+  ) %>% 
+    mutate(feat_level = paste("Accountability:", feat_acc_short)) %>% 
+    select(-feat_acc_short)
+) %>% 
+  relocate(feat_level) %>% 
+  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
+  group_by(feat_govt) %>% 
+  gt() %>% 
+  sub_missing(columns = everything(), missing_text = "—") %>% 
+  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
+  cols_align(align = "center", columns = everything()) %>% 
+  cols_align(align = "left", columns = c(feat_level, contrast)) %>% 
+  cols_label(
+    feat_level = "Feature", 
+    nice = "Posterior EMM",
+    contrast = "Contrast",
+    diff_nice = "Posterior ∆",
+    p_neq_0 = "*p*~direction~",
+    .fn = md
+  ) %>% 
+  tab_style(
+    style = cell_text(v_align = "top"),
+    locations = cells_body()
+  ) %>% 
+  tab_style(
+    style = cell_fill(color = "grey90"),
+    locations = cells_row_groups()
+  ) %>% 
+  tab_footnote(
+    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
+    locations = cells_column_labels(columns = c(nice, diff_nice))
+  ) %>% 
+  tab_footnote(
+    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
+    locations = cells_column_labels(columns = p_neq_0)
+  ) %>% 
+  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
+  opt_footnote_marks(marks = "standard") %>% 
+  opt_horizontal_padding(3) %>% 
+  opts_theme() %>% 
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
+```
+
+Marginal means and AMCEs for interaction between transparency, accountability, and government relationships
+
+:::
+
+## Original model coefficients
+
+::: {#apptbl-coefs-orig}
+
+```{r}
+#| label: table-coefs-orig
+#| include: true
+notes <- c(
+  "Estimates are median posterior log odds from a multinomial logistic regression model with three possible categories, and the columns for µ1, µ2, and µ3 represent estimates for each of the outcomes;",
+  "95% credible intervals (equal-tailed quantile intervals) in brackets."
+)
+
+base_table <- modelsummary(
+  list("Posterior medians" = model_summary_table, "95% credible intervals" = model_summary_table),
+  shape = Feature + term ~ group,
+  estimate = c("estimate", "[{conf.low}, {conf.high}]"),
+  statistic = NULL,
+  output = "gt",
+  fmt = fmt_significant(2)
+)
+
+base_table$`_data` <- base_table$`_data` %>% 
+  mutate(Feature = ifelse(!duplicated(Feature), as.character(Feature), ""))
+
+base_table %>% 
+  tab_footnote(footnote = notes) %>% 
+  opts_theme() |>
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
+```
+
+Original model coefficients
+
+:::
+
+## Original survey
+
+TODO: That goes here.
+
+## Preregistration
+
+TODO: That goes here.
+
+::::

### 2023-11-15 R/funs_data.R

@@ -1,3 +1,14 @@
+get_from_osf <- function(osf_url, out_dir) {
+  library(osfr)
+  
+  get_osf <- osf_retrieve_file(osf_url) %>%
+    osf_download(path = out_dir,
+      conflicts = "overwrite",
+      progress = TRUE)
+  
+  return(get_osf$local_path)
+}
+
 make_clean_data <- function(path) {
   # Load original pre-anonymized Qualtrics data
   data_raw <- read_csv(path, guess_max = 1500, show_col_types = FALSE)

### 2023-11-15 R/funs_graphics.R

@@ -9,19 +9,38 @@ clrs <- list(
 # Theme stuff
 theme_ngo <- function() {
   theme_minimal(base_family = "Libre Franklin") +
-    theme(panel.grid.minor = element_blank(),
-      plot.title = element_text(family = "Libre Franklin", face = "bold"),
+    theme(
+      panel.grid.minor = element_blank(),
+      plot.title = element_text(
+        family = "Libre Franklin", face = "bold",
+        size = rel(0.95)
+      ),
       axis.title.x = element_text(
         family = "Libre Franklin SemiBold", face = "plain",
-        hjust = 0, size = rel(0.9), 
-        margin = margin(t = 10)),
+        hjust = 0, size = rel(0.9),
+        margin = margin(t = 10)
+      ),
       axis.title.y = element_text(
         family = "Libre Franklin SemiBold", face = "plain",
-        hjust = 1, size = rel(0.9), 
-        margin = margin(r = 10)),
-      strip.text = element_text(family = "Libre Franklin", face = "bold",
-        size = rel(0.75), hjust = 0),
-      strip.background = element_rect(fill = "grey90", color = NA))
+        hjust = 1, size = rel(0.9),
+        margin = margin(r = 10)
+      ),
+      strip.text = element_text(
+        family = "Libre Franklin", face = "bold",
+        size = rel(0.75), hjust = 0
+      ),
+      strip.background = element_rect(fill = "grey90", color = NA),
+      legend.position = "bottom",
+      legend.title = element_text(
+        size = rel(0.7), vjust = 0.5,
+        family = "Libre Franklin SemiBold", face = "plain"
+      ),
+      legend.key.size = unit(0.7, "line"),
+      legend.key = element_blank(),
+      legend.spacing = unit(0.1, "lines"),
+      legend.justification = "left",
+      legend.margin = margin(t = -5, b = 0, l = 0, r = 0)
+    )
 }
 
 set_annotation_fonts <- function() {
@@ -38,6 +57,9 @@ build_ci <- function(lower, upper) {
 # Put these scales things in functions so that they work like regular functions,
 # otherwise {targets} complains that "... may be used in an incorrect context"
 fmt_decimal <- \(x) scales::label_number(accuracy = 0.001, style_negative = "minus")(x)
+fmt_decimal2 <- \(x) scales::label_number(accuracy = 0.01, style_negative = "minus")(x)
+
[…]

### 2023-11-15 R/funs_misc_analysis.R

@@ -1,0 +1,121 @@
+build_modelsummary <- function(model) {
+  suppressPackageStartupMessages(library(modelsummary))
+  
+  coef_lookup <- tribble(
+    ~term, ~feature, ~level,
+    "feat_transpTransparency:Yes", "Transparency", "Transparency:Yes",
+    "feat_accAccountability:Yes", "Accountability", "Accountability:Yes",
+    "feat_govtCriticizedbygovernment", "Relationship with host government", "Criticized",
+    "feat_govtUndergovernmentcrackdown", "Relationship with host government", "Under crackdown",
+    "feat_orgGreenpeace", "Organizations", "Greenpeace",
+    "feat_orgOxfam", "Organizations", "Oxfam",
+    "feat_orgRedCross", "Organizations", "Red Cross",
+    "feat_issueEnvironment", "Issue areas", "Environment",
+    "feat_issueHumanrights", "Issue areas", "Human rights",
+    "feat_issueRefugeerelief", "Issue areas", "Refugee relief",
+    "feat_fundingFundedprimarilybyahandfulofwealthyprivatedonors", "Funding sources", "Few wealthy donors",
+    "feat_fundingFundedprimarilybygovernmentgrants", "Funding sources", "Government grants",
+    "Intercept", "Intercept", "Intercept"
+  ) %>% 
+    mutate(across(c(feature, level), ~fct_inorder(.x)))
+
+  # Need to use <<- so that these functions go to the parent environment so that
+  # modelsummary() can see them
+  tidy.brmsimple <<- function(x, ...) {
+    class(x) <- "brmsfit"
+    s <- summary(x)
+    
+    ret <- data.frame(
+      term = row.names(s$fixed),
+      estimate = s$fixed[, 1],
+      conf.low = s$fixed[, 3],
+      conf.high = s$fixed[, 4]
+    ) %>% 
+      separate_wider_delim(term, delim = "_", names = c("group", "term"), too_many = "merge") %>% 
+      mutate(group = str_replace(group, "mu", "µ")) %>% 
+      left_join(coef_lookup, by = join_by(term)) %>% 
+      mutate(Level = level) %>% 
+      rename(term_original = term, term = level, Feature = feature) %>% 
+      arrange(Feature, Level)
+    
+    return(ret)
+  }
+  
+  glance.brmsimple <<- function(x, ...) {
+    ret <- data.frame(
+      N = nrow(x$data)
+    )
+    
+    return(ret)
+  }
+  
+  # Make a fake simplified version of brms's class
[…]

### 2023-11-15 R/funs_tables.R

@@ -9,3 +9,23 @@ opts_theme <- function(x) {
     tab_options(column_labels.font.weight = "bold",
       row_group.font.weight = "bold")
 }
+
+#' Inline Listify
+#'
+#' This function takes a vector of characters, prefixes each element with a
+#' number in parentheses, and collapses them into a single string separated by
+#' semicolons.
+#'
+#' @param x A vector of characters.
+#'
+#' @return A single string where each element from the input vector is prefixed
+#'   with a number in parentheses and separated by semicolons.
+#'
+#' @examples
+#' inline_listify(c("apple", "banana", "cherry"))
+inline_listify <- function(x) {
+  numbers <- seq_along(x)
+  prefixed <- paste0("(", numbers, ") ", x)
+  collapsed <- paste(prefixed, collapse = "; ")
+  return(collapsed)
+}

### 2023-11-15 _targets.R

@@ -46,6 +46,12 @@ lapply(list.files("R", full.names = TRUE, recursive = TRUE), source)
 # Actual pipeline ---------------------------------------------------------
 list(
   ## Data and draws ----
+  tar_target(survey_results_file,
+    get_from_osf(osf_url = "https://osf.io/n2hwm/",
+      out_dir = here_rel("data", "raw_data")),
+    format = "file"),
+  tar_target(survey_results, read_rds(survey_results_file)),
+  
   tar_target(
     qualtrics_anonymized_file,
     here_rel("data", "raw_data", "conjointqsf_final.csv"),
@@ -59,9 +65,9 @@ list(
   ## Graphics and tables ----
   tar_target(graphic_functions, lst(
     theme_ngo, set_annotation_fonts, clrs, 
-    build_ci, fmt_decimal, label_pp
+    build_ci, fmt_decimal, fmt_decimal2, fmt_pp_int, label_pp
   )),
-  tar_target(table_functions, lst(opts_int, opts_theme)),
+  tar_target(table_functions, lst(opts_int, opts_theme, inline_listify)),
   tar_target(diagnostic_functions, lst(plot_trace, plot_trank, plot_pp)),
   
   ## Models ----
@@ -87,6 +93,10 @@ list(
   ## Helper objects like lookup tables
   tar_target(level_lookup, make_level_lookup(grid_treatment_only)),
   tar_target(feature_lookup, make_feature_lookup()),
+  
+  ## Miscellaneous analysis stuff
+  tar_target(participant_summary, create_sample_summary(survey_results)),
+  tar_target(model_summary_table, build_modelsummary(m_treatment_only)),
   
   ## Manuscript and notebook ----
   tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),

### 2023-11-18 manuscript/manuscript.qmd
OMG handle all tables with gt across ALL outputs!

@@
 
-knitr::opts_chunk$set(echo = FALSE, include = FALSE, 
-                      warning = FALSE, message = FALSE)
-
-knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
+knitr::opts_chunk$set(
+  echo = FALSE, include = FALSE,
+  warning = FALSE, message = FALSE
+)
+
+knitr::opts_chunk$set(
+  fig.align = "center", fig.retina = 3,
   fig.width = 6, fig.height = (6 * 0.618),
-                      out.width = "100%", collapse = TRUE)
-
-options(digits = 3, width = 120,
-        dplyr.summarise.inform = FALSE,
-        knitr.kable.NA = "")
+  out.width = "100%", collapse = TRUE
+)
+
+options(
+  digits = 3, width = 120,
+  dplyr.summarise.inform = FALSE
+)
 ```
@@
 library(gtExtras)
-library(kableExtra)
 library(modelsummary)
@@
 theme_set(theme_ngo())
+
+gt_linebreak <- function(x) {
+  if (fmt_out == "latex") {
+    x %>% 
+      str_replace_all("\\[", "{[}") %>% 
+      str_replace_all("\\]", "{]}") %>% 
+      kableExtra::linebreak(align = "c")
+  } else {
+    str_replace(x, "\\n", "<br>")
+  }
+}
+
+fmt_markdown_latex <- function(x, columns) {
+  if (fmt_out == "latex") {
+    fmt_passthrough(x, columns = columns, escape = FALSE)
+  } else {
+    fmt_markdown(x, columns = columns)
+  }
+}
+
+gt_pct <- function(x, page_width = 6) {
+  if (knitr::pandoc_to("latex")) {
+    paste0(page_width * (x / 100), "in")
+  } else {
+    gt::pct(x)
+  }
+}
 ```
@@
 Following screening, we received 1,016 viable responses.
-@apptbl-sample-details provides a detailed breakdown of the individual characteristics of our sample.
+@apptbl-sample-details-demographics, @apptbl-sample-details-charity, and @apptbl-sample-details-politics provide a detailed breakdown of the individual characteristics of our sample.
 In general, respondents were well balanced across genders and tended to be older than the national median age of 36---less than 20% of respondents were under 36 years old.
@@
 
+::: {.content-visible when-profile="nice"}
+\clearpage
+:::
+
 ## Experimental design
@@
 
+::: {#tbl-design}
+
+\footnotesize
+\renewcommand*{\arraystretch}{1.75}
+
 ```{r}
-#| label: tbl-design
-#| tbl-cap: "All experimental features and levels included in the conjoint experiment"
+#| label: table-design
 #| include: true
@@
 
-tribble(
+tbl_features_levels <- tribble(
   ~type, ~feature, ~levels,
@@
   "Comparison", "Funding source", inline_listify(funding)
-) %>% 
+)
+
+tbl_features_levels %>%
+  rowwise() %>% 
+  mutate(type = ifelse(
+    fmt_out == "latex",
+    str_replace_all(type, "~([^~]+)~", "\\\\textsubscript{\\1}"),
+    type
+  )) %>%
   gt() %>%
   cols_label(feature = "Feature/Attribute", levels = "Levels", type = "Purpose") %>%
-  fmt_markdown(columns = c(type)) %>% 
+  cols_width(feature ~ gt_pct(20), levels ~ gt_pct(50), type ~ gt_pct(15)) %>% 
+  fmt_markdown_latex(columns = c("type")) %>%
   tab_style(
@@
 ```
+
+All experimental features and levels included in the conjoint experiment
+
+:::
 
@@
 
+::: {#tbl-example}
+
+\footnotesize
+\renewcommand*{\arraystretch}{1.75}
+
 ```{r}
-#| label: tbl-example
-#| tbl-cap: "Example possible experimental task, with three randomized combinations of organizational attributes"
+#| label: table-example
 #| include: true
 withr::with_seed(12345, {
-  tribble(
+  tbl_example_task <- tribble(
     ~Attribute, ~`Option 1`, ~`Option 2`, ~`Option 3`, ~None,
@@
     "Relationship with host government", sample(govt, 1), sample(govt, 1), sample(govt, 1), "—"
-  ) %>%
+  )
+})
+
+tbl_example_task %>%
   gt() %>%
@@
   cols_align(align = "left", columns = Attribute) %>%
-    cols_width(everything() ~ pct(20)) %>%
+  cols_width(everything() ~ gt_pct(17)) %>%
   tab_style(
@@
   opts_theme()
-})
-```
+```
+
+Example possible experimental task, with three randomized combinations of organizational attributes
+
+:::
 
@@
 
-::: {#refs}
+::: {#refs .bibliography}
 :::
@@
 
-## Sample details
-
-::: {#apptbl-sample-details}
+```{=latex}
+\floatstyle{plaintop}
+\restylefloat{apptbl}
+```
+
+::: {#apptbl-sample-details-demographics}
+
+\footnotesize
 
 ```{r}
-#| label: table-sample-details
+#| label: table-sample-details-demographics
 #| include: true
@@
     `%` = nice_prop
-  )
-
-base_table <- tbl_participant_summary %>% 
-  group_by(category) %>% 
-  gt()
-
-base_table$`_data` <- base_table$`_data` %>% 
-  mutate(Question = ifelse(!duplicated(Question), as.character(Question), ""))
-
-base_table %>% 
-  tab_style(
-    style = cell_fill(color = "grey90"),
-    locations = cells_row_groups()
-  ) %>% 
+  ) %>% 
+  split(~category)
+
+tbl_participant_summary$Demographics %>% 
+  select(-category) %>% 
+  group_by(Question) %>% 
+  gt() %>% 
+  tab_spanner(label = "Demographics", columns = everything()) %>% 
+  cols_width(Response ~ gt_pct(30), everything() ~ gt_pct(15)) %>% 
+  cols_align(align = "center", columns = everything()) %>% 
+  cols_align(align = "left", columns = Response) %>% 
   opts_theme() |>
@@
   )
-# tbl_participant_summary %>%
-#   kbl(
-#     align = c("l", "l", "c", "c"),
-#     longtable = TRUE, booktabs = TRUE, linesep = ""
-#   ) %>%
-#   pack_rows(
-#     index = table(fct_inorder(participant_summary$category)),
-#     latex_gap_space = "1.5em", indent = FALSE
-#   ) %>%
-#   collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>% 
-#   kable_styling(latex_options = c("repeat_header"))
-```
-
-Summary of individual respondent characteristics
+```
+
+Demographics
 
@@
 
-## All marginal means and AMCEs
+\newpage
+
+::: {#apptbl-sample-details-charity}
+
+\footnotesize
+
+```{r}
+#| label: table-sample-details-charity
+#| include: true
+tbl_participant_summary$`Attitudes toward charity` %>% 
+  select(-category) %>% 
+  group_by(Question) %>% 
+  gt() %>% 
+  tab_spanner(label = "Attitudes toward charity", columns = everything()) %>% 
+  cols_width(Response ~ gt_pct(30), everything() ~ gt_pct(15)) %>% 
+  cols_align(align = "center", columns = everything()) %>% 
+  cols_align(align = "left", columns = Response) %>% 
+  opts_theme() |>
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
+```
+
+Attitudes toward charity
+
+:::
+
+::: {#apptbl-sample-details-politics}
+
+\footnotesize
+
+```{r}
+#| label: table-sample-details-politics
+#| include: true
+tbl_participant_summary$`Politics, ideology, and religion` %>% 
+  select(-category) %>% 
+  group_by(Question) %>% 
+  gt() %>% 
+  tab_spanner(label = "Politics, ideology, and religion", columns = everything()) %>% 
+  cols_width(Response ~ gt_pct(30), everything() ~ gt_pct(15)) %>% 
+  cols_align(align = "center", columns = everything()) %>% 
+  cols_align(align = "left", columns = Response) %>% 
+  opts_theme() |>
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
+```
+
+Politics, ideology, and religion
+
+:::
+
+\newpage
 
 ::: {#apptbl-all-results}
+
+\scriptsize
 
@@
   median_qi(avg) %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
+  mutate(nice = glue("{fmt_decimal(avg)}\n{build_ci(.lower, .upper)}")) %>% 
   select(feature_nice_paper, feature_level, mm_nice = nice)
@@
   mutate(contrast = ifelse(is_reference, "*(Reference)*", contrast)) %>% 
-  mutate(nice = ifelse(is_reference, NA, glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}"))) %>% 
+  mutate(nice = ifelse(is_reference, NA, glue("{fmt_decimal(y)}\n{build_ci(ymin, ymax)}"))) %>% 
   mutate(pd = ifelse(is_reference, NA, fmt_decimal2(p_neq_0))) %>% 
@@
   # mutate(contrast = str_replace_all(contrast, "[Transparency: |Accountability: ]", "")) %>% 
+  mutate(across(c(mm_nice, amce_nice), ~gt_linebreak(.))) %>% 
   group_by(feature_nice_paper) %>% 
@@
   sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(mm_nice, amce_nice, contrast)) %>%
+  fmt_markdown_latex(columns = c("mm_nice", "amce_nice")) %>% 
+  fmt_markdown(columns = c(contrast)) %>%
   cols_align(align = "center", columns = everything()) %>% 
@@
   ) %>% 
+  cols_width(
+    feature_level ~ gt_pct(18),
+    mm_nice ~ gt_pct(12),
+    contrast ~ gt_pct(35),
+    amce_nice ~ gt_pct(12),
+    pd ~ gt_pct(6)
+  ) %>% 
   tab_style(
@@
 
-## Additional marginal means and AMCEs
+\newpage
 
 ::: {#apptbl-mms-trans-acc}
+
+\footnotesize
 
@@
   median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
+  mutate(nice = glue("{fmt_decimal(avg)}\n{build_ci(.lower, .upper)}")) %>% 
+  mutate(across(c(nice), ~gt_linebreak(.))) %>% 
   select(feat_transp, feat_acc, nice) %>% 
@@
   gt() %>% 
-  fmt_markdown(columns = c(nice)) %>%
+  fmt_markdown_latex(columns = c("nice")) %>% 
   cols_align(align = "center", columns = c(nice)) %>% 
@@
 
+\footnotesize
+
 ```{r}
@@
   median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
+  mutate(nice = glue("{fmt_decimal(avg)}\n{build_ci(.lower, .upper)}")) %>% 
   ungroup() %>% 
@@
   ungroup() %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_transp_short = str_replace(feat_transp_short, " - ", "−<br>")) %>% 
+  mutate(nice = glue("{fmt_decimal(y)}\n{build_ci(ymin, ymax)}")) %>% 
+  mutate(feat_transp_short = str_replace(feat_transp_short, " - ", "−")) %>% 
   mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
@@
   ungroup() %>% 
-  mutate(nice = glue("{fmt_decimal(y)}<br>{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_acc_short = str_replace(feat_acc_short, " - ", "−<br>")) %>% 
+  mutate(nice = glue("{fmt_decimal(y)}\n{build_ci(ymin, ymax)}")) %>% 
+  mutate(feat_acc_short = str_replace(feat_acc_short, " - ", "−")) %>% 
   mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
@@
 ) %>%
+  mutate(contrast = ifelse(is.na(contrast), "*(Reference)*", contrast)) %>% 
+  mutate(across(c(nice, diff_nice), ~gt_linebreak(.))) %>% 
   relocate(feat_level) %>% 
@@
   sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown(columns = c(nice, diff_nice, contrast)) %>%
+  fmt_markdown_latex(columns = c("nice", "diff_nice")) %>% 
+  fmt_markdown(columns = contrast) %>% 
   cols_align(align = "center", columns = everything()) %>% 
@@
 
-## Original model coefficients
+\blandscape
 
 ::: {#apptbl-coefs-orig}
+
+\footnotesize
 
@@
 
+# lol there's a weird bug in {gt} where there's an error if the footnote is a
+# vector with multiple elements? So we flatten it when knitting to latex
 base_table %>% 
-  tab_footnote(footnote = notes) %>% 
+  tab_footnote(
+    footnote = ifelse(fmt_out == "latex", paste(notes, collapse = " "), notes)
+  ) %>%
   opts_theme() |>
@@
 
+\elandscape
+
+\newpage
+
 ## Original survey
@@
 
+\newpage
+
 ## Preregistration

### 2023-11-18 manuscript/manuscript.qmd
Suparna edits

@@
 abstract: |
-  Prior research on nonprofit fundraising has primarily examined how financial transparency and organizational accountability influence individual donor behavior.
-Over the past two decades, however, an increasing number of host governments have cracked down on non-governmental organizations (NGOs).
-QUESTION.
-We test these questions by administering a series of conjoint experiments in the US that examine...We find....
-This suggests...
+  Non-governmental organizations (NGOs) are a core component of global governance.
+Over the last two decades, however, an increasing number of host governments have cracked down on NGOs using a series of laws that adversely affect the availability and use of official aid funds for these organizations.
+In response to this dramatic shift in the NGO funding landscape, international NGOs (INGOs) have increasingly turned to individual donors to offset the loss of traditional funding sources.
+Prior research on NGO fundraising has primarily examined how financial transparency and organizational accountability influence individual donor behavior.
+How do these elements of private donor decision-making interact with structural-level factors such as host country politics and worsening civic environments when deciding to donate?
+Using a conjoint experiment with likely potential donors in the US, we find that financial transparency and accountability can protect against the dampening effect of host government crackdown and criticism of NGOs.
+Our results have important implications for how NGOs can adapt to worsening civic environments.
 keywords:
@@
 
-Over the last three decades, governments globally have increasingly sought to crack down on NGOs [@ChristensenWeinstein:2013; @DupuyRonPrakash:2016, @Heiss:2017; @GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022].
+Over the last two decades, governments globally have increasingly cracked down on NGOs [@ChristensenWeinstein:2013; @DupuyRonPrakash:2016; @Heiss:2017; @GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022].
 Repressive governments have cracked down on these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs [@DupuyRonPrakash:2016; @Chaudhry:2022].
@@
 This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [@GivingUSA:2019].
-This turn to private donors opens INGOs up to new dynamics in seeking out aid.
+This turn to private donors opens INGOs up to new dynamics in seeking out funds.
 Many organizations that had previously relied on governments and foundations had optimized their fundraising strategies for those donors, but now need to tailor their fundraising strategies to private individuals, who behave differently from governments and foundations.
 
-Individuals have different preferences and rely on signals of effectiveness that differ from the benchmarks that large donor agencies rely on, including financial transparency and accountability.
-While INGOs have control over these organizational-level factors that motivate donations, the political environment in the host countries INGOs work in---including the global crackdown on civil society that is causing many organizations to seek out private funding in the first place---is a structural factor that INGOs can rarely influence on their own.
+Individual donors have different preferences and rely on signals of effectiveness that differ from the benchmarks that large donor agencies rely on.
+While INGOs have control over these organizational-level factors such as financial transparency and accountability that motivate donations, the political environment in the host countries INGOs work in---including the global crackdown on civil society that is causing many organizations to seek out private funding in the first place---is a structural factor that INGOs can rarely influence on their own.
 How do organizational elements of private donor decision-making interact with broader structural limits on INGO fundraising?
@@
 feel about donating to legally besieged NGOs abroad?
-How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country politics when deciding to donate?
+How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country civic environments when deciding to donate?
 
 Existing research shows that organizational accountability and financial transparency play an important role in motivating individual donors to donate to NGOs [@HarrisNeely:2021; @SaxtonKuoHo:2012; @Vaccaro:2006; @VaccaroMadsen:2006; @Tremblay-BoirePrakash:2017; @Becker:2018].
-In this article, we extend this literature by evaluating how these organization-level characteristics influence private donor behavior in an era of shrinking civic space.
+We extend this literature by evaluating how these organization-level characteristics influence private donor behavior in an era of shrinking civic space.
 In considering this question, we engage with a growing body of research on the consequences of closing civic space on NGOs and donors [@DupuyPrakash:2018; @RightSpringmanWibbels:2022; @FransenDupuyHinfelaar:2021; @SundstromHenrySperling:2022; @Herrold:2020; @ChaudhryHeiss:2021].
@@
 Second, research shows that NGO leaders often have difficulty in attracting new donors and also find it challenging to motivate current donors [@GaudreauCao:2015].
-Examining the organizational-level factors in a group that make the average donor increase their charitable-giving towards these groups, especially when facing restricted civic space abroad, can help NGOs better target their programming and frame their funding appeals towards these donors.
-Our results thus have important implications for international NGOs facing increased antagonism by government abroad and point to possible methods of adapting to worsening or shrinking civic environments.
-
-Below, we summarize existing research on determinants of individual giving to foreign NGOs, laying out our expectations regarding how financial transparency, accountability shape individuals' philanthropic preferences in an environment of closing civic space.
-We then describe our conjoint experiment and and present the results.
+Examining organizational-level factors that make the average donor increase their charitable giving, especially when facing restricted civic space abroad, can help NGOs better frame their funding appeals towards these donors.
+Our results have important implications for INGOs facing increased antagonism by governments abroad and point to possible methods of adapting to worsening or shrinking civic environments.
+
+Below, we summarize existing research on determinants of individual giving to foreign NGOs, laying out our expectations regarding how financial transparency and accountability shape individuals' philanthropic preferences in an environment of closing civic space.
+We then describe our conjoint experiment and present the results.
 We conclude with implications for NGOs working in repressive countries.
@@
 Globally, a large amount of official aid resources were channeled to NGOs focusing on service provision and development.
-public and private donors perceived them as more efficient than states with weak institutions and poor governance; there was a high risk that such states would use aid transfers inefficiently [@Dietrich:2013].
+Public and private donors perceived these organizations as more efficient than states with weak institutions and poor governance; there was a high risk that such states would use aid transfers inefficiently [@Dietrich:2013].
 Less bureaucratic and more nimble than state institutions, NGOs were seen as key agents of development and democratization [@Herrold:2020, 142--43].
@@
 Private donors, however, do not necessarily seek out complete information about an organization's deservingness and efficiency, since this is a costly and time-consuming process [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
-As such, these donors respond to a host of heuristics and signals when deciding whether to donate to an NGO.
-Nonprofits fundraising internationally may therefore rely on framing to control perceptions [@ChaudhryHeiss:2021].
+As such, these donors respond to a range of heuristics and signals when deciding whether to donate to an NGO.
+Nonprofits fundraising from individual donors may therefore rely on framing to control perceptions [@ChaudhryHeiss:2021].
 Below, we theorize the effect of different frames surrounding a country's legal environment and nonprofit organizational characteristics on individual donor preferences.
@@
 Instead, individuals rely on heuristics to simplify their decision-making.
-One common signal for donors is organizational efficacy or the belief that an individual's donation will make a real difference [@ChaudhryHeiss:2021].
+One heuristic for potential donors is organizational efficacy or the belief that an individual's donation will make a real difference [@ChaudhryHeiss:2021].
 This can manifest itself through multiple mechanisms such as the amount an organization spends on overhead costs, whether an organization makes its finances public, or whether an organization participates in voluntary accountability practices, such as listing organizational details on websites like GuideStar and Charity Navigator.
 
-An NGO's financial transparency, defined as the degree of completeness of information, provided by organizations to the public concerning its business activities, is one tangible heuristics that donors use to make their decisions.
-NGOs can engage in financial transparency in a variety of ways such as distribution of audited financial statements, third party intermediaries.
-Research shows that transparency is associated with greater donations, lower debt and better governance [@HarrisNeely:2021; @SaxtonKuoHo:2012].
+Financial transparency, or the degree of completeness of information provided by organizations to the public concerning their activities, is one tangible heuristic that donors use to make their decisions.
+NGOs can engage in financial transparency in a variety of ways such as distribution of audited financial statements and third party intermediaries.
+Research shows that transparency is associated with greater donations, lower debt, and better governance [@HarrisNeely:2021; @SaxtonKuoHo:2012].
 It can also enhance donor trust and confidence in organizations [@Vaccaro:2006; @VaccaroMadsen:2006].
@@
 This effect becomes even stronger with media coverage of diversion [@HarrisPetrovitsYetman:2023].
-Organizational financial transparent can reduce actual or perceived information asymmetries between donors and charities, this potentially increasing donor likelihood of donating to an INGO.
+Organizational financial transparency can reduce actual or perceived information asymmetries between donors and charities, thus potentially increasing donor likelihood of donating to an INGO.
 
@@
 Private donors, subsequently, may be more likely to dislike NGOs that spend a large share of their revenues for unproductive purposes [@Rose-Ackerman:1982], or rather, a large share of resources on administration, management and fundraising.
+Lack of accountability is associated with lesser public trust, reputation, perceived quality and donation behavior [@Becker:2018].
 As @Tremblay-BoirePrakash:2017 point out, while individuals would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead, donors do not necessarily have the time to research charities thoroughly.
-Lack of accountability is associated with lesser public trust, reputation, perceived quality and donation behavior [@Becker:2018].
 
@@
 
-While NGOs have control over organizational factors such as transparency and accountability, and can work to improve these characteristics and public perception of them, these NGOs may have little to no control over structural factors that can also influence philanthropy.
+While NGOs have control over organizational factors such as transparency and accountability and can work to improve these characteristics and public perception of them, NGOs may have little to no control over structural factors that can also influence philanthropy.
 These structural factors include political contexts in NGO host countries, especially their environments for civil society organizations.
@@
 
-Some NGOs have adapted to their repressive environments by recreating their organizations and changing their mission to avoid directly confronting the government.
-Analyzing the impact of anti-NGO laws in Bangladesh and Zambia, scholars have similarly found that NGOs with a broad mission ended up restricting themselves to service work and giving up on their advocacy work.
-Those that continued to engage in transnational advocacy changed the targets of their advocacy, the issues they focused on, and the language they used.
-For instance, many NGOs stopped lobbying the central government and focused their advocacy efforts on lower levels of government [@FransenDupuyHinfelaar:2021].
+Some NGOs have adapted to repressive environments by recreating their organizations and changing their mission to avoid directly confronting the government.
+Analyzing the impact of anti-NGO laws in Bangladesh and Zambia, scholars have found that NGOs with a broad mission ended up restricting themselves to service work and giving up on their advocacy work.
+Those that continued to engage in transnational advocacy changed the targets of their advocacy, the issues they focused on, and the language they used [@FransenDupuyHinfelaar:2021].
 Similarly, in Russia, many NGOs working with foreign partners and lobbying the central government no longer consider it an effective strategy [@SundstromHenrySperling:2022].
@@
 The changes in civic environments impacting NGO activity have also influenced official donor responses.
-In response to the passage of these laws, scholars have found that while multilateral donors do not reduce aid following the passage of anti-NGO laws, they are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018].
+Scholars have found that while multilateral donors do not reduce aid following the passage of anti-NGO laws, they are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018].
 Further, advocacy-oriented donors---i.e., those that fund democracy and civil society promotion activities---reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022].
-However, previous literature has established that individual private donors may not necessarily use the same metrics as official donors [@DesaiKharas:2018; @ChaudhryHeiss:2021].
+However, previous literature has established that individual private donors may not necessarily use the same metrics as official donors when deciding to donate [@DesaiKharas:2018; @ChaudhryHeiss:2021].
 Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the grounds [@EasterlyWilliamson:2011].
@@
 Importantly, when testing these hypotheses, we do not assume that individual donors have perfect knowledge about an NGO or the country an NGO operates in.
-Moreover, the average donor will not know exactly what "crackdown" entails for any given organization (i.e., does it mean an NGO was expelled, or that its assets were frozen, or that it received a fine?).
+The average donor will not know exactly what "crackdown" entails for any given organization (i.e., does it mean an NGO was expelled, or that its assets were frozen, or that it received a fine?).
 For the sake of this experiment, this ambiguity is not a central concern as the heuristics we explore here are explicitly simplified short- cuts to donor information-gathering.
-Knowing that an organization is financially transparent (even if donors are not familiar with specific kinds of requirements regarding transparency) or knowing that an NGO faces legal trouble abroad should be enough to trigger the effect of these frames on donor preferences.
+Knowing that an organization is financially transparent (even if donors are not familiar with specific kinds of requirements regarding transparency), or knowing that an NGO faces legal trouble abroad should be enough to trigger the effect of these frames on donor preferences.
 Moreover, although many NGOs make information about their operations accessible through annual reports, it is time-consuming to track down that information.
@@
 Brand recognition appears to be a powerful heuristic for donor decision making.
-Respondents were substantially more likely to prefer an organization when it was identified as the Red Cross, with an median posterior marginal mean of `r mms$red_cross$pct` (95% cred.
+Respondents were substantially more likely to prefer an organization when it was identified as the Red Cross, with a median posterior marginal mean of `r mms$red_cross$pct` (95% cred.
 int.
@@
 Compared to Amnesty International, Greenpeace causes a small `r amce$greenpeace$pp` percentage point increase (`r amce$greenpeace$nice_ci_pd`) and Oxfam causes a small `r amce$oxfam$pp_abs` percentage point decrease (`r amce$oxfam$nice_ci_pd`) in the probability of selecting an organization.
-The Red Cross brand name heuristic is actually the strongest of all the experimental treatments and features, signifying the organization's brand power and goodwill among potential donors.
+The Red Cross brand name heuristic is the strongest of all the experimental treatments and features, signifying the organization's brand power and goodwill among potential donors.
 
@@
 Finally, organization funding source also serves as a reliable donor heuristic.
-Organizations that are funded by many small donors are substantially more popular than those funded by government grants or a a small group of wealthy donors---when compared to many small donors, both government and wealthy individual funding cause `r amce$funded_primarily_by_government_grants$pp_abs` and `r amce$funded_primarily_by_a_handful_of_wealthy_private_donors$pp_abs` percentage point decreases in the probability of selection (`r amce$funded_primarily_by_government_grants$nice_ci_pd` and `r amce$funded_primarily_by_a_handful_of_wealthy_private_donors$nice_ci_pd`).
+Organizations that are funded by many small donors are substantially more popular than those funded by government grants or a small group of wealthy donors---when compared to many small donors, both government and wealthy individual funding cause `r amce$funded_primarily_by_government_grants$pp_abs` and `r amce$funded_primarily_by_a_handful_of_wealthy_private_donors$pp_abs` percentage point decreases in the probability of selection (`r amce$funded_primarily_by_government_grants$nice_ci_pd` and `r amce$funded_primarily_by_a_handful_of_wealthy_private_donors$nice_ci_pd`).
 These effects follow existing research on donor efficacy [@ChaudhryHeiss:2021]---when donors know that an organization is funded by others like themselves and that the marginal benefit of their individual donation is important, they are more likely to donate.
@@
 Contrary to our expectations, respondents appear to prefer donating to NGOs that have friendly relationships with their host governments, with a marginal mean of `r mms$friendly_relationship_with_government$pct` (compared to a baseline of 25%; `r mms$friendly_relationship_with_government$nice_ci`).
-Respondents are less likely to donate when an organization is criticized by its host government, and far less likely when an organization is under legal crackdown.
-Compared to other treatments, an organization facing legal crackdown has roughly the same negative preference as an organization without transparency or accountability measures, while having a friendly relationship is generally equivalent to engaging in transparency or accountability.
-
-In addition to these overall trends in preferences, we can measure the causal effect of moving from friendly relations to something more restrictive.
+Respondents are less likely to donate when an organization is criticized by its host government, and far less likely when an organization faces crackdown.
+Compared to other treatments, an organization facing crackdown has roughly the same negative preference as an organization without transparency or accountability measures, while having a friendly relationship is generally equivalent to engaging in transparency or accountability.
+
+In addition to these overall trends in preferences, we can measure the causal effect of moving from friendly NGO–government relations to a more antagonistic relationship.
 Using friendly relationship as the reference category, facing criticism by the host government causes a `r amce$criticized_by_government$pp_abs` percentage point reduction in the probability of selection (`r amce$criticized_by_government$nice_ci_pd`).
 Participants respond more strongly as the relationship becomes more conflictual and restricted---an NGO facing crackdown sees a `r amce$under_government_crackdown$pp_abs` percentage point reduction (`r amce$under_government_crackdown$nice_ci_pd`) in support.
-We thus find strong evidence against H~2~: if NGOs face legal crackdown abroad, individual donors are *less* likely to donate to them.
+We thus find strong evidence against H~2~: if NGOs face crackdown abroad, individual donors are *less* likely to donate to them.
 For context, the causal effect of facing crackdown is the same magnitude as the Red Cross branding effect, but in the opposite direction---donors seem to penalize NGOs facing criticism to the same extent that they reward the Red Cross.
@@
 An NGO facing criticism or crackdown abroad, on the other hand, may signal that potential donations could be used for legal fees, or signal that the NGO had perhaps done something to deserve the legal limitations it faces.
-Legal crackdown thus serves as a negative heuristic, signaling that donations might not be used as effectively as donors might hope.
+Crackdown thus serves as a negative heuristic, signaling that donations might not be used as effectively as donors might hope.
 
@@
 The estimated marginal mean for an organization with friendly host government relationships and no transparency is `r mms_tc$no_friendly_relationship_with_government$pct`, which is equivalent to the estimated marginal mean for an organization under government crackdown that does engage in transparency.
-On average, donors are indifferent to both of these situations---again, a marginal mean of 25% represents the probability of selecting an organization at random---but the presence of transparency shifts NGOs facing crackdown from negatively preferred to indifferent, while the absence of transparency shifts NGOs with friendly relationships from positively preferred to indifferent.
-From a practical perspective, this suggests that NGOs under crackdown can engage in specific organizational practices to offset the negative signals that accompany their legal difficulties.
+On average, donors are indifferent to both situations---again, a marginal mean of 25% represents the probability of selecting an organization at random---but the presence of transparency shifts NGOs facing crackdown from negatively preferred to indifferent, while the absence of transparency shifts NGOs with friendly relationships from positively preferred to indifferent.
+From a practical perspective, this suggests that NGOs under crackdown can focus on improving specific organizational practices to offset the negative signals that accompany their legal difficulties.
 
@@
 
-Over the last two decades, governments globally have systematically controlled and repressed NGOs using both violent tactics and administrative means over the last three decades---a phenomenon known as "closing" or "shrinking" civic space.
+Over recent years, governments globally have systematically controlled and repressed NGOs using both violent tactics and legal means---a phenomenon known as "closing" or "shrinking" civic space.
 This trend of closing civic space has important implications for local and international NGOs as well as donors.
@@
 However, we know relatively little about how state repression of NGOs affects the preferences of foreign private donors [@ChaudhryHeiss:2021].
-The responses of elite donors and foundations to government crackdown on civil society organizations remains a ripe area for research.
 Unlike state donors, individual and elite donors may not necessarily withdraw or reduce support for NGOs facing harassment abroad.
@@
 feel about donating to legally besieged NGOs abroad?
-How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country politics when deciding to donate?
+How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country civic environments when deciding to donate?
 We argue that informational heuristics about NGOs’ legal and political environments and organizational-level attributes can influence donor preferences for international giving.
@@
 population, we find that both financial transparency and accountability increases individuals' willingness to donate NGOs.
-Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability protect against this dampening effect, increasing the probability of support by nine percentage points under the worst conditions of legal crackdown.
-
-These results have important implications for NGO operations, fundraising, and survivability at a time when a number of INGOs are dealing with hostile host governments.
+Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability protect against this dampening effect, increasing the probability of philanthropic domations by nine percentage points under the worst conditions of legal crackdown.
+Our results highlight the importance of organizational characteristics like transparency and accountability even in an era of closing civic space.
+
+These results have important implications for NGO operations, fundraising, and survivability at a time when many INGOs are dealing with hostile host governments.
 A comparison of the effects of these organizational and structural factors is critical to NGO fundraising---while NGOs have control over transparency and accountability, as well as public perception of these organizational characteristics, they may little to no control over host government crackdowns over their organizations.
-As a result, they may need to rely entirely on improving individual donor perception of the causes of such crackdown, its impact on NGO operations and the need for private donor funds.
-This article provides insight into the importance of different framing or informational heuristics that can motivate such individual donor giving.
-
+As a result, they may need to rely entirely on improving individual donor perception of organizational transparency and accountability, its impact on NGO operations and the need for private donor funds at a time of shrinking civic space.
+This article thus provides insight into the importance of different framing or informational heuristics that can motivate such individual donor giving.
+
+The responses of elite donors and foundations to government crackdown on civil society organizations remains a ripe area for research.
+Future research should test how well these results map on to elite individual donors, not just the average private donor, as well as determine the extent to which these preferences translate into behavior.
+Future research should also test the generalizability of these findings to non-American populations.
+Donors in European countries may have different preferences when choosing to donate to NGOs, as nonprofits in the European sector typically do not rely as much on government funding, and already receive more support from private donors compared to the American context.
 Government crackdown on civil society organizations is even more challenging for local NGOs in Global South countries, where much government and public support is channeled via service delivery organizations.
@@
 Even local philanthropists may be deterred from giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to poor tax incentives or a fear of retribution [@Brechenmacher:2017; @DupuyRonPrakash:2015; @Baoumi:2016].
-Our results highlight the importance of organizational characteristics like transparency and accountability even in an era of closing civic space.
-By finding new ways to communicate about organizational transparency and accountability to potential donors, as well as the causes of government crackdowns on even transparent organizations, NGOs can help overcome individual donors' concerns about host governments' criticisms of and crackdown on these groups.
-
-Future research should test how well these results map on to elite individual donors, not just the average private donor, as well as determine the extent to which these preferences translate into behavior.
-Future research should also test the generalizability of these findings to non-American populations.
-Donors in European countries may have different preferences when choosing to donate to NGOs, as nonprofits in the European sector typically do not rely as much on government funding, and already receive more support from private donors compared to the American context.
+Future research should examine how local NGOs can overcome individual foreign donors’ concerns about host governments' criticisms of and crackdown on these groups.
 

### 2023-11-18 manuscript/manuscript.qmd
Address Suparna's remaining issues/questions

@@
 Conversely, learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability can protect against this dampening effect.
-These effect sizes are substantial: ten percentage point increases and decreases in the predicted probability of choosing to donate to an NGO.
+These effect sizes are substantial: our key treatment effects have a magnitude of around ten percentage points in the predicted probability of choosing to donate to an NGO.
 
 Our findings make two main contributions.
-While recent research on private foreign aid has examined funding decisions of donor NGOs and foundations[^1], we know less about the funding choices of the individuals responsible for much of these private aid flows [@DesaiKharas:2018].
+While recent research on private foreign aid has examined funding decisions of donor NGOs and foundations,[^1] we know less about the funding choices of the individuals responsible for much of these private aid flows [@DesaiKharas:2018].
 The systematic study of private foreign aid is still in its infancy---there is an absence of expansive and high quality data [@GreenhillPrizzonRogerson:2013], and most research has been restricted to elite, high net-worth donors [@USTrust2014].
@@
 A conjoint research design also allows us to calculate treatment effects even if respondents do not see every combination of organization attributes, and correspondingly provides a substantial increase in statistical power.
-In standard factorial experimental designs, every combination of treatment attributes would need to be shown to some number of participants would ordinarily need to be shown all possible combinations of experimental attributes.
-In our experiment, we presented respondents with six possible treatments with varying counts of attributes for each treatment, yielding 576 possible unique combinations of features.
+In standard factorial experimental designs, participants would ordinarily need to be shown all possible combinations of experimental attributes.
+In our experiment, we presented respondents with six possible treatments with randomized attributes for each treatment, yielding 576 possible unique combinations of features.
 Even with respondents answering twelve iterations of the experiment, not every combination was seen.
@@
 
-After collecting baseline information on respondent demographics and attitudes toward charity and voluntarism, we presented respondents with three randomly generated hypothetical international nonprofit organizations with six randomly assigned features.
+After collecting baseline information on respondent demographics and attitudes toward charity and voluntarism, we presented respondents with three randomly generated hypothetical international nonprofit organizations with six randomly assigned features, along with an option to select none.
 In this paper, we hypothesize and empirically test the effect of financial transparency, accountability, and host country relationship on the likelihood of donations.
@@
 
-Charity Navigator---a large database of U.S.
-nonprofit financial information---categorizes its nonprofit organizations into four core sectors: humanitarian relief, human rights, development, and the environment.
-Accordingly, we used four nonprofits that are stereotypical for each issue: the International Committee of the Red Cross (humanitarian relief), Amnesty International (human rights), Oxfam (development), and Greenpeace (environment).
+At the time of designing the study, Charity Navigator---a large database of U.S.
+nonprofit financial information---categorized international nonprofit activities into four general causes: (1) development, (2) humanitarian relief, (3) international affairs and human rights advocacy, and (4) environment.[^cn] Accordingly, we used four nonprofits that are stereotypical for each cause: the International Committee of the Red Cross (humanitarian relief), Amnesty International (human rights), Oxfam (development), and Greenpeace (environment).
 We also varied several other features, including four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), two organizational practices (financial transparency and third-party accountability audits), three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and three relationships with host governments (friendly, criticized by the government, and under government crackdown).
 
-After presenting respondents with three organizations, we asked them which of the three they would be willing to donate to, along with an option for no selection (see @tbl-example for an example).
+[^cn]: See <http://web.archive.org/web/20170315000746/https://www.charitynavigator.org/index.cfm?bay=search.categories&categoryid=7>.
+Under the explicitly "International" category, Charity Navigator listed Development and Relief Services; International Peace, Security, and Affairs; and Humanitarian Relief Supplies.
+The "Environment" category is listed separately but contains many INGOs such as Greenpeace and the World Wide Fund for Nature (WWF).
+At the time of writing, Charity Navigator had changed its taxonomy to include 18 broader categories.
+
+After presenting respondents with a set of organizations, we asked them which of the three they would be willing to donate to, along with an option for no selection (see @tbl-example for an example).
 We then repeated the process eleven more times for a total of twelve randomized iterations of hypothetical combinations of attributes, resulting in 12,192 completed experimental tasks (12 iterations × 1,016 respondents).

### 2023-11-18 manuscript/manuscript.qmd
Add EMM explanation and preregistration

@@
 
+## Calculating marginal means and AMCEs from a multinomial model using a reference grid
+
+To find the causal effects defined in each of our estimands, we calculate estimated marginal means (EMMs) by finding the fitted probability-scale values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding = 576 rows).
+We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.
+At its core, a "marginal mean" refers to the literal mean in the margins in a contingency table of model predictions, and differences in marginal means are equivalent to marginal effects or regression coefficients.
+
+When working with the results for our multinomial regression model, we rely on estimated marginal means rather than raw regression coefficients because of the complexity of the model.
+As seen in @apptbl-coefs-orig, the model returns three sets of coefficients per conjoint level.
+Each coefficient shows the shift in probability that someone will choose an organization from column 1, column 2, or column 3, so we get a coefficient for each of those outcomes (or µ1, µ2, and µ3).
+Under experimental conditions where cells in the contingency table are randomly assigned, it is safe to assume that the cell proportions are equal and then marginalize (i.e.
+find the average) across the rows or columns.
+This allows us to take the average of each set of coefficients (e.g.
+µ1, µ2, and µ3 for "Transparency = Yes") to create a single value per coefficient.
+
+To convert EMMs and AMCEs to a more interpretable probability scale (rather than the original log odds scale), we generate predicted values (marginalized across the three µ terms) for each of the 576 unique combinations of feature levels.
+@apptbl-grid-example provides an excerpt from this grid, showing six rows where accountability, organization, issue area, and funding are identical and held constant, while transparency and government relations vary.
+
+::: {#apptbl-grid-example}
+
+\footnotesize
+
+```{r}
+#| label: table-grid-example
+#| include: true
+grid_example <- expand_grid(
+  feat_transp = c("Transparency: Yes", "Transparency: No"), 
+  feat_acc = "Accountability: Yes", 
+  feat_govt = c("Friendly relationship with government", "Criticized by government", "Under government crackdown"),
+  feat_org = "Red Cross", 
+  feat_issue = "Emergency response", 
+  feat_funding = "Funded primarily by many small private donations"
+)
+
+preds_small <- preds_all %>% 
+  group_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>% 
+  summarize(avg = mean(.epred)) %>% 
+  inner_join(
+    grid_example, 
+    by = join_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt)
+  ) %>% 
+  mutate(avg_nice = label_comma(accuracy = 0.001)(avg))
+
+p_sm <- preds_small %>% 
+  group_by(feat_transp) %>% 
+  summarize(
+    emm_numeric = mean(avg),
+    emm = label_comma(accuracy = 0.001)(mean(avg)),
+    list = knitr::combine_words(avg_nice, sep = " + ", and = "")
+  ) %>% 
+  mutate(feat_transp = janitor::make_clean_names(feat_transp)) %>% 
+  split(~feat_transp)
+
+amce_fake <- p_sm$transparency_yes$emm_numeric - p_sm$transparency_no$emm_numeric
+amce_tr_fake <- label_comma(accuracy = 0.001)(amce_fake)
+amce_tr_fake_pp <- label_comma(accuracy = 1, scale = 100)(amce_fake)
+
+preds_small %>% 
+  select(-avg) %>% 
+  ungroup() %>% 
+  gt() %>% 
+  cols_label(
+    feat_transp = "Transparency", 
+    feat_acc = "Accountability", 
+    feat_govt = "Government",
+    feat_org = "Organization",
+    feat_issue = "Issue",
+    feat_funding = "Funding",
+    avg_nice = "EMM"
+  ) %>%
+  cols_width(everything() ~ gt_pct(12)) %>% 
+  cols_width(avg_nice ~ gt_pct(7)) %>% 
+  tab_style(
+    style = cell_text(v_align = "top"),
+    locations = cells_body()
+  ) %>%
+  opts_theme() |>
+  tab_options(
+    quarto.disable_processing = TRUE
+  )
+```
+
+Excerpt from complete reference grid of all 576 possible combinations of attribute features and levels
+
+:::
+
+To calculate the marginal mean for a feature, we find the average predicted value across each the levels of that feature.
+To illustrate, assume that @apptbl-grid-example represents the full reference grid of all experimental features and levels.
+The marginal means for transparency would be (`r p_sm$transparency_no$list`)/3 = `r p_sm$transparency_no$emm` when transparency is set to "no", and (`r p_sm$transparency_yes$list`)/3 = `r p_sm$transparency_yes$emm` when transparency is set to "yes".
+In reality, the marginal mean for transparency reported in @fig-all-results and @apptbl-all-results represent the average of 288 rows where transparency is no and 288 rows where transparency is yes.
+
+To calculate the AMCE for a feature, we find the difference in estimated marginal means.
+If we again assume that @apptbl-grid-example contains the full reference grid, the AMCE for transparency would be `r p_sm$transparency_yes$emm` − `r p_sm$transparency_no$emm`, or `r amce_tr_fake`, or `r amce_tr_fake_pp` percentage points.
+Again, this is not actually the true causal effect—the real AMCE in @fig-all-results and @apptbl-all-results is the difference in marginal means for the 288 rows where transparency is no and the 288 rows where transparency is yes.
+
+## Additional tables
+
 ```{=latex}
@@
 
-## Original survey
-
-TODO: That goes here.
-
-\newpage
+::: {.content-visible when-profile="ms"}
+\singlespacing
+:::
 
@@
 
-TODO: That goes here.
+::: {.callout-important icon=false}
+### Consensed preregistration
+
+This is an anonymized and condensed version of our full OSF preregistration protocol.
+:::
+
+{{< include text/preregistration.md >}}
 

### 2023-11-18 manuscript/manuscript.qmd
Minor tweaks

@@
 short-title: "Why Donors Donate"
-date: "2023-11-14"
+date: "2023-11-18"
 author:
@@
 link-citations: true
-word-count: 9324
+word-count: 9350
 
@@
 
+:::
+
+::: {.content-visible when-profile="ms"}
+\clearpage
 :::
@@
 We do not work with the raw results of the model directly (though a complete table of results is included in @apptbl-coefs-orig).
-Given the conjoint design, we instead create a complete balanced grid of all 576 combinations of feature levels (4 organizations × 4 issues × 2 transparency × 2 accountability × 3 funding × 3 government relationships) and use the model to calculate predicted probabilities of choice selection for each row of possible treatment values.
+Given the conjoint design, we instead create a complete balanced grid of all 576 combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding) and use the model to calculate predicted probabilities of choice selection for each row of possible treatment values.
 We then collapse this set of predicted probabilities into estimated marginal means (EMMs) for specific features of interested while marginalizing or averaging over all other predicted variables.
 To calculate the causal effect of a treatment, we find the average marginal component effect (AMCE), which is equivalent to the difference in estimated marginal means for specific feature levels.
-For example, when estimating the marginal means of the transparency treatment, we find the average predicted probability across the 288 rows of the reference grid where transparency is true and across the 288 rows where transparency is false---the difference between these two estimated marginal means is the AMCE, or the causal effect of the treatment holding all other values constant, on the probability scale.
+For example, when estimating the marginal means of the transparency treatment, we find the average predicted probability across the 288 rows of the reference grid where transparency is true and across the 288 rows where transparency is false---the difference between these two estimated marginal means is the AMCE, or the causal effect of the treatment holding all other values constant, on the probability scale (see the appendix for an extended illustration and demonstration of the EMM and AMCE calculating process).
 
@@
 #| label: fig-all-results
-#| fig-width: 12
-#| fig-height: 6
+#| fig-width: 7.5
+#| fig-height: 8.5
 #| out-width: "100%"
 #| fig-cap: "Estimated marginal means and average marginal component effects for conjoint experiment results"
-#| column: page
 #| include: true
@@
   scale_x_continuous(labels = label_percent()) +
+  scale_y_discrete(labels = label_wrap(20)) +
   scale_fill_manual(values = clrs$prism[1:6]) +
@@
   scale_x_continuous(labels = label_pp) +
+  scale_y_discrete(labels = label_wrap(20)) +
   scale_fill_manual(values = clrs$prism[1:6]) +
   labs(
-    x = "Percentage point change in probability of choice selection",
+    x = "Percentage point change in\nprobability of choice selection",
     y = NULL,
@@
 
-Second, worsening host government relationships weaken the positive effect of transparency.
-On its own, as seen in @fig-all-results, engaging in transparency causes a `r amce$transparency_yes$pp_abs` percentage point increase in the probability of a respondent selecting an organization.
-The right panel of @fig-transp-crackdown (and @apptbl-transp-crackdown) shows how the causal effect of transparency changes across different types of government relationships.
-These AMCEs represent the difference in the estimated posterior marginal means of the two levels of transparency in the left panel.
-The effect shrinks as relationships become more negative: under friendly conditions, the median posterior AMCE of transparency is `r amce_tc$friendly_relationship_with_government$pp` percentage points (`r amce_tc$friendly_relationship_with_government$nice_ci_pd`); when an NGO is criticized, the transparency effect is `r amce_tc$criticized_by_government$pp` percentage points (`r amce_tc$criticized_by_government$nice_ci_pd`); when an NGO faces crackdown, the effect drops to `r amce_tc$under_government_crackdown$pp` percentage points (`r amce_tc$under_government_crackdown$nice_ci_pd`).
-The causal effect remains substantially positive regardless of the relationship---even under the worst conditions, engaging in transparency causes a 9 percentage point boost---suggesting that NGOs facing crackdown can still increase their favorability with donors by signalling their commitment to transparency and accountability.
-
-[^transp-only]: We only show the interaction of transparency and crackdown in @fig-transp-crackdown.
-Given the near interchangeability of the two treatments, the interaction between accountability and crackdown is nearly identical.
-We include both transparency and accountability in @apptbl-transp-crackdown.
-
 ```{r}
@@
 
+Second, worsening host government relationships weaken the positive effect of transparency.
+On its own, as seen in @fig-all-results, engaging in transparency causes a `r amce$transparency_yes$pp_abs` percentage point increase in the probability of a respondent selecting an organization.
+The right panel of @fig-transp-crackdown (and @apptbl-transp-crackdown) shows how the causal effect of transparency changes across different types of government relationships.
+These AMCEs represent the difference in the estimated posterior marginal means of the two levels of transparency in the left panel.
+The effect shrinks as relationships become more negative: under friendly conditions, the median posterior AMCE of transparency is `r amce_tc$friendly_relationship_with_government$pp` percentage points (`r amce_tc$friendly_relationship_with_government$nice_ci_pd`); when an NGO is criticized, the transparency effect is `r amce_tc$criticized_by_government$pp` percentage points (`r amce_tc$criticized_by_government$nice_ci_pd`); when an NGO faces crackdown, the effect drops to `r amce_tc$under_government_crackdown$pp` percentage points (`r amce_tc$under_government_crackdown$nice_ci_pd`).
+The causal effect remains substantially positive regardless of the relationship---even under the worst conditions, engaging in transparency causes a 9 percentage point boost---suggesting that NGOs facing crackdown can still increase their favorability with donors by signalling their commitment to transparency and accountability.
+
+[^transp-only]: We only show the interaction of transparency and crackdown in @fig-transp-crackdown.
+Given the near interchangeability of the two treatments, the interaction between accountability and crackdown is nearly identical.
+We include both transparency and accountability in @apptbl-transp-crackdown.
+
 # Conclusion

### 2023-11-20 manuscript/manuscript.qmd
Add Marc's ORCID id

@@
   email: marc_dotson@byu.edu
+  orcid: 0000-0001-7846-3660
 - name: Andrew Heiss

### 2023-11-20 manuscript/manuscript.qmd
Minor typos

@@
 To judge organizational accountability, donors may use ratings by watchdog organizations like Charity Navigator and GuideStar as heuristics to guide their decisions.
-Research shows that initiatives to address accountability gaps by these organizations can affect donations to organizations in a significant manner [@Sloan:2009; @GordonKnockNeely:2009]
+Research shows that initiatives to address accountability gaps by these organizations can affect donations to organizations in a significant manner [@Sloan:2009; @GordonKnockNeely:2009].
 
@@
 #| out-width: "80%"
-#| fig-cap: "Estimated marginal means for the four combinations of transparency and accountability"
+#| fig-cap: "Estimated marginal means for the four combinations of transparency and accountability."
 #| include: true
@@
 The marginal means for transparency would be (`r p_sm$transparency_no$list`)/3 = `r p_sm$transparency_no$emm` when transparency is set to "no", and (`r p_sm$transparency_yes$list`)/3 = `r p_sm$transparency_yes$emm` when transparency is set to "yes".
-In reality, the marginal mean for transparency reported in @fig-all-results and @apptbl-all-results represent the average of 288 rows where transparency is no and 288 rows where transparency is yes.
+In reality, the marginal mean for transparency reported in @fig-all-results and @apptbl-all-results reflects the average of 288 rows where transparency is no and 288 rows where transparency is yes.
 

### 2023-11-20 manuscript/manuscript.qmd
Add other citations

@@
 Conjoint analysis is generally applicable whenever individuals face complex, multi-dimensional tradeoffs that make it difficult (or even impossible) to explicitly elicit preferences.
-Conjoint designs have been used extensively in political science to study complex preferences for elections, laws, public policy, and public opinion [@HainmuellerHopkinsYamamoto:2014; @Mummolo:2016; @KertzerRenshonYarhi-Milo:2021; @BansakHainmuellerHopkins:2021].
+Conjoint designs have been used extensively in political science to study complex preferences for elections, laws, public policy, and public opinion [@HainmuellerHopkinsYamamoto:2014; @Mummolo:2016; @KertzerRenshonYarhi-Milo:2021; @BansakHainmuellerHopkins:2021; @BremerBurgisser:2023].
 @KnudsenJohannesson:2019 argue that research related to respondent opinions requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility.
@@
 
-We analyze the results using a multilevel Bayesian multinomial model.
-Our experimental data has a natural hierarchical structure, with 3 questions nested inside 12 separate experimental tasks, nested inside each of the 1,016 respondents, which lends itself to multilevel modeling.
+We analyze the results using a multilevel Bayesian multinomial model.[^stan] Our experimental data has a natural hierarchical structure, with 3 questions nested inside 12 separate experimental tasks, nested inside each of the 1,016 respondents, which lends itself to multilevel modeling.
 Relying on standard OLS regression can discard valuable information about (1) the relationships and covariance between the different combinations of feature levels offered to respondents, and (2) individual-specific differences in how respondents react to different feature levels [@JensenMarbleScheve:2021].
@@
 Moreover, using random respondent effects provides natural regularization and shrinkage for our estimates---experimental tasks that happened to appear more often due to chance will be accounted for and their frequency will not bias the overall causal effect.
+
+[^stan]: We use Stan [@Stan-2-26-1 v2.26.1; @cmdstan-2-3-1 v2.3.1] through R [@rproject-4-3-1 v4.3.1] and **brms** [@Burkner:2017 v2.20.5] to estimate the model.
+We simulate 4 MCMC chains with 5,000 draws in each chain, 1,000 of which are used for warmup, resulting in 16,000 (4,000 × 4) draws per model parameter.
+We assess convergence with visual inspection, and all chains converge.
+Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and model diagnostics---as well as our code and data---are available `ANONYMIZED_URL`.
 
@@
 Given the conjoint design, we instead create a complete balanced grid of all 576 combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding) and use the model to calculate predicted probabilities of choice selection for each row of possible treatment values.
-We then collapse this set of predicted probabilities into estimated marginal means (EMMs) for specific features of interested while marginalizing or averaging over all other predicted variables.
+We then collapse this set of predicted probabilities into estimated marginal means (EMMs) for specific features of interested while marginalizing or averaging over all other predicted variables [LeeperHoboltTilley:2020; @BremerBurgisser:2023].
 To calculate the causal effect of a treatment, we find the average marginal component effect (AMCE), which is equivalent to the difference in estimated marginal means for specific feature levels.

### 2023-11-20 manuscript/manuscript.qmd
Shorter abstract

@@
   Non-governmental organizations (NGOs) are a core component of global governance.
-Over the last two decades, however, an increasing number of host governments have cracked down on NGOs using a series of laws that adversely affect the availability and use of official aid funds for these organizations.
-In response to this dramatic shift in the NGO funding landscape, international NGOs (INGOs) have increasingly turned to individual donors to offset the loss of traditional funding sources.
-Prior research on NGO fundraising has primarily examined how financial transparency and organizational accountability influence individual donor behavior.
-How do these elements of private donor decision-making interact with structural-level factors such as host country politics and worsening civic environments when deciding to donate?
-Using a conjoint experiment with likely potential donors in the US, we find that financial transparency and accountability can protect against the dampening effect of host government crackdown and criticism of NGOs.
+Over the last two decades, however, many host governments have cracked down on NGOs using a series of laws that adversely affect the availability and use of traditional NGO funding.
+In response to this dramatic shift in the funding landscape, international NGOs have increasingly turned to individual donors to offset the loss funding.
+Prior research on NGO fundraising has examined how financial transparency and organizational accountability influence individual donor behavior.
+How do these elements of private donor decision-making interact with structural-level factors such as worsening host country civic environments when deciding to donate?
+Using a conjoint experiment with likely donors in the US, we find that transparency and accountability can protect against the dampening effect of host government crackdown and criticism of NGOs.
 Our results have important implications for how NGOs can adapt to worsening civic environments.

### 2023-11-20 manuscript/manuscript.qmd
Add extra BJPS statements

@@
 
+# Data availability statement
+
+All data and replication code is available at `DATAVERSE DOI` and at `OSF DOI`.
+
+# Supplementary material
+
+A companion statistical analysis notebook with a fuller description of the data, modeling details and diagnostics, and additional explanations of the Bayesian multinomial modeling approach, along with links to the data and replication code, is available at `ANONYMIZED URL/DOI`.
+
+# Funding
+
+This research received no external funding.
+
+# Competing interests
+
+The authors report there are no competing interests to declare.
+
 # References

### 2023-11-20 manuscript/manuscript.qmd
Update word count

@@
 link-citations: true
-word-count: 9350
+word-count: 7912
 

### 2023-11-20 README.qmd
Remove errant |>
User newer abstract

@@
 
-As space for civil society has closed around the world, transnational NGOs have faced a crisis of funding.
-We explore how NGOs have shifted from traditionally Northern funding sources toward grassroots private philanthropic money.
-How do individual donors in the US feel about donating to legally besieged NGOs abroad?
-Do legal restrictions on NGOs influence donors’ decision to donate?
-We use a conjoint survey experiment to argue that domestic political environments of NGO host countries influence preferences of private donors and that legal crackdowns on NGOs serve as a heuristic of organizational deservingness.
+Non-governmental organizations (NGOs) are a core component of global governance.
+Over the last two decades, however, many host governments have cracked down on NGOs using a series of laws that adversely affect the availability and use of traditional NGO funding.
+In response to this dramatic shift in the funding landscape, international NGOs have increasingly turned to individual donors to offset the loss funding.
+Prior research on NGO fundraising has examined how financial transparency and organizational accountability influence individual donor behavior.
+How do these elements of private donor decision-making interact with structural-level factors such as worsening host country civic environments when deciding to donate?
+Using a conjoint experiment with likely donors in the US, we find that transparency and accountability can protect against the dampening effect of host government crackdown and criticism of NGOs.
+Our results have important implications for how NGOs can adapt to worsening civic environments.
 
@@
 
-codename(type = "nicka", seed = "why donors donate") |> 
+codename(type = "nicka", seed = "why donors donate")
 #> [1] "silent skywalk"

### 2023-11-20 index.qmd
User newer abstract

@@
 
-Abstract goes here
+Non-governmental organizations (NGOs) are a core component of global governance.
+Over the last two decades, however, many host governments have cracked down on NGOs using a series of laws that adversely affect the availability and use of traditional NGO funding.
+In response to this dramatic shift in the funding landscape, international NGOs have increasingly turned to individual donors to offset the loss funding.
+Prior research on NGO fundraising has examined how financial transparency and organizational accountability influence individual donor behavior.
+How do these elements of private donor decision-making interact with structural-level factors such as worsening host country civic environments when deciding to donate?
+Using a conjoint experiment with likely donors in the US, we find that transparency and accountability can protect against the dampening effect of host government crackdown and criticism of NGOs.
+Our results have important implications for how NGOs can adapt to worsening civic environments.
 

### 2023-11-20 manuscript/manuscript.qmd
Fix broken citation

@@
 short-title: "Why Donors Donate"
-date: "2023-11-18"
+date: "2023-11-20"
 author:
@@
 Given the conjoint design, we instead create a complete balanced grid of all 576 combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding) and use the model to calculate predicted probabilities of choice selection for each row of possible treatment values.
-We then collapse this set of predicted probabilities into estimated marginal means (EMMs) for specific features of interested while marginalizing or averaging over all other predicted variables [LeeperHoboltTilley:2020; @BremerBurgisser:2023].
+We then collapse this set of predicted probabilities into estimated marginal means (EMMs) for specific features of interested while marginalizing or averaging over all other predicted variables [@LeeperHoboltTilley:2020; @BremerBurgisser:2023].
 To calculate the causal effect of a treatment, we find the average marginal component effect (AMCE), which is equivalent to the difference in estimated marginal means for specific feature levels.

### 2023-11-20 manuscript/manuscript.qmd
Add corresponding details

@@
 - name: Andrew Heiss
-  affiliation: Georgia State University
+  affiliations: 
+    - id: gsu
+      name: Georgia State University
+      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
+      address: "55 Park Place NE, #464"
+      city: Atlanta
+      region: GA
+      country: USA
+      postal-code: 30303
   url: https://www.andrewheiss.com/
@@
   orcid: 0000-0002-3948-3914
+  attributes:
+    corresponding: true
+correspondence-prefix: "Correspondence concerning this article should be addressed to"
 abstract: |

### 2023-11-20 manuscript/manuscript.qmd
Final Suparna edits

@@
 Repressive governments have cracked down on these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs [@DupuyRonPrakash:2016; @Chaudhry:2022].
-Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" [@CarothersBrechenmacher:2014; @Rutzen:2015] and data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in more than 60% of countries---117 in total [@CIVICUSMonitor].
+Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" [@CarothersBrechenmacher:2014; @Rutzen:2015].
+Data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in more than 60% of countries---117 in total [@CIVICUSMonitor].
 These attacks---most of which have been implemented through anti-NGO laws---have adversely affected the ability of both domestic and international NGOs to operate and raise funds.
-Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official aid donors channel fewer funds to contentious issues and instead choose to fund "tame" causes [@ChaudhryHeiss:2018; @Bush:2015; @Herrold:2020; @RightSpringmanWibbels:2022].
-In response to this dramatic shift in the NGO funding landscape, international NGOs (INGOs) have increasingly turned to foreign individual donors to offset the loss of funding from government and foundation sources [@BanksHulmeEdwards:2015].
+Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official aid donors channel fewer funds to contentious issues such as human rights, elections, and advocacy, and instead choose to fund "tame" causes bush as health, education, and development, among others [@ChaudhryHeiss:2018; @Bush:2015; @Herrold:2020; @RightSpringmanWibbels:2022].
+In response to this dramatic shift in the NGO funding landscape, international NGOs (INGOs) have increasingly turned to individual donors abroad to offset the loss of funding from government and foundation sources [@BanksHulmeEdwards:2015].
 
@@
 This turn to private donors opens INGOs up to new dynamics in seeking out funds.
-Many organizations that had previously relied on governments and foundations had optimized their fundraising strategies for those donors, but now need to tailor their fundraising strategies to private individuals, who behave differently from governments and foundations.
+Many organizations that had previously relied on governments and foundations had optimized their fundraising strategies for those donors.
+But individual donors may behave differently from governments and foundations, so INGOs need to adapt their fundraising strategies to a different set of potential donors.
 
 Individual donors have different preferences and rely on signals of effectiveness that differ from the benchmarks that large donor agencies rely on.
-While INGOs have control over these organizational-level factors such as financial transparency and accountability that motivate donations, the political environment in the host countries INGOs work in---including the global crackdown on civil society that is causing many organizations to seek out private funding in the first place---is a structural factor that INGOs can rarely influence on their own.
+While INGOs have control over organizational-level factors such as financial transparency and accountability that motivate donations, the political environment in the host countries INGOs work in---including the global crackdown on civil society that is causing many organizations to seek out private funding in the first place---is a structural factor that INGOs can rarely influence on their own.
 How do organizational elements of private donor decision-making interact with broader structural limits on INGO fundraising?
@@
 We argue that NGO-level organizational factors and domestic political environments of NGO host countries serve as heuristics and can influence foreign private donors' preferences.
+
 We fielded a conjoint experiment to a nationally representative sample of 1,016 adults in the US, which allows us to directly compare the relative impact of host government repression of NGOs and organizational financial transparency and accountability on individual donor preferences.
@@
 
-The third wave of democratization, the collapse of the Soviet Union, and the spread of a "pro-NGO norm" led to an increased role and visibility for NGOs.
+The third wave of democratization, the collapse of the Soviet Union, and the spread of a "pro-NGO norm" led to an increased role and visibility for NGOs [@Reimann:2006].
 Globally, a large amount of official aid resources were channeled to NGOs focusing on service provision and development.
@@
 One heuristic for potential donors is organizational efficacy or the belief that an individual's donation will make a real difference [@ChaudhryHeiss:2021].
-This can manifest itself through multiple mechanisms such as the amount an organization spends on overhead costs, whether an organization makes its finances public, or whether an organization participates in voluntary accountability practices, such as listing organizational details on websites like GuideStar and Charity Navigator.
+This can manifest itself through multiple mechanisms such as the amount an organization spends on overhead costs, whether it makes its finances public, or whether it participates in voluntary accountability practices, such as listing organizational details on websites like GuideStar and Charity Navigator.
 
@@
 This effect becomes even stronger with media coverage of diversion [@HarrisPetrovitsYetman:2023].
-Organizational financial transparency can reduce actual or perceived information asymmetries between donors and charities, thus potentially increasing donor likelihood of donating to an INGO.
+Organizational financial transparency can reduce actual or perceived information asymmetries between donors and charities, thus potentially increasing an individual's likelihood of donating to an INGO.
 
@@
 
-Explaining actions to stakeholders can be important because many NGOs, even when well-intentioned ones, can devote excessive resources towards marketing and overheads [@Bowman:2006].
+Explaining actions to stakeholders can be important because many NGOs, even well-intentioned ones, can devote excessive resources towards marketing and overheads [@Bowman:2006].
 Private donors, subsequently, may be more likely to dislike NGOs that spend a large share of their revenues for unproductive purposes [@Rose-Ackerman:1982], or rather, a large share of resources on administration, management and fundraising.
@@
 The changes in civic environments impacting NGO activity have also influenced official donor responses.
-Scholars have found that while multilateral donors do not reduce aid following the passage of anti-NGO laws, they are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018].
+Scholars have found that while multilateral donors do not reduce aid following the passage of anti-NGO laws, these laws are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018].
 Further, advocacy-oriented donors---i.e., those that fund democracy and civil society promotion activities---reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022].
@@
 
-Finally, organization funding source also serves as a reliable donor heuristic.
+Finally, an organization's primary funding source also serves as a reliable donor heuristic.
 Organizations that are funded by many small donors are substantially more popular than those funded by government grants or a small group of wealthy donors---when compared to many small donors, both government and wealthy individual funding cause `r amce$funded_primarily_by_government_grants$pp_abs` and `r amce$funded_primarily_by_a_handful_of_wealthy_private_donors$pp_abs` percentage point decreases in the probability of selection (`r amce$funded_primarily_by_government_grants$nice_ci_pd` and `r amce$funded_primarily_by_a_handful_of_wealthy_private_donors$nice_ci_pd`).
@@
 Having explored the effects of general organizational characteristics on the propensity to donate, we can test our first hypotheses and examine the effects of our treatments of interest.
-As seen in the marginal means in @fig-all-results, both transparency and accountability are surprisingly strong signals of organizational deservingness.
+As seen in the marginal means in @fig-all-results, both transparency and accountability are strong signals of organizational deservingness.
 Respondents strongly prefer organizations that engage in either transparency or accountability---both treatments have a posterior marginal mean of roughly 30% compared to a baseline equally-at-random probability of 25% (transparency: `r mms$transparency_yes$nice_simple`; accountability: `r mms$accountability_yes$nice_simple`).
@@
 Respondents are less likely to donate when an organization is criticized by its host government, and far less likely when an organization faces crackdown.
-Compared to other treatments, an organization facing crackdown has roughly the same negative preference as an organization without transparency or accountability measures, while having a friendly relationship is generally equivalent to engaging in transparency or accountability.
+Compared to other treatments, an organization facing crackdown elicits a similar negative preference among potential donors as an organization without transparency or accountability measures.
+However, an organization with a friendly relationship with the host government leads potential donors to perceive it as equivalent to engaging in transparency or accountability.
 
@@
 However, we know relatively little about how state repression of NGOs affects the preferences of foreign private donors [@ChaudhryHeiss:2021].
-Unlike state donors, individual and elite donors may not necessarily withdraw or reduce support for NGOs facing harassment abroad.
+Unlike state donors, individual donors have different motivations for engaging in philanthropy, and they may not necessarily withdraw or reduce support for NGOs facing harassment abroad.
 This is important because private philanthropy towards organizations working in international affairs continues to grow despite inflation---from 2021 to 2022, individual giving to nonprofits in international affairs grew by over 10.9% in the US [@GivingUSA:2023].
@@
 Using a conjoint experiment with a nationally representative sample of the U.S.
-population, we find that both financial transparency and accountability increases individuals' willingness to donate NGOs.
+population, we find that both financial transparency and accountability increases individuals' willingness to donate to NGOs.
 Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability protect against this dampening effect, increasing the probability of philanthropic domations by nine percentage points under the worst conditions of legal crackdown.
@@
 These results have important implications for NGO operations, fundraising, and survivability at a time when many INGOs are dealing with hostile host governments.
-A comparison of the effects of these organizational and structural factors is critical to NGO fundraising---while NGOs have control over transparency and accountability, as well as public perception of these organizational characteristics, they may little to no control over host government crackdowns over their organizations.
-As a result, they may need to rely entirely on improving individual donor perception of organizational transparency and accountability, its impact on NGO operations and the need for private donor funds at a time of shrinking civic space.
+A comparison of the effects of these organizational and structural factors is critical to NGO fundraising---while NGOs have control over transparency and accountability, as well as public perception of these organizational characteristics, they have little to no control over host government crackdowns over their organizations.
+As a result, they may need to rely entirely on improving individual donor perceptions of organizational transparency and accountability and emphasizing the need for private donor funds at a time of shrinking civic space.
 This article thus provides insight into the importance of different framing or informational heuristics that can motivate such individual donor giving.

### 2023-11-20 manuscript/manuscript.qmd
Update word count + keywords

@@
   - philanthropy
-  - civil society
   - conjoint experiments
   - donor heuristics
+  - repression
+  - NGOs
+  - civil society
+  - nonprofits
 code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/silent-skywalk>"
@@
 link-citations: true
-word-count: 7912
+word-count: "7,955"
 

### 2023-12-16 manuscript/manuscript.qmd
Update for next journal

--- 2023-11-20 manuscript/manuscript.qmd
@@
 short-title: "Why Donors Donate"
-date: "2023-11-20"
+date: "2023-12-15"
 author:
@@
 Our results have important implications for how NGOs can adapt to worsening civic environments.
+additional-info: |
+  **Data Availability:** All data and replication code are publicly available at <https://github.com/andrewheiss/silent-skywalk>
 keywords:
   - philanthropy
-  - civil society
   - conjoint experiments
   - donor heuristics
+  - repression
+  - NGOs
+  - civil society
+  - nonprofits
 code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/silent-skywalk>"
 bibliography: references.bib
-csl: csl/british-journal-of-political-science.csl
+csl: csl/apa.csl
 link-citations: true
-word-count: 7912
+word-count: "9,878"
 
@@
     - kind: float
-      prefix: Table A
+      key: apptbl
+      latex-env: apptbl
+      reference-prefix: Table A
       space-before-numbering: false
-      name: Table A
-      ref-type: apptbl
-      latex-env: apptbl
-      latex-list-of-file-extension: lost
       latex-list-of-description: Appendix Table
@@
 Conjoint analysis is generally applicable whenever individuals face complex, multi-dimensional tradeoffs that make it difficult (or even impossible) to explicitly elicit preferences.
-Conjoint designs have been used extensively in political science to study complex preferences for elections, laws, public policy, and public opinion [@HainmuellerHopkinsYamamoto:2014; @Mummolo:2016; @KertzerRenshonYarhi-Milo:2021; @BansakHainmuellerHopkins:2021; @BremerBurgisser:2023].
+Conjoint designs have been used extensively in political science to study complex preferences for elections, laws, public policy, and public opinion [@HainmuellerHopkinsYamamoto:2014; @Mummolo:2016; @KertzerRenshonYarhi-Milo:2021; @BansakHainmuellerHopkins:2021; @BremerBurgisser:2023], and conjoint experiments are becoming more common in nonprofit studies, particularly for studying individual donor behavior [@SilviaChildWitesman:2023; @HirschmannMoritzBlock:2022; @BachkeAlfnesWik:2014; @Kottasz:2004].
 @KnudsenJohannesson:2019 argue that research related to respondent opinions requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility.
@@
 
+::: {.content-visible when-profile="ms"}
+```{=latex}
+\newpage
+\begingroup
+\singlespacing
+\parindent 0pt
+\parskip 2ex
+\def\enotesize{\normalsize}
+\theendnotes
+\endgroup
+\newpage
+```
+:::
+
 # References
 
-::: {#refs .bibliography}
+::: {#refs}
 :::

### 2024-03-28 deploy.sh
Change remote folder path

@@ -1,5 +1,5 @@
-REMOTE_HOST="cloud"
-REMOTE_DIR="~/sites/stats/public_html/silent-skywalk"
+REMOTE_HOST="ath-cloud"
+REMOTE_DIR="~/sites/stats.andrewheiss.com/public_html/silent-skywalk"
 REMOTE_DEST=$REMOTE_HOST:$REMOTE_DIR
 
 echo "Uploading new changes to remote server..."

### 2024-03-28 manuscript/manuscript.qmd
Mega update for resubmission to NVSQ

@@
 short-title: "Why Donors Donate"
-date: "2023-12-15"
+date: "2024-03-27"
 author:
@@
 link-citations: true
-word-count: "9,878"
+word-count: "9,300"
 
@@
   } else {
-    str_replace(x, "\\n", "<br>")
+    str_replace_all(x, "\\n", "<br>")
   }
@@
 gt_pct <- function(x, page_width = 6) {
-  if (knitr::pandoc_to("latex")) {
+  if (fmt_out == "latex") {
     paste0(page_width * (x / 100), "in")
@@
 
-Over the last two decades, governments globally have increasingly cracked down on NGOs [@ChristensenWeinstein:2013; @DupuyRonPrakash:2016; @Heiss:2017; @GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022].
-Repressive governments have cracked down on these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs [@DupuyRonPrakash:2016; @Chaudhry:2022].
+Non-governmental organizations (NGOs) face stricter regulations from their host governments [@ChristensenWeinstein:2013; @DupuyRonPrakash:2016; @GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020].
+Repressive governments have cracked down on these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs [@DupuyRonPrakash:2016; @Chaudhry:2022; @Heiss:2017].
 Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" [@CarothersBrechenmacher:2014; @Rutzen:2015].
@@
 These attacks---most of which have been implemented through anti-NGO laws---have adversely affected the ability of both domestic and international NGOs to operate and raise funds.
-Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official aid donors channel fewer funds to contentious issues such as human rights, elections, and advocacy, and instead choose to fund "tame" causes bush as health, education, and development, among others [@ChaudhryHeiss:2018; @Bush:2015; @Herrold:2020; @RightSpringmanWibbels:2022].
+Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official donors channel fewer funds to contentious issues such as human rights, elections, and advocacy, and instead choose to fund "tame" causes bush as health, education, and development, among others [@ChaudhryHeiss:2018; @Bush:2015; @Herrold:2020; @RightSpringmanWibbels:2022].
 In response to this dramatic shift in the NGO funding landscape, international NGOs (INGOs) have increasingly turned to individual donors abroad to offset the loss of funding from government and foundation sources [@BanksHulmeEdwards:2015].
@@
 entities towards international causes doubled in real terms [@DesaiKharas:2018, 505].
-In 2016, U.S.
-private philanthropy towards international NGOs amounted to \$22.06 billion [@GivingUSA:2017].
-Most notably, a large portion of this growth was driven by individuals making small-scale donations.
-In 2017, individuals gave \$286.7 billion or approximately 70% of total giving to international affairs.
-This further increased to \$427.71 billion in 2018, 85.7% of which was through individuals [@GivingUSA:2019].
+In 2018, this amounted to \$22.88 billion in individual donations earmarked specifically for international affairs INGOs [@GivingUSA:2019].
 This turn to private donors opens INGOs up to new dynamics in seeking out funds.
@@
 
-Existing research shows that organizational accountability and financial transparency play an important role in motivating individual donors to donate to NGOs [@HarrisNeely:2021; @SaxtonKuoHo:2012; @Vaccaro:2006; @VaccaroMadsen:2006; @Tremblay-BoirePrakash:2017; @Becker:2018].
+Existing research shows that organizational accountability [@Becker:2018; @Tremblay-BoirePrakash:2017] and financial transparency [@HarrisNeely:2021; @SaxtonKuoHo:2012; @Vaccaro:2006; @VaccaroMadsen:2006] play an important role in motivating individual donors to donate to NGOs.
 We extend this literature by evaluating how these organization-level characteristics influence private donor behavior in an era of shrinking civic space.
-In considering this question, we engage with a growing body of research on the consequences of closing civic space on NGOs and donors [@DupuyPrakash:2018; @RightSpringmanWibbels:2022; @FransenDupuyHinfelaar:2021; @SundstromHenrySperling:2022; @Herrold:2020; @ChaudhryHeiss:2021].
-We argue that NGO-level organizational factors and domestic political environments of NGO host countries serve as heuristics and can influence foreign private donors' preferences.
+In considering this question, we engage with research on the consequences of closing civic space on NGOs and donors [@DupuyPrakash:2018; @RightSpringmanWibbels:2022; @FransenDupuyHinfelaar:2021; @SundstromHenrySperling:2022; @Herrold:2020; @ChaudhryHeiss:2021].
+We argue that both organization characteristics---such as an NGO's issue area, funding sources, and transparency and accountability practices---and external factors like an NGO's host-country political environment act as heuristics that influence foreign private donors' preferences.
 
@@
 Our findings make two main contributions.
-While recent research on private foreign aid has examined funding decisions of donor NGOs and foundations,[^1] we know less about the funding choices of the individuals responsible for much of these private aid flows [@DesaiKharas:2018].
-The systematic study of private foreign aid is still in its infancy---there is an absence of expansive and high quality data [@GreenhillPrizzonRogerson:2013], and most research has been restricted to elite, high net-worth donors [@USTrust2014].
-Our research makes a significant contribution to research on individual giving and indicates the promise and limits of different framing appeals on individual donor preferences.
-
-[^1]: On aid from world's largest NGOs, see @Koch:2009, on private aid flows from NGOs based in the US, see @ButheMajorMello-e-Souza:2012.
-
+First, existing research on privately-provided foreign aid primarily looks at organizations like foundations and large donor NGOs, and not private individuals [@ButheMajorMello-e-Souza:2012; @Koch:2009; @DesaiKharas:2018], and studies that do examine individual giving behavior typically only examine wealthy individuals [@USTrust2014].
+Our research expands work on private international philanthropy by exploring how non-elite individuals decide to donate to NGOs focused on international affairs.
 Second, research shows that NGO leaders often have difficulty in attracting new donors and also find it challenging to motivate current donors [@GaudreauCao:2015].
-Examining organizational-level factors that make the average donor increase their charitable giving, especially when facing restricted civic space abroad, can help NGOs better frame their funding appeals towards these donors.
-Our results have important implications for INGOs facing increased antagonism by governments abroad and point to possible methods of adapting to worsening or shrinking civic environments.
-
-Below, we summarize existing research on determinants of individual giving to foreign NGOs, laying out our expectations regarding how financial transparency and accountability shape individuals' philanthropic preferences in an environment of closing civic space.
-We then describe our conjoint experiment and present the results.
-We conclude with implications for NGOs working in repressive countries.
+Examining organizational-level factors that make the average donor increase their charitable giving, especially when facing restricted civic space abroad, can help NGOs better frame their funding appeals.
+Moreover, our results provide guidance to organizations facing increased antagonism by governments abroad and point to possible methods of adapting to worsening or shrinking civic space.
+
+In the remainder of the paper, we provide an overview of current research on private philanthropic giving to international NGOs.
+We use these existing theories to hypothesize how organizational practices like financial transparency and accountability influence individual donor behavior in an environment of closing civic space.
+We then detail our conjoint study methodology and discuss our findings.
+Finally, we use our results to offer insights for NGOs facing legal restriction abroad.
 
@@
 
-Substantial research on NGOs has looked at the motivation of individual donors, including altruism, reputational benefits, and alignment with personal values [@BilodeauSlivinski:1997; @Wiepking:2010; @BekkersWiepking:2011].
-However, this research has overwhelmingly looked at individual donor behavior and motivation for giving to local---rather than international---causes [@BekkersWiepking:2011; @Tremblay-BoirePrakash:2017].
-Understanding the latter is important as philanthropy to international causes can be harder to motivate because the number of recipients is larger and further removed from the donor [@CasaleBaumann:2015, 100].
-Further, as @MicklewrightSchnepf:2009 point out, motivations for donating to ongoing international causes differ from donating money to natural disasters or emergency international causes.
-Under ordinary circumstances, "donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad" [@Tremblay-BoirePrakash:2017, 644].
-However, we lack adequate data and theory regarding the conditions under which private donors engage in increased philanthropy towards INGOs.
-This gap also exists because conventionally, public donors or official aid donors have been among the main funders of INGOs.
-
-The third wave of democratization, the collapse of the Soviet Union, and the spread of a "pro-NGO norm" led to an increased role and visibility for NGOs [@Reimann:2006].
-Globally, a large amount of official aid resources were channeled to NGOs focusing on service provision and development.
-Public and private donors perceived these organizations as more efficient than states with weak institutions and poor governance; there was a high risk that such states would use aid transfers inefficiently [@Dietrich:2013].
-Less bureaucratic and more nimble than state institutions, NGOs were seen as key agents of development and democratization [@Herrold:2020, 142--43].
+A large body of work in philanthropy explores the factors that shape private donor motivation, including altruism, reputational benefits, and alignment with personal values [@BilodeauSlivinski:1997; @Wiepking:2010; @BekkersWiepking:2011].
+However, this research has overwhelmingly looked at individual donor behavior and motivation for giving to *domestic* organizations instead of international causes [@BekkersWiepking:2011; @Tremblay-BoirePrakash:2017].
+The geographic scope of an organization's mission matters to donors.
+Giving to local organizations involves fewer recipients and more observable results, while the benefits of donating to organizations working abroad are less visible and more removed from donors [@CasaleBaumann:2015].
+In a survey experiment, @Tremblay-BoirePrakash:2017 confirm this, finding that "donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad" [-@Tremblay-BoirePrakash:2017, 644].
+This difference in donor preferences for international NGO services has been understudied because conventionally, states and foundations have been among the main funders of INGOs.
+
+The third wave of democratization, the collapse of the Soviet Union, and the spread of a "pro-NGO norm" have led to an increased role and visibility for NGOs in recent decades [@Reimann:2006].
+Donor states have channeled substantial resources through humanitarian and development NGOs, often in response to donor fears that recipient states would use aid inefficiently [@Dietrich:2013].
+Institutional donors and private funders perceived NGOs as more efficient, more nimble, less bureaucratic, and more trustworthy than states that face poor governance and weak political institutions [@Chaudhry:2022], and as a result, NGOs have become crucial actors in both development and democratization [@Herrold:2020, 142--43].
 
@@
 Misappropriation of assets and embezzlement schemes are among the most common forms of financial fraud [@LamotheTer-MkrtchyanRuddle:2023].
-These criticisms and concerns, in turn, have led donors to demand greater NGO responsiveness, especially in terms of financial transparency and accountability.
-
-Private donors, however, do not necessarily seek out complete information about an organization's deservingness and efficiency, since this is a costly and time-consuming process [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
-As such, these donors respond to a range of heuristics and signals when deciding whether to donate to an NGO.
-Nonprofits fundraising from individual donors may therefore rely on framing to control perceptions [@ChaudhryHeiss:2021].
-Below, we theorize the effect of different frames surrounding a country's legal environment and nonprofit organizational characteristics on individual donor preferences.
-
-## Organizational heuristics: The impact of NGO organizational practices on individual philanthropy
-
-In theory, donors should scrutinize each aspect of an NGO's organizational structure and programmatic performance prior to donation, but this rarely happens in practice [@Tremblay-BoirePrakash:2017].
-Instead, individuals rely on heuristics to simplify their decision-making.
-One heuristic for potential donors is organizational efficacy or the belief that an individual's donation will make a real difference [@ChaudhryHeiss:2021].
+These criticisms and concerns, in turn, have led donors to demand greater NGO responsiveness, especially regarding financial transparency and accountability.
+
+Assessing an NGO's deservingness and efficiency demands substantial time and resources, which individual donors typically lack [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
+As such, these donors rely on various cues and heuristics when deciding to support an NGO.
+Nonprofits fundraising from individuals work to shape donor perceptions through the use of framing [@ChaudhryHeiss:2021].
+We explore two possible categories of heuristic frames: (1) organization-level heuristics, reflected in NGO practices, and (2) structural heuristics, particularly an NGO's relationship with its host country.
+We hypothesize that each type plays a role in shaping individual preferences for engaging in philanthropy.
+
+## Organizational heuristics: NGO practices
+
+One powerful heuristic for potential donors is organizational efficacy or the belief that an individual's donation will make a real difference [@ChaudhryHeiss:2021].
 This can manifest itself through multiple mechanisms such as the amount an organization spends on overhead costs, whether it makes its finances public, or whether it participates in voluntary accountability practices, such as listing organizational details on websites like GuideStar and Charity Navigator.
 
-Financial transparency, or the degree of completeness of information provided by organizations to the public concerning their activities, is one tangible heuristic that donors use to make their decisions.
+Financial transparency, or the "degree of completeness of information provided by [organizations] to the [public] concerning [their] activities," [@VaccaroMadsen:2006, p.
+146] is one tangible heuristic that donors turn to when making decisions decisions.
 NGOs can engage in financial transparency in a variety of ways such as distribution of audited financial statements and third party intermediaries.
-Research shows that transparency is associated with greater donations, lower debt, and better governance [@HarrisNeely:2021; @SaxtonKuoHo:2012].
+Research shows that transparency is associated with greater donations, lower debt, and better governance [@HarrisNeely:2021; @HarrisPetrovitsYetman:2023; @SaxtonKuoHo:2012].
 It can also enhance donor trust and confidence in organizations [@Vaccaro:2006; @VaccaroMadsen:2006].
@@
 
-> **H~1a~**: If NGOs are financially transparent, then individual private donors will be more likely to donate to them.
-
-Accountability is another factor that can impact donor willingness to donate.
-Accountability is necessary to promote public trust in NGOs.
-While transparency is an organization's willingness to make critical data about the organization public, accountability is the willingness of the organization to explain its action to shareholders.
+> **H~1a~**: If NGOs are financially transparent, then individual private donors will have a higher likelihood of supporting or donating to them.
+
+Accountability is another factor that can impact donor willingness to donate, and it is necessary for promoting public trust in NGOs.
+While transparency is an organization's willingness to make critical data about the organization public, accountability is the willingness of the organization to explain its action to shareholders [@CharityNavigator:2020].
 It also encompasses how well an organization's mission is aligned with its resources and how it manages resources to optimize performance [@Sloan:2009].
-
-Explaining actions to stakeholders can be important because many NGOs, even well-intentioned ones, can devote excessive resources towards marketing and overheads [@Bowman:2006].
-Private donors, subsequently, may be more likely to dislike NGOs that spend a large share of their revenues for unproductive purposes [@Rose-Ackerman:1982], or rather, a large share of resources on administration, management and fundraising.
-Lack of accountability is associated with lesser public trust, reputation, perceived quality and donation behavior [@Becker:2018].
-As @Tremblay-BoirePrakash:2017 point out, while individuals would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead, donors do not necessarily have the time to research charities thoroughly.
-
-To judge organizational accountability, donors may use ratings by watchdog organizations like Charity Navigator and GuideStar as heuristics to guide their decisions.
-Research shows that initiatives to address accountability gaps by these organizations can affect donations to organizations in a significant manner [@Sloan:2009; @GordonKnockNeely:2009].
-
-> **H~1b~**: If NGOs are accountable and hold regular third-party audits, then individual private donors will be more likely to donate to them.
+As NGOs gain more prominence, donors demand more information about their activities and strategies [@Tremblay-BoirePrakash:2015].
+Explaining actions to stakeholders can be important because many NGOs---even well-intentioned ones---can devote excessive resources towards marketing and overheads [@Bowman:2006].
+Private donors, subsequently, tend to avoid NGOs that spend a large share of their revenues for overhead, non-mission-related purposes like administration, management and fundraising.
+The absence of accountability is associated with decreased public trust, worse reputation, and lower perceived quality [@Becker:2018].
+
+Though individual donors would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead, individuals interested in supporting charities cannot thoroughly vet every aspect of the organization [@Tremblay-BoirePrakash:2017; @ChaudhryHeiss:2021].
+To more easily judge organizational accountability, donors may use ratings by watchdog organizations like Charity Navigator and GuideStar as heuristics to guide their decisions.
+Research shows that initiatives to address accountability gaps by these organizations can substantially increase donations [@Sloan:2009; @GordonKnockNeely:2009; @Tremblay-BoirePrakash:2017].
+
+> **H~1b~**: If NGOs are accountable and hold regular third-party audits, then individual private donors will have a higher likelihood of supporting or donating to them.
 
@@
 Some NGOs have adapted to repressive environments by recreating their organizations and changing their mission to avoid directly confronting the government.
-Analyzing the impact of anti-NGO laws in Bangladesh and Zambia, scholars have found that NGOs with a broad mission ended up restricting themselves to service work and giving up on their advocacy work.
+Analyzing the impact of anti-NGO laws in Bangladesh and Zambia, scholars have found that when faced with government restrictions, NGOs with broad missions restricted their strategies to service work and abandoned their advocacy work.
 Those that continued to engage in transnational advocacy changed the targets of their advocacy, the issues they focused on, and the language they used [@FransenDupuyHinfelaar:2021].
@@
 The changes in civic environments impacting NGO activity have also influenced official donor responses.
-Scholars have found that while multilateral donors do not reduce aid following the passage of anti-NGO laws, these laws are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018].
+Scholars have found that while multilateral donors do not reduce aid in response to anti-NGO laws, these laws are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018].
 Further, advocacy-oriented donors---i.e., those that fund democracy and civil society promotion activities---reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022].
-However, previous literature has established that individual private donors may not necessarily use the same metrics as official donors when deciding to donate [@DesaiKharas:2018; @ChaudhryHeiss:2021].
+However, previous literature has established that individual private donors do not make the same considerations as official donors when deciding to donate [@DesaiKharas:2018; @ChaudhryHeiss:2021].
 Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the grounds [@EasterlyWilliamson:2011].
-These anti-NGO laws may signal to private donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and crack down on them.
-Therefore, we expect that government restrictions abroad will increase respondents' likelihood of donating to the organization.
-
-> **H~2~**: If NGOs face legal crackdowns abroad, then individual donors will be more likely to donate to them.
+Anti-NGO repression and civil society laws may act as a heuristic to individuals donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and crack down on them.
+Therefore, restrictions imposed by host-country governments are likely to boost donors' inclination to donate to affected organizations.
+
+> **H~2~**: If NGOs face legal crackdowns abroad, then individual private donors will have a higher likelihood of supporting or donating to them.
 
@@
 Identifying the causal link between structural factors and donor behavior is more difficult than measuring the link between organizational factors and donor behavior because (1) NGOs have less direct control over their political environments, and (2) organizational characteristics like financial transparency and accountability can sour the NGO-government relationship---governments may be more likely to target NGOs that lack financial transparency and accountability.
-Governments do not enact anti-NGO laws in isolation.
-Countries are more likely to repress NGOs when organizational features are in tension with government preferences and when organizations receive substantial funding from abroad [@DupuyRonPrakash:2015].
-Therefore, the same organizational characteristic that can increase the likelihood of government crackdown can also simultaneously serve as a donor heuristic and influence perceptions of NGO deservingness.
-
-Donors therefore may show increased willingness to donate to NGOs facing government crackdown/criticism while being financial transparent and accountable.
+Moreover, states pass anti-civil society laws in response to broader political trends within their borders, and they regulate NGOs strategically to maximize the benefits and minimize the costs of working with international NGOs [@Heiss:2017].
+States are more likely to restrict NGOs when organizations pose a threat to regime stability or preferences—for instance, when INGO issue areas threaten government policies, or when INGOs receive substantial foreign funding [@DupuyRonPrakash:2015].
+
+Donors show increased willingness to donate to NGOs facing government crackdown/criticism while being financial transparent and accountable.
 While concerns about NGO mismanagement and lack of financial transparency may signal concerns about an NGO's operations and its ability to abide by the host country's regulatory environment, the presence of such transparency and accountability may instead convince donors that government targeting of NGOs may be ill-intentioned rather than simply a manifestation of financial oversight.
@@
 
-As a result, we are uncertain about the interaction between transparency, accountability, and host country legal environment.
-We suspect that there is a relationship, but we are uncertain about the exact direction or magnitude.
-Accordingly, we do not propose any confirmatory hypothesis testing, but instead explore the interaction between our primary treatment variables to inform future research on the interplay between organizational and structural dynamics.
-
-Importantly, when testing these hypotheses, we do not assume that individual donors have perfect knowledge about an NGO or the country an NGO operates in.
-The average donor will not know exactly what "crackdown" entails for any given organization (i.e., does it mean an NGO was expelled, or that its assets were frozen, or that it received a fine?).
-For the sake of this experiment, this ambiguity is not a central concern as the heuristics we explore here are explicitly simplified short- cuts to donor information-gathering.
-Knowing that an organization is financially transparent (even if donors are not familiar with specific kinds of requirements regarding transparency), or knowing that an NGO faces legal trouble abroad should be enough to trigger the effect of these frames on donor preferences.
-Moreover, although many NGOs make information about their operations accessible through annual reports, it is time-consuming to track down that information.
-In each of these hypotheses, we assume that donors will not spend additional effort to research the exact details concerning crackdown, transparency and accountability.
-Instead, donors rely on signals and heuristics about the organization to shape their preferences and behavior [@SzperPrakash:2011].
+Therefore, both states and individual donors expand and contract their regulatory environments (for states) and support (for donors) for NGOs in response to the interplay between domestic politics and organizational characteristics.
+The same NGO feature that can increase the likelihood of government crackdown can also simultaneously serve as a donor heuristic and influence perceptions of NGO deservingness.
 
@@
 @KnudsenJohannesson:2019 argue that research related to respondent opinions requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility.
-Because we also want to capture the complexity of a respondent's judgment of philanthropic preferences, we use a conjoint design to evaluate the effect of organizational and structural heuristics on philanthropic preferences.
+Because we also want to capture the complexity of a respondent's judgment of philanthropic preferences, we use a conjoint experiment to measure the causal effect of both organizational and structural heuristics on individuals' preferences for donating to international NGOs.
 
@@
 We instead focus here on the simplest, non-nested hypotheses.
-H~1a~ and H~1b~ correspond to preregistration question #5; H~2~ corresponds to preregistration question #2; our comparison treatments correspond to preregistration questions #1, #3, and #4.
-Our exploration of the interaction between transparency, accountability, and crackdown corresponds to part 2 of preregistration question #5.
+Following @WillrothAtherton:2024, we outline all the deviations from our preregistration protocol in the appendix.
 
@@
 
-We recruited survey participants through Centiment, a commercial online provider of high quality non-probability opt-in survey panels.
-Centiment ensures panel quality by actively recruiting representative samples of the US population and provides monetary incentives and rewards to participants.
+We fielded our survey experiment through Centiment, which recruits representative samples of paid (and highly engaged) survey participants online.
 To see how varying NGO characteristics influence the decision to donate, our sample was representative of the population of people who are likely to donate to charity.
@@
 Importantly, these screening questions were presented *prior to* the experimental manipulation to avoid post-treatment bias [@MontgomeryNyhanTorres:2018].
-
 Following screening, we received 1,016 viable responses.
 @apptbl-sample-details-demographics, @apptbl-sample-details-charity, and @apptbl-sample-details-politics provide a detailed breakdown of the individual characteristics of our sample.
-In general, respondents were well balanced across genders and tended to be older than the national median age of 36---less than 20% of respondents were under 36 years old.
-The majority of respondents (45%) had never been married, while nearly 40% were married, with 10% divorced.
-A quarter of the sample had a high school degree, with the remainder attending some level of college or university.
-The majority (58%) earned less than the national median income (\$61,372).
-Since we limited the sample to people who frequently donate to charities, most respondents have a favorable opinion of nonprofits and charities, with more than half reporting a 5 or greater (on a 7-point scale) of trust in charities.
-Nearly 90% of respondents indicated that it is important to trust charities, rating importance of trust at least a 3 on a 7-point scale.
-The majority of respondents volunteer at least once a year, donate to charity at least once a year, and give between \$1--\$999 annually.
-Most rarely attend church, but feel that religion is important.
-Respondents are also engaged civically (three quarters voted in the last election) and follow national news closely (70% follow the news daily).
-Respondents are fairly balanced ideologically, with the majority reporting a 3, 4, or 5 on a 7-point scale of liberal--conservative political ideology.
+In general, respondents were well balanced across all pre-treatment characteristics, including gender, age, education, income, and attitudes toward charity.
 
@@
 
-After collecting baseline information on respondent demographics and attitudes toward charity and voluntarism, we presented respondents with three randomly generated hypothetical international nonprofit organizations with six randomly assigned features, along with an option to select none.
+After collecting baseline information on respondent demographics and attitudes toward charity and voluntarism, we showed participants a set of randomly shuffled hypothetical international NGOs described with randomly shuffled features or attributes.
 In this paper, we hypothesize and empirically test the effect of financial transparency, accountability, and host country relationship on the likelihood of donations.
@@
 In total, we varied six different organizational and structural attributes that might have an effect on donor behavior: (1) organization name and branding, (2) organization issue area, (3) financial transparency practices, (4) accountability practices, (5) funding sources, and (6) relationship with host government (see @tbl-design).
+
+\begingroup
+
+::: {.content-visible when-profile="ms"}
+\singlespacing
+:::
 
@@
 
+\endgroup
+
 At the time of designing the study, Charity Navigator---a large database of U.S.
@@
 We then repeated the process eleven more times for a total of twelve randomized iterations of hypothetical combinations of attributes, resulting in 12,192 completed experimental tasks (12 iterations × 1,016 respondents).
+
+::: {.content-visible when-profile="ms"}
+\clearpage
+:::
+
+\begingroup
+
+::: {.content-visible when-profile="ms"}
+\singlespacing
+:::
 
@@
 
-::: {.content-visible when-profile="ms"}
-\clearpage
-:::
+\endgroup
 
@@
 Moreover, using random respondent effects provides natural regularization and shrinkage for our estimates---experimental tasks that happened to appear more often due to chance will be accounted for and their frequency will not bias the overall causal effect.
+We define our model and priors in @eq-model.
 
@@
 Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and model diagnostics---as well as our code and data---are available `ANONYMIZED_URL`.
-
-We analyze the effect of the various combinations of organizational features and donor characteristics with the following Bayesian multinomial logit model and priors:
 
@@
 \end{aligned}
-$$
+$$ {#eq-model}
+
+\
 
@@
 We then collapse this set of predicted probabilities into estimated marginal means (EMMs) for specific features of interested while marginalizing or averaging over all other predicted variables [@LeeperHoboltTilley:2020; @BremerBurgisser:2023].
-To calculate the causal effect of a treatment, we find the average marginal component effect (AMCE), which is equivalent to the difference in estimated marginal means for specific feature levels.
+We report the causal effect of each manipulated feature using the average marginal component effect (AMCE), which is equivalent to the difference in estimated marginal means for specific feature levels.
 For example, when estimating the marginal means of the transparency treatment, we find the average predicted probability across the 288 rows of the reference grid where transparency is true and across the 288 rows where transparency is false---the difference between these two estimated marginal means is the AMCE, or the causal effect of the treatment holding all other values constant, on the probability scale (see the appendix for an extended illustration and demonstration of the EMM and AMCE calculating process).
@@
 
-We use median values of the posterior marginal means and AMCEs as point estimates and calculate credible intervals using a 95% equal-tailed quantile interval.
-However, we are generally less concerned with the exact point estimates of our causal effects and instead focus on the direction and relative magnitude of their posterior distributions.
+We provide viusalizations of the full posterior distributions of each of the effects of interest, and we report two distributional summary statistics: (1) the posterior median, (2) credible intervals based on a 95% equal-tailed quantile interval, However, we are generally less concerned with the exact point estimates of our causal effects and instead focus on the direction and relative magnitude of their posterior distributions.
 For inference, we calculate the probability of direction ($p_d$), or the probability that the posterior AMCE is strictly positive or negative---it is the proportion of the posterior AMCE that is the sign of the median.
@@
 To test our second hypothesis regarding structural heuristics, we explore the effect of an NGO's host country conditions on the propensity to donate.
-Contrary to our expectations, respondents appear to prefer donating to NGOs that have friendly relationships with their host governments, with a marginal mean of `r mms$friendly_relationship_with_government$pct` (compared to a baseline of 25%; `r mms$friendly_relationship_with_government$nice_ci`).
+Contrary to our expectations, respondents appear to prefer donating to NGOs with friendly host government relationships, with a marginal mean of `r mms$friendly_relationship_with_government$pct` (compared to a baseline of 25%; `r mms$friendly_relationship_with_government$nice_ci`).
 Respondents are less likely to donate when an organization is criticized by its host government, and far less likely when an organization faces crackdown.
@@
 This result is surprising, but clarifies findings in previous research.
-In a similar vignette-based experiment, @ChaudhryHeiss:2021 find no substantial effect of legal crackdown on the likelihood of donation, and any substantive crackdown-related effects are moderated by other treatments like NGO issue area or funding source.
+In a similar vignette-based experiment, @ChaudhryHeiss:2021 find no substantial effect of legal restrictions on the probability of donation, and any substantive crackdown-related effects are moderated by other treatments like NGO issue area or funding source.
 This negative effect might also be related to the notion of donor efficacy.
@@
 Financial transparency and accountability practices both have a positive (and likely interchangeable) effect on NGO favorability, while government criticism and crackdown have a negative effect and discourage potential donors from donating.
-As seen in @fig-transp-crackdown (and @apptbl-transp-crackdown), these heuristics also interact with each other.[^transp-only] The estimated posterior marginal means for different relationships with host governments move in the same direction regardless of whether an organization engages in transparency practices: organizations with friendly relationships with their host governments are most preferred, while organizations under government crackdown are least preferred.
+As seen in @fig-transp-crackdown (and @apptbl-transp-crackdown), these heuristics also interact with each other.[^transp-only] The estimated posterior marginal means for different relationships with host governments move in the same direction regardless of whether an organization engages in transparency practices: organizations with no conflict are most preferred, while organizations under government crackdown are least preferred.
 Transparency practices in the presence of crackdown seem to have two general effects.
@@
 
-Over recent years, governments globally have systematically controlled and repressed NGOs using both violent tactics and legal means---a phenomenon known as "closing" or "shrinking" civic space.
+Over recent years, governments globally have systematically controlled and repressed NGOs using both violent tactics and legal means.
 This trend of closing civic space has important implications for local and international NGOs as well as donors.
@@
 How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country civic environments when deciding to donate?
-We argue that informational heuristics about NGOs’ legal and political environments and organizational-level attributes can influence donor preferences for international giving.
-Using a conjoint experiment with a nationally representative sample of the U.S.
-population, we find that both financial transparency and accountability increases individuals' willingness to donate to NGOs.
-Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability protect against this dampening effect, increasing the probability of philanthropic domations by nine percentage points under the worst conditions of legal crackdown.
+Using a conjoint experiment, we demonstrate that organizational and structural characteristics of NGOs serve as cues or heuristics that influence donor preferences.
+Organizational practices like financial transparency and accountability increase willingness to donate to NGOs.
+Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, financial transparency and accountability protect against this dampening effect, increasing the probability of philanthropic donations by nine percentage points under the worst conditions of legal crackdown.
 Our results highlight the importance of organizational characteristics like transparency and accountability even in an era of closing civic space.
@@
 The responses of elite donors and foundations to government crackdown on civil society organizations remains a ripe area for research.
-Future research should test how well these results map on to elite individual donors, not just the average private donor, as well as determine the extent to which these preferences translate into behavior.
-Future research should also test the generalizability of these findings to non-American populations.
-Donors in European countries may have different preferences when choosing to donate to NGOs, as nonprofits in the European sector typically do not rely as much on government funding, and already receive more support from private donors compared to the American context.
-Government crackdown on civil society organizations is even more challenging for local NGOs in Global South countries, where much government and public support is channeled via service delivery organizations.
-Local groups tackling contentious issues may not be able to raise funds domestically, as individuals may prefer donating to service organizations focusing on health, education, and poverty [@AbsarCrowRon:2017].
-Even local philanthropists may be deterred from giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to poor tax incentives or a fear of retribution [@Brechenmacher:2017; @DupuyRonPrakash:2015; @Baoumi:2016].
+Future research should test how well these results map on to elite individual donors and foundations---not just the average private donor.
+As large foundations are more likely to publish data about their giving than the average private donor, it may be possible to determine how the changes in preferences elicited by these heuristics translate into actual donation behavior.
+Future work should also test how these findings translate to non-American populations.
+Due to structural differences in the European nonprofit sector, where NGOs rely less on government funding and more on private funding [@Stroup:2012], donors are likely motivated by different concerns.
+Government crackdown on civil society organizations is even more challenging for local NGOs in Global South countries, where much government and public support is channeled through service delivery organizations.
+Domestic NGOs that work on more contentious issues may not be able to raise money locally, as individuals may prefer donating to service organizations focusing on health, education, and poverty [@AbsarCrowRon:2017].
+Moreover, individual donors might also avoid giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to unfavorable tax benefits or fear of retribution [@Brechenmacher:2017; @DupuyRonPrakash:2015; @Baoumi:2016].
 Future research should examine how local NGOs can overcome individual foreign donors’ concerns about host governments' criticisms of and crackdown on these groups.
@@
 
-\newpage
+\clearpage
 
@@
 
-## Preregistration
+## Preregistration deviations
+
+We made the following deviations from our preregistered protocol [@WillrothAtherton:2024]:
+
+1. Type
+
+   :   Analysis
+
+   Reason
+
+   :   New knowledge
+
+   Timing
+
+   :   After results known
+
+   Original wording
+
+   :   "We will examine the aggregate marginal posterior distributions of the attribute levels"
+
+   Deviation description
+
+   :   This statement was vague and seemed to imply that we would analyze the results of the model by looking only at the raw model coefficients.
+While is is possible to calculate exact feature contrasts by summing specific combinations of coefficients, we instead calculated estimated marginal means and their contrasts (or AMCEs) using the fitted model.
+
+   Reader impact
+
+   :   This deviation should improve readers' interpretation of the findings, since the reported results are no longer on a log-odds or logit scale, and instead are on a more interpretable percentage point scale—estimated marginal means show the percent of respondents who support an NGO given a specific features, while AMCEs show the percentage point change in support when moving from one feature to another.
+The risk of bias is minimal as the underlying results are identical whether reported as logit-scale coefficients or marginal means.
+
+2. Type
+
+   :   Hypotheses
+
+   Reason
+
+   :   Stylistic
+
+   Timing
+
+   :   After results known
+
+   Original wording
+
+   :   Q5a: "Donors will show increased willingness to donate to NGOs that are financially transparent"
+
+   Deviation description
+
+   :   We rephrased this as H~1a~: "If NGOs are financially transparent, then individual private donors will have a higher likelihood of supporting or donating to them."
+
+   Reader impact
+
+   :   This deviation has minimal impact on readers' interpretation of the findings—it is only rephrased to follow an "if… then…" formulation.
+
+3. Type
+
+   :   Hypotheses
+
+   Reason
+
+   :   New knowledge + stylistic
+
+   Timing
+
+   :   Direction restated after data collection, but before results were known; "if… then…" formulation added after results known
+
+   Original wording
+
+   :   Q5f: "Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits"
+
+   Deviation description
+
+   :   We rephrased this as H~1b~: "If NGOs are accountable and hold regular third-party audits, then individual private donors will have a higher likelihood of supporting or donating to them."
+
+   Reader impact
+
+   :   This deviation might have some impact on readers' interpretation of the findings.
+This deviation was the result of misunderstanding existing work on the effect of nonprofit accountability on donor behavior, and we hypothesized that there would be no effect, contrary to what is predicted by previous research.
+The risk of bias is low, however—we reversed our prediction after data collection but before we analyzed the data and before the results were known.
+
+4. Type
+
+   :   Hypotheses
+
+   Reason
+
+   :   Stylistic
+
+   Timing
+
+   :   After results known
+
+   Original wording
+
+   :   Q2a: "Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism"
+
+   Deviation description
+
+   :   We rephrased this as H~2~: "If NGOs face legal crackdowns abroad, then individual private donors will have a higher likelihood of supporting or donating to them."
+
+   Reader impact
+
+   :   This deviation has minimal impact on readers' interpretation of the findings—it is only rephrased to follow an "if… then…" formulation.
+
+5. Type
+
+   :   Hypotheses
+
+   Reason
+
+   :   New knowledge
+
+   Timing
+
+   :   Accountability prediction added after data collection, but before results were known; "if… then…" formulation added after results known
+
+   Original wording
+
+   :   Q5b: "Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent"
+
+   Deviation description
+
+   :   We explore the interaction between (1) government crackdown and financial transparency and (2) government crackdown and accountability in the paper, but we only specified the first interaction in the preregistration.
+
+   Reader impact
+
+   :   This deviation might have some impact on readers' interpretation of the findings.
+The omission of a prediction of the relationship between government crackdown and accountability was inadvertent and we had intended to specify it.
+The risk of bias is low, as we added the new crackdown+accountability hypothesis after data collection and before the results were known.
+
+6. Type
+
+   :   Hypotheses
+
+   Reason
+
+   :   Narrative
+
+   Timing
+
+   :   After data collection, before results were known
+
+   Original wording
+
+   :   Q1: Branding; Q3: Issue area; Q4: Funding sources
+
+   Deviation description
+
+   :   For the sake of narrative simplicity, we do not explicitly test these three predictions as hypotheses.
+In this paper, our primary interest is crackdown, transparency, and accountability, but we look at branding, issue area, and funding sources to help compare and give context to the magnitude of our main hypotheses.
+
+   Reader impact
+
+   :   This deviation might have some impact on readers' interpretation of the findings, as it might appear that we have selectively reported a handful of our predictions.
+To avoid this, and for the sake of full transparency, we include these results in @fig-all-results and @apptbl-all-results.
+The risk of bias is low—we decided on the narrative framing for this paper after collecting the data but before analyzing the results.
+
+## Condensed preregistration
 

### 2024-03-28 manuscript/manuscript.qmd
renv update

@@
 short-title: "Why Donors Donate"
-date: "2024-03-27"
+date: "2024-03-28"
 author:

### 2024-07-23 manuscript/manuscript.qmd
Update affiliation

@@
 - name: Marc Dotson
-  affiliation: Brigham Young University
-  url: https://marriottschool.byu.edu/directory/details?id=50683
-  email: marc_dotson@byu.edu
+  affiliation: Utah State University
+  url: https://occasionaldivergences.com/
+  email: marc.dotson@usu.edu
   orcid: 0000-0001-7846-3660

### 2024-07-30 manuscript/submissions/NVSQ/response_nvsq.qmd
Update templates

---
title: Responses to reviewer concerns
format: hikmah-response-typst
bibliography: ../../references.bib
csl: ../../csl/chicago-author-date.csl
citeproc: true
link-citations: true
---

Thank you for giving us the opportunity to revise and resubmit our research article "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy" (Manuscript ID `NVSQ-AR-23-0438`). We found the Reviewers' comments to be very insightful and helpful, as they identified several parts of the manuscript that were unclear and incomplete. In this memo, we describe how we have revised the paper in response to these comments. The Reviewers' comments are cited or summarized in [red italicized text]{.memo-reviewer-inline}, and our responses are in black Roman text. We include excerpts from our revised manuscript in [blue]{.memo-excerpt-inline}.

# Reviewer 1

::: {.memo-reviewer}
1. The authors may need to explain more about why choosing transparency and accountability as two organizational factors, given that there are many different organizational factors that donors may use for their donations.
:::

We thank Reviewer 1 for blah blah blah

::: {.memo-excerpt}
**[pp. 4–5]**: PASTE FROM RENDERED .QMD FILE
:::

---

::: {.memo-reviewer}
2. In Table 1, Relationship with host government has three levels: (a) Friendly relationship with government; (b) Criticized by government; (c) Under government crackdown. This organizational level measurement may not exactly capture the macro level shrinking civic space in many countries. Also, the authors may clearly state that the INGOs operate in countries where INGOs are controlled and constrained in the experiment.
:::

We thank Reviewer 1 for blah blah blah

::: {.memo-excerpt}
**[pp. x-xx]**: PASTE FROM RENDERED .QMD FILE
:::

# Reviewer 2

::: {.memo-reviewer}
X. Reviewer request/comment
:::

We thank Reviewer 2 for blah blah blah

::: {.memo-excerpt}
**[pp. x-xx]**: PASTE FROM RENDERED .QMD FILE
:::

---

::: {.memo-reviewer}
X. Reviewer request/comment
:::

We thank Reviewer 2 for blah blah blah

::: {.memo-excerpt}
**[pp. x-xx]**: PASTE FROM RENDERED .QMD FILE
:::

# Reviewer 3

::: {.memo-reviewer}
1. Why did you ask each respondent to review 12 scenarios?

   On page 16 line 33, you suggest that three NGOs were mentioned in each scenario the respondents considered (and then did this twelve tines). Is this a typo as it sounds very complex?
:::

Blah blah how we responded

::: {.memo-excerpt}
**[pp. x-xx]**: What we did
:::

---

::: {.memo-reviewer}
1. You should include some clearer discussion of how donation intention was operationalised in this discussion.
:::

Blah blah how we responded

::: {.memo-excerpt}
**[pp. x-xx]**: What we did
:::

---

::: {.memo-reviewer}
X. Reviewer request/comment
:::

We thank Reviewer 3 for blah blah blah

::: {.memo-excerpt}
**[pp. x-xx]**: PASTE FROM RENDERED .QMD FILE
:::

---

::: {.memo-reviewer}
X. Reviewer request/comment
:::

We thank Reviewer 3 for blah blah blah

::: {.memo-excerpt}
**[pp. x-xx]**: PASTE FROM RENDERED .QMD FILE
:::

---

# References

### 2024-08-12 manuscript/manuscript.qmd
Added to experimental design discussion

@@
 We then repeated the process eleven more times for a total of twelve randomized iterations of hypothetical combinations of attributes, resulting in 12,192 completed experimental tasks (12 iterations × 1,016 respondents).
+In order to estimate individual-specific differences using a multilevel model, each respondent had to complete multiple experimental tasks.
+Having choice of hypothetical organization indicate donation intention and asking respondents to iteratively make this choice across 12 experimental tasks are both typical of conjoint analysis.
 

### 2025-01-11 manuscript/manuscript.qmd
Update updated citekeys

@@
 Repressive governments have cracked down on these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs [@DupuyRonPrakash:2016; @Chaudhry:2022; @Heiss:2017].
-Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" [@CarothersBrechenmacher:2014; @Rutzen:2015].
+Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" [@CarothersBrechenmacher:2014; @Rutzen:2015b].
 Data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in more than 60% of countries---117 in total [@CIVICUSMonitor].
@@
 Our findings make two main contributions.
-First, existing research on privately-provided foreign aid primarily looks at organizations like foundations and large donor NGOs, and not private individuals [@ButheMajorMello-e-Souza:2012; @Koch:2009; @DesaiKharas:2018], and studies that do examine individual giving behavior typically only examine wealthy individuals [@USTrust2014].
+First, existing research on privately-provided foreign aid primarily looks at organizations like foundations and large donor NGOs, and not private individuals [@ButheMajordeMelloeSouza:2012; @Koch:2009; @DesaiKharas:2018], and studies that do examine individual giving behavior typically only examine wealthy individuals [@USTrust2014].
 Our research expands work on private international philanthropy by exploring how non-elite individuals decide to donate to NGOs focused on international affairs.
@@
 Conjoint designs have been used extensively in political science to study complex preferences for elections, laws, public policy, and public opinion [@HainmuellerHopkinsYamamoto:2014; @Mummolo:2016; @KertzerRenshonYarhi-Milo:2021; @BansakHainmuellerHopkins:2021; @BremerBurgisser:2023], and conjoint experiments are becoming more common in nonprofit studies, particularly for studying individual donor behavior [@SilviaChildWitesman:2023; @HirschmannMoritzBlock:2022; @BachkeAlfnesWik:2014; @Kottasz:2004].
-@KnudsenJohannesson:2019 argue that research related to respondent opinions requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility.
+@KnudsenJohannesson:2018 argue that research related to respondent opinions requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility.
 Because we also want to capture the complexity of a respondent's judgment of philanthropic preferences, we use a conjoint experiment to measure the causal effect of both organizational and structural heuristics on individuals' preferences for donating to international NGOs.
@@
 We also included an attention check question early in the survey and removed respondents who failed the question.
-Importantly, these screening questions were presented *prior to* the experimental manipulation to avoid post-treatment bias [@MontgomeryNyhanTorres:2018].
+Importantly, these screening questions were presented *prior to* the experimental manipulation to avoid post-treatment bias [@MontgomeryNyhanTorres:2018a].
 Following screening, we received 1,016 viable responses.
@@
 
-[^stan]: We use Stan [@Stan-2-26-1 v2.26.1; @cmdstan-2-3-1 v2.3.1] through R [@rproject-4-3-1 v4.3.1] and **brms** [@Burkner:2017 v2.20.5] to estimate the model.
+[^stan]: We use Stan [@Stan-2-26-1 v2.26.1; @cmdstan-2-3-1 v2.3.1] through R [@rproject-4-3-3 v4.3.1] and **brms** [@Burkner:2017 v2.20.5] to estimate the model.
 We simulate 4 MCMC chains with 5,000 draws in each chain, 1,000 of which are used for warmup, resulting in 16,000 (4,000 × 4) draws per model parameter.
@@
 
-We provide viusalizations of the full posterior distributions of each of the effects of interest, and we report two distributional summary statistics: (1) the posterior median, (2) credible intervals based on a 95% equal-tailed quantile interval, However, we are generally less concerned with the exact point estimates of our causal effects and instead focus on the direction and relative magnitude of their posterior distributions.
+We provide visualizations of the full posterior distributions of each of the effects of interest, and we report two distributional summary statistics: (1) the posterior median, (2) credible intervals based on a 95% equal-tailed quantile interval, However, we are generally less concerned with the exact point estimates of our causal effects and instead focus on the direction and relative magnitude of their posterior distributions.
 For inference, we calculate the probability of direction ($p_d$), or the probability that the posterior AMCE is strictly positive or negative---it is the proportion of the posterior AMCE that is the sign of the median.

### 2025-01-11 manuscript/manuscript.qmd
Move appendix out

@@
 :::
-
-\newpage
-
-:::: {#appendix-count}
-
-# Appendix
-
-## Calculating marginal means and AMCEs from a multinomial model using a reference grid
-
-To find the causal effects defined in each of our estimands, we calculate estimated marginal means (EMMs) by finding the fitted probability-scale values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding = 576 rows).
-We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.
-At its core, a "marginal mean" refers to the literal mean in the margins in a contingency table of model predictions, and differences in marginal means are equivalent to marginal effects or regression coefficients.
-
-When working with the results for our multinomial regression model, we rely on estimated marginal means rather than raw regression coefficients because of the complexity of the model.
-As seen in @apptbl-coefs-orig, the model returns three sets of coefficients per conjoint level.
-Each coefficient shows the shift in probability that someone will choose an organization from column 1, column 2, or column 3, so we get a coefficient for each of those outcomes (or µ1, µ2, and µ3).
-Under experimental conditions where cells in the contingency table are randomly assigned, it is safe to assume that the cell proportions are equal and then marginalize (i.e.
-find the average) across the rows or columns.
-This allows us to take the average of each set of coefficients (e.g.
-µ1, µ2, and µ3 for "Transparency = Yes") to create a single value per coefficient.
-
-To convert EMMs and AMCEs to a more interpretable probability scale (rather than the original log odds scale), we generate predicted values (marginalized across the three µ terms) for each of the 576 unique combinations of feature levels.
-@apptbl-grid-example provides an excerpt from this grid, showing six rows where accountability, organization, issue area, and funding are identical and held constant, while transparency and government relations vary.
-
-::: {#apptbl-grid-example}
-
-\footnotesize
-
-```{r}
-#| label: table-grid-example
-#| include: true
-grid_example <- expand_grid(
-  feat_transp = c("Transparency: Yes", "Transparency: No"), 
-  feat_acc = "Accountability: Yes", 
-  feat_govt = c("Friendly relationship with government", "Criticized by government", "Under government crackdown"),
-  feat_org = "Red Cross", 
-  feat_issue = "Emergency response", 
-  feat_funding = "Funded primarily by many small private donations"
-)
-
-preds_small <- preds_all %>% 
-  group_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>% 
-  summarize(avg = mean(.epred)) %>% 
-  inner_join(
-    grid_example, 
-    by = join_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt)
-  ) %>% 
-  mutate(avg_nice = label_comma(accuracy = 0.001)(avg))
-
-p_sm <- preds_small %>% 
-  group_by(feat_transp) %>% 
-  summarize(
-    emm_numeric = mean(avg),
-    emm = label_comma(accuracy = 0.001)(mean(avg)),
-    list = knitr::combine_words(avg_nice, sep = " + ", and = "")
-  ) %>% 
-  mutate(feat_transp = janitor::make_clean_names(feat_transp)) %>% 
-  split(~feat_transp)
-
-amce_fake <- p_sm$transparency_yes$emm_numeric - p_sm$transparency_no$emm_numeric
-amce_tr_fake <- label_comma(accuracy = 0.001)(amce_fake)
-amce_tr_fake_pp <- label_comma(accuracy = 1, scale = 100)(amce_fake)
-
-preds_small %>% 
-  select(-avg) %>% 
-  ungroup() %>% 
-  gt() %>% 
-  cols_label(
-    feat_transp = "Transparency", 
-    feat_acc = "Accountability", 
-    feat_govt = "Government",
-    feat_org = "Organization",
-    feat_issue = "Issue",
-    feat_funding = "Funding",
-    avg_nice = "EMM"
-  ) %>%
-  cols_width(everything() ~ gt_pct(12)) %>% 
-  cols_width(avg_nice ~ gt_pct(7)) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>%
-  opts_theme() |>
-  tab_options(
-    quarto.disable_processing = TRUE
-  )
-```
-
-Excerpt from complete reference grid of all 576 possible combinations of attribute features and levels
-
-:::
-
-To calculate the marginal mean for a feature, we find the average predicted value across each the levels of that feature.
-To illustrate, assume that @apptbl-grid-example represents the full reference grid of all experimental features and levels.
-The marginal means for transparency would be (`r p_sm$transparency_no$list`)/3 = `r p_sm$transparency_no$emm` when transparency is set to "no", and (`r p_sm$transparency_yes$list`)/3 = `r p_sm$transparency_yes$emm` when transparency is set to "yes".
-In reality, the marginal mean for transparency reported in @fig-all-results and @apptbl-all-results reflects the average of 288 rows where transparency is no and 288 rows where transparency is yes.
-
-To calculate the AMCE for a feature, we find the difference in estimated marginal means.
-If we again assume that @apptbl-grid-example contains the full reference grid, the AMCE for transparency would be `r p_sm$transparency_yes$emm` − `r p_sm$transparency_no$emm`, or `r amce_tr_fake`, or `r amce_tr_fake_pp` percentage points.
-Again, this is not actually the true causal effect—the real AMCE in @fig-all-results and @apptbl-all-results is the difference in marginal means for the 288 rows where transparency is no and the 288 rows where transparency is yes.
-
-## Additional tables
-
-```{=latex}
-\floatstyle{plaintop}
-\restylefloat{apptbl}
-```
-
-::: {#apptbl-sample-details-demographics}
-
-\footnotesize
-
-```{r}
-#| label: table-sample-details-demographics
-#| include: true
-tbl_participant_summary <- participant_summary %>% 
-  select(
-    category, 
-    Question = clean_name,
-    Response = level,
-    N = count,
-    `%` = nice_prop
-  ) %>% 
-  split(~category)
-
-tbl_participant_summary$Demographics %>% 
-  select(-category) %>% 
-  group_by(Question) %>% 
-  gt() %>% 
-  tab_spanner(label = "Demographics", columns = everything()) %>% 
-  cols_width(Response ~ gt_pct(30), everything() ~ gt_pct(15)) %>% 
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = Response) %>% 
-  opts_theme() |>
-  tab_options(
-    quarto.disable_processing = TRUE
-  )
-```
-
-Demographics
-
-:::
-
-\newpage
-
-::: {#apptbl-sample-details-charity}
-
-\footnotesize
-
-```{r}
-#| label: table-sample-details-charity
-#| include: true
-tbl_participant_summary$`Attitudes toward charity` %>% 
-  select(-category) %>% 
-  group_by(Question) %>% 
-  gt() %>% 
-  tab_spanner(label = "Attitudes toward charity", columns = everything()) %>% 
-  cols_width(Response ~ gt_pct(30), everything() ~ gt_pct(15)) %>% 
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = Response) %>% 
-  opts_theme() |>
-  tab_options(
-    quarto.disable_processing = TRUE
-  )
-```
-
-Attitudes toward charity
-
-:::
-
-::: {#apptbl-sample-details-politics}
-
-\footnotesize
-
-```{r}
-#| label: table-sample-details-politics
-#| include: true
-tbl_participant_summary$`Politics, ideology, and religion` %>% 
-  select(-category) %>% 
-  group_by(Question) %>% 
-  gt() %>% 
-  tab_spanner(label = "Politics, ideology, and religion", columns = everything()) %>% 
-  cols_width(Response ~ gt_pct(30), everything() ~ gt_pct(15)) %>% 
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = Response) %>% 
-  opts_theme() |>
-  tab_options(
-    quarto.disable_processing = TRUE
-  )
-```
-
-Politics, ideology, and religion
-
-:::
-
-\newpage
-
-::: {#apptbl-all-results}
-
-\scriptsize
-
-```{r}
-#| label: table-all-results
-#| include: true
-mms_all_tbl <- mms_all %>% 
-  drop_na(feature_level) %>% 
-  group_by(feature_nice_paper, feature_level = fct_rev(feature_level)) %>% 
-  median_qi(avg) %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}\n{build_ci(.lower, .upper)}")) %>% 
-  select(feature_nice_paper, feature_level, mm_nice = nice)
-
-amces_all_tbl <- amces_all %>% 
-  mutate(feature_level = factor(feature_level, levels = levels(mms_all$feature_level))) %>% 
-  mutate(contrast = glue("{feature_level}−{reference_level}")) %>% 
-  group_by(feature_nice_paper, feature_level = fct_rev(feature_level), contrast) %>% 
-  summarize(
-    median_qi(avg),
-    p_gt_0 = sum(avg > 0) / n()
-  ) %>% 
-  ungroup() %>% 
-  mutate(is_reference = str_detect(contrast, "−NA")) %>% 
-  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
-  mutate(contrast = ifelse(is_reference, "*(Reference)*", contrast)) %>% 
-  mutate(nice = ifelse(is_reference, NA, glue("{fmt_decimal(y)}\n{build_ci(ymin, ymax)}"))) %>% 
-  mutate(pd = ifelse(is_reference, NA, fmt_decimal2(p_neq_0))) %>% 
-  select(feature_nice_paper, feature_level, contrast, amce_nice = nice, pd)
-
-left_join(
-  mms_all_tbl, amces_all_tbl, 
-  by = join_by(feature_nice_paper, feature_level)
-) %>% 
-  mutate(across(c(feature_level, contrast), ~{
-    .x %>% 
-      str_replace_all("Transparency: ", "") %>% 
-      str_replace_all("Accountability: ", "")
-  })) %>% 
-  # mutate(contrast = str_replace_all(contrast, "[Transparency: |Accountability: ]", "")) %>% 
-  mutate(across(c(mm_nice, amce_nice), ~gt_linebreak(.))) %>% 
-  group_by(feature_nice_paper) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown_latex(columns = c("mm_nice", "amce_nice")) %>% 
-  fmt_markdown(columns = c(contrast)) %>%
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feature_level, contrast)) %>% 
-  cols_label(
-    feature_level = "Feature", 
-    mm_nice = "Posterior EMM",
-    contrast = "Contrast",
-    amce_nice = "Posterior AMCE",
-    pd = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  cols_width(
-    feature_level ~ gt_pct(18),
-    mm_nice ~ gt_pct(12),
-    contrast ~ gt_pct(35),
-    amce_nice ~ gt_pct(12),
-    pd ~ gt_pct(6)
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_style(
-    style = cell_fill(color = "grey90"),
-    locations = cells_row_groups()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(mm_nice, amce_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."),
-    locations = cells_column_labels(columns = pd)
-  ) %>% 
-  gt_add_divider(columns = mm_nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme() %>% 
-  tab_options(
-    quarto.disable_processing = TRUE
-  )
-```
-
-Complete results
-
-:::
-
-\newpage
-
-::: {#apptbl-mms-trans-acc}
-
-\footnotesize
-
-```{r}
-#| label: table-mms-trans-acc
-#| include: true
-mms_trans_acc_all %>% 
-  group_by(feat_transp, feat_acc) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}\n{build_ci(.lower, .upper)}")) %>% 
-  mutate(across(c(nice), ~gt_linebreak(.))) %>% 
-  select(feat_transp, feat_acc, nice) %>% 
-  group_by(feat_transp) %>% 
-  gt() %>% 
-  fmt_markdown_latex(columns = c("nice")) %>% 
-  cols_align(align = "center", columns = c(nice)) %>% 
-  cols_align(align = "left", columns = c(feat_transp, feat_acc)) %>% 
-  cols_label(
-    feat_acc = "Features", 
-    nice = "Posterior EMM",
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_style(
-    style = cell_fill(color = "grey90"),
-    locations = cells_row_groups()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice))
-  ) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme() %>% 
-  tab_options(
-    quarto.disable_processing = TRUE
-  )
-```
-
-Marginal means for all combinations of transparency and accountability
-
-:::
-
-::: {#apptbl-transp-crackdown}
-
-\footnotesize
-
-```{r}
-#| label: table-transp-crackdown
-#| include: true
-
-mms_transp_crackdown_tbl <- mms_transp_crackdown %>% 
-  group_by(feat_transp_short, feat_govt) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}\n{build_ci(.lower, .upper)}")) %>% 
-  ungroup() %>% 
-  arrange(desc(feat_govt), desc(feat_transp_short)) %>% 
-  select(feat_transp_short, feat_govt, nice)
-
-amces_transp_crackdown_tbl <- amces_transp_crackdown_medians %>% 
-  ungroup() %>% 
-  mutate(nice = glue("{fmt_decimal(y)}\n{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_transp_short = str_replace(feat_transp_short, " - ", "−")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(contrast = feat_transp_short, diff_nice = nice, p_neq_0)
-
-mms_acc_crackdown_tbl <- mms_acc_crackdown %>% 
-  group_by(feat_acc_short, feat_govt) %>% 
-  median_qi() %>% 
-  mutate(nice = glue("{fmt_decimal(avg)}\n{build_ci(.lower, .upper)}")) %>% 
-  ungroup() %>% 
-  arrange(desc(feat_govt), desc(feat_acc_short)) %>% 
-  select(feat_acc_short, feat_govt, nice)
-
-amces_acc_crackdown_tbl <- amces_acc_crackdown_medians %>% 
-  ungroup() %>% 
-  mutate(nice = glue("{fmt_decimal(y)}\n{build_ci(ymin, ymax)}")) %>% 
-  mutate(feat_acc_short = str_replace(feat_acc_short, " - ", "−")) %>% 
-  mutate(across(starts_with("p_"), ~fmt_decimal(.))) %>% 
-  arrange(desc(feat_govt)) %>% 
-  select(contrast = feat_acc_short, diff_nice = nice, p_neq_0)
-
-bind_rows(
-  bind_cols(
-    mms_transp_crackdown_tbl, 
-    amces_transp_crackdown_tbl %>% 
-      add_row(contrast = NA, .after = 1) %>% 
-      add_row(contrast = NA, .after = 3) %>% 
-      add_row(contrast = NA, .after = 5)
-  ) %>% 
-    mutate(feat_level = paste("Transparency:", feat_transp_short)) %>% 
-    select(-feat_transp_short),
-  bind_cols(
-    mms_acc_crackdown_tbl, 
-    amces_acc_crackdown_tbl %>% 
-      add_row(contrast = NA, .after = 1) %>% 
-      add_row(contrast = NA, .after = 3) %>% 
-      add_row(contrast = NA, .after = 5)
-  ) %>% 
-    mutate(feat_level = paste("Accountability:", feat_acc_short)) %>% 
-    select(-feat_acc_short)
-) %>%
-  mutate(contrast = ifelse(is.na(contrast), "*(Reference)*", contrast)) %>% 
-  mutate(across(c(nice, diff_nice), ~gt_linebreak(.))) %>% 
-  relocate(feat_level) %>% 
-  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
-  group_by(feat_govt) %>% 
-  gt() %>% 
-  sub_missing(columns = everything(), missing_text = "—") %>% 
-  fmt_markdown_latex(columns = c("nice", "diff_nice")) %>% 
-  fmt_markdown(columns = contrast) %>% 
-  cols_align(align = "center", columns = everything()) %>% 
-  cols_align(align = "left", columns = c(feat_level, contrast)) %>% 
-  cols_label(
-    feat_level = "Feature", 
-    nice = "Posterior EMM",
-    contrast = "Contrast",
-    diff_nice = "Posterior ∆",
-    p_neq_0 = "*p*~direction~",
-    .fn = md
-  ) %>% 
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>% 
-  tab_style(
-    style = cell_fill(color = "grey90"),
-    locations = cells_row_groups()
-  ) %>% 
-  tab_footnote(
-    footnote = "Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.",
-    locations = cells_column_labels(columns = c(nice, diff_nice))
-  ) %>% 
-  tab_footnote(
-    footnote = md("The probability of direction (*p*~direction~) is the probability that the posterior difference in marginal means is strictly positive or negative—it is the proportion of the posterior difference in marginal means that is the sign of the median."),
-    locations = cells_column_labels(columns = p_neq_0)
-  ) %>% 
-  gt_add_divider(columns = nice, style = "dashed", weight = px(1)) %>% 
-  opt_footnote_marks(marks = "standard") %>% 
-  opt_horizontal_padding(3) %>% 
-  opts_theme() %>% 
-  tab_options(
-    quarto.disable_processing = TRUE
-  )
-```
-
-Marginal means and AMCEs for interaction between transparency, accountability, and government relationships
-
-:::
-
-\blandscape
-
-::: {#apptbl-coefs-orig}
-
-\footnotesize
-
-```{r}
-#| label: table-coefs-orig
-#| include: true
-notes <- c(
-  "Estimates are median posterior log odds from a multinomial logistic regression model with three possible categories, and the columns for µ1, µ2, and µ3 represent estimates for each of the outcomes;",
-  "95% credible intervals (equal-tailed quantile intervals) in brackets."
-)
-
-base_table <- modelsummary(
-  list("Posterior medians" = model_summary_table, "95% credible intervals" = model_summary_table),
-  shape = Feature + term ~ group,
-  estimate = c("estimate", "[{conf.low}, {conf.high}]"),
-  statistic = NULL,
-  output = "gt",
-  fmt = fmt_significant(2)
-)
-
-base_table$`_data` <- base_table$`_data` %>%
-  mutate(Feature = ifelse(!duplicated(Feature), as.character(Feature), ""))
-
-# lol there's a weird bug in {gt} where there's an error if the footnote is a
-# vector with multiple elements? So we flatten it when knitting to latex
-base_table %>% 
-  tab_footnote(
-    footnote = ifelse(fmt_out == "latex", paste(notes, collapse = " "), notes)
-  ) %>%
-  opts_theme() |>
-  tab_options(
-    quarto.disable_processing = TRUE
-  )
-```
-
-Original model coefficients
-
-:::
-
-\elandscape
-
-\clearpage
-
-::: {.content-visible when-profile="ms"}
-\singlespacing
-:::
-
-## Preregistration deviations
-
-We made the following deviations from our preregistered protocol [@WillrothAtherton:2024]:
-
-1. Type
-
-   :   Analysis
-
-   Reason
-
-   :   New knowledge
-
-   Timing
-
-   :   After results known
-
-   Original wording
-
-   :   "We will examine the aggregate marginal posterior distributions of the attribute levels"
-
-   Deviation description
-
-   :   This statement was vague and seemed to imply that we would analyze the results of the model by looking only at the raw model coefficients.
-While is is possible to calculate exact feature contrasts by summing specific combinations of coefficients, we instead calculated estimated marginal means and their contrasts (or AMCEs) using the fitted model.
-
-   Reader impact
-
-   :   This deviation should improve readers' interpretation of the findings, since the reported results are no longer on a log-odds or logit scale, and instead are on a more interpretable percentage point scale—estimated marginal means show the percent of respondents who support an NGO given a specific features, while AMCEs show the percentage point change in support when moving from one feature to another.
-The risk of bias is minimal as the underlying results are identical whether reported as logit-scale coefficients or marginal means.
-
-2. Type
-
-   :   Hypotheses
-
-   Reason
-
-   :   Stylistic
-
-   Timing
-
-   :   After results known
-
-   Original wording
-
-   :   Q5a: "Donors will show increased willingness to donate to NGOs that are financially transparent"
-
-   Deviation description
-
-   :   We rephrased this as H~1a~: "If NGOs are financially transparent, then individual private donors will have a higher likelihood of supporting or donating to them."
-
-   Reader impact
-
-   :   This deviation has minimal impact on readers' interpretation of the findings—it is only rephrased to follow an "if… then…" formulation.
-
-3. Type
-
-   :   Hypotheses
-
-   Reason
-
-   :   New knowledge + stylistic
-
-   Timing
-
-   :   Direction restated after data collection, but before results were known; "if… then…" formulation added after results known
-
-   Original wording
-
-   :   Q5f: "Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits"
-
-   Deviation description
-
-   :   We rephrased this as H~1b~: "If NGOs are accountable and hold regular third-party audits, then individual private donors will have a higher likelihood of supporting or donating to them."
-
-   Reader impact
-
-   :   This deviation might have some impact on readers' interpretation of the findings.
-This deviation was the result of misunderstanding existing work on the effect of nonprofit accountability on donor behavior, and we hypothesized that there would be no effect, contrary to what is predicted by previous research.
-The risk of bias is low, however—we reversed our prediction after data collection but before we analyzed the data and before the results were known.
-
-4. Type
-
-   :   Hypotheses
-
-   Reason
-
-   :   Stylistic
-
-   Timing
-
-   :   After results known
-
-   Original wording
-
-   :   Q2a: "Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism"
-
-   Deviation description
-
-   :   We rephrased this as H~2~: "If NGOs face legal crackdowns abroad, then individual private donors will have a higher likelihood of supporting or donating to them."
-
-   Reader impact
-
-   :   This deviation has minimal impact on readers' interpretation of the findings—it is only rephrased to follow an "if… then…" formulation.
-
-5. Type
-
-   :   Hypotheses
-
-   Reason
-
-   :   New knowledge
-
-   Timing
-
-   :   Accountability prediction added after data collection, but before results were known; "if… then…" formulation added after results known
-
-   Original wording
-
-   :   Q5b: "Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent"
-
-   Deviation description
-
-   :   We explore the interaction between (1) government crackdown and financial transparency and (2) government crackdown and accountability in the paper, but we only specified the first interaction in the preregistration.
-
-   Reader impact
-
-   :   This deviation might have some impact on readers' interpretation of the findings.
-The omission of a prediction of the relationship between government crackdown and accountability was inadvertent and we had intended to specify it.
-The risk of bias is low, as we added the new crackdown+accountability hypothesis after data collection and before the results were known.
-
-6. Type
-
-   :   Hypotheses
-
-   Reason
-
-   :   Narrative
-
-   Timing
-
-   :   After data collection, before results were known
-
-   Original wording
-
-   :   Q1: Branding; Q3: Issue area; Q4: Funding sources
-
-   Deviation description
-
-   :   For the sake of narrative simplicity, we do not explicitly test these three predictions as hypotheses.
-In this paper, our primary interest is crackdown, transparency, and accountability, but we look at branding, issue area, and funding sources to help compare and give context to the magnitude of our main hypotheses.
-
-   Reader impact
-
-   :   This deviation might have some impact on readers' interpretation of the findings, as it might appear that we have selectively reported a handful of our predictions.
-To avoid this, and for the sake of full transparency, we include these results in @fig-all-results and @apptbl-all-results.
-The risk of bias is low—we decided on the narrative framing for this paper after collecting the data but before analyzing the results.
-
-## Condensed preregistration
-
-::: {.callout-important icon=false}
-### Consensed preregistration
-
-This is an anonymized and condensed version of our full OSF preregistration protocol.
-:::
-
-{{< include text/preregistration.md >}}
-
-::::

### 2025-01-11 manuscript/manuscript.qmd
Switch to {tinytable}

@@
 library(glue)
-library(gt)
-library(gtExtras)
+library(tinytable)
 library(modelsummary)
@@
 theme_set(theme_ngo())
-
-gt_linebreak <- function(x) {
-  if (fmt_out == "latex") {
-    x %>% 
-      str_replace_all("\\[", "{[}") %>% 
-      str_replace_all("\\]", "{]}") %>% 
-      kableExtra::linebreak(align = "c")
-  } else {
-    str_replace_all(x, "\\n", "<br>")
-  }
-}
-
-fmt_markdown_latex <- function(x, columns) {
-  if (fmt_out == "latex") {
-    fmt_passthrough(x, columns = columns, escape = FALSE)
-  } else {
-    fmt_markdown(x, columns = columns)
-  }
-}
-
-gt_pct <- function(x, page_width = 6) {
-  if (fmt_out == "latex") {
-    paste0(page_width * (x / 100), "in")
-  } else {
-    gt::pct(x)
-  }
-}
 ```
@@
 
-\begingroup
-
-::: {.content-visible when-profile="ms"}
-\singlespacing
-:::
-
-::: {#tbl-design}
-
-\footnotesize
-\renewcommand*{\arraystretch}{1.75}
-
 ```{r}
-#| label: table-design
+#| label: tbl-design
+#| tbl-cap: "All experimental features and levels included in the conjoint experiment"
 #| include: true
@@
 tbl_features_levels %>%
-  rowwise() %>% 
-  mutate(type = ifelse(
-    fmt_out == "latex",
-    str_replace_all(type, "~([^~]+)~", "\\\\textsubscript{\\1}"),
-    type
-  )) %>%
-  gt() %>%
-  cols_label(feature = "Feature/Attribute", levels = "Levels", type = "Purpose") %>%
-  cols_width(feature ~ gt_pct(20), levels ~ gt_pct(50), type ~ gt_pct(15)) %>%
-  fmt_markdown_latex(columns = c("type")) %>%
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>%
-  opts_theme() |>
-  tab_options(
-    quarto.disable_processing = TRUE
+  setNames(c("Type", "Feature/Attribute", "Levels")) %>%
+  tt(width = c(0.15, 0.25, 0.5)) %>%
+  style_tt(j = 1:3, align = "l") %>%
+  format_tt(j = 1, markdown = TRUE) %>%
+  style_tt(
+    bootstrap_class = "table table-sm table-striped",
+    tabularray_inner = "rowsep=2pt, cells={font=\\footnotesize}, row{1}={valign=b}"
   )
 ```
-
-All experimental features and levels included in the conjoint experiment
-
-:::
-
-\endgroup
 
@@
 In order to estimate individual-specific differences using a multilevel model, each respondent had to complete multiple experimental tasks.
-Having choice of hypothetical organization indicate donation intention and asking respondents to iteratively make this choice across 12 experimental tasks are both typical of conjoint analysis.
-
-::: {.content-visible when-profile="ms"}
-\clearpage
-:::
-
-\begingroup
-
-::: {.content-visible when-profile="ms"}
-\singlespacing
-:::
-
-::: {#tbl-example}
-
-\footnotesize
-\renewcommand*{\arraystretch}{1.75}
+Having the choice of hypothetical organization indicate donation intention and asking respondents to iteratively make this choice across twelve experimental tasks are both typical of conjoint analysis.
 
 ```{r}
-#| label: table-example
+#| label: tbl-example
+#| tbl-cap: "Example possible experimental task, with three randomized combinations of organizational attributes"
 #| include: true
@@
 tbl_example_task %>%
-  gt() %>%
-  cols_align(align = "center", columns = everything()) %>%
-  cols_align(align = "left", columns = Attribute) %>%
-  cols_width(everything() ~ gt_pct(17)) %>%
-  tab_style(
-    style = cell_text(v_align = "top"),
-    locations = cells_body()
-  ) %>%
-  tab_style(
-    style = cell_text(weight = "bold"),
-    location = cells_body(columns = Attribute)
-  ) %>%
-  opts_theme()
+  tt(width = rep(0.19, times = 5)) %>%
+  style_tt(j = 1, align = "l", bold = TRUE) %>%
+  style_tt(j = 2:5, align = "c") %>%
+  style_tt(
+    bootstrap_class = "table table-sm table-striped",
+    tabularray_inner = "rowsep=2pt, cells={font=\\footnotesize}, row{1}={valign=b}"
+  )
 ```
-
-Example possible experimental task, with three randomized combinations of organizational attributes
-
-:::
-
-\endgroup
 

### 2025-01-12 manuscript/appendix.qmd
Appendix tables with {tinytable}!

---
title: 'Appendix for "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy"'
short-title: 'Appendix for "Why Donors Donate'
date: "2025-01-11"
author:
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  url: http://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
  orcid: 0000-0003-3506-7590
- name: Marc Dotson
  affiliation: Utah State University
  url: https://occasionaldivergences.com/
  email: marc.dotson@usu.edu
  orcid: 0000-0001-7846-3660
- name: Andrew Heiss
  affiliations: 
    - id: gsu
      name: Georgia State University
      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
      address: "55 Park Place NE, #464"
      city: Atlanta
      region: GA
      country: USA
      postal-code: 30303
  url: https://www.andrewheiss.com/
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
  attributes:
    corresponding: true
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/silent-skywalk>"
bibliography: references.bib
csl: csl/apa.csl
link-citations: true
crossref:
  custom:
    - kind: float
      key: appfig
      latex-env: appfig
      reference-prefix: Figure A
      space-before-numbering: false
      latex-list-of-description: Appendix Figure
    - kind: float
      key: apptbl
      latex-env: apptbl
      reference-prefix: Table A
      space-before-numbering: false
      latex-list-of-description: Appendix Table
apptbl-cap-location: top
toc: true
toc-depth: 2
---

```{r setup, include=FALSE}
if (is.null(knitr::pandoc_to())) {
  fmt_out <- "interactive"
} else {
  fmt_out <- knitr::pandoc_to()
}

knitr::opts_chunk$set(
  echo = FALSE, include = FALSE,
  warning = FALSE, message = FALSE
)

knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "100%", collapse = TRUE
)

options(
  digits = 3, width = 120,
  dplyr.summarise.inform = FALSE
)
```

```{r libraries-data}
library(tidyverse)
library(targets)
library(tidybayes)
library(scales)
library(glue)
library(tinytable)
library(modelsummary)
library(here)

# Targets stuff
tar_config_set(
  store = here("_targets"),
  script = here("_targets.R")
)

tar_load(c(
  participant_summary, model_summary_table, feature_lookup, level_lookup
))

preds_all <- tar_read(preds_conditional_treatment_only)

invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))

if (fmt_out == "latex") {
  theme_appendix <- function(x) theme_tt(x, "tabular", style = "tabularray")
  options(tinytable_tt_theme = theme_appendix)
}

tt_md <- function(text) {
  if (fmt_out %in% c("html", "interactive")) {
    map_chr(text, \(x) {
      x %>%
        markdown::mark_html(text = ., template = FALSE) %>%
        trimws() %>%
        str_remove_all("<p>") %>%
        str_remove_all("</p>")
    })
  } else if (fmt_out == "latex") {
    map_chr(text, \(x) {
      x %>%
        markdown::mark_latex(text = ., template = FALSE) %>%
        trimws()
    })
  } else {
    map_chr(text, \(x) x)
  }
}

tt_linebreak <- function(text) {
  if (fmt_out == "latex") {
    map_chr(text, \(x) {
      if (is.na(x)) {
        return(x)
      }
      x %>%
        str_replace_all("\\[", "{[}") %>% 
        str_replace_all("\\]", "{]}") %>% 
        str_replace_all("\\n", r"(\\\\)") %>%
        paste0("{", ., "}")
    })
  } else {
    map_chr(text, \(x) {
      if (is.na(x)) {
        return(x)
      }
      str_replace(x, "\\n", "<br>")
    })
  }
}

get_row_group_index <- function(x) {
  if (is.factor(x)) {
    x <- as.character(x)
  }

  x_rle <- rle(x)
  x_i <- cumsum(c(1, utils::head(x_rle$lengths, -1)))
  x_i_adjusted <- as.numeric(x_i) + 0:(length(x_i) - 1)
  return(x_i_adjusted)
}
```

```{r calc-mms}
mms_org <- preds_all %>% 
  group_by(feature_level = feat_org, .draw) %>% 
  summarize(avg = mean(.epred)) %>% 
  ungroup()

mms_issue <- preds_all %>% 
  group_by(feature_level = feat_issue, .draw) %>% 
  summarize(avg = mean(.epred)) %>% 
  ungroup()

mms_transp <- preds_all %>% 
  group_by(feature_level = feat_transp, .draw) %>% 
  summarize(avg = mean(.epred)) %>% 
  ungroup()

mms_acc <- preds_all %>% 
  group_by(feature_level = feat_acc, .draw) %>% 
  summarize(avg = mean(.epred)) %>% 
  ungroup()

mms_funding <- preds_all %>% 
  group_by(feature_level = feat_funding, .draw) %>% 
  summarize(avg = mean(.epred)) %>% 
  ungroup()

mms_govt <- preds_all %>% 
  group_by(feature_level = feat_govt, .draw) %>% 
  summarize(avg = mean(.epred)) %>% 
  ungroup()

mms_all <- bind_rows(
  lst(mms_org, mms_issue, mms_transp, mms_acc, mms_funding, mms_govt),
  .id = "mm_var"
) %>%
  left_join(select(feature_lookup, mm_var, feature_nice_paper), by = join_by(mm_var))

mms_all_medians <- mms_all %>% 
  group_by(feature_nice_paper, feature_level) %>% 
  summarize(
    median_qi(avg),
    p_gt_25 = sum(avg > 0.25) / n()
  ) %>% 
  mutate(p_neq_25 = ifelse(y >= 0.25, p_gt_25, 1 - p_gt_25))
```

```{r calc-amces}
amces_org <- mms_org %>% 
  group_by(feature_level) %>% 
  compare_levels(variable = avg, by = feature_level, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feature_level,
    delim = " - ", 
    names = c("feature_level", "reference_level")
  ) %>% 
  add_row(avg = 0, feature_level = unique(.$reference_level))

amces_issue <- mms_issue %>% 
  group_by(feature_level) %>% 
  compare_levels(variable = avg, by = feature_level, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feature_level,
    delim = " - ", 
    names = c("feature_level", "reference_level")
  ) %>% 
  add_row(avg = 0, feature_level = unique(.$reference_level))

amces_transp <- mms_transp %>% 
  group_by(feature_level) %>% 
  compare_levels(variable = avg, by = feature_level, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feature_level,
    delim = " - ", 
    names = c("feature_level", "reference_level")
  ) %>% 
  add_row(avg = 0, feature_level = unique(.$reference_level))

amces_acc <- mms_acc %>% 
  group_by(feature_level) %>% 
  compare_levels(variable = avg, by = feature_level, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feature_level,
    delim = " - ", 
    names = c("feature_level", "reference_level")
  ) %>% 
  add_row(avg = 0, feature_level = unique(.$reference_level))

amces_funding <- mms_funding %>% 
  group_by(feature_level) %>% 
  compare_levels(variable = avg, by = feature_level, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feature_level,
    delim = " - ", 
    names = c("feature_level", "reference_level")
  ) %>% 
  add_row(avg = 0, feature_level = unique(.$reference_level))

amces_govt <- mms_govt %>% 
  group_by(feature_level) %>% 
  compare_levels(variable = avg, by = feature_level, comparison = "control") %>% 
  ungroup() %>% 
    separate_wider_delim(
    feature_level,
    delim = " - ", 
    names = c("feature_level", "reference_level")
  ) %>% 
  add_row(avg = 0, feature_level = unique(.$reference_level))

amces_all <- bind_rows(
  lst(amces_org, amces_issue, amces_transp, amces_acc, amces_funding, amces_govt),
  .id = "amce_var"
) %>%
  left_join(select(feature_lookup, amce_var, feature_nice_paper), by = join_by(amce_var)) %>%
  left_join(
    select(level_lookup, contains("_level")), 
    by = join_by(feature_level)
  )

amces_all_medians <- amces_all %>% 
  group_by(feature_nice_paper, feature_level) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>% 
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0))
```

\clearpage

# Additional tables

::: {#apptbl-sample-details-demographics}

```{r}
#| label: apptable-sample-details-demographics
#| include: true
tbl_participant_summary <- participant_summary %>% 
  select(
    category, 
    Question = clean_name,
    Response = level,
    N = count,
    `%` = nice_prop
  ) %>% 
  split(~category)

inner <- glue("
rowsep=0pt, row{<<header_rows>>}={abovesep=3pt, belowsep=0pt},
cells={font=\\footnotesize}
",
  header_rows = paste0(get_row_group_index(tbl_participant_summary$Demographics$Question) + 2, collapse = ","),
  .open = "<<", .close = ">>"
)

tbl_participant_summary$Demographics %>% 
  select(-category, -Question) %>% 
  tt(width = c(0.6, 0.15, 0.15)) %>%
  group_tt(j = list("Demographics" = 1:3)) %>%
  group_tt(
    i = tbl_participant_summary$Demographics$Question, 
    indent = 1
  ) %>%
  style_tt(i = -1, align = "c", bold = TRUE) %>%
  style_tt(j = 1, align = "l") %>%
  style_tt(j = 2:3, align = "c") %>%
  style_tt(
    i = get_row_group_index(tbl_participant_summary$Demographics$Question),
    line = "b", line_width = 0.05, align = "l", bold = TRUE
  ) %>%
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = inner
  ) %>%
  format_tt(escape = TRUE)
```

Demographics

:::

\newpage

::: {#apptbl-sample-details-charity}

```{r}
#| label: table-sample-details-charity
#| include: true

inner <- glue("
rowsep=0pt, row{<<header_rows>>}={abovesep=3pt, belowsep=0pt},
cells={font=\\footnotesize}
",
  header_rows = paste0(get_row_group_index(tbl_participant_summary$`Attitudes toward charity`$Question) + 2, collapse = ","),
  .open = "<<", .close = ">>"
)

tbl_participant_summary$`Attitudes toward charity` %>% 
  select(-category, -Question) %>% 
  tt(width = c(0.6, 0.15, 0.15)) %>%
  group_tt(j = list("Attitudes toward charity" = 1:3)) %>%
  group_tt(
    i = tbl_participant_summary$`Attitudes toward charity`$Question, 
    indent = 1
  ) %>%
  style_tt(i = -1, align = "c", bold = TRUE) %>%
  style_tt(j = 1, align = "l") %>%
  style_tt(j = 2:3, align = "c") %>%
  style_tt(
    i = get_row_group_index(tbl_participant_summary$`Attitudes toward charity`$Question),
    line = "b", line_width = 0.05, align = "l", bold = TRUE
  ) %>%
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = inner
  ) %>%
  format_tt(escape = TRUE)
```

Attitudes toward charity

:::

::: {#apptbl-sample-details-politics}

```{r}
#| label: table-sample-details-politics
#| include: true

inner <- glue("
rowsep=0pt, row{<<header_rows>>}={abovesep=3pt, belowsep=0pt},
cells={font=\\footnotesize}
",
  header_rows = paste0(get_row_group_index(tbl_participant_summary$`Politics, ideology, and religion`$Question) + 2, collapse = ","),
  .open = "<<", .close = ">>"
)

tbl_participant_summary$`Politics, ideology, and religion` %>% 
  select(-category, -Question) %>% 
  tt(width = c(0.6, 0.15, 0.15)) %>%
  group_tt(j = list("Politics, ideology, and religion" = 1:3)) %>%
  group_tt(
    i = tbl_participant_summary$`Politics, ideology, and religion`$Question, 
    indent = 1
  ) %>%
  style_tt(i = -1, align = "c", bold = TRUE) %>%
  style_tt(j = 1, align = "l") %>%
  style_tt(j = 2:3, align = "c") %>%
  style_tt(
    i = get_row_group_index(tbl_participant_summary$`Politics, ideology, and religion`$Question),
    line = "b", line_width = 0.05, align = "l", bold = TRUE
  ) %>%
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = inner
  ) %>%
  format_tt(escape = TRUE)
```

Politics, ideology, and religion

:::

\newpage

::: {#apptbl-all-results}

\scriptsize

```{r}
#| label: table-all-results
#| include: true
mms_all_tbl <- mms_all %>% 
  drop_na(feature_level) %>% 
  group_by(feature_nice_paper, feature_level = fct_rev(feature_level)) %>% 
  median_qi(avg) %>% 
  mutate(nice = glue("{fmt_decimal(avg)}\n{build_ci(.lower, .upper)}")) %>% 
  select(feature_nice_paper, feature_level, mm_nice = nice)

amces_all_tbl <- amces_all %>% 
  mutate(feature_level = factor(feature_level, levels = levels(mms_all$feature_level))) %>% 
  mutate(contrast = glue("{feature_level}−{reference_level}")) %>% 
  group_by(feature_nice_paper, feature_level = fct_rev(feature_level), contrast) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>% 
  ungroup() %>% 
  mutate(is_reference = str_detect(contrast, "−NA")) %>% 
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0)) %>% 
  mutate(contrast = ifelse(is_reference, "*(Reference)*", contrast)) %>% 
  mutate(nice = ifelse(is_reference, NA, glue("{fmt_decimal(y)}\n{build_ci(ymin, ymax)}"))) %>% 
  mutate(pd = ifelse(is_reference, NA, fmt_decimal2(p_neq_0))) %>% 
  select(feature_nice_paper, feature_level, contrast, amce_nice = nice, pd)

all_tbl <- left_join(
  mms_all_tbl, amces_all_tbl, 
  by = join_by(feature_nice_paper, feature_level)
) %>% 
  mutate(across(c(feature_level, contrast), ~{
    .x %>% 
      str_replace_all("Transparency: ", "") %>% 
      str_replace_all("Accountability: ", "")
  }))

inner <- glue("
rowsep=1.5pt, row{<<header_rows>>}={abovesep=6pt, belowsep=0pt},
cells={font=\\scriptsize}, row{1}={valign=b}
",
  header_rows = paste0(get_row_group_index(all_tbl$feature_nice_paper) + 1, collapse = ","),
  .open = "<<", .close = ">>"
)

notes <- list(
  `*` = list(i = 0, j = c(2, 4), text = tt_md("Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.")),
  `†` = list(i = 0, j = 5, text = tt_md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."))
)

all_tbl %>% 
  select(-feature_nice_paper) %>%
  mutate(across(c(mm_nice, amce_nice), ~tt_linebreak(.))) %>%
  setNames(
    c("Feature", "Posterior EMM", "Contrast", "Posterior AMCE", tt_md("*p*~direction~"))
  ) %>%
  tt(width = c(0.18, 0.18, 0.40, 0.18, 0.06), notes = notes) %>%
  group_tt(
    i = as.character(all_tbl$feature_nice_paper), 
    indent = 0
  ) %>%
  format_tt(replace = "—") %>%
  format_tt(j = 3, markdown = TRUE, replace = "—") %>%
  format_tt(j = c(2, 4, 5), escape = FALSE, replace = "—") %>%
  style_tt(j = c(1, 3), align = "l") %>%
  style_tt(j = c(2, 4, 5), align = "c") %>%
  style_tt(
    i = get_row_group_index(all_tbl$feature_nice_paper),
    line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
  ) %>%
  style_tt(
    i = tail(get_row_group_index(all_tbl$feature_nice_paper), -1),
    line = "t", line_width = 0.05, line_color = "#d3d8dc",
  ) %>%
  style_tt(j = 2, line = "r", line_width = 0.1, line_color = "#d3d8dc") %>%
  style_tt(
    bootstrap_class = "table",
    tabularray_inner = inner
  )
```

Complete results

:::

\newpage

::: {#apptbl-mms-trans-acc}

```{r}
#| label: table-mms-trans-acc
#| include: true

mms_transp_acc <- preds_all %>% 
  group_by(feat_transp, feat_acc, .draw) %>% 
  summarize(avg = mean(.epred)) %>% 
  ungroup()

mms_trans_acc_all <- mms_transp_acc %>% 
  filter(
    (feat_transp == "Transparency: Yes" & feat_acc == "Accountability: Yes") | 
      (feat_transp == "Transparency: No" & feat_acc == "Accountability: No")) %>% 
  bind_rows(
    mms_transp %>% 
      filter(feature_level == "Transparency: Yes") %>% 
      rename(feat_transp = feature_level) %>% 
      mutate(feat_acc = "Accountability: No"),
    mms_acc %>% 
      filter(feature_level == "Accountability: Yes") %>% 
      rename(feat_acc = feature_level) %>% 
      mutate(feat_transp = "Transparency: No")
  )

mms_trans_acc_all_tbl <- mms_trans_acc_all %>% 
  group_by(feat_transp, feat_acc) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}\n{build_ci(.lower, .upper)}")) %>% 
  mutate(across(c(nice), ~tt_linebreak(.)))

inner <- glue("
rowsep=1pt, row{<<header_rows>>}={abovesep=6pt, belowsep=0pt},
cells={font=\\footnotesize}, row{1}={valign=b}
",
  header_rows = paste0(get_row_group_index(mms_trans_acc_all_tbl$feat_transp) + 1, collapse = ","),
  .open = "<<", .close = ">>"
)

notes <- list(
  `*` = list(i = 0, j = 2, text = tt_md("Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets."))
)

mms_trans_acc_all_tbl %>%
  select(Features = feat_acc, `Posterior EMM` = nice) %>% 
  tt(width = c(0.25, 0.2), notes = notes) %>%
  group_tt(
    i = as.character(mms_trans_acc_all_tbl$feat_transp), 
    indent = 0
  ) %>%
  style_tt(
    i = get_row_group_index(mms_trans_acc_all_tbl$feat_transp),
    line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
  ) %>%
  style_tt(j = 1, align = "l") %>%
  style_tt(j = 2, align = "c") %>%
  style_tt(
    bootstrap_class = "table",
    tabularray_inner = inner
  )
```

Marginal means for all combinations of transparency and accountability

:::

\newpage

::: {#apptbl-transp-crackdown}

```{r}
#| label: table-transp-crackdown
#| include: true

mms_transp_crackdown <- preds_all %>% 
  group_by(feat_transp_short, feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

mms_transp_crackdown_tbl <- mms_transp_crackdown %>% 
  group_by(feat_transp_short, feat_govt) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}\n{build_ci(.lower, .upper)}")) %>% 
  ungroup() %>% 
  arrange(desc(feat_govt), desc(feat_transp_short)) %>% 
  select(feat_transp_short, feat_govt, nice)

amces_transp_crackdown <- mms_transp_crackdown %>% 
  group_by(feat_govt) %>% 
  compare_levels(variable = avg, by = feat_transp_short, comparison = "control")

amces_transp_crackdown_medians <- amces_transp_crackdown %>% 
  group_by(feat_govt, feat_transp_short) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>% 
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0))

amces_transp_crackdown_tbl <- amces_transp_crackdown_medians %>% 
  ungroup() %>% 
  mutate(nice = glue("{fmt_decimal(y)}\n{build_ci(ymin, ymax)}")) %>% 
  mutate(feat_transp_short = str_replace(feat_transp_short, " - ", "−")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal2(.))) %>% 
  arrange(desc(feat_govt)) %>% 
  select(contrast = feat_transp_short, diff_nice = nice, p_neq_0)

mms_acc_crackdown <- preds_all %>% 
  group_by(feat_acc_short, feat_govt, .draw) %>% 
  summarize(avg = mean(.epred))

mms_acc_crackdown_tbl <- mms_acc_crackdown %>% 
  group_by(feat_acc_short, feat_govt) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}\n{build_ci(.lower, .upper)}")) %>% 
  ungroup() %>% 
  arrange(desc(feat_govt), desc(feat_acc_short)) %>% 
  select(feat_acc_short, feat_govt, nice)

amces_acc_crackdown_medians <- mms_acc_crackdown %>% 
  group_by(feat_govt) %>% 
  compare_levels(variable = avg, by = feat_acc_short, comparison = "control") %>% 
  group_by(feat_govt, feat_acc_short) %>% 
  summarize(
    median_qi(avg),
    p_gt_0 = sum(avg > 0) / n()
  ) %>% 
  mutate(p_neq_0 = ifelse(y >= 0, p_gt_0, 1 - p_gt_0))

amces_acc_crackdown_tbl <- amces_acc_crackdown_medians %>% 
  ungroup() %>% 
  mutate(nice = glue("{fmt_decimal(y)}\n{build_ci(ymin, ymax)}")) %>% 
  mutate(feat_acc_short = str_replace(feat_acc_short, " - ", "−")) %>% 
  mutate(across(starts_with("p_"), ~fmt_decimal2(.))) %>% 
  arrange(desc(feat_govt)) %>% 
  select(contrast = feat_acc_short, diff_nice = nice, p_neq_0)

trans_acc_crackdown_tbl <- bind_rows(
  bind_cols(
    mms_transp_crackdown_tbl, 
    amces_transp_crackdown_tbl %>% 
      add_row(contrast = NA, .after = 1) %>% 
      add_row(contrast = NA, .after = 3) %>% 
      add_row(contrast = NA, .after = 5)
  ) %>% 
    mutate(feat_level = paste("Transparency:", feat_transp_short)) %>% 
    select(-feat_transp_short),
  bind_cols(
    mms_acc_crackdown_tbl, 
    amces_acc_crackdown_tbl %>% 
      add_row(contrast = NA, .after = 1) %>% 
      add_row(contrast = NA, .after = 3) %>% 
      add_row(contrast = NA, .after = 5)
  ) %>% 
    mutate(feat_level = paste("Accountability:", feat_acc_short)) %>% 
    select(-feat_acc_short)
) %>%
  mutate(contrast = ifelse(is.na(contrast), "*(Reference)*", contrast)) %>% 
  mutate(across(c(nice, diff_nice), ~tt_linebreak(.))) %>% 
  relocate(feat_level) %>%
  mutate(feat_govt = fct_relabel(feat_govt, ~paste("Relationship with government:", .x))) %>% 
  arrange(desc(feat_govt))

inner <- glue("
rowsep=1.5pt, row{<<header_rows>>}={abovesep=6pt, belowsep=0pt},
cells={font=\\footnotesize}, row{1}={valign=b}
",
  header_rows = paste0(get_row_group_index(trans_acc_crackdown_tbl$feat_govt) + 1, collapse = ","),
  .open = "<<", .close = ">>"
)

notes <- list(
  `*` = list(i = 0, j = c(2, 4), text = tt_md("Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.")),
  `†` = list(i = 0, j = 5, text = tt_md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."))
)

trans_acc_crackdown_tbl %>%
  select(-feat_govt) %>%
  mutate(across(c(nice, diff_nice), ~tt_linebreak(.))) %>%
  setNames(
    c("Feature", "Posterior EMM", "Contrast", "Posterior ∆", tt_md("*p*~direction~"))
  ) %>%
  tt(width = c(0.30, 0.18, 0.25, 0.18, 0.06), notes = notes) %>%
  group_tt(
    i = as.character(trans_acc_crackdown_tbl$feat_govt), 
    indent = 0
  ) %>%
  format_tt(replace = "—") %>%
  format_tt(j = 3, markdown = TRUE) %>%
  format_tt(j = c(2, 4, 5), escape = FALSE, replace = "—") %>%
  style_tt(j = c(1, 3), align = "l") %>%
  style_tt(j = c(2, 4, 5), align = "c") %>%
  style_tt(
    i = get_row_group_index(trans_acc_crackdown_tbl$feat_govt),
    line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
  ) %>%
  style_tt(
    i = tail(get_row_group_index(trans_acc_crackdown_tbl$feat_govt), -1),
    line = "t", line_width = 0.05, line_color = "#d3d8dc",
  ) %>%
  style_tt(j = 2, line = "r", line_width = 0.1, line_color = "#d3d8dc") %>%
  style_tt(
    bootstrap_class = "table",
    tabularray_inner = inner
  )
```

Marginal means and AMCEs for interaction between transparency, accountability, and government relationships

:::

\newpage

::: {#apptbl-coefs-orig}

```{r}
#| label: table-coefs-orig
#| include: true
notes <- c(
  "Estimates are median posterior log odds from a multinomial logistic regression model with three possible categories, and the columns for µ1, µ2, and µ3 represent estimates for each of the outcomes;",
  "95% credible intervals (equal-tailed quantile intervals) in brackets."
)

inner <- "
rowsep=0pt,
row{odd[2-27]}={abovesep=0pt},
row{even[4-28]}={belowsep=6pt},
cells={font=\\footnotesize}, row{1}={valign=b}
"

modelsummary(
  list("Posterior medians" = model_summary_table),
  shape = Feature + term ~ group,
  estimate = "estimate",
  statistic = "[{conf.low}, {conf.high}]",
  output = "tinytable",
  fmt = fmt_significant(2),
  notes = tt_md(paste(notes, collapse = " "))
) %>%
  style_tt(
    bootstrap_class = "table",
    tabularray_inner = inner
  )
```

Original model coefficients

:::

\clearpage

::: {.content-visible when-meta="appendix-single-spacing"}
\singlespacing
:::

# Preregistration deviations

We made the following deviations from our preregistered protocol [@WillrothAtherton:2024]:

1. Type

   :   Analysis

   Reason

   :   New knowledge

   Timing

   :   After results known

   Original wording

   :   "We will examine the aggregate marginal posterior distributions of the attribute levels"

   Deviation description

   :   This statement was vague and seemed to imply that we would analyze the results of the model by looking only at the raw model coefficients. While is is possible to calculate exact feature contrasts by summing specific combinations of coefficients, we instead calculated estimated marginal means and their contrasts (or AMCEs) using the fitted model.

   Reader impact

   :   This deviation should improve readers' interpretation of the findings, since the reported results are no longer on a log-odds or logit scale, and instead are on a more interpretable percentage point scale—estimated marginal means show the percent of respondents who support an NGO given a specific features, while AMCEs show the percentage point change in support when moving from one feature to another. The risk of bias is minimal as the underlying results are identical whether reported as logit-scale coefficients or marginal means.

2. Type

   :   Hypotheses

   Reason

   :   Stylistic

   Timing

   :   After results known

   Original wording

   :   Q5a: "Donors will show increased willingness to donate to NGOs that are financially transparent"

   Deviation description

   :   We rephrased this as H~1a~: "If NGOs are financially transparent, then individual private donors will have a higher likelihood of supporting or donating to them."

   Reader impact

   :   This deviation has minimal impact on readers' interpretation of the findings—it is only rephrased to follow an "if… then…" formulation.

3. Type

   :   Hypotheses

   Reason

   :   New knowledge + stylistic

   Timing

   :   Direction restated after data collection, but before results were known; "if… then…" formulation added after results known

   Original wording

   :   Q5f: "Donors should be no more or less likely to donate to NGOs that are accountable and hold regular third party audits"

   Deviation description

   :   We rephrased this as H~1b~: "If NGOs are accountable and hold regular third-party audits, then individual private donors will have a higher likelihood of supporting or donating to them."

   Reader impact

   :   This deviation might have some impact on readers' interpretation of the findings. This deviation was the result of misunderstanding existing work on the effect of nonprofit accountability on donor behavior, and we hypothesized that there would be no effect, contrary to what is predicted by previous research. The risk of bias is low, however—we reversed our prediction after data collection but before we analyzed the data and before the results were known.

4. Type

   :   Hypotheses

   Reason

   :   Stylistic

   Timing

   :   After results known

   Original wording

   :   Q2a: "Donors will show increased willingness to donate to NGOs that are facing government crackdown or criticism"

   Deviation description

   :   We rephrased this as H~2~: "If NGOs face legal crackdowns abroad, then individual private donors will have a higher likelihood of supporting or donating to them."

   Reader impact

   :   This deviation has minimal impact on readers' interpretation of the findings—it is only rephrased to follow an "if… then…" formulation.

5. Type

   :   Hypotheses

   Reason

   :   New knowledge

   Timing

   :   Accountability prediction added after data collection, but before results were known; "if… then…" formulation added after results known

   Original wording

   :   Q5b: "Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent"

   Deviation description

   :   We explore the interaction between (1) government crackdown and financial transparency and (2) government crackdown and accountability in the paper, but we only specified the first interaction in the preregistration.

   Reader impact

   :   This deviation might have some impact on readers' interpretation of the findings. The omission of a prediction of the relationship between government crackdown and accountability was inadvertent and we had intended to specify it. The risk of bias is low, as we added the new crackdown+accountability hypothesis after data collection and before the results were known.

6. Type

   :   Hypotheses

   Reason

   :   Narrative

   Timing

   :   After data collection, before results were known

   Original wording

   :   Q1: Branding; Q3: Issue area; Q4: Funding sources

   Deviation description

   :   For the sake of narrative simplicity, we do not explicitly test these three predictions as hypotheses. In this paper, our primary interest is crackdown, transparency, and accountability, but we look at branding, issue area, and funding sources to help compare and give context to the magnitude of our main hypotheses.

   Reader impact

   :   This deviation might have some impact on readers' interpretation of the findings, as it might appear that we have selectively reported a handful of our predictions. To avoid this, and for the sake of full transparency, we include these results in @fig-all-results and @apptbl-all-results. The risk of bias is low—we decided on the narrative framing for this paper after collecting the data but before analyzing the results.

\newpage

# Condensed preregistration

::: {.callout-important icon=false}
### Consensed preregistration

This is an anonymized and condensed version of our full OSF preregistration protocol.
:::

{{< include text/preregistration.md >}}

\newpage

# References

### 2025-01-12 manuscript/manuscript.qmd
Hardcode appendix cross references bc it's a separate document now

@@
 short-title: "Why Donors Donate"
-date: "2024-03-28"
+date: "2025-01-11"
 author:
@@
 word-count: "9,300"
-
-crossref:
-  custom:
-    - kind: float
-      key: apptbl
-      latex-env: apptbl
-      reference-prefix: Table A
-      space-before-numbering: false
-      latex-list-of-description: Appendix Table
-apptbl-cap-location: top
 ---
@@
 library(tinytable)
-library(modelsummary)
 library(here)
@@
 
-tar_load(c(
-  grid_treatment_only, level_lookup, feature_lookup,
-  participant_summary, model_summary_table
-))
+tar_load(c(grid_treatment_only, level_lookup, feature_lookup))
 
@@
 Following screening, we received 1,016 viable responses.
-@apptbl-sample-details-demographics, @apptbl-sample-details-charity, and @apptbl-sample-details-politics provide a detailed breakdown of the individual characteristics of our sample.
+Tables A1, A2, and A3 provide a detailed breakdown of the individual characteristics of our sample.
 In general, respondents were well balanced across all pre-treatment characteristics, including gender, age, education, income, and attitudes toward charity.
@@
 Because this is an experimental design, any statistical confounding is accounted for during the process of randomization and covariates should have no systematic effect on treatment effects.
-We do not work with the raw results of the model directly (though a complete table of results is included in @apptbl-coefs-orig).
+We do not work with the raw results of the model directly (though a complete table of results is included in Table A4).
 Given the conjoint design, we instead create a complete balanced grid of all 576 combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding) and use the model to calculate predicted probabilities of choice selection for each row of possible treatment values.
@@
 We report the causal effect of each manipulated feature using the average marginal component effect (AMCE), which is equivalent to the difference in estimated marginal means for specific feature levels.
-For example, when estimating the marginal means of the transparency treatment, we find the average predicted probability across the 288 rows of the reference grid where transparency is true and across the 288 rows where transparency is false---the difference between these two estimated marginal means is the AMCE, or the causal effect of the treatment holding all other values constant, on the probability scale (see the appendix for an extended illustration and demonstration of the EMM and AMCE calculating process).
+For example, when estimating the marginal means of the transparency treatment, we find the average predicted probability across the 288 rows of the reference grid where transparency is true and across the 288 rows where transparency is false---the difference between these two estimated marginal means is the AMCE, or the causal effect of the treatment holding all other values constant, on the probability scale.
 
@@
 
-We present the posterior distributions of the marginal means and AMCEs for each of our experimental conditions in @fig-all-results and provide posterior medians, credible intervals, and other model diagnostics in @apptbl-all-results and @apptbl-coefs-orig.
+We present the posterior distributions of the marginal means and AMCEs for each of our experimental conditions in @fig-all-results and provide posterior medians, credible intervals, and other model diagnostics in Table A4 and Table A7.
 Because AMCEs are relative statements (i.e.
@@
 There is also some evidence that these two effects are equivalent and perhaps interchangeable.
-@fig-transp-acc (and @apptbl-mms-trans-acc) shows the posterior marginal means for all four combinations of possible levels of transparency and accountability.
+@fig-transp-acc (and Table A5) shows the posterior marginal means for all four combinations of possible levels of transparency and accountability.
 When respondents see both as "no" simultaneously, the estimated marginal mean is lower than any of the individual treatments in @fig-all-results, at `r mms_ta$transparency_no_accountability_no$pct` (`r mms_ta$transparency_no_accountability_no$nice_ci`), or 9 percentage points lower than the baseline probability of 25%.
@@
 Financial transparency and accountability practices both have a positive (and likely interchangeable) effect on NGO favorability, while government criticism and crackdown have a negative effect and discourage potential donors from donating.
-As seen in @fig-transp-crackdown (and @apptbl-transp-crackdown), these heuristics also interact with each other.[^transp-only] The estimated posterior marginal means for different relationships with host governments move in the same direction regardless of whether an organization engages in transparency practices: organizations with no conflict are most preferred, while organizations under government crackdown are least preferred.
+As seen in @fig-transp-crackdown (and Table A6), these heuristics also interact with each other.[^transp-only] The estimated posterior marginal means for different relationships with host governments move in the same direction regardless of whether an organization engages in transparency practices: organizations with no conflict are most preferred, while organizations under government crackdown are least preferred.
 Transparency practices in the presence of crackdown seem to have two general effects.
@@
 On its own, as seen in @fig-all-results, engaging in transparency causes a `r amce$transparency_yes$pp_abs` percentage point increase in the probability of a respondent selecting an organization.
-The right panel of @fig-transp-crackdown (and @apptbl-transp-crackdown) shows how the causal effect of transparency changes across different types of government relationships.
+The right panel of @fig-transp-crackdown (and Table A6) shows how the causal effect of transparency changes across different types of government relationships.
 These AMCEs represent the difference in the estimated posterior marginal means of the two levels of transparency in the left panel.
@@
 Given the near interchangeability of the two treatments, the interaction between accountability and crackdown is nearly identical.
-We include both transparency and accountability in @apptbl-transp-crackdown.
+We include both transparency and accountability in Table A6.
 

### 2025-01-13 manuscript/appendix.qmd
Hardcode appendix cross references bc it's a separate document now
Turn off line colors for now
They break in LaTeX: https://github.com/vincentarelbundock/tinytable/issues/415

@@
     i = get_row_group_index(all_tbl$feature_nice_paper),
-    line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
+    # line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
+    line = "b", line_width = 0.05, align = "l", bold = TRUE
   ) %>%
@@
     i = tail(get_row_group_index(all_tbl$feature_nice_paper), -1),
-    line = "t", line_width = 0.05, line_color = "#d3d8dc",
+    # line = "t", line_width = 0.05, line_color = "#d3d8dc",
+    line = "t", line_width = 0.05
   ) %>%
-  style_tt(j = 2, line = "r", line_width = 0.1, line_color = "#d3d8dc") %>%
+  # style_tt(j = 2, line = "r", line_width = 0.1, line_color = "#d3d8dc") %>%
+  style_tt(j = 2, line = "r", line_width = 0.1) %>%
   style_tt(
@@
     i = get_row_group_index(mms_trans_acc_all_tbl$feat_transp),
-    line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
+    # line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
+    line = "b", line_width = 0.05, align = "l", bold = TRUE
   ) %>%
@@
     i = get_row_group_index(trans_acc_crackdown_tbl$feat_govt),
-    line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
+    # line = "b", line_width = 0.05, line_color = "#d3d8dc", align = "l", bold = TRUE,
+    line = "b", line_width = 0.05, align = "l", bold = TRUE
   ) %>%
@@
     i = tail(get_row_group_index(trans_acc_crackdown_tbl$feat_govt), -1),
-    line = "t", line_width = 0.05, line_color = "#d3d8dc",
+    # line = "t", line_width = 0.05, line_color = "#d3d8dc"
+    line = "t", line_width = 0.05
   ) %>%
-  style_tt(j = 2, line = "r", line_width = 0.1, line_color = "#d3d8dc") %>%
+  # style_tt(j = 2, line = "r", line_width = 0.1, line_color = "#d3d8dc") %>%
+  style_tt(j = 2, line = "r", line_width = 0.1) %>%
   style_tt(
@@
    :   This deviation might have some impact on readers' interpretation of the findings, as it might appear that we have selectively reported a handful of our predictions.
-To avoid this, and for the sake of full transparency, we include these results in @fig-all-results and @apptbl-all-results.
+To avoid this, and for the sake of full transparency, we include these results in Figure 1 in the paper and @apptbl-all-results.
 The risk of bias is low—we decided on the narrative framing for this paper after collecting the data but before analyzing the results.

### 2025-01-13 _targets.R
Remove profiles from manuscript targets

@@ -99,8 +99,7 @@ list(
   tar_target(model_summary_table, build_modelsummary(m_treatment_only)),
   
   ## Manuscript and notebook ----
-  tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),
-  tar_quarto(output_ms, path = "manuscript", quiet = FALSE, profile = "ms"),
+  tar_quarto(manuscript, path = "manuscript", quiet = FALSE),
   tar_quarto(website, path = ".", quiet = FALSE),
   tar_target(deploy_script, here_rel("deploy.sh"), format = "file"),
   tar_target(deploy, {

### 2025-01-13 notebook/appendix.qmd
Add appendix page to website

---
title: Appendix
toc: false
page-layout: full
---

```{r include=FALSE}
# Add the manuscript target as a dependency to the overall website
targets::tar_load(manuscript)
```

```{=html}
<p class="text-center">
  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/appendix.html" target="appendix">
  <i class="fa-solid fa-file-lines"></i> &ensp;HTML
  </a>

  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/appendix.html" target="_blank">
  <i class="fa-solid fa-arrow-up-right-from-square"></i>&ensp;HTML <small>(new window)</small>
  </a>

  <a class="btn btn-danger btn-sm mb-1" href="/manuscript/output/appendix.pdf" target="appendix">
  <i class="fa-solid fa-file-pdf"></i>&ensp;PDF
  </a>

  <a class="btn btn-danger btn-sm mb-1" target="_blank" href="/manuscript/output/appendix.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;PDF <small>(download)</small>
  </a>

  <a class="btn btn-warning btn-sm mb-1" href="/manuscript/output/appendix+ms.pdf" target="appendix">
  <i class="fa-solid fa-file-pdf"></i>&ensp;Manuscripty PDF
  </a>

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output/appendix+ms.pdf">
  <i class="fa-solid fa-file-arrow-down"></i>&ensp;Manuscripty PDF <small>(download)</small>
  </a>
</p>

<iframe src="/manuscript/output/appendix.html" frameborder="0" style="overflow:hidden;height:90%;width:100%;border:2px solid #ccc;" height="90%" width="100%" name="appendix"></iframe>
```

### 2025-01-13 notebook/manuscript.qmd
targets-ify manuscript, website, and readme
Add appendix page to website

--- 2023-09-08 notebook/manuscript.qmd
@@
 ---
-title: "Manuscript"
+title: Manuscript
+toc: false
+page-layout: full
 ---
 
-Manuscript iframe stuff goes here.
+```{r include=FALSE}
+# Add the manuscript target as a dependency to the overall website
+targets::tar_load(manuscript)
+```
+
+```{=html}
+<p class="text-center">
+  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/manuscript.html" target="manuscript">
+  <i class="fa-solid fa-file-lines"></i> &ensp;HTML
+  </a>
+
+  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/manuscript.html" target="_blank">
+  <i class="fa-solid fa-arrow-up-right-from-square"></i>&ensp;HTML <small>(new window)</small>
+  </a>
+
+  <a class="btn btn-danger btn-sm mb-1" href="/manuscript/output/manuscript.pdf" target="manuscript">
+  <i class="fa-solid fa-file-pdf"></i>&ensp;PDF
+  </a>
+
+  <a class="btn btn-danger btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript.pdf">
+  <i class="fa-solid fa-file-arrow-down"></i>&ensp;PDF <small>(download)</small>
+  </a>
+
+  <a class="btn btn-warning btn-sm mb-1" href="/manuscript/output/manuscript+ms.pdf" target="manuscript">
+  <i class="fa-solid fa-file-pdf"></i>&ensp;Manuscripty PDF
+  </a>
+
+  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript+ms.pdf">
+  <i class="fa-solid fa-file-arrow-down"></i>&ensp;Manuscripty PDF <small>(download)</small>
+  </a>
+</p>
+
+<iframe src="/manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:90%;width:100%;border:2px solid #ccc;" height="90%" width="100%" name="manuscript"></iframe>
+```

### 2025-01-13 README.qmd
Marc BYU → USU

@@
 [Suparna Chaudhry](http://www.suparnachaudhry.com/) • Lewis & Clark College  
-[Marc Dotson](https://marriottschool.byu.edu/directory/details?id=50683) • Brigham Young University  
+[Marc Dotson](https://occasionaldivergences.com/about) • Utah State University  
 [Andrew Heiss](https://www.andrewheiss.com) • Georgia State University

### 2025-01-18 manuscript/manuscript.qmd
Add Suparna edits

@@
 short-title: "Why Donors Donate"
-date: "2025-01-11"
+date: "2025-01-17"
 author:
@@
 abstract: |
-  Non-governmental organizations (NGOs) are a core component of global governance.
-Over the last two decades, however, many host governments have cracked down on NGOs using a series of laws that adversely affect the availability and use of traditional NGO funding.
-In response to this dramatic shift in the funding landscape, international NGOs have increasingly turned to individual donors to offset the loss funding.
-Prior research on NGO fundraising has examined how financial transparency and organizational accountability influence individual donor behavior.
-How do these elements of private donor decision-making interact with structural-level factors such as worsening host country civic environments when deciding to donate?
-Using a conjoint experiment with likely donors in the US, we find that transparency and accountability can protect against the dampening effect of host government crackdown and criticism of NGOs.
-Our results have important implications for how NGOs can adapt to worsening civic environments.
+  Governments across the world have increasingly used laws to restrict the work of nonprofits, which has led to a reduction in public or official foreign aid directed towards these groups.
+Many international nonprofits, in response, have turned to individual donors to offset the loss of traditional fundings.
+What are individual donors' preferences regarding donating to legally besieged nonprofits abroad?
+We conducted a conjoint experiment on a nationally representative sample of likely donors in the US and found that learning about host government criticism and restrictions on nonprofits decreases individuals' preferences to donate to them.
+However, organizational features such as financial transparency and accountability can protect against this dampening effect.
+Our results have important implications both for understanding private international philanthropy and how nonprofits can better frame their fundraising appeals at a time when they are facing restrictive civic spaces and hostile governments abroad.
 additional-info: |
@@
 
-Non-governmental organizations (NGOs) face stricter regulations from their host governments [@ChristensenWeinstein:2013; @DupuyRonPrakash:2016; @GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020].
-Repressive governments have cracked down on these organizations using both violence, as well as administrative crackdown, which create barriers to funding and advocacy for a variety of NGOs [@DupuyRonPrakash:2016; @Chaudhry:2022; @Heiss:2017].
+Non-governmental organizations (NGOs) are a core component of global governance and service delivery.
+Non-governmental organizations (NGOs) are a core component of global governance and service delivery.
+Over the last two decades, however, NGOs face restrictive civic spaces abroad [@ChristensenWeinstein:2013; @DupuyRonPrakash:2016; @GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020].
+Repressive governments have increasingly used legal measures to create barriers to funding and advocacy for a variety of NGOs [@DupuyRonPrakash:2016; @Chaudhry:2022; @Heiss:2017].
+For instance, in 2012 Russia passed its infamous "Foreign Agent" law (Federal Law No.
+121-F2), which forced organizations receiving foreign funding and engaging in political activities to register as foreign agents, which forced hundreds of organizations to close down [@Kirova:2024].
+These developments were not limited to authoritarian regimes.
+Hybrid and democratic states have also restricted NGOs' operations within their territories.
+Between 2014 and 2019, the Indian government banned 14,500 NGOs from receiving money from abroad, including prominent international groups such as the Ford Foundation and Greenpeace [@PressTrustofIndia:2019].
 Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" [@CarothersBrechenmacher:2014; @Rutzen:2015b].
 Data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in more than 60% of countries---117 in total [@CIVICUSMonitor].
-These attacks---most of which have been implemented through anti-NGO laws---have adversely affected the ability of both domestic and international NGOs to operate and raise funds.
-Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO legislation [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official donors channel fewer funds to contentious issues such as human rights, elections, and advocacy, and instead choose to fund "tame" causes bush as health, education, and development, among others [@ChaudhryHeiss:2018; @Bush:2015; @Herrold:2020; @RightSpringmanWibbels:2022].
+This phenomenon of closing civic space has a large deterrent effect on both advocacy *and* service-delivery NGOs [@SpringmanMaleskyRight:2022].
+
+These restrictions have adversely affected the ability of both domestic and international NGOs to operate and raise funds.
+Official aid funds have decreased substantially in countries that have imposed restrictive anti-NGO laws [@ChaudhryHeiss:2018; @DupuyPrakash:2018] and official donors channel fewer funds to contentious issues such as human rights, elections, and advocacy, and instead choose to fund "tame" causes bush as health, education, and development, among others [@ChaudhryHeiss:2018; @Bush:2015; @Herrold:2020; @RightSpringmanWibbels:2022].
 In response to this dramatic shift in the NGO funding landscape, international NGOs (INGOs) have increasingly turned to individual donors abroad to offset the loss of funding from government and foundation sources [@BanksHulmeEdwards:2015].
 
-The amount of private foreign aid is not insignificant---from 2000--2010, private giving by U.S.
-entities towards international causes doubled in real terms [@DesaiKharas:2018, 505].
+The amount of private foreign aid is not insignificant---from 2000--2010, private giving by US entities towards international causes doubled in real terms [@DesaiKharas:2018, 505].
 In 2018, this amounted to \$22.88 billion in individual donations earmarked specifically for international affairs INGOs [@GivingUSA:2019].
 This turn to private donors opens INGOs up to new dynamics in seeking out funds.
-Many organizations that had previously relied on governments and foundations had optimized their fundraising strategies for those donors.
-But individual donors may behave differently from governments and foundations, so INGOs need to adapt their fundraising strategies to a different set of potential donors.
+Individual donor behavior is unlike official donor behavior [@DesaiKharas:2018].
+They have different preferences---while official donors channel funds to countries with better institutional quality or to reward governmental performance, [@Bermeo:2011; @DietrichWright:2015], individual donors are more inclined to donate to NGOs in countries experiencing a humanitarian crisis [@DesaiKharas:2018].
+As such, individual donors may have separate metrics of effectiveness or impact that can differ from the benchmarks that large donor agencies rely on, and INGOs may need to adapt their fundraising strategies to a different set of potential donors.
 
-Individual donors have different preferences and rely on signals of effectiveness that differ from the benchmarks that large donor agencies rely on.
-While INGOs have control over organizational-level factors such as financial transparency and accountability that motivate donations, the political environment in the host countries INGOs work in---including the global crackdown on civil society that is causing many organizations to seek out private funding in the first place---is a structural factor that INGOs can rarely influence on their own.
+While INGOs have control over organizational-level factors that determine their effectiveness, the political environment in the host countries INGOs work in---including the global restrictions on civil society that is causing many organizations to seek out private funding in the first place---is a structural factor that INGOs can rarely influence on their own.
+How do individual donors in the US feel about donating to legally besieged NGOs abroad?
 How do organizational elements of private donor decision-making interact with broader structural limits on INGO fundraising?
-How do individual donors in the U.S.
-feel about donating to legally besieged NGOs abroad?
-How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country civic environments when deciding to donate?
+While there are many organizational-level factors that can determine an NGO's impact, including such as organizational structure, financial transparency, accountability, leadership, and strategy [@MitchellSchmitzBruno-vanVijfeijken:2020], in this paper, we focus on the two factors that are most visible to donors outside of the organizations and on which information is available publicly---financial transparency and accountability.
 
@@
 In considering this question, we engage with research on the consequences of closing civic space on NGOs and donors [@DupuyPrakash:2018; @RightSpringmanWibbels:2022; @FransenDupuyHinfelaar:2021; @SundstromHenrySperling:2022; @Herrold:2020; @ChaudhryHeiss:2021].
-We argue that both organization characteristics---such as an NGO's issue area, funding sources, and transparency and accountability practices---and external factors like an NGO's host-country political environment act as heuristics that influence foreign private donors' preferences.
+We argue that organization characteristics---such as an NGO's transparency and accountability practices---can serve as important heuristics that influence foreign private donors' preferences even during closing civic space.
 
-We fielded a conjoint experiment to a nationally representative sample of 1,016 adults in the US, which allows us to directly compare the relative impact of host government repression of NGOs and organizational financial transparency and accountability on individual donor preferences.
+We fielded a conjoint experiment to a nationally representative sample of 1,016 adults in the US.
+This experiment allows us to assess individual level giving preferences among likely donors in the US towards NGOs abroad working in a variety of issue areas---human rights, environment, emergency response, and refugee relief.[^not-elite] More importantly, it allows us to directly compare the relative impact of host government restriction of NGOs and organizational financial transparency and accountability on individual donor preferences.
 The result of this experiment shows that both financial transparency and accountability increase individuals' willingness to donate to NGOs.
-Conversely, learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability can protect against this dampening effect.
-These effect sizes are substantial: our key treatment effects have a magnitude of around ten percentage points in the predicted probability of choosing to donate to an NGO.
+Conversely, learning about host government criticism of and restrictions on NGOs decreases the likelihood of donation by itself; however, organizational features such as financial transparency and accountability can protect against this dampening effect.
+
+[^not-elite]: To be clear, we do not examine elite-level giving or philanthropy by wealthy donors in the US.
 
@@
 However, this research has overwhelmingly looked at individual donor behavior and motivation for giving to *domestic* organizations instead of international causes [@BekkersWiepking:2011; @Tremblay-BoirePrakash:2017].
-The geographic scope of an organization's mission matters to donors.
-Giving to local organizations involves fewer recipients and more observable results, while the benefits of donating to organizations working abroad are less visible and more removed from donors [@CasaleBaumann:2015].
-In a survey experiment, @Tremblay-BoirePrakash:2017 confirm this, finding that "donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad" [-@Tremblay-BoirePrakash:2017, 644].
-This difference in donor preferences for international NGO services has been understudied because conventionally, states and foundations have been among the main funders of INGOs.
+Giving to local organizations involves more observable results, while the benefits of donating to organizations working abroad are less visible and more removed from donors [@CasaleBaumann:2015].
+@Tremblay-BoirePrakash:2017 confirm this, finding that "donors are more likely to donate to a charity operating locally than to a charity providing identical service abroad" [-@Tremblay-BoirePrakash:2017, 644].
 
-The third wave of democratization, the collapse of the Soviet Union, and the spread of a "pro-NGO norm" have led to an increased role and visibility for NGOs in recent decades [@Reimann:2006].
-Donor states have channeled substantial resources through humanitarian and development NGOs, often in response to donor fears that recipient states would use aid inefficiently [@Dietrich:2013].
-Institutional donors and private funders perceived NGOs as more efficient, more nimble, less bureaucratic, and more trustworthy than states that face poor governance and weak political institutions [@Chaudhry:2022], and as a result, NGOs have become crucial actors in both development and democratization [@Herrold:2020, 142--43].
+This difference in donor preferences for giving to international NGOs has been understudied because conventionally, states and foundations have been among the main funders of INGOs.
+The third wave of democratization and the collapse of the Soviet Union led donor states to channel substantial resources through NGOs, often in response to donor fears that recipient states would use aid inefficiently [@Dietrich:2013].
+Institutional donors and private foundations perceived NGOs as more efficient, more nimble, less bureaucratic, and more trustworthy than states that face poor governance and weak political institutions.
 
@@
 Many organizations struggle with the conflicting imperatives of being large organizations that can operate efficiently at scale, while maintaining the grassroots contacts and consensus building that contributed to their early successes [@MitchellSchmitzBruno-vanVijfeijken:2020; @Jalali:2008; @Bano:2012; @Rahman:2006].
+In response, many nonprofits sought to establish and enhance their accountability, responsiveness, and legitimacy [@edwardshulme; @GourevitchLake:2012].
+These actions were a result of many organizational-level factors impact nonprofit efficacy, including organizational structure, leadership, strategy, transparency and accountability.
+Organizational and governance structures define how decisions are made and who participates in decision making.
+While some nonprofits follow more democratic governance models---such as expanded membership to Global South countries, devolving more decision-making powers to the regional or country levels, others have a more centralized structure [@Wong:2012; @MitchellSchmitzBruno-vanVijfeijken:2020, 155].
+Leadership can be defined as how leaders "handle the external and internal politics of making their organizations more effective and responsive," and what sort of organizational cultures they create [@MitchellSchmitzBruno-vanVijfeijken:2020, 178].
+Finally, strategy is whether the organization has a long-term strategic plan that emphasizes sustainability, innovation, learning and adaptation [@MitchellSchmitzBruno-vanVijfeijken:2020, 100].
+
+However, organizational structure, leadership, and strategy (among other organizational-level factors) are often not visible to the average individual (non-elite) donor, especially in the context of international NGOs.
+Therefore, in this paper, we focus on the two organizational-level factors that are most visible to the average donor---financial transparency and accountability.
+Assessing an NGO's deservingness and efficiency demands substantial time and resources, which individual donors typically lack [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
+As such, these donors rely on various easily available cues and heuristics when deciding to support an NGO.
+News about financial mismanagement and lack of transparency and accountability may be more easily available to these donors.
 Many nonprofit scandals involve some form of financial wrongdoing [@PrakashGugerty:2010b].
+Notable examples include the Oil-for-Food program, initiated by the United Nations in 1996 to allow Iraq to sell enough oil to pay for food and other necessities for its population, which has been suffering from sanctions imposed on Iraq since the First Gulf War.
+However, in 2004, the widespread financial fraud by the program, limited distribution of food by nonprofits and lack of accountability was widely publicized.
+Numerous other such cases---covered in @GibelmanGelman:2001 and @GibelmanGelman:2004---show how financial mismanagement, embezzlement, fraud, and lack of accountability can decrease public trust in and donations towards these nonprofits.
 Globally, around 5% of revenue is lost annually due to fraud [@ACFE:2021].
 Misappropriation of assets and embezzlement schemes are among the most common forms of financial fraud [@LamotheTer-MkrtchyanRuddle:2023].
-These criticisms and concerns, in turn, have led donors to demand greater NGO responsiveness, especially regarding financial transparency and accountability.
+To save time and present easily accessible information, watch dogs such as Charity Navigator and Better Business Bureau Wise Giving Alliance often rate charities on financial and accountability metrics and present this information in a quick, user-friendly format.
 
-Assessing an NGO's deservingness and efficiency demands substantial time and resources, which individual donors typically lack [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
-As such, these donors rely on various cues and heuristics when deciding to support an NGO.
-Nonprofits fundraising from individuals work to shape donor perceptions through the use of framing [@ChaudhryHeiss:2021].
-We explore two possible categories of heuristic frames: (1) organization-level heuristics, reflected in NGO practices, and (2) structural heuristics, particularly an NGO's relationship with its host country.
+Thus, in this paper, we explore the effects of two possible categories of heuristic frames that can impact individual-level giving: (1) organization-level heuristics, reflected in practices of transparency and accountability, and (2) structural heuristics, particularly an NGO's relationship with its host country.
 We hypothesize that each type plays a role in shaping individual preferences for engaging in philanthropy.
@@
 
-One powerful heuristic for potential donors is organizational efficacy or the belief that an individual's donation will make a real difference [@ChaudhryHeiss:2021].
-This can manifest itself through multiple mechanisms such as the amount an organization spends on overhead costs, whether it makes its finances public, or whether it participates in voluntary accountability practices, such as listing organizational details on websites like GuideStar and Charity Navigator.
-
+We first examine the impact of two organizational practices---financial transparency and accountability---on individual donor preferences.
 Financial transparency, or the "degree of completeness of information provided by [organizations] to the [public] concerning [their] activities," [@VaccaroMadsen:2006, p.
-146] is one tangible heuristic that donors turn to when making decisions decisions.
-NGOs can engage in financial transparency in a variety of ways such as distribution of audited financial statements and third party intermediaries.
+146] is one tangible heuristic that donors turn to when making decisions.
+Transparency can involve proactive sharing of information with stakeholders, participation in data transparency platforms, avoiding financial misconduct, and exhibiting trustworthiness.
+NGOs can engage in financial transparency in a variety of ways such as distribution of audited financial statements and voluntarily sharing information with third party intermediaries.
 Research shows that transparency is associated with greater donations, lower debt, and better governance [@HarrisNeely:2021; @HarrisPetrovitsYetman:2023; @SaxtonKuoHo:2012].
@@
 
-> **H~1a~**: If NGOs are financially transparent, then individual private donors will have a higher likelihood of supporting or donating to them.
-
-Accountability is another factor that can impact donor willingness to donate, and it is necessary for promoting public trust in NGOs.
-While transparency is an organization's willingness to make critical data about the organization public, accountability is the willingness of the organization to explain its action to shareholders [@CharityNavigator:2020].
-It also encompasses how well an organization's mission is aligned with its resources and how it manages resources to optimize performance [@Sloan:2009].
-As NGOs gain more prominence, donors demand more information about their activities and strategies [@Tremblay-BoirePrakash:2015].
-Explaining actions to stakeholders can be important because many NGOs---even well-intentioned ones---can devote excessive resources towards marketing and overheads [@Bowman:2006].
-Private donors, subsequently, tend to avoid NGOs that spend a large share of their revenues for overhead, non-mission-related purposes like administration, management and fundraising.
+Accountability is another factor that can impact donor preferences.
+Accountability is the willingness of the organization to explain its action to shareholders [@CharityNavigator:2020] and build and manage relationships with stakeholders or client populations and donor groups.
+It also encompasses how well an organization's mission is aligned with its resources [@Sloan:2009].
+As NGOs gain more prominence, stakeholders, or "any group or individual who can affect or is affected by the achievement of an organization's objectives," [@MitchellAgleWood:1997, 854] want to be assured that their donations or support or support of an organization will make a real difference.
+More effective accountability can encourage NGOs to become more closely aligned with community practices, provide greater assurances to stakeholders and help expand their support [@Murtaza:2012].
+Problems with accountability usually occur when organizations ignore their stakeholders' preferences and use judgements or actions which may not align with one or more of their constituent groups [@McCambridge:2019].
 The absence of accountability is associated with decreased public trust, worse reputation, and lower perceived quality [@Becker:2018].
@@
 Though individual donors would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead, individuals interested in supporting charities cannot thoroughly vet every aspect of the organization [@Tremblay-BoirePrakash:2017; @ChaudhryHeiss:2021].
-To more easily judge organizational accountability, donors may use ratings by watchdog organizations like Charity Navigator and GuideStar as heuristics to guide their decisions.
-Research shows that initiatives to address accountability gaps by these organizations can substantially increase donations [@Sloan:2009; @GordonKnockNeely:2009; @Tremblay-BoirePrakash:2017].
+To more easily judge financial transparency and accountability, donors may use ratings by watchdog organizations like Charity Navigator and GuideStar as heuristics to guide their decisions.[^cn-multiple] Research shows that initiatives to address information gaps by these organizations can substantially increase donations [@Sloan:2009; @GordonKnockNeely:2009; @Tremblay-BoirePrakash:2017].
 
-> **H~1b~**: If NGOs are accountable and hold regular third-party audits, then individual private donors will have a higher likelihood of supporting or donating to them.
+> **H~1a~**: If NGOs are financially transparent, then individual private donors will have a higher likelihood of supporting or donating to them.
+
+> **H~1b~**: If NGOs are accountable, then individual private donors will have a higher likelihood of supporting or donating to them.
+
+[^cn-multiple]: For instance, Charity Navigator lists multiple different accountability and financial metrics in an easily available user-friendly format on its website: <https://www.charitynavigator.org/about-us/our-methodology/ratings/accountability-finance/>
 
@@
 While NGOs have control over organizational factors such as transparency and accountability and can work to improve these characteristics and public perception of them, NGOs may have little to no control over structural factors that can also influence philanthropy.
-These structural factors include political contexts in NGO host countries, especially their environments for civil society organizations.
+These structural factors include political contexts in NGO host countries, especially a restrictive environment for civil society organizations.
 A global cascade of anti-NGO laws in recent decades has created barriers to entry, funding, and advocacy for civic organizations [@GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022; @Heiss:2017; @DupuyRonPrakash:2016].
+The use of such anti-NGO laws, also referred to as administrative crackdown [@Chaudhry:2022], is different from regulations that simply set standards for appropriate organizational behavior and set penalties for violations [@North:1990].[^violent-crackdown] However, the anti-NGO laws discussed in this paper, such as Russian Foreign Agent law, are not grounded in international legal principles, and do not give nonprofits the freedom of association or the freedom to freely access human and material resources [@Voule:2023; @Robinson:2024].
 As a result, NGOs must spend more time, effort, and resources to ensure their survival---at the expense of pursuing their missions.
 
-Some NGOs have adapted to repressive environments by recreating their organizations and changing their mission to avoid directly confronting the government.
+[^violent-crackdown]: Crackdowns can also be violent.
+However, unlike administrative crackdowns, violent crackdowns are often hard to attribute to governments, since governments often outsource repression.
+Moreover, given the ubiquity of anti-NGO laws in recent decades, we focus on the impact of these legal crackdowns on donor preferences.
+
+Some NGOs have adapted to these legal crackdowns by recreating their organizations and changing their mission to avoid directly confronting the government.
 Analyzing the impact of anti-NGO laws in Bangladesh and Zambia, scholars have found that when faced with government restrictions, NGOs with broad missions restricted their strategies to service work and abandoned their advocacy work.
@@
 Similarly, in Russia, many NGOs working with foreign partners and lobbying the central government no longer consider it an effective strategy [@SundstromHenrySperling:2022].
-Overall, fewer groups may end up focusing on contentious causes, instead focusing on regime-compatible causes.
+Overall, fewer groups may end up focusing on contentious causes, instead focusing on issues that are less likely to invoke the ire of the host government, including in areas such as health and education.
 
-The changes in civic environments impacting NGO activity have also influenced official donor responses.
+The changes in civic environments impacting NGO activity have already influenced official donor responses.
 Scholars have found that while multilateral donors do not reduce aid in response to anti-NGO laws, these laws are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018].
 Further, advocacy-oriented donors---i.e., those that fund democracy and civil society promotion activities---reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022].
+
 However, previous literature has established that individual private donors do not make the same considerations as official donors when deciding to donate [@DesaiKharas:2018; @ChaudhryHeiss:2021].
 Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the grounds [@EasterlyWilliamson:2011].
-Anti-NGO repression and civil society laws may act as a heuristic to individuals donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and crack down on them.
-Therefore, restrictions imposed by host-country governments are likely to boost donors' inclination to donate to affected organizations.
+When a potential recipient NGO faces legal crackdown in its host country, private individual donors can respond by (1) increasing their donations as a sign of support and solidarity, (2) decreasing their donations, punishing the NGO for doing something to run afoul of its host government, or (3) not considering the host country legal environment and making no change in their donation behavior.
+@ChaudhryDotsonHeiss:2021 explore how different combinations of donor characteristics determine which response individuals are likely to take when NGOs face crackdown.
+They find that donors with longer experiences with the nonprofit sector and high levels of social trust---i.e.
+those who frequently volunteer, regularly donate to charity, and trust political institutions---are more likely to maintain their support for international NGOs that face criticism or crackdown abroad.
+Thus, anti-NGO laws may act as a heuristic to individuals donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and seek to restrict their work.
+
+This is especially true for nonprofits that rely more heavily on private funds, rather than government funds.
+Previous research finds that, "individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds." [@ChaudhryHeiss:2021, 496].
+Similar trends can be seen even after nonprofits face restrictive political and civic environments in other specific issue areas.
+For instance, in 2022, after the Supreme Court overturned Roe v.
+Wade, private philanthropy towards abortion funds skyrocketed [@PBSNews:2022]---a significant development as abortion funds rely largely on individual donors [@Cohen:2022].
+Therefore, we expect that anti-NGO restrictions imposed by host-country governments are likely to boost individual donors' inclination to donate to affected organizations.
 
@@
 Moreover, states pass anti-civil society laws in response to broader political trends within their borders, and they regulate NGOs strategically to maximize the benefits and minimize the costs of working with international NGOs [@Heiss:2017].
-States are more likely to restrict NGOs when organizations pose a threat to regime stability or preferences—for instance, when INGO issue areas threaten government policies, or when INGOs receive substantial foreign funding [@DupuyRonPrakash:2015].
+States are more likely to restrict NGOs when organizations pose a threat to regime stability or preferences---for instance, when INGO issue areas threaten government policies, or when INGOs receive substantial foreign funding [@DupuyRonPrakash:2015].
 
-Donors show increased willingness to donate to NGOs facing government crackdown/criticism while being financial transparent and accountable.
+Donors show increased willingness to donate to NGOs facing government restrictions/criticism while being financial transparent and accountable.
 While concerns about NGO mismanagement and lack of financial transparency may signal concerns about an NGO's operations and its ability to abide by the host country's regulatory environment, the presence of such transparency and accountability may instead convince donors that government targeting of NGOs may be ill-intentioned rather than simply a manifestation of financial oversight.
@@
 Therefore, both states and individual donors expand and contract their regulatory environments (for states) and support (for donors) for NGOs in response to the interplay between domestic politics and organizational characteristics.
-The same NGO feature that can increase the likelihood of government crackdown can also simultaneously serve as a donor heuristic and influence perceptions of NGO deservingness.
+The same NGO feature that can increase the likelihood of government restriction can also simultaneously serve as a donor heuristic and influence perceptions of NGO deservingness.
 
@@
 
-[^prereg]: For narrative purposes, we do not explore all our preregistered hypotheses in this study—many of them are nested inside each other (e.g., the effect of branding and issue area and transparency and crackdown simultaneously).
+[^prereg]: For narrative purposes, we do not explore all our preregistered hypotheses in this study---many of them are nested inside each other (e.g., the effect of branding and issue area and transparency and crackdown simultaneously).
 We instead focus here on the simplest, non-nested hypotheses.
@@
 
-At the time of designing the study, Charity Navigator---a large database of U.S.
-nonprofit financial information---categorized international nonprofit activities into four general causes: (1) development, (2) humanitarian relief, (3) international affairs and human rights advocacy, and (4) environment.[^cn] Accordingly, we used four nonprofits that are stereotypical for each cause: the International Committee of the Red Cross (humanitarian relief), Amnesty International (human rights), Oxfam (development), and Greenpeace (environment).
+At the time of designing the study, Charity Navigator---a large database of US nonprofit financial information---categorized international nonprofit activities into four general causes: (1) development, (2) humanitarian relief, (3) international affairs and human rights advocacy, and (4) environment.[^cn] Accordingly, we used four nonprofits that are stereotypical for each cause: the International Committee of the Red Cross (humanitarian relief), Amnesty International (human rights), Oxfam (development), and Greenpeace (environment).
 We also varied several other features, including four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), two organizational practices (financial transparency and third-party accountability audits), three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and three relationships with host governments (friendly, criticized by the government, and under government crackdown).
@@
 
-[^stan]: We use Stan [@Stan-2-26-1 v2.26.1; @cmdstan-2-3-1 v2.3.1] through R [@rproject-4-3-3 v4.3.1] and **brms** [@Burkner:2017 v2.20.5] to estimate the model.
+[^stan]: We use Stan [@Stan-2-26-1 v2.26.1; @cmdstan-2-3-1 v2.3.1] through R [@rproject-4-3-3 v4.3.1] and {brms} [@Burkner:2017 v2.20.5] to estimate the model.
 We simulate 4 MCMC chains with 5,000 draws in each chain, 1,000 of which are used for warmup, resulting in 16,000 (4,000 × 4) draws per model parameter.
@@
 
-## Effect of crackdown
+## Effect of restrictions
 
@@
 Contrary to our expectations, respondents appear to prefer donating to NGOs with friendly host government relationships, with a marginal mean of `r mms$friendly_relationship_with_government$pct` (compared to a baseline of 25%; `r mms$friendly_relationship_with_government$nice_ci`).
-Respondents are less likely to donate when an organization is criticized by its host government, and far less likely when an organization faces crackdown.
-Compared to other treatments, an organization facing crackdown elicits a similar negative preference among potential donors as an organization without transparency or accountability measures.
+Respondents are less likely to donate when an organization is criticized by its host government, and far less likely when an organization faces restrictions.
+Compared to other treatments, an organization facing restrictions elicits a similar negative preference among potential donors as an organization without transparency or accountability measures.
 However, an organization with a friendly relationship with the host government leads potential donors to perceive it as equivalent to engaging in transparency or accountability.
 
-In addition to these overall trends in preferences, we can measure the causal effect of moving from friendly NGO–government relations to a more antagonistic relationship.
+In addition to these overall trends in preferences, we can measure the causal effect of moving from friendly NGO--government relations to a more antagonistic relationship.
 Using friendly relationship as the reference category, facing criticism by the host government causes a `r amce$criticized_by_government$pp_abs` percentage point reduction in the probability of selection (`r amce$criticized_by_government$nice_ci_pd`).
-Participants respond more strongly as the relationship becomes more conflictual and restricted---an NGO facing crackdown sees a `r amce$under_government_crackdown$pp_abs` percentage point reduction (`r amce$under_government_crackdown$nice_ci_pd`) in support.
-We thus find strong evidence against H~2~: if NGOs face crackdown abroad, individual donors are *less* likely to donate to them.
-For context, the causal effect of facing crackdown is the same magnitude as the Red Cross branding effect, but in the opposite direction---donors seem to penalize NGOs facing criticism to the same extent that they reward the Red Cross.
+Participants respond more strongly as the relationship becomes more conflictual and restricted---an NGO facing restrictions on its work sees a `r amce$under_government_crackdown$pp_abs` percentage point reduction (`r amce$under_government_crackdown$nice_ci_pd`) in support.
+We thus find strong evidence against H~2~: if NGOs face restrictions abroad, individual donors are *less* likely to donate to them.
+For context, the causal effect of facing restrictions is the same magnitude as the Red Cross branding effect, but in the opposite direction---donors seem to penalize NGOs facing criticism to the same extent that they reward the Red Cross.
 This result is surprising, but clarifies findings in previous research.
@@
 Transparency and accountability practices, in addition to knowing that other individuals regularly support the organization, all act as heuristics of efficacy.
-An NGO facing criticism or crackdown abroad, on the other hand, may signal that potential donations could be used for legal fees, or signal that the NGO had perhaps done something to deserve the legal limitations it faces.
-Crackdown thus serves as a negative heuristic, signaling that donations might not be used as effectively as donors might hope.
+An NGO facing criticism or restrictions abroad, on the other hand, may signal that potential donations could be used for legal fees, or signal that the NGO had perhaps done something to deserve the legal limitations it faces.
+These restrictions thus serve as a negative heuristic, signaling that donations might not be used as effectively as donors might hope.
 
-## The interaction between transparency, accountability, and crackdown
+## The interaction between transparency, accountability, and restriction
 
-Financial transparency and accountability practices both have a positive (and likely interchangeable) effect on NGO favorability, while government criticism and crackdown have a negative effect and discourage potential donors from donating.
-As seen in @fig-transp-crackdown (and Table A6), these heuristics also interact with each other.[^transp-only] The estimated posterior marginal means for different relationships with host governments move in the same direction regardless of whether an organization engages in transparency practices: organizations with no conflict are most preferred, while organizations under government crackdown are least preferred.
-Transparency practices in the presence of crackdown seem to have two general effects.
-First, engaging in transparency offsets most of the negative effect of facing crackdown.
-The estimated marginal mean for an organization with friendly host government relationships and no transparency is `r mms_tc$no_friendly_relationship_with_government$pct`, which is equivalent to the estimated marginal mean for an organization under government crackdown that does engage in transparency.
-On average, donors are indifferent to both situations---again, a marginal mean of 25% represents the probability of selecting an organization at random---but the presence of transparency shifts NGOs facing crackdown from negatively preferred to indifferent, while the absence of transparency shifts NGOs with friendly relationships from positively preferred to indifferent.
-From a practical perspective, this suggests that NGOs under crackdown can focus on improving specific organizational practices to offset the negative signals that accompany their legal difficulties.
+Financial transparency and accountability practices both have a positive (and likely interchangeable) effect on NGO favorability, while government criticism and restriction have a negative effect and discourage potential donors from donating.
+As seen in @fig-transp-crackdown (and Table A6), these heuristics also interact with each other.[^transp-only] The estimated posterior marginal means for different relationships with host governments move in the same direction regardless of whether an organization engages in transparency practices: organizations with no conflict are most preferred, while organizations facing restrictions are least preferred.
+Transparency practices in the presence of restrictions seem to have two general effects.
+First, engaging in transparency offsets most of the negative effect of facing hostile civic environments.
+The estimated marginal mean for an organization with friendly host government relationships and no transparency is `r mms_tc$no_friendly_relationship_with_government$pct`, which is equivalent to the estimated marginal mean for an organization facing government restrictions that does engage in transparency.
+On average, donors are indifferent to both situations---again, a marginal mean of 25% represents the probability of selecting an organization at random---but the presence of transparency shifts NGOs facing restrictions from negatively preferred to indifferent, while the absence of transparency shifts NGOs with friendly relationships from positively preferred to indifferent.
+From a practical perspective, this suggests that NGOs operating in hostile civic environments can focus on improving specific organizational practices to offset the negative signals that accompany their legal difficulties.
 
@@
 These AMCEs represent the difference in the estimated posterior marginal means of the two levels of transparency in the left panel.
-The effect shrinks as relationships become more negative: under friendly conditions, the median posterior AMCE of transparency is `r amce_tc$friendly_relationship_with_government$pp` percentage points (`r amce_tc$friendly_relationship_with_government$nice_ci_pd`); when an NGO is criticized, the transparency effect is `r amce_tc$criticized_by_government$pp` percentage points (`r amce_tc$criticized_by_government$nice_ci_pd`); when an NGO faces crackdown, the effect drops to `r amce_tc$under_government_crackdown$pp` percentage points (`r amce_tc$under_government_crackdown$nice_ci_pd`).
+The effect shrinks as relationships become more negative: under friendly conditions, the median posterior AMCE of transparency is `r amce_tc$friendly_relationship_with_government$pp` percentage points (`r amce_tc$friendly_relationship_with_government$nice_ci_pd`); when an NGO is criticized, the transparency effect is `r amce_tc$criticized_by_government$pp` percentage points (`r amce_tc$criticized_by_government$nice_ci_pd`); when an NGO faces hostile restrictions, the effect drops to `r amce_tc$under_government_crackdown$pp` percentage points (`r amce_tc$under_government_crackdown$nice_ci_pd`).
 The causal effect remains substantially positive regardless of the relationship---even under the worst conditions, engaging in transparency causes a 9 percentage point boost---suggesting that NGOs facing crackdown can still increase their favorability with donors by signalling their commitment to transparency and accountability.
@@
 
-Over recent years, governments globally have systematically controlled and repressed NGOs using both violent tactics and legal means.
+Over recent years, governments globally have systematically restricted NGOs using legal means.
 This trend of closing civic space has important implications for local and international NGOs as well as donors.
@@
 feel about donating to legally besieged NGOs abroad?
-How do organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country civic environments when deciding to donate?
-Using a conjoint experiment, we demonstrate that organizational and structural characteristics of NGOs serve as cues or heuristics that influence donor preferences.
-Organizational practices like financial transparency and accountability increase willingness to donate to NGOs.
-Learning about host government criticism and crackdown against NGOs decreases the likelihood of donation by itself; however, financial transparency and accountability protect against this dampening effect, increasing the probability of philanthropic donations by nine percentage points under the worst conditions of legal crackdown.
+How does the effect of organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country civic environments in individual donors' preferences to donate?
+Using a conjoint experiment of likely donors in the US, we find that organizational practices like financial transparency and accountability increase individuals' preferences to donate to NGOs.
+Learning about host government criticism and restrictions against NGOs decreases the likelihood of donation by itself; however, financial transparency and accountability protect against this dampening effect, increasing the probability of philanthropic donations by nine percentage points under the worst conditions of legal crackdown.
 Our results highlight the importance of organizational characteristics like transparency and accountability even in an era of closing civic space.
 
-These results have important implications for NGO operations, fundraising, and survivability at a time when many INGOs are dealing with hostile host governments.
-A comparison of the effects of these organizational and structural factors is critical to NGO fundraising---while NGOs have control over transparency and accountability, as well as public perception of these organizational characteristics, they have little to no control over host government crackdowns over their organizations.
+These results have two important practical implications for NGO operations, fundraising, and survivability at a time when many INGOs are dealing with hostile host governments.
+First, while  NGOs have little to no control over host government crackdowns over their organizations, they do have control over organizational practices transparency and accountability, and more importantly, public perception of these organizational characteristics.
 As a result, they may need to rely entirely on improving individual donor perceptions of organizational transparency and accountability and emphasizing the need for private donor funds at a time of shrinking civic space.
 This article thus provides insight into the importance of different framing or informational heuristics that can motivate such individual donor giving.
+In addition to voluntarily emphasizing or sharing this information with likely donors, nonprofits could also potentially brainstorm how to get more positive media exposure regarding these characteristics in restrictive civic environments.
 
-The responses of elite donors and foundations to government crackdown on civil society organizations remains a ripe area for research.
-Future research should test how well these results map on to elite individual donors and foundations---not just the average private donor.
+Second, our results also show the importance of brand recognition and goodwill---respondents were more likely to prefer donating to an organization when it was identified as the Red Cross, a signal to the ubiquity of its brand across the globe and its emphasis on neutrality in hostile environments.
+Previous research shows that both brand awareness and brand trust are critical to non-involved consumers [@YenCaskeyWarden:2023]---in this case, donors who have previously not donated to an organization.
+Others show that donors are loyal to brands whose values are congruent to their own [@SargeantFordHudson:2008].
+Our results thus have important implications on why nonprofits in hostile environments should focus on building brand awareness, as well as highlighting their values---both to engage likely and less likely donors.
+
+Our results also have multiple important theoretical implications that should be explored in future research.
+First, future research should test how well these results map on to elite individual donors and foundations---not just the average private donor.
 As large foundations are more likely to publish data about their giving than the average private donor, it may be possible to determine how the changes in preferences elicited by these heuristics translate into actual donation behavior.
-Future work should also test how these findings translate to non-American populations.
+Second, it is also important to test how these findings translate to non-American populations.
 Due to structural differences in the European nonprofit sector, where NGOs rely less on government funding and more on private funding [@Stroup:2012], donors are likely motivated by different concerns.
-Government crackdown on civil society organizations is even more challenging for local NGOs in Global South countries, where much government and public support is channeled through service delivery organizations.
-Domestic NGOs that work on more contentious issues may not be able to raise money locally, as individuals may prefer donating to service organizations focusing on health, education, and poverty [@AbsarCrowRon:2017].
-Moreover, individual donors might also avoid giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to unfavorable tax benefits or fear of retribution [@Brechenmacher:2017; @DupuyRonPrakash:2015; @Baoumi:2016].
-Future research should examine how local NGOs can overcome individual foreign donors’ concerns about host governments' criticisms of and crackdown on these groups.
+Third, many states use negative rhetoric designed to sow mistrust between these groups and communities that support them.
+While donor responses have largely focused on navigating and adapting to legal restrictions, the use of such rhetoric raises broader questions about research and policy in the nonprofit sector: how is such rhetoric changing public attitudes and donations towards these groups?
+Are the effects of transparency and accountability found in this paper still likely to hold true if the home country also starts smearing these NGOs?
+Finally, though this paper examined legal crackdowns on INGOs, this issue is even more challenging for local NGOs in Global South countries, where individual donors might avoid giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to unfavorable tax benefits or fear of retribution [@Brechenmacher:2017; @DupuyRonPrakash:2015; @Baoumi:2016].
+Future research should examine how local NGOs can overcome individual foreign donors' concerns about host governments' criticisms of and crackdown on these groups.
 

### 2025-01-20 manuscript/appendix.qmd
Mega rearrange of appendix

@@
 title: 'Appendix for "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy"'
-short-title: 'Appendix for "Why Donors Donate'
+short-title: 'Appendix for "Why Donors Donate"'
 date: "2025-01-11"
@@
 crossref: 
-  custom:
-    - kind: float
-      key: appfig
-      latex-env: appfig
-      reference-prefix: Figure A
-      space-before-numbering: false
-      latex-list-of-description: Appendix Figure
-    - kind: float
-      key: apptbl
-      latex-env: apptbl
-      reference-prefix: Table A
-      space-before-numbering: false
-      latex-list-of-description: Appendix Table
-apptbl-cap-location: top
+  tbl-title: "Table&nbsp;A"
+  fig-title: "Figure&nbsp;A"
 toc: true
 toc-depth: 2
+format: 
+  hikmah-pdf:
+    include-in-header: 
+      - tex/tbl-fig-to-toc.tex
+  hikmah-manuscript-pdf+ms:
+    include-in-header: 
+      - tex/tbl-fig-to-toc.tex
 ---
@@
 
+```{=latex}
 \clearpage
+```
 
-# Additional tables
+::: {.content-visible when-meta="appendix-single-spacing"}
+```{=latex}
+\begin{singlespace}
+```
+:::
 
-::: {#apptbl-sample-details-demographics}
+# Respondent demographics
 
 ```{r}
-#| label: apptable-sample-details-demographics
+#| label: tbl-sample-details-demographics
+#| tbl-cap: Respondent demographics
+#| tbl-pos: H
 #| include: true
@@
 
-Demographics
-
+::: {.content-visible when-meta="appendix-single-spacing"}
+```{=latex}
+\end{singlespace}
+```
 :::
@@
 
-::: {#apptbl-sample-details-charity}
-
 ```{r}
-#| label: table-sample-details-charity
+#| label: tbl-sample-details-charity
+#| tbl-cap: Respondent attitudes toward charity
 #| include: true
@@
 
-Attitudes toward charity
-
-:::
-
-::: {#apptbl-sample-details-politics}
-
 ```{r}
-#| label: table-sample-details-politics
+#| label: tbl-sample-details-politics
+#| tbl-cap: Respondent politics, ideology, and religion
 #| include: true
@@
 
-Politics, ideology, and religion
+\clearpage
 
-:::
+# Model coefficients and estimated marginal means
 
-\newpage
+When working with the results for our multinomial regression model, we rely on estimated marginal means (EMMs) rather than raw regression coefficients because of the complexity of the model.
+At its core, a "marginal mean" refers to the literal mean in the margins in a contingency table of model predictions, and differences in marginal means are equivalent to marginal effects or regression coefficients.
 
-::: {#apptbl-all-results}
+To find the causal effects defined in each of our estimands, we calculate EMMs by finding the fitted probability-scale values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding = 576 rows).
+We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.
 
-\scriptsize
+## Raw model coefficients
+
+As seen in @tbl-coefs-orig, the model returns three sets of coefficients per conjoint level.
+Each coefficient shows the shift in probability that someone will choose an organization from that appears as the first, second, and third option in the experimental task, represented by µ1, µ2, and µ3.
+Under experimental conditions where all the feature levels are randomly assigned, it is safe to assume that the cell proportions are equal and then marginalize (i.e.
+find the average) across the rows or columns.
+This allows us to take the average of each set of coefficients (e.g.
+µ1, µ2, and µ3 for "Transparency = Yes") to create a single value per coefficient.
 
 ```{r}
-#| label: table-all-results
+#| label: tbl-coefs-orig
+#| tbl-cap: Original multinomial logistic regression model coefficients
+#| include: true
+notes <- c(
+  "Estimates are median posterior log odds from a multinomial logistic regression model with three possible categories, and the columns for µ1, µ2, and µ3 represent estimates for each of the outcomes;",
+  "95% credible intervals (equal-tailed quantile intervals) in brackets."
+)
+
+inner <- "
+rowsep=0pt,
+row{odd[2-27]}={abovesep=0pt},
+row{even[4-28]}={belowsep=6pt},
+cells={font=\\footnotesize}, row{1}={valign=b}
+"
+
+modelsummary(
+  list("Posterior medians" = model_summary_table),
+  shape = Feature + term ~ group,
+  estimate = "estimate",
+  statistic = "[{conf.low}, {conf.high}]",
+  output = "tinytable",
+  fmt = fmt_significant(2),
+  notes = tt_md(paste(notes, collapse = " "))
+) %>%
+  style_tt(
+    bootstrap_class = "table",
+    tabularray_inner = inner
+  )
+```
+
+## Converting coefficients to estimated marginal means
+
+To convert EMMs and AMCEs to a more interpretable probability scale (rather than the original log odds scale), we generate predicted values (marginalized across the three µ terms) for each of the 576 unique combinations of feature levels.
+@tbl-grid-example provides an excerpt from this grid, showing six rows where accountability, organization, issue area, and funding are identical and held constant, while transparency and government relations vary.
+
+```{r}
+#| label: tbl-grid-example
+#| tbl-cap: Excerpt from complete reference grid of all 576 possible combinations of attribute features and levels
+#| include: true
+grid_example <- expand_grid(
+  feat_transp = c("Transparency: Yes", "Transparency: No"), 
+  feat_acc = "Accountability: Yes", 
+  feat_govt = c("Friendly relationship with government", "Criticized by government", "Under government crackdown"),
+  feat_org = "Red Cross", 
+  feat_issue = "Emergency response", 
+  feat_funding = "Funded primarily by many small private donations"
+)
+
+preds_small <- preds_all %>% 
+  group_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>% 
+  summarize(avg = mean(.epred)) %>% 
+  inner_join(
+    grid_example, 
+    by = join_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt)
+  ) %>% 
+  mutate(avg_nice = label_comma(accuracy = 0.001)(avg))
+
+p_sm <- preds_small %>% 
+  group_by(feat_transp) %>% 
+  summarize(
+    emm_numeric = mean(avg),
+    emm = label_comma(accuracy = 0.001)(mean(avg)),
+    list = knitr::combine_words(avg_nice, sep = " + ", and = "")
+  ) %>% 
+  mutate(feat_transp = janitor::make_clean_names(feat_transp)) %>% 
+  split(~feat_transp)
+
+amce_fake <- p_sm$transparency_yes$emm_numeric - p_sm$transparency_no$emm_numeric
+amce_tr_fake <- label_comma(accuracy = 0.001)(amce_fake)
+amce_tr_fake_pp <- label_comma(accuracy = 1, scale = 100)(amce_fake)
+
+preds_small %>% 
+  select(
+    Organization = feat_org, Issue = feat_issue, Transparency = feat_transp,
+    Accountability = feat_acc, Funding = feat_funding, Government = feat_govt,
+    EMM = avg_nice) %>%
+  tt(width = c(rep(0.15, 6), 0.07)) %>%
+  style_tt(
+    align = "l",
+    bootstrap_class = "table table-sm",
+    tabularray_inner = "rowsep=2pt, cells={font=\\footnotesize}, row{1}={valign=b}"
+  )
+```
+
+To calculate the marginal mean for a feature, we find the average predicted value across each the levels of that feature.
+To illustrate, assume that @tbl-grid-example represents the full reference grid of all experimental features and levels.
+The marginal means for transparency would be (`r p_sm$transparency_no$list`)/3 = `r p_sm$transparency_no$emm` when transparency is set to "no", and (`r p_sm$transparency_yes$list`)/3 = `r p_sm$transparency_yes$emm` when transparency is set to "yes".
+In reality, the marginal mean for transparency reported in thee paper reflects the average of 288 rows where transparency is no and 288 rows where transparency is yes.
+
+To calculate the AMCE for a feature, we find the difference in estimated marginal means.
+If we again assume that @tbl-grid-example contains the full reference grid, the AMCE for transparency would be `r p_sm$transparency_yes$emm` − `r p_sm$transparency_no$emm`, or `r amce_tr_fake`, or `r amce_tr_fake_pp` percentage points.
+Again, this is not actually the true causal effect—the real AMCE for transparency reported in the paper is the difference in marginal means for the 288 rows where transparency is no and the 288 rows where transparency is yes.
+
+In the main paper, we include plots of the marginal means and AMCEs for all experimental features. The tables below correspond to each figure in the paper.
+
+```{r}
+#| label: tbl-all-results
+#| tbl-cap: "Complete marginal means and AMCEs (see Figure 1 in main paper)"
 #| include: true
@@
   ) %>%
-  # style_tt(j = 2, line = "r", line_width = 0.1, line_color = "#d3d8dc") %>%
-  style_tt(j = 2, line = "r", line_width = 0.1) %>%
   style_tt(
@@
 
-Complete results
-
-:::
-
 \newpage
 
-::: {#apptbl-mms-trans-acc}
-
 ```{r}
-#| label: table-mms-trans-acc
+#| label: tbl-mms-trans-acc
+#| tbl-cap: "Marginal means for all combinations of transparency and accountability (see Figure 2 in main paper)"
 #| include: true
@@
 
-Marginal means for all combinations of transparency and accountability
-
-:::
-
 \newpage
 
-::: {#apptbl-transp-crackdown}
-
 ```{r}
-#| label: table-transp-crackdown
+#| label: tbl-transp-crackdown
+#| tbl-cap: "Marginal means and AMCEs for interaction between transparency, accountability, and government relationships (see Figure 3 in paper)"
 #| include: true
@@
 ```
-
-Marginal means and AMCEs for interaction between transparency, accountability, and government relationships
-
-:::
-
-\newpage
-
-::: {#apptbl-coefs-orig}
-
-```{r}
-#| label: table-coefs-orig
-#| include: true
-notes <- c(
-  "Estimates are median posterior log odds from a multinomial logistic regression model with three possible categories, and the columns for µ1, µ2, and µ3 represent estimates for each of the outcomes;",
-  "95% credible intervals (equal-tailed quantile intervals) in brackets."
-)
-
-inner <- "
-rowsep=0pt,
-row{odd[2-27]}={abovesep=0pt},
-row{even[4-28]}={belowsep=6pt},
-cells={font=\\footnotesize}, row{1}={valign=b}
-"
-
-modelsummary(
-  list("Posterior medians" = model_summary_table),
-  shape = Feature + term ~ group,
-  estimate = "estimate",
-  statistic = "[{conf.low}, {conf.high}]",
-  output = "tinytable",
-  fmt = fmt_significant(2),
-  notes = tt_md(paste(notes, collapse = " "))
-) %>%
-  style_tt(
-    bootstrap_class = "table",
-    tabularray_inner = inner
-  )
-```
-
-Original model coefficients
-
-:::
 
@@
    :   This deviation might have some impact on readers' interpretation of the findings, as it might appear that we have selectively reported a handful of our predictions.
-To avoid this, and for the sake of full transparency, we include these results in Figure 1 in the paper and @apptbl-all-results.
+To avoid this, and for the sake of full transparency, we include these results in Figure 1 in the paper and @tbl-all-results.
 The risk of bias is low—we decided on the narrative framing for this paper after collecting the data but before analyzing the results.

### 2025-01-21 manuscript/appendix.qmd
Mega revisions (almost done!)

@@
 short-title: 'Appendix for "Why Donors Donate"'
-date: "2025-01-11"
+date: "2025-01-20"
 author:
@@
 
-   :   We rephrased this as H~1b~: "If NGOs are accountable and hold regular third-party audits, then individual private donors will have a higher likelihood of supporting or donating to them."
+   :   We rephrased this as H~1b~: "If NGOs are accountable, then individual private donors will have a higher likelihood of supporting or donating to them."
 

### 2025-01-21 manuscript/manuscript.qmd
Mega revisions (almost done!)

@@
 short-title: "Why Donors Donate"
-date: "2025-01-17"
+date: "2025-01-20"
 author:
@@
 In the remainder of the paper, we provide an overview of current research on private philanthropic giving to international NGOs.
-We use these existing theories to hypothesize how organizational practices like financial transparency and accountability influence individual donor behavior in an environment of closing civic space.
+We use these existing theories to hypothesize how organizational practices like financial transparency and accountability---in isolation and when interacted with other organizational features---influence individual donor behavior in an environment of closing civic space.
 We then detail our conjoint study methodology and discuss our findings.
@@
 
-Though individual donors would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead, individuals interested in supporting charities cannot thoroughly vet every aspect of the organization [@Tremblay-BoirePrakash:2017; @ChaudhryHeiss:2021].
+Though individual donors would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead [@HungHagerTian:2023], individuals interested in supporting charities cannot thoroughly vet every aspect of the organization [@Tremblay-BoirePrakash:2017; @ChaudhryHeiss:2021].
 To more easily judge financial transparency and accountability, donors may use ratings by watchdog organizations like Charity Navigator and GuideStar as heuristics to guide their decisions.[^cn-multiple] Research shows that initiatives to address information gaps by these organizations can substantially increase donations [@Sloan:2009; @GordonKnockNeely:2009; @Tremblay-BoirePrakash:2017].
+We expect that donors will respond to signals that organizations engage in transparency and accountability practices:
 
@@
 When a potential recipient NGO faces legal crackdown in its host country, private individual donors can respond by (1) increasing their donations as a sign of support and solidarity, (2) decreasing their donations, punishing the NGO for doing something to run afoul of its host government, or (3) not considering the host country legal environment and making no change in their donation behavior.
+@ChaudhryHeiss:2021 find conflicting donor responses to foreign restrictions---while some prospective donors punish nonprofits for doing something "wrong" to incur host government restrictions, most tended to increase their support, stating that restricted NGOs are "doing good work in countries where it is tough for groups like them to operate and they need all the help they can get" [@ChaudhryHeiss:2021, 496].
 @ChaudhryDotsonHeiss:2021 explore how different combinations of donor characteristics determine which response individuals are likely to take when NGOs face crackdown.
@@
 
-> **H~2~**: If NGOs face legal crackdowns abroad, then individual private donors will have a higher likelihood of supporting or donating to them.
+> **H~2~**: If NGOs face legal restrictions abroad, then individual private donors will have a higher likelihood of supporting or donating to them.
 
@@
 While concerns about NGO mismanagement and lack of financial transparency may signal concerns about an NGO's operations and its ability to abide by the host country's regulatory environment, the presence of such transparency and accountability may instead convince donors that government targeting of NGOs may be ill-intentioned rather than simply a manifestation of financial oversight.
-Donors may view anti-NGO laws and inhospitable civic environments as a sign of governments looking to crack down on groups that seek to keep governments accountable, rather than merely auditing and punishing groups that violate routine regulations.
+Donors may view anti-NGO laws and inhospitable civic environments as a sign of governments looking to restrict groups that seek to keep governments accountable, rather than merely auditing and punishing groups that violate routine regulations.
 
@@
 The same NGO feature that can increase the likelihood of government restriction can also simultaneously serve as a donor heuristic and influence perceptions of NGO deservingness.
+Based on the importance of transparency and accountability for donors in general, we expect that legal restriction will interact with these practices and shape donor preferences:
+
+> **H~3~**: If NGOs face legal restrictions abroad *and* are financially transparent, then individual private donors will have a higher likelihood of supporting or donating to them.
 
@@
 In general, respondents were well balanced across all pre-treatment characteristics, including gender, age, education, income, and attitudes toward charity.
-
-::: {.content-visible when-profile="nice"}
-\clearpage
-:::
 
@@
 
-At the time of designing the study, Charity Navigator---a large database of US nonprofit financial information---categorized international nonprofit activities into four general causes: (1) development, (2) humanitarian relief, (3) international affairs and human rights advocacy, and (4) environment.[^cn] Accordingly, we used four nonprofits that are stereotypical for each cause: the International Committee of the Red Cross (humanitarian relief), Amnesty International (human rights), Oxfam (development), and Greenpeace (environment).
-We also varied several other features, including four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), two organizational practices (financial transparency and third-party accountability audits), three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and three relationships with host governments (friendly, criticized by the government, and under government crackdown).
+At the time of designing the study, Charity Navigator---a large database of US nonprofit financial information---categorized international nonprofit activities into four general causes: (1) development, (2) humanitarian relief, (3) international affairs and human rights advocacy, and (4) environment.[^cn] Accordingly, we used four nonprofits that are stereotypical for each cause: the International Committee of the Red Cross (humanitarian relief), Amnesty International (human rights), Oxfam (development), and Greenpeace (environment).[^real-names] We also varied several other features, including four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), two organizational practices (financial transparency and third-party accountability audits), three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and three relationships with host governments (friendly, criticized by the government, and under government crackdown).
 
@@
 At the time of writing, Charity Navigator had changed its taxonomy to include 18 broader categories.
+
+[^real-names]: We used real organization names rather than hypothetical, fictionalized names to allow the experimental task to better mirror reality [@McDonald:2020] and to reduce respondent cognitive burden when reflecting on organization characteristics [@MajnemerMeibauer:2022].
 
@@
 Because this is an experimental design, any statistical confounding is accounted for during the process of randomization and covariates should have no systematic effect on treatment effects.
-We do not work with the raw results of the model directly (though a complete table of results is included in Table A4).
-Given the conjoint design, we instead create a complete balanced grid of all 576 combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding) and use the model to calculate predicted probabilities of choice selection for each row of possible treatment values.
+We do not work with the raw results of the multinomial model directly.
+Given the conjoint design, we instead create a complete balanced grid of all 576 combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding) and use the model to calculate predicted probabilities of choice selection for each combination of possible treatment values.
 We then collapse this set of predicted probabilities into estimated marginal means (EMMs) for specific features of interested while marginalizing or averaging over all other predicted variables [@LeeperHoboltTilley:2020; @BremerBurgisser:2023].
+This marginalization process allows us to isolate the statistical effect of each feature in isolation.
+We include a complete table of model results in Table A4, along with a brief illustration of converting from regression coefficients to estimated marginal means.
+
 We report the causal effect of each manipulated feature using the average marginal component effect (AMCE), which is equivalent to the difference in estimated marginal means for specific feature levels.
-For example, when estimating the marginal means of the transparency treatment, we find the average predicted probability across the 288 rows of the reference grid where transparency is true and across the 288 rows where transparency is false---the difference between these two estimated marginal means is the AMCE, or the causal effect of the treatment holding all other values constant, on the probability scale.
+For example, when estimating the marginal means of the transparency treatment, we find the average predicted probability across the 288 rows of the reference grid where transparency is true and across the 288 rows where transparency is false, holding all other experimental features and individual covariates constant---the difference between these two estimated marginal means is the AMCE, or the causal effect of the treatment on the probability scale.
 
@@
 
-We present the posterior distributions of the marginal means and AMCEs for each of our experimental conditions in @fig-all-results and provide posterior medians, credible intervals, and other model diagnostics in Table A4 and Table A7.
+We present the posterior distributions of the marginal means and AMCEs for each of our experimental conditions in @fig-all-results and provide posterior medians, credible intervals, and other model diagnostics in Tables A6 and A8.
 Because AMCEs are relative statements (i.e.
@@
 
-To contextualize the magnitude of the causal effects for our hypotheses of interest, we begin our analysis with a brief overview of the effects of organizational characteristics that nonprofits have less direct control over: their brand name, their issue area, and their funding sources.
+To contextualize the magnitude of the causal effects for our hypotheses of interest, we begin our analysis with a brief overview of the effects of more foundational organizational characteristics: their organization name, their issue area, and their funding sources.
 Brand recognition appears to be a powerful heuristic for donor decision making.
@@
 There is also some evidence that these two effects are equivalent and perhaps interchangeable.
-@fig-transp-acc (and Table A5) shows the posterior marginal means for all four combinations of possible levels of transparency and accountability.
+@fig-transp-acc (and Table A7) shows the posterior marginal means for all four combinations of possible levels of transparency and accountability.
 When respondents see both as "no" simultaneously, the estimated marginal mean is lower than any of the individual treatments in @fig-all-results, at `r mms_ta$transparency_no_accountability_no$pct` (`r mms_ta$transparency_no_accountability_no$nice_ci`), or 9 percentage points lower than the baseline probability of 25%.
@@
 This result is surprising, but clarifies findings in previous research.
-In a similar vignette-based experiment, @ChaudhryHeiss:2021 find no substantial effect of legal restrictions on the probability of donation, and any substantive crackdown-related effects are moderated by other treatments like NGO issue area or funding source.
+In a similar vignette-based experiment, @ChaudhryHeiss:2021 find no substantial effect of legal restrictions on the probability of donation, and any substantive crackdown-related effects interact with and are dampened by other treatments like NGO issue area or funding source.
 This negative effect might also be related to the notion of donor efficacy.
@@
 Financial transparency and accountability practices both have a positive (and likely interchangeable) effect on NGO favorability, while government criticism and restriction have a negative effect and discourage potential donors from donating.
-As seen in @fig-transp-crackdown (and Table A6), these heuristics also interact with each other.[^transp-only] The estimated posterior marginal means for different relationships with host governments move in the same direction regardless of whether an organization engages in transparency practices: organizations with no conflict are most preferred, while organizations facing restrictions are least preferred.
+For our third hypothesis, we posit that these heuristics also interact with each other.
+This is confirmed in @fig-transp-crackdown (and Table A8)---the estimated posterior marginal means for different relationships with host governments move in the same direction regardless of whether an organization engages in transparency practices:[^transp-only] organizations with no conflict are most preferred, while organizations facing restrictions are least preferred.
 Transparency practices in the presence of restrictions seem to have two general effects.
@@
 On its own, as seen in @fig-all-results, engaging in transparency causes a `r amce$transparency_yes$pp_abs` percentage point increase in the probability of a respondent selecting an organization.
-The right panel of @fig-transp-crackdown (and Table A6) shows how the causal effect of transparency changes across different types of government relationships.
+The right panel of @fig-transp-crackdown (and Table A8) shows how the causal effect of transparency changes across different types of government relationships.
 These AMCEs represent the difference in the estimated posterior marginal means of the two levels of transparency in the left panel.
@@
 
-# Conclusion
+# Discussion and conclusion
 
@@
 Unlike state donors, individual donors have different motivations for engaging in philanthropy, and they may not necessarily withdraw or reduce support for NGOs facing harassment abroad.
-This is important because private philanthropy towards organizations working in international affairs continues to grow despite inflation---from 2021 to 2022, individual giving to nonprofits in international affairs grew by over 10.9% in the US [@GivingUSA:2023].
+This is important because private philanthropy towards organizations working in international affairs continues to grow---following a decades-long trend, from 2021 to 2022, individual giving to nonprofits in international affairs grew by nearly 11% in the US [@GivingUSA:2023].
 
@@
 In addition to voluntarily emphasizing or sharing this information with likely donors, nonprofits could also potentially brainstorm how to get more positive media exposure regarding these characteristics in restrictive civic environments.
+Moreover, we find that nonprofit transparency and accountability practices share the same causal effect, implying that donors might see these as interchangable concepts.
 

### 2025-01-21 notebook/model-diagnostics.qmd
This reference changed

---
title: "Model diagnostics"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", fig.retina = 3,
  fig.width = 6, fig.height = (6 * 0.618),
  out.width = "80%", collapse = TRUE,
  dev = "ragg_png"
)

options(
  digits = 3, width = 120,
  dplyr.summarise.inform = FALSE,
  knitr.kable.NA = ""
)
```

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(tidybayes)
library(glue)
library(gt)
library(gtExtras)

tar_config_set(
  store = here::here("_targets"),
  script = here::here("_targets.R")
)

tar_load(m_treatment_only)

invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(diagnostic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))

theme_set(theme_ngo())
```

## MCMC journeys

These multilevel multinomial models are huge and unwieldy—the model with just the treatment variables and respondent-specific intercepts has `r scales::label_comma()(length(get_variables(m_treatment_only)))` coefficients/parameters (!!).

So here, for the sake of illustration, we show just four parameters: one of the intercepts and a treatment coefficient from each of the µs. These plots show that the chains are stable, well-mixed, and converged.

### Traceplots

These should look like hairy caterpillars.

They do.

```{r mcmc-trace}
params_to_show <- c(
  "b_mu1_Intercept", "b_mu1_feat_orgGreenpeace",
  "b_mu2_feat_issueHumanrights", "b_mu3_feat_govtUndergovernmentcrackdown"
)

plot_trace(m_treatment_only, params_to_show)
```

### Trace rank plots (trank plots)

These are histograms of the ranks of the parameter draws across the four chains. If the chains are exploring the same space efficiently, the histograms should be similar and overlapping and no one chain should have a specific rank for a long time [@McElreath:2020a, 284].

They do.

```{r mcmc-trank}
plot_trank(m_treatment_only, params_to_show)
```

## Posterior predictions

The model should generate predictions that align with the observed outcomes. It does.

```{r pp-check}
plot_pp(m_treatment_only)
```

### 2025-01-22 manuscript/appendix.qmd
Compare sample to CPS

@@
 toc: true
-toc-depth: 2
+toc-depth: 3
 format: 
+  html: default
   hikmah-pdf:
@@
 tar_load(c(
-  participant_summary, model_summary_table, feature_lookup, level_lookup
+  participant_summary, model_summary_table, feature_lookup, level_lookup, cps_diffs
 ))
@@
 #| include: true
-tbl_participant_summary <- participant_summary %>% 
+tbl_participant_summary <- participant_summary$participant_summary %>% 
+  mutate(level = case_match(
+    level,
+    "Age: Less than median" ~ "Less than 2017 national median (36)",
+    "Income: Less than median" ~ "Less than 2017 national median ($61,372)",
+    .default = level
+  )) %>%
+  mutate(level = str_remove(level, "^[^:]+: ")) %>%
   select(
@@
   format_tt(escape = TRUE)
+```
+
+\clearpage
+
+```{r}
+#| label: tbl-sample-cps
+#| tbl-cap: Sample characteristics compared to nationally representative Current Population Survey (CPS) estimates
+#| include: true
+
+rows_with_dagger <- cps_diffs %>%
+  mutate(row = row_number()) %>%
+  filter(cps_prop_outside_ci == TRUE) %>%
+  pull(row)
+
+notes <- list(
+  `*` = list(i = 0, j = 4, text = tt_md("Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.")),
+  `†` = list(i = rows_with_dagger, j = 3, text = tt_md("National value is substantially different from the sample; the 95% posterior credible interval for the difference between the sample and national proportions contains 0.")),
+  a = list(i = 1:5, j = 1, text = "Annual Social and Economic Supplement (ASEC) of the Current Population Survey (CPS), March 2019"),
+  b = list(i = 6:7, j = 1, text = "Monthly CPS, September 2019"),
+  c = list(i = 8, j = 1, text = "Monthly CPS, November 2018")
+)
+
+cps_diffs %>%
+  mutate(across(c(prop_sample, national_value,), fmt_pct)) %>%
+  mutate(diff_ci = glue::glue(
+    "{fmt_pp_int(y)}\n[{fmt_pp_int(ymin)}, {fmt_pp_int(ymax)}]"
+  )) %>%
+  select(
+    Variable = variable,
+    Sample = prop_sample,
+    National = national_value,
+    `∆` = diff_ci
+  ) %>%
+  mutate(`∆` = tt_linebreak(`∆`)) %>%
+  tt(width = c(0.45, 0.1, 0.1, 0.15), notes = notes) %>%
+  format_tt(j = 4, escape = FALSE) %>%
+  format_tt(j = 1:3, escape = TRUE) %>%
+  style_tt(j = 1, align = "l") %>%
+  style_tt(j = 2:4, align = "c") %>%
+  style_tt(
+    bootstrap_class = "table table-sm",
+    tabularray_inner = "rowsep=2pt, cells={font=\\footnotesize}, row{1}={valign=b}"
+  )
 ```

### 2025-01-22 manuscript/manuscript.qmd
Compare sample to CPS

@@
 We asked potential participants a screening question about their philanthropic behavior early in the survey---if a participant responded that they give once every few years or never, they were disqualified from the study.
-Our reported causal effects are therefore not representative of the entire population and instead are only valid for people interested in charitable giving.
 We also included an attention check question early in the survey and removed respondents who failed the question.
@@
 In general, respondents were well balanced across all pre-treatment characteristics, including gender, age, education, income, and attitudes toward charity.
+Additionally, Table A4 compares sample characteristics with nationally representative estimates from the 2019 Current Population Survey (CPS).
+Our sample matches national proportions of age, marital status, and education, and contains slightly more men and slightly higher income levels than the general population.
+Due to the initial screening question that limited participants to those with an interest in charitable activity, respondents are far more likely to have donated, volunteered, or voted in the past year than population CPS estimates.
+Our reported causal effects are therefore not representative of the entire population and instead are only valid for people interested in charitable giving.
 
@@
 When using emergency response (the most popular issue) as the reference category for AMCEs, working with human rights causes a `r amce$human_rights$pp_abs` percentage point decrease (`r amce$human_rights$nice_ci_pd`), while environmental and refugee relief issues see `r amce$environment$pp_abs` (`r amce$environment$nice_ci_pd`) and `r amce$refugee_relief$pp_abs` (`r amce$refugee_relief$nice_ci_pd`) percentage point decreases, respectively.
-To put these effects in context, these effects are smaller than the the Red Cross effect and a little larger than the Oxfam and Greenpeace effects.
+To put these effects in context, these effects are smaller than the Red Cross effect and a little larger than the Oxfam and Greenpeace effects.
 

### 2025-01-22 R/funs_data.R

@@ -624,19 +624,19 @@ make_clean_data <- function(path) {
       Q5.16_6 = factor(Q5.16_6, labels = str_c("Race: ", c("Not Other", "Other"))),
       # *Q5.17*: How old are you?
       # 
-      # - Under 18 → More/less than median (base case = less than median)
-      # - 18 - 24 → More/less than median
-      # - 25 - 34 → More/less than median
-      # - 35 - 44 → More/less than median
-      # - 45 - 54 → More/less than median
-      # - 55 - 64 → More/less than median
-      # - 65 - 74 → More/less than median
-      # - 75 - 84 → More/less than median
-      # - 85 or older → More/less than median
+      # - 1: Under 18 → More/less than median (base case = less than median)
+      # - 2: 18 - 24 → More/less than median
+      # - 3: 25 - 34 → More/less than median
+      # - 4: 35 - 44 → More/less than median
+      # - 5: 45 - 54 → More/less than median
+      # - 6: 55 - 64 → More/less than median
+      # - 7: 65 - 74 → More/less than median
+      # - 8: 75 - 84 → More/less than median
+      # - 9: 85 or older → More/less than median
       Q5.17 = factor(
         case_when(
-          Q5.17 >= 3 ~ "More than median", # Median age in 2017 was 36
-          Q5.17 < 3 ~ "Less than median"
+          Q5.17 >= 4 ~ "More than median", # Median age in 2017 was 36
+          Q5.17 < 4 ~ "Less than median"
         ),
         levels = c("Less than median", "More than median"),
         labels = str_c(

### 2025-01-22 R/funs_graphics.R

@@ -59,7 +59,14 @@ build_ci <- function(lower, upper) {
 fmt_decimal <- \(x) scales::label_number(accuracy = 0.001, style_negative = "minus")(x)
 fmt_decimal2 <- \(x) scales::label_number(accuracy = 0.01, style_negative = "minus")(x)
 
+fmt_pct <- \(x) scales::label_percent(accuracy = 0.01, style_negative = "minus")(x)
+
 fmt_pp_int <- \(x) scales::label_number(accuracy = 0.1, scale = 100, style_negative = "minus")(x)
+
+fmt_pp2 <- function(x) {
+  scales::label_number(accuracy = 0.1, scale = 100, 
+    suffix = " pp.", style_negative = "minus")(x)
+}
 
 label_pp <- function(x) {
   scales::label_number(accuracy = 1, scale = 100, 

### 2025-01-22 R/funs_misc_analysis.R

@@ -71,19 +71,19 @@ create_sample_summary <- function(survey_results) {
     "Demographics", "Q5.15", "Income",
     "Attitudes toward charity", "Q2.5", "Frequency of donating to charity",
     "Attitudes toward charity", "Q2.6", "Amount of donations to charity last year",
-    "Attitudes toward charity", "Q2.7_f", "Importance of trusting charities",
-    "Attitudes toward charity", "Q2.8_f", "Level of trust in charities",
+    "Attitudes toward charity", "Q2.7", "Importance of trusting charities",
+    "Attitudes toward charity", "Q2.8", "Level of trust in charities",
     "Attitudes toward charity", "Q2.10", "Frequency of volunteering",
     "Politics, ideology, and religion", "Q2.1", "Frequency of following national news",
     "Politics, ideology, and religion", "Q5.7", "Traveled to a developing country",
     "Politics, ideology, and religion", "Q5.1", "Voted in last election",
-    "Politics, ideology, and religion", "Q5.6_f", "Trust in political institutions and the state",
-    "Politics, ideology, and religion", "Q5.2_f", "Political ideology",
+    "Politics, ideology, and religion", "Q5.6", "Trust in political institutions and the state",
+    "Politics, ideology, and religion", "Q5.2", "Political ideology",
     "Politics, ideology, and religion", "Q5.4", "Involvement in activist causes",
     "Politics, ideology, and religion", "Q5.8", "Frequency of attending religious services",
     "Politics, ideology, and religion", "Q5.9", "Importance of religion"
   )
-  
+
   summarize_factor <- function(x) {
     output <- table(x) %>% 
       as_tibble() %>% 
@@ -91,10 +91,28 @@ create_sample_summary <- function(survey_results) {
       mutate(level = factor(level, levels = levels(x))) %>%
       mutate(prop = count / sum(count),
         nice_prop = scales::label_percent(accuracy = 0.1)(prop))
-    
+
     return(list(output))
   }
-  
+
+  results_to_test <- survey_results %>%
+    mutate(
+      female = Q5.12 == "Gender: Female",
+      age = Q5.17 == "Age: More than median",
[…]

### 2025-01-22 _targets.R

@@ -45,16 +45,21 @@ lapply(list.files("R", full.names = TRUE, recursive = TRUE), source)
 
 # Actual pipeline ---------------------------------------------------------
 list(
-  ## Data and draws ----
-  tar_target(survey_results_file,
-    get_from_osf(osf_url = "https://osf.io/n2hwm/",
-      out_dir = here_rel("data", "raw_data")),
-    format = "file"),
-  tar_target(survey_results, read_rds(survey_results_file)),
-  
+  ## Data and draws ----  
   tar_target(
     qualtrics_anonymized_file,
     here_rel("data", "raw_data", "conjointqsf_final.csv"),
+    format = "file"
+  ),
+
+  tar_target(
+    ipums_dat_file,
+    here_rel("data", "raw_data", "ipums-cps", "cps_00006.dat.gz"),
+    format = "file"
+  ),
+  tar_target(
+    ipums_ddi_file,
+    here_rel("data", "raw_data", "ipums-cps", "cps_00006.xml"),
     format = "file"
   ),
   
@@ -65,7 +70,7 @@ list(
   ## Graphics and tables ----
   tar_target(graphic_functions, lst(
     theme_ngo, set_annotation_fonts, clrs, 
-    build_ci, fmt_decimal, fmt_decimal2, fmt_pp_int, label_pp
+    build_ci, fmt_decimal, fmt_decimal2, fmt_pp_int, label_pp, fmt_pct, fmt_pp2
   )),
   tar_target(table_functions, lst(opts_int, opts_theme, inline_listify)),
   tar_target(diagnostic_functions, lst(plot_trace, plot_trank, plot_pp)),
@@ -95,8 +100,11 @@ list(
   tar_target(feature_lookup, make_feature_lookup()),
   
   ## Miscellaneous analysis stuff
-  tar_target(participant_summary, create_sample_summary(survey_results)),
   tar_target(model_summary_table, build_modelsummary(m_treatment_only)),
+  
+  tar_target(participant_summary, create_sample_summary(data_sans_conjoint)),
+  tar_target(cps_props, calc_population_props(ipums_dat_file, ipums_ddi_file)),
+  tar_target(cps_diffs, calc_cps_diffs(participant_summary, cps_props)),
   
   ## Manuscript and notebook ----
   tar_quarto(manuscript, path = "manuscript", quiet = FALSE),

### 2025-01-22 manuscript/manuscript.qmd
Suparna and Marc edits

@@
 short-title: "Why Donors Donate"
-date: "2025-01-20"
+date: "2025-01-22"
 author:
@@
   Governments across the world have increasingly used laws to restrict the work of nonprofits, which has led to a reduction in public or official foreign aid directed towards these groups.
-Many international nonprofits, in response, have turned to individual donors to offset the loss of traditional fundings.
+Many international nonprofits, in response, have turned to individual donors to offset the loss of traditional funding.
 What are individual donors' preferences regarding donating to legally besieged nonprofits abroad?
-We conducted a conjoint experiment on a nationally representative sample of likely donors in the US and found that learning about host government criticism and restrictions on nonprofits decreases individuals' preferences to donate to them.
+We conducted a conjoint experiment on a nationally representative sample of likely donors in the US and found that learning about host government criticism and legal restrictions on nonprofits decreases individuals' preferences to donate to them.
 However, organizational features such as financial transparency and accountability can protect against this dampening effect.
@@
 Non-governmental organizations (NGOs) are a core component of global governance and service delivery.
-Non-governmental organizations (NGOs) are a core component of global governance and service delivery.
 Over the last two decades, however, NGOs face restrictive civic spaces abroad [@ChristensenWeinstein:2013; @DupuyRonPrakash:2016; @GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020].
@@
 121-F2), which forced organizations receiving foreign funding and engaging in political activities to register as foreign agents, which forced hundreds of organizations to close down [@Kirova:2024].
-These developments were not limited to authoritarian regimes.
+These developments are not limited to authoritarian regimes.
 Hybrid and democratic states have also restricted NGOs' operations within their territories.
-Between 2014 and 2019, the Indian government banned 14,500 NGOs from receiving money from abroad, including prominent international groups such as the Ford Foundation and Greenpeace [@PressTrustofIndia:2019].
+Between 2014 and 2019, the Indian government banned 14,500 NGOs from receiving money from abroad, including prominent international nonprofits such as the Ford Foundation and Greenpeace [@PressTrustofIndia:2019].
 Policymakers have referred to this phenomenon as the "closing of civic space" or "shrinking civic space" [@CarothersBrechenmacher:2014; @Rutzen:2015b].
@@
 Individual donor behavior is unlike official donor behavior [@DesaiKharas:2018].
-They have different preferences---while official donors channel funds to countries with better institutional quality or to reward governmental performance, [@Bermeo:2011; @DietrichWright:2015], individual donors are more inclined to donate to NGOs in countries experiencing a humanitarian crisis [@DesaiKharas:2018].
+They have different preferences---while official donors channel funds to countries with better institutional quality or to reward governmental performance [@Bermeo:2011; @DietrichWright:2015], individual donors are more inclined to donate to NGOs in countries experiencing a humanitarian crisis [@DesaiKharas:2018].
 As such, individual donors may have separate metrics of effectiveness or impact that can differ from the benchmarks that large donor agencies rely on, and INGOs may need to adapt their fundraising strategies to a different set of potential donors.
 
-While INGOs have control over organizational-level factors that determine their effectiveness, the political environment in the host countries INGOs work in---including the global restrictions on civil society that is causing many organizations to seek out private funding in the first place---is a structural factor that INGOs can rarely influence on their own.
+While INGOs have control over organization-level factors that determine their effectiveness, the political environment in the host countries INGOs work in---including the restrictions on civil society that cause many organizations to seek out private funding in the first place---is a structural factor that INGOs can rarely influence on their own.
 How do individual donors in the US feel about donating to legally besieged NGOs abroad?
 How do organizational elements of private donor decision-making interact with broader structural limits on INGO fundraising?
-While there are many organizational-level factors that can determine an NGO's impact, including such as organizational structure, financial transparency, accountability, leadership, and strategy [@MitchellSchmitzBruno-vanVijfeijken:2020], in this paper, we focus on the two factors that are most visible to donors outside of the organizations and on which information is available publicly---financial transparency and accountability.
+While there are many organization-level factors that can determine an NGO's impact, including organizational structure, financial transparency, accountability, leadership, and strategy [@MitchellSchmitzBruno-vanVijfeijken:2020], in this paper, we focus on the two factors that are most visible to donors outside of the organizations and on which information is available publicly---financial transparency and accountability.
 
@@
 We fielded a conjoint experiment to a nationally representative sample of 1,016 adults in the US.
-This experiment allows us to assess individual level giving preferences among likely donors in the US towards NGOs abroad working in a variety of issue areas---human rights, environment, emergency response, and refugee relief.[^not-elite] More importantly, it allows us to directly compare the relative impact of host government restriction of NGOs and organizational financial transparency and accountability on individual donor preferences.
+This experiment allows us to assess individual-level giving preferences among likely donors in the US towards NGOs abroad working in a variety of issue areas---human rights, environment, emergency response, and refugee relief.[^not-elite] More importantly, it allows us to directly compare the relative impact of host government restriction of NGOs and organizational financial transparency and accountability on individual donor preferences.
 The result of this experiment shows that both financial transparency and accountability increase individuals' willingness to donate to NGOs.
@@
 Second, research shows that NGO leaders often have difficulty in attracting new donors and also find it challenging to motivate current donors [@GaudreauCao:2015].
-Examining organizational-level factors that make the average donor increase their charitable giving, especially when facing restricted civic space abroad, can help NGOs better frame their funding appeals.
+Examining organization-level factors that make the average donor increase their charitable giving, especially when facing restricted civic space abroad, can help NGOs better frame their funding appeals.
 Moreover, our results provide guidance to organizations facing increased antagonism by governments abroad and point to possible methods of adapting to worsening or shrinking civic space.
@@
 Many organizations struggle with the conflicting imperatives of being large organizations that can operate efficiently at scale, while maintaining the grassroots contacts and consensus building that contributed to their early successes [@MitchellSchmitzBruno-vanVijfeijken:2020; @Jalali:2008; @Bano:2012; @Rahman:2006].
-In response, many nonprofits sought to establish and enhance their accountability, responsiveness, and legitimacy [@edwardshulme; @GourevitchLake:2012].
-These actions were a result of many organizational-level factors impact nonprofit efficacy, including organizational structure, leadership, strategy, transparency and accountability.
+As a result, many nonprofits sought to establish and enhance their accountability, responsiveness, and legitimacy [@edwardshulme; @GourevitchLake:2012].
+These actions were a result of many organization-level factors that can potentially impact nonprofit efficacy, including organizational and governance structure, leadership, strategy, transparency, and accountability.
 Organizational and governance structures define how decisions are made and who participates in decision making.
-While some nonprofits follow more democratic governance models---such as expanded membership to Global South countries, devolving more decision-making powers to the regional or country levels, others have a more centralized structure [@Wong:2012; @MitchellSchmitzBruno-vanVijfeijken:2020, 155].
+While some nonprofits follow more democratic governance models---such as expanded membership to Global South countries and devolving more decision-making powers to the regional or country levels, others have a more centralized structure [@Wong:2012; @MitchellSchmitzBruno-vanVijfeijken:2020, 155].
 Leadership can be defined as how leaders "handle the external and internal politics of making their organizations more effective and responsive," and what sort of organizational cultures they create [@MitchellSchmitzBruno-vanVijfeijken:2020, 178].
-Finally, strategy is whether the organization has a long-term strategic plan that emphasizes sustainability, innovation, learning and adaptation [@MitchellSchmitzBruno-vanVijfeijken:2020, 100].
-
-However, organizational structure, leadership, and strategy (among other organizational-level factors) are often not visible to the average individual (non-elite) donor, especially in the context of international NGOs.
-Therefore, in this paper, we focus on the two organizational-level factors that are most visible to the average donor---financial transparency and accountability.
+Finally, strategy involves whether the organization has a long-term strategic plan that emphasizes sustainability, innovation, learning, and adaptation [@MitchellSchmitzBruno-vanVijfeijken:2020, 100].
+
+However, organizational structure, leadership, and strategy (among other organization-level factors) are often not visible to the average individual (non-elite) donor, especially in the context of international NGOs.
+Therefore, in this paper, we focus on the two organization-level factors that are most visible to the average donor---financial transparency and accountability.
 Assessing an NGO's deservingness and efficiency demands substantial time and resources, which individual donors typically lack [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
 As such, these donors rely on various easily available cues and heuristics when deciding to support an NGO.
-News about financial mismanagement and lack of transparency and accountability may be more easily available to these donors.
+Compared to other organization-level factors, news about financial mismanagement and lack of transparency and accountability may be more easily available.
 Many nonprofit scandals involve some form of financial wrongdoing [@PrakashGugerty:2010b].
-Notable examples include the Oil-for-Food program, initiated by the United Nations in 1996 to allow Iraq to sell enough oil to pay for food and other necessities for its population, which has been suffering from sanctions imposed on Iraq since the First Gulf War.
-However, in 2004, the widespread financial fraud by the program, limited distribution of food by nonprofits and lack of accountability was widely publicized.
-Numerous other such cases---covered in @GibelmanGelman:2001 and @GibelmanGelman:2004---show how financial mismanagement, embezzlement, fraud, and lack of accountability can decrease public trust in and donations towards these nonprofits.
+Notable examples include the Oil-for-Food program, initiated by the United Nations in 1996 to allow Iraq to sell enough oil to pay for food and other necessities for its population, which had been suffering from sanctions imposed on Iraq since the First Gulf War.
+However, in 2004, the program's widespread financial fraud, limited distribution of food by nonprofits, and lack of accountability was widely publicized.
+Numerous other such cases---covered in @GibelmanGelman:2001 and @GibelmanGelman:2004---show how financial mismanagement, embezzlement, fraud, and lack of accountability can decrease public trust in and donations to these nonprofits.
 Globally, around 5% of revenue is lost annually due to fraud [@ACFE:2021].
@@
 Transparency can involve proactive sharing of information with stakeholders, participation in data transparency platforms, avoiding financial misconduct, and exhibiting trustworthiness.
-NGOs can engage in financial transparency in a variety of ways such as distribution of audited financial statements and voluntarily sharing information with third party intermediaries.
+NGOs can engage in financial transparency in a variety of ways, such as distribution of audited financial statements and voluntarily sharing information with third party intermediaries.
 Research shows that transparency is associated with greater donations, lower debt, and better governance [@HarrisNeely:2021; @HarrisPetrovitsYetman:2023; @SaxtonKuoHo:2012].
@@
 Previous research has found that media exposés about charity mismanagement can generate negative reputational spillovers for the charitable sector [@GibelmanGelman:2004].
-Diversions, or the unauthorized use of an organization's assets, including embezzlement and theft can result in a decrease in donations.
+Diversions---or the unauthorized use of an organization's assets, including embezzlement and theft---can result in a decrease in donations.
 This effect becomes even stronger with media coverage of diversion [@HarrisPetrovitsYetman:2023].
@@
 As NGOs gain more prominence, stakeholders, or "any group or individual who can affect or is affected by the achievement of an organization's objectives," [@MitchellAgleWood:1997, 854] want to be assured that their donations or support or support of an organization will make a real difference.
-More effective accountability can encourage NGOs to become more closely aligned with community practices, provide greater assurances to stakeholders and help expand their support [@Murtaza:2012].
+More effective accountability can encourage NGOs to become more closely aligned with community practices, provide greater assurances to stakeholders, and help expand their support [@Murtaza:2012].
 Problems with accountability usually occur when organizations ignore their stakeholders' preferences and use judgements or actions which may not align with one or more of their constituent groups [@McCambridge:2019].
-The absence of accountability is associated with decreased public trust, worse reputation, and lower perceived quality [@Becker:2018].
+The absence of accountability is associated with decreased public trust, deteriorated reputation, and lower perceived quality [@Becker:2018].
 
@@
 A global cascade of anti-NGO laws in recent decades has created barriers to entry, funding, and advocacy for civic organizations [@GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022; @Heiss:2017; @DupuyRonPrakash:2016].
-The use of such anti-NGO laws, also referred to as administrative crackdown [@Chaudhry:2022], is different from regulations that simply set standards for appropriate organizational behavior and set penalties for violations [@North:1990].[^violent-crackdown] However, the anti-NGO laws discussed in this paper, such as Russian Foreign Agent law, are not grounded in international legal principles, and do not give nonprofits the freedom of association or the freedom to freely access human and material resources [@Voule:2023; @Robinson:2024].
+The use of such anti-NGO laws, also referred to as administrative crackdown [@Chaudhry:2022], is different from regulations that simply set standards for appropriate organizational behavior and set penalties for violations [@North:1990].[^violent-crackdown] However, the anti-NGO laws discussed in this paper, such as the Russian Foreign Agent law, are not grounded in international legal principles and do not give nonprofits the freedom of association or access to resources [@Voule:2023; @Robinson:2024].
 As a result, NGOs must spend more time, effort, and resources to ensure their survival---at the expense of pursuing their missions.
@@
 However, previous literature has established that individual private donors do not make the same considerations as official donors when deciding to donate [@DesaiKharas:2018; @ChaudhryHeiss:2021].
-Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the grounds [@EasterlyWilliamson:2011].
-When a potential recipient NGO faces legal crackdown in its host country, private individual donors can respond by (1) increasing their donations as a sign of support and solidarity, (2) decreasing their donations, punishing the NGO for doing something to run afoul of its host government, or (3) not considering the host country legal environment and making no change in their donation behavior.
+Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the ground [@EasterlyWilliamson:2011].
+When a potential recipient NGO faces legal crackdown in its host country, private individual donors can respond by (1) increasing their donations as a sign of support and solidarity, (2) decreasing their donations, punishing the NGO for perhaps doing something to run afoul of its host government, or (3) not considering the host country legal environment and making no change in their donation behavior.
 @ChaudhryHeiss:2021 find conflicting donor responses to foreign restrictions---while some prospective donors punish nonprofits for doing something "wrong" to incur host government restrictions, most tended to increase their support, stating that restricted NGOs are "doing good work in countries where it is tough for groups like them to operate and they need all the help they can get" [@ChaudhryHeiss:2021, 496].
 @ChaudhryDotsonHeiss:2021 explore how different combinations of donor characteristics determine which response individuals are likely to take when NGOs face crackdown.
-They find that donors with longer experiences with the nonprofit sector and high levels of social trust---i.e.
-those who frequently volunteer, regularly donate to charity, and trust political institutions---are more likely to maintain their support for international NGOs that face criticism or crackdown abroad.
+They find that donors with longer experiences with the nonprofit sector and high levels of social trust---i.e., those who frequently volunteer, regularly donate to charity, and trust political institutions---are more likely to maintain their support for international NGOs that face criticism or crackdown abroad.
 Thus, anti-NGO laws may act as a heuristic to individuals donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and seek to restrict their work.
@@
 This is especially true for nonprofits that rely more heavily on private funds, rather than government funds.
-Previous research finds that, "individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds." [@ChaudhryHeiss:2021, 496].
+Previous research finds that, "individual donors thus seem to be more willing to support besieged human rights organizations when they are unencumbered by government funds" [@ChaudhryHeiss:2021, 496].
 Similar trends can be seen even after nonprofits face restrictive political and civic environments in other specific issue areas.
@@
 
-Donors show increased willingness to donate to NGOs facing government restrictions/criticism while being financial transparent and accountable.
+Donors show increased willingness to donate to NGOs facing government restrictions/criticism while being financially transparent and accountable.
 While concerns about NGO mismanagement and lack of financial transparency may signal concerns about an NGO's operations and its ability to abide by the host country's regulatory environment, the presence of such transparency and accountability may instead convince donors that government targeting of NGOs may be ill-intentioned rather than simply a manifestation of financial oversight.
@@
 Even with respondents answering twelve iterations of the experiment, not every combination was seen.
-However, as long as all the possible organizational attributes are well randomized and there are no systematic biases toward specific options (i.e.
-more respondents select the first option because it is the first) or toward earlier iterations of attribute choices (i.e.
-respondents are more careful and attentive for the first hypothetical organization than the last), we can pool all observations together for specific attributes of interest while marginalizing across all other attributes [@KertzerRenshonYarhi-Milo:2021].
+However, as long as all the possible organizational attributes are well randomized and there are no systematic biases toward specific options (i.e., more respondents select the first option because it is the first) or toward earlier iterations of attribute choices (i.e., respondents are more careful and attentive for the first hypothetical organization than the last), we can pool all observations together for specific attributes of interest while marginalizing across all other attributes [@KertzerRenshonYarhi-Milo:2021].
 This allows us to (1) estimate the effect of each experimental treatment even if some unique combinations of attributes were unseen, and (2) use a much smaller sample size than would be required in a more traditional factorial design.
@@
 
-After presenting respondents with a set of organizations, we asked them which of the three they would be willing to donate to, along with an option for no selection (see @tbl-example for an example).
+After presenting respondents with a set of three randomly generated organizations, we asked them which of the three they would be willing to donate to, along with an option for no selection (see @tbl-example for an example).This choice indicated donation intention and reflected the option the respondent preferred most within that set.
 We then repeated the process eleven more times for a total of twelve randomized iterations of hypothetical combinations of attributes, resulting in 12,192 completed experimental tasks (12 iterations × 1,016 respondents).
-In order to estimate individual-specific differences using a multilevel model, each respondent had to complete multiple experimental tasks.
-Having the choice of hypothetical organization indicate donation intention and asking respondents to iteratively make this choice across twelve experimental tasks are both typical of conjoint analysis.
+This iterative process across twelve experimental tasks is typical of conjoint analysis and allows us to estimate individual-level differences using a multilevel model and determine both aggregate respondent preferences and the causal effect of each experimental feature on those preferences.
 
@@
 Relying on standard OLS regression can discard valuable information about (1) the relationships and covariance between the different combinations of feature levels offered to respondents, and (2) individual-specific differences in how respondents react to different feature levels [@JensenMarbleScheve:2021].
-Since it was impossible for every respondent to see every possible all 12,000 experimental tasks, multilevel modeling allows us to pool together information about respondents with similar characteristics facing similar sets of choices.
+Since it was impossible for every respondent to see every possible combination of all 12,000 experimental tasks, multilevel modeling allows us to pool together information about respondents with similar characteristics facing similar sets of choices.
 Moreover, using random respondent effects provides natural regularization and shrinkage for our estimates---experimental tasks that happened to appear more often due to chance will be accounted for and their frequency will not bias the overall causal effect.
@@
 
-[^stan]: We use Stan [@Stan-2-26-1 v2.26.1; @cmdstan-2-3-1 v2.3.1] through R [@rproject-4-3-3 v4.3.1] and {brms} [@Burkner:2017 v2.20.5] to estimate the model.
+[^stan]: We use Stan [@Stan-2-32-2 v2.32.2; @cmdstan-2-36 v2.36] through R [@rproject-4-4-2 v4.4.2] and {brms} [@Burkner:2017 v2.22] to estimate the model.
 We simulate 4 MCMC chains with 5,000 draws in each chain, 1,000 of which are used for warmup, resulting in 16,000 (4,000 × 4) draws per model parameter.
@@
 Given the conjoint design, we instead create a complete balanced grid of all 576 combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding) and use the model to calculate predicted probabilities of choice selection for each combination of possible treatment values.
-We then collapse this set of predicted probabilities into estimated marginal means (EMMs) for specific features of interested while marginalizing or averaging over all other predicted variables [@LeeperHoboltTilley:2020; @BremerBurgisser:2023].
+We then collapse this set of predicted probabilities into estimated marginal means (EMMs) for specific features of interest while marginalizing or averaging over all other predicted variables [@LeeperHoboltTilley:2020; @BremerBurgisser:2023].
 This marginalization process allows us to isolate the statistical effect of each feature in isolation.
@@
 We present the posterior distributions of the marginal means and AMCEs for each of our experimental conditions in @fig-all-results and provide posterior medians, credible intervals, and other model diagnostics in Tables A6 and A8.
-Because AMCEs are relative statements (i.e.
-contrasts between one feature level and a reference level), we try to use logical reference levels: for binary treatments like transparency and accountability, we calculate the difference between false and true levels; for ordered treatments like host country relationship, we calculate the differences between different levels of crackdown compared to no crackdown.
+Because AMCEs are relative statements (i.e., contrasts between one feature level and a reference level), we try to use logical reference levels: for binary treatments like transparency and accountability, we calculate the difference between false and true levels; for ordered treatments like host country relationship, we calculate the differences between different levels of crackdown compared to no crackdown.
 To avoid imposing an artificial order on other unordered treatment variables, we report both marginal means and AMCEs [@LeeperHoboltTilley:2020].
@@
 
-We provide visualizations of the full posterior distributions of each of the effects of interest, and we report two distributional summary statistics: (1) the posterior median, (2) credible intervals based on a 95% equal-tailed quantile interval, However, we are generally less concerned with the exact point estimates of our causal effects and instead focus on the direction and relative magnitude of their posterior distributions.
+We provide visualizations of the full posterior distributions of each of the effects of interest, and we report two distributional summary statistics: (1) the posterior median, (2) credible intervals based on a 95% equal-tailed quantile interval.
+However, we are generally less concerned with the exact point estimates of our causal effects and instead focus on the direction and relative magnitude of their posterior distributions.
 For inference, we calculate the probability of direction ($p_d$), or the probability that the posterior AMCE is strictly positive or negative---it is the proportion of the posterior AMCE that is the sign of the median.
@@
 
-To contextualize the magnitude of the causal effects for our hypotheses of interest, we begin our analysis with a brief overview of the effects of more foundational organizational characteristics: their organization name, their issue area, and their funding sources.
+To contextualize the magnitude of the causal effects for our hypotheses of interest, we begin our analysis with a brief overview of the effects of more foundational organizational characteristics: their organization name, issue area, and funding sources.
 Brand recognition appears to be a powerful heuristic for donor decision making.
@@
 The Red Cross brand name heuristic is the strongest of all the experimental treatments and features, signifying the organization's brand power and goodwill among potential donors.
+This finding also reflects previous research on the importance of nonprofit image management, which attributes the Red Cross's longevity to its powerful brand, among other factors [@Torres:2010].
 
@@
 
-Given the increasing hurdles faced by these nonprofits, how do individual donors in the U.S.
-feel about donating to legally besieged NGOs abroad?
-How does the effect of organizational-level factors such as financial transparency and accountability compare with more structural-level factors such as host country civic environments in individual donors' preferences to donate?
+Given the increasing hurdles faced by these nonprofits, how do individual donors in the US feel about donating to legally besieged NGOs abroad?
+How does the effect of organization-level factors such as financial transparency and accountability compare with more structural-level factors such as host country civic environments in individual donors' preferences to donate?
 Using a conjoint experiment of likely donors in the US, we find that organizational practices like financial transparency and accountability increase individuals' preferences to donate to NGOs.
@@
 These results have two important practical implications for NGO operations, fundraising, and survivability at a time when many INGOs are dealing with hostile host governments.
-First, while NGOs have little to no control over host government crackdowns over their organizations, they do have control over organizational practices transparency and accountability, and more importantly, public perception of these organizational characteristics.
+First, while NGOs have little to no control over host government crackdowns over their organizations, they do have control over organizational practices such as transparency and accountability, and more importantly, public perception of these organizational characteristics.
 As a result, they may need to rely entirely on improving individual donor perceptions of organizational transparency and accountability and emphasizing the need for private donor funds at a time of shrinking civic space.
@@
 In addition to voluntarily emphasizing or sharing this information with likely donors, nonprofits could also potentially brainstorm how to get more positive media exposure regarding these characteristics in restrictive civic environments.
-Moreover, we find that nonprofit transparency and accountability practices share the same causal effect, implying that donors might see these as interchangable concepts.
+Moreover, we find that nonprofit transparency and accountability practices share the same causal effect, implying that donors might see these as interchangeable concepts.
 
@@
 Others show that donors are loyal to brands whose values are congruent to their own [@SargeantFordHudson:2008].
-Our results thus have important implications on why nonprofits in hostile environments should focus on building brand awareness, as well as highlighting their values---both to engage likely and less likely donors.
+Our results thus have important implications on why nonprofits in hostile environments should focus on building brand awareness, as well as highlighting their values---to engage both likely and less likely donors.
 

### 2025-01-22 manuscript/appendix.qmd
Show more of TOC

@@
 short-title: 'Appendix for "Why Donors Donate"'
-date: "2025-01-20"
+date: "2025-01-22"
 author:
@@
 toc: true
-toc-depth: 3
+toc-depth: 4
 format: 

### 2025-01-22 manuscript/appendix.qmd
MEGA EDITS for word count issues

@@
 ---
-title: 'Appendix for "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy"'
-short-title: 'Appendix for "Why Donors Donate"'
+title: 'Appendix for "Navigating Hostility: The Effect of Nonprofit Transparency and Accountability on Donor Preferences in the Face of Shrinking Civic Space"'
+short-title: 'Appendix for "Navigating Hostility"'
 date: "2025-01-22"
@@
 toc: true
-toc-depth: 4
 format: 
@@
 
+# Model details
+
+We use Stan [@Stan-2-32-2 v2.32.2; @cmdstan-2-36 v2.36] through R [@rproject-4-4-2 v4.4.2] and {brms} [@Burkner:2017 v2.22] to estimate the model.
+We simulate 4 MCMC chains with 5,000 draws in each chain, 1,000 of which are used for warmup, resulting in 16,000 (4,000 × 4) draws per model parameter.
+We assess convergence with visual inspection, and all chains converge.
+
+Complete results from the model, along with posterior predictive checks, goodness-of-fit measures, and model diagnostics---as well as our code and data---are available at a companion statistical analysis compendium at `ANONYMIZED_URL`.
+
 # Model coefficients and estimated marginal means
@@
 
+   :   Stylistic
+
+   Timing
+
+   :   After results known
+
+   Original wording
+
+   :   Q5b: "Donors will show increased willingness to donate to NGOs that are criticized by the government/under government crackdown when they are also financially transparent"
+
+   Deviation description
+
+   :   We rephrased this as H~3~: "If NGOs face legal restrictions abroad *and* are financially transparent, then individual private donors will have a higher likelihood of supporting or donating to them."
+
+   Reader impact
+
+   :   This deviation has minimal impact on readers' interpretation of the findings—it is only rephrased to follow an "if… then…" formulation.
+
+6. Type
+
+   :   Hypotheses
+
+   Reason
+
    :   New knowledge
@@
 
-6. Type
+7. Type
 

### 2025-01-22 manuscript/manuscript.qmd
MEGA EDITS for word count issues

@@
 ---
-title: "Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy"
-short-title: "Why Donors Donate"
+title: "Navigating Hostility: The Effect of Nonprofit Transparency and Accountability on Donor Preferences in the Face of Shrinking Civic Space"
+short-title: "Navigating Hostility"
 date: "2025-01-22"
@@
 link-citations: true
-word-count: "9,300"
+word-count: "10,149"  # Subtract 77 for the final statements at the end
 ---
@@
 Data from the CIVICUS Civil Society Monitor shows that civil society groups face serious restrictions in more than 60% of countries---117 in total [@CIVICUSMonitor].
-This phenomenon of closing civic space has a large deterrent effect on both advocacy *and* service-delivery NGOs [@SpringmanMaleskyRight:2022].
+This phenomenon of closing civic space has a large deterrent effect on both advocacy and service-delivery NGOs [@SpringmanMaleskyRight:2022].
 
@@
 The amount of private foreign aid is not insignificant---from 2000--2010, private giving by US entities towards international causes doubled in real terms [@DesaiKharas:2018, 505].
-In 2018, this amounted to \$22.88 billion in individual donations earmarked specifically for international affairs INGOs [@GivingUSA:2019].
 This turn to private donors opens INGOs up to new dynamics in seeking out funds.
@@
 
-Existing research shows that organizational accountability [@Becker:2018; @Tremblay-BoirePrakash:2017]  and financial transparency [@HarrisNeely:2021; @SaxtonKuoHo:2012; @Vaccaro:2006; @VaccaroMadsen:2006] play an important role in motivating individual donors to donate to NGOs.
+Existing research shows that organizational accountability [@Becker:2018; @Tremblay-BoirePrakash:2017]  and financial transparency [@HarrisNeely:2021; @SaxtonKuoHo:2012; @VaccaroMadsen:2006] play an important role in motivating individual donors to donate to NGOs.
 We extend this literature by evaluating how these organization-level characteristics influence private donor behavior in an era of shrinking civic space.
@@
 Our findings make two main contributions.
-First, existing research on privately-provided foreign aid primarily looks at organizations like foundations and large donor NGOs, and not private individuals [@ButheMajordeMelloeSouza:2012; @Koch:2009; @DesaiKharas:2018], and studies that do examine individual giving behavior typically only examine wealthy individuals [@USTrust2014].
+First, existing research on privately-provided foreign aid primarily looks at organizations like foundations and large donor NGOs, and not private individuals [@ButheMajordeMelloeSouza:2012; @DesaiKharas:2018], and studies that do examine individual giving behavior typically only examine wealthy individuals [@USTrust2014].
 Our research expands work on private international philanthropy by exploring how non-elite individuals decide to donate to NGOs focused on international affairs.
@@
 
-A large body of work in philanthropy explores the factors that shape private donor motivation, including altruism, reputational benefits, and alignment with personal values [@BilodeauSlivinski:1997; @Wiepking:2010; @BekkersWiepking:2011].
+A large body of work in philanthropy explores the factors that shape private donor motivation, including altruism, reputational benefits, and alignment with personal values [@Wiepking:2010; @BekkersWiepking:2011].
 However, this research has overwhelmingly looked at individual donor behavior and motivation for giving to *domestic* organizations instead of international causes [@BekkersWiepking:2011; @Tremblay-BoirePrakash:2017].
@@
 
-But as INGOs became increasingly powerful actors in global policy circles, they faced a number of criticisms.
-Many organizations struggle with the conflicting imperatives of being large organizations that can operate efficiently at scale, while maintaining the grassroots contacts and consensus building that contributed to their early successes [@MitchellSchmitzBruno-vanVijfeijken:2020; @Jalali:2008; @Bano:2012; @Rahman:2006].
-As a result, many nonprofits sought to establish and enhance their accountability, responsiveness, and legitimacy [@edwardshulme; @GourevitchLake:2012].
+But as INGOs gained more power in global policy circles, they faced a number of criticisms.
+Many organizations struggle to balance efficient large-scale operations with the grassroots connections and consensus-building that drove their early success [@MitchellSchmitzBruno-vanVijfeijken:2020; @Jalali:2008].
+As a result, many INGOs worked to establish and enhance their accountability, responsiveness, and legitimacy [@edwardshulme; @GourevitchLake:2012].
 These actions were a result of many organization-level factors that can potentially impact nonprofit efficacy, including organizational and governance structure, leadership, strategy, transparency, and accountability.
@@
 
-However, organizational structure, leadership, and strategy (among other organization-level factors) are often not visible to the average individual (non-elite) donor, especially in the context of international NGOs.
-Therefore, in this paper, we focus on the two organization-level factors that are most visible to the average donor---financial transparency and accountability.
+However, organizational structure, leadership, and strategy (among other organization-level factors) are often not visible to the average individual donor.
+We therefore focus on two organization-level factors that are most visible to the average donor---financial transparency and accountability.
 Assessing an NGO's deservingness and efficiency demands substantial time and resources, which individual donors typically lack [@CrosonShang:2011; @Tremblay-BoirePrakash:2017].
-As such, these donors rely on various easily available cues and heuristics when deciding to support an NGO.
+As such, donors rely on cues and heuristics when deciding to support an NGO.
 Compared to other organization-level factors, news about financial mismanagement and lack of transparency and accountability may be more easily available.
 Many nonprofit scandals involve some form of financial wrongdoing [@PrakashGugerty:2010b].
-Notable examples include the Oil-for-Food program, initiated by the United Nations in 1996 to allow Iraq to sell enough oil to pay for food and other necessities for its population, which had been suffering from sanctions imposed on Iraq since the First Gulf War.
-However, in 2004, the program's widespread financial fraud, limited distribution of food by nonprofits, and lack of accountability was widely publicized.
-Numerous other such cases---covered in @GibelmanGelman:2001 and @GibelmanGelman:2004---show how financial mismanagement, embezzlement, fraud, and lack of accountability can decrease public trust in and donations to these nonprofits.
+Notable examples include the United Nations' Oil-for-Food program, aimed at alleviated Iraq's sanctions-induced hardships in the 1990s, which was marred by revelations of widespred financial fraud, limited food distribution, and lack of accountability in 2004.
+Numerous other cases [see @GibelmanGelman:2001 and @GibelmanGelman:2004] demonstrate how financial mismanagement, embezzlement, fraud, and lack of accountability can decrease public trust and reduce donations to nonprofits.
 Globally, around 5% of revenue is lost annually due to fraud [@ACFE:2021].
 Misappropriation of assets and embezzlement schemes are among the most common forms of financial fraud [@LamotheTer-MkrtchyanRuddle:2023].
-To save time and present easily accessible information, watch dogs such as Charity Navigator and Better Business Bureau Wise Giving Alliance often rate charities on financial and accountability metrics and present this information in a quick, user-friendly format.
+To save time and present easily accessible information, watchdogs such as Charity Navigator often rate charities on financial and accountability metrics and present this information in a quick, user-friendly format.
 
@@
 Research shows that transparency is associated with greater donations, lower debt, and better governance [@HarrisNeely:2021; @HarrisPetrovitsYetman:2023; @SaxtonKuoHo:2012].
-It can also enhance donor trust and confidence in organizations [@Vaccaro:2006; @VaccaroMadsen:2006].
+It can also enhance donor trust and confidence in organizations [@VaccaroMadsen:2006].
 
@@
 
-Accountability is another factor that can impact donor preferences.
+Accountability also influences donor preferences.
 Accountability is the willingness of the organization to explain its action to shareholders [@CharityNavigator:2020] and build and manage relationships with stakeholders or client populations and donor groups.
-It also encompasses how well an organization's mission is aligned with its resources [@Sloan:2009].
-As NGOs gain more prominence, stakeholders, or "any group or individual who can affect or is affected by the achievement of an organization's objectives," [@MitchellAgleWood:1997, 854] want to be assured that their donations or support or support of an organization will make a real difference.
-More effective accountability can encourage NGOs to become more closely aligned with community practices, provide greater assurances to stakeholders, and help expand their support [@Murtaza:2012].
+It also reflects how well an organization's mission is aligned with its resources [@Sloan:2009].
+As NGOs gain more prominence, stakeholders seek assurance that their donations will make a real difference---effective accountability can encourage NGOs to become more closely aligned with community practices and help expand stakeholder support [@Murtaza:2012].
 Problems with accountability usually occur when organizations ignore their stakeholders' preferences and use judgements or actions which may not align with one or more of their constituent groups [@McCambridge:2019].
@@
 A global cascade of anti-NGO laws in recent decades has created barriers to entry, funding, and advocacy for civic organizations [@GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022; @Heiss:2017; @DupuyRonPrakash:2016].
-The use of such anti-NGO laws, also referred to as administrative crackdown [@Chaudhry:2022], is different from regulations that simply set standards for appropriate organizational behavior and set penalties for violations [@North:1990].[^violent-crackdown] However, the anti-NGO laws discussed in this paper, such as the Russian Foreign Agent law, are not grounded in international legal principles and do not give nonprofits the freedom of association or access to resources [@Voule:2023; @Robinson:2024].
+The use of such anti-NGO laws, also referred to as administrative crackdown [@Chaudhry:2022], is different from regulations that simply set standards for appropriate organizational behavior and set penalties for violations [@North:1990].[^violent-crackdown] However, the anti-NGO laws discussed in this paper, such as the Russian Foreign Agent law, are not grounded in international legal principles and do not give nonprofits the freedom of association or access to resources [@Robinson:2024].
 As a result, NGOs must spend more time, effort, and resources to ensure their survival---at the expense of pursuing their missions.
@@
 Some NGOs have adapted to these legal crackdowns by recreating their organizations and changing their mission to avoid directly confronting the government.
-Analyzing the impact of anti-NGO laws in Bangladesh and Zambia, scholars have found that when faced with government restrictions, NGOs with broad missions restricted their strategies to service work and abandoned their advocacy work.
-Those that continued to engage in transnational advocacy changed the targets of their advocacy, the issues they focused on, and the language they used [@FransenDupuyHinfelaar:2021].
+Research on anti-NGO laws in Bangladesh and Zambia shows that NGOs with broad missions shifted from advocacy to service work, while those focused mainly on transnational advocacy altered their targets, issues, and language [@FransenDupuyHinfelaar:2021].
 Similarly, in Russia, many NGOs working with foreign partners and lobbying the central government no longer consider it an effective strategy [@SundstromHenrySperling:2022].
-Overall, fewer groups may end up focusing on contentious causes, instead focusing on issues that are less likely to invoke the ire of the host government, including in areas such as health and education.
-
-The changes in civic environments impacting NGO activity have already influenced official donor responses.
-Scholars have found that while multilateral donors do not reduce aid in response to anti-NGO laws, these laws are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018].
+Overall, fewer organizations work on contentious causes, instead focusing on safer issues like health and education.
+These changes in the civil society legal environment have influenced official donor responses.
+While multilateral donors do not reduce aid in response to anti-NGO laws, these laws are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018].
 Further, advocacy-oriented donors---i.e., those that fund democracy and civil society promotion activities---reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022].
@@
 
-It is possible to study the effects of both organizational and structural heuristics on donor decision making individually, but disentangling the interaction of the two heuristics from individual donor characteristics adds complex dimensionality and makes more standard experimental work difficult, costly, and statistically fraught.
-To address this, we use conjoint analysis to simultaneously test individual donor preferences in the face of both organizational and structural heuristics.
-Conjoint analysis is generally applicable whenever individuals face complex, multi-dimensional tradeoffs that make it difficult (or even impossible) to explicitly elicit preferences.
-Conjoint designs have been used extensively in political science to study complex preferences for elections, laws, public policy, and public opinion [@HainmuellerHopkinsYamamoto:2014; @Mummolo:2016; @KertzerRenshonYarhi-Milo:2021; @BansakHainmuellerHopkins:2021; @BremerBurgisser:2023], and conjoint experiments are becoming more common in nonprofit studies, particularly for studying individual donor behavior [@SilviaChildWitesman:2023; @HirschmannMoritzBlock:2022; @BachkeAlfnesWik:2014; @Kottasz:2004].
-@KnudsenJohannesson:2018 argue that research related to respondent opinions requires conjoint analysis because it accounts for the masking effects of factors as well as the complexity of a respondent's judgment of credibility.
-Because we also want to capture the complexity of a respondent's judgment of philanthropic preferences, we use a conjoint experiment to measure the causal effect of both organizational and structural heuristics on individuals' preferences for donating to international NGOs.
-
-A conjoint research design also allows us to calculate treatment effects even if respondents do not see every combination of organization attributes, and correspondingly provides a substantial increase in statistical power.
+It is possible to study the effects of both organizational and structural heuristics on donor preferences individually, but disentangling the interaction of these heuristics adds complex dimensionality and makes more standard experimental work costly and statistically fraught.
+To address this, we use a conjoint experiment to measure the causal effect of both organizational and structural heuristics on individuals' preferences for donating to international NGOs.
+[@HainmuellerHopkinsYamamoto:2014].
+Conjoint experiments are increasingly common in nonprofit studies, particularly for studying individual donor behavior [@SilviaChildWitesman:2023; @HirschmannMoritzBlock:2022; @BachkeAlfnesWik:2014].
+
+A conjoint research design also allows us to estimate treatment effects even if respondents do not see every combination of organization attributes, and correspondingly provides a substantial increase in statistical power.
 In standard factorial experimental designs, participants would ordinarily need to be shown all possible combinations of experimental attributes.
@@
 
-[^prereg]: For narrative purposes, we do not explore all our preregistered hypotheses in this study---many of them are nested inside each other (e.g., the effect of branding and issue area and transparency and crackdown simultaneously).
-We instead focus here on the simplest, non-nested hypotheses.
+[^prereg]: For clarity, we focus on our simplest, non-nested hypotheses, omitting many preregistered ones that overlap (e.g., the effect of branding and issue area and transparency and crackdown simultaneously).
 Following @WillrothAtherton:2024, we outline all the deviations from our preregistration protocol in the appendix.
@@
 Due to the initial screening question that limited participants to those with an interest in charitable activity, respondents are far more likely to have donated, volunteered, or voted in the past year than population CPS estimates.
-Our reported causal effects are therefore not representative of the entire population and instead are only valid for people interested in charitable giving.
+Our reported causal effects are therefore not representative of the entire population and instead are generalizable to people interested in charitable giving.
 
@@
 
-[^real-names]: We used real organization names rather than hypothetical, fictionalized names to allow the experimental task to better mirror reality [@McDonald:2020] and to reduce respondent cognitive burden when reflecting on organization characteristics [@MajnemerMeibauer:2022].
-
-After presenting respondents with a set of three randomly generated organizations, we asked them which of the three they would be willing to donate to, along with an option for no selection (see @tbl-example for an example).This choice indicated donation intention and reflected the option the respondent preferred most within that set.
+[^real-names]: We used real organization names rather than fictionalized names to allow the experimental task to better mirror reality [@McDonald:2020] and to reduce respondent cognitive burden when reflecting on organization characteristics [@MajnemerMeibauer:2022].
+
+After presenting respondents with a set of three randomly generated organizations, we asked them which of the three they would be willing to donate to, along with an option for no selection (see @tbl-example for an example).
+This choice indicated donation intention and reflected the option the respondent preferred most within that set.
 We then repeated the process eleven more times for a total of twelve randomized iterations of hypothetical combinations of attributes, resulting in 12,192 completed experimental tasks (12 iterations × 1,016 respondents).
@@
 
-We analyze the results using a multilevel Bayesian multinomial model.[^stan] Our experimental data has a natural hierarchical structure, with 3 questions nested inside 12 separate experimental tasks, nested inside each of the 1,016 respondents, which lends itself to multilevel modeling.
-Relying on standard OLS regression can discard valuable information about (1) the relationships and covariance between the different combinations of feature levels offered to respondents, and (2) individual-specific differences in how respondents react to different feature levels [@JensenMarbleScheve:2021].
+We analyze the results using a multilevel Bayesian multinomial model (see the appendix for complete model details).
+Our experimental data has a natural hierarchical structure, with 3 questions nested inside 12 separate experimental tasks, nested inside each of the 1,016 respondents, which lends itself to multilevel modeling [@JensenMarbleScheve:2021].
 Since it was impossible for every respondent to see every possible combination of all 12,000 experimental tasks, multilevel modeling allows us to pool together information about respondents with similar characteristics facing similar sets of choices.
@@
 We define our model and priors in @eq-model.
-
-[^stan]: We use Stan [@Stan-2-32-2 v2.32.2; @cmdstan-2-36 v2.36] through R [@rproject-4-4-2 v4.4.2] and {brms} [@Burkner:2017 v2.22] to estimate the model.
-We simulate 4 MCMC chains with 5,000 draws in each chain, 1,000 of which are used for warmup, resulting in 16,000 (4,000 × 4) draws per model parameter.
-We assess convergence with visual inspection, and all chains converge.
-Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and model diagnostics---as well as our code and data---are available `ANONYMIZED_URL`.
 
@@
 This marginalization process allows us to isolate the statistical effect of each feature in isolation.
-We include a complete table of model results in Table A4, along with a brief illustration of converting from regression coefficients to estimated marginal means.
+We include a complete table of model results in Table A5, along with a brief illustration of converting from regression coefficients to estimated marginal means.
 
@@
 
-We present the posterior distributions of the marginal means and AMCEs for each of our experimental conditions in @fig-all-results and provide posterior medians, credible intervals, and other model diagnostics in Tables A6 and A8.
+We present the posterior distributions of the marginal means and AMCEs for each of our experimental conditions in @fig-all-results and provide posterior medians, credible intervals, and other model diagnostics in Tables A7 and A9.
 Because AMCEs are relative statements (i.e., contrasts between one feature level and a reference level), we try to use logical reference levels: for binary treatments like transparency and accountability, we calculate the difference between false and true levels; for ordered treatments like host country relationship, we calculate the differences between different levels of crackdown compared to no crackdown.
@@
 There is also some evidence that these two effects are equivalent and perhaps interchangeable.
-@fig-transp-acc (and Table A7) shows the posterior marginal means for all four combinations of possible levels of transparency and accountability.
+@fig-transp-acc (and Table A8) shows the posterior marginal means for all four combinations of possible levels of transparency and accountability.
 When respondents see both as "no" simultaneously, the estimated marginal mean is lower than any of the individual treatments in @fig-all-results, at `r mms_ta$transparency_no_accountability_no$pct` (`r mms_ta$transparency_no_accountability_no$nice_ci`), or 9 percentage points lower than the baseline probability of 25%.
@@
 For our third hypothesis, we posit that these heuristics also interact with each other.
-This is confirmed in @fig-transp-crackdown (and Table A8)---the estimated posterior marginal means for different relationships with host governments move in the same direction regardless of whether an organization engages in transparency practices:[^transp-only] organizations with no conflict are most preferred, while organizations facing restrictions are least preferred.
-Transparency practices in the presence of restrictions seem to have two general effects.
+This is confirmed in @fig-transp-crackdown (and Table A9)---the estimated posterior marginal means for different relationships with host governments move in the same direction regardless of whether an organization engages in transparency practices:[^transp-only] organizations with no conflict are most preferred, while organizations facing restrictions are least preferred.
+Transparency practices in the presence of restrictions have two general effects.
 First, engaging in transparency offsets most of the negative effect of facing hostile civic environments.
@@
 On its own, as seen in @fig-all-results, engaging in transparency causes a `r amce$transparency_yes$pp_abs` percentage point increase in the probability of a respondent selecting an organization.
-The right panel of @fig-transp-crackdown (and Table A8) shows how the causal effect of transparency changes across different types of government relationships.
+The right panel of @fig-transp-crackdown (and Table A9) shows how the causal effect of transparency changes across different types of government relationships.
 These AMCEs represent the difference in the estimated posterior marginal means of the two levels of transparency in the left panel.
@@
 Given the near interchangeability of the two treatments, the interaction between accountability and crackdown is nearly identical.
-We include both transparency and accountability in Table A6.
+We include both transparency and accountability in Table A8.
 

### 2025-01-22 index.qmd
Change title

--- 2023-08-26 index.qmd
@@
 ---
-title: "Why Donors Donate"
+title: "Navigating Hostility"
+subtitle: "The Effect of Nonprofit Transparency and Accountability on Donor Preferences in the Face of Shrinking Civic Space"
 author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
@@
 
-Abstract goes here
+Governments across the world have increasingly used laws to restrict the work of nonprofits, which has led to a reduction in public or official foreign aid directed towards these groups.
+Many international nonprofits, in response, have turned to individual donors to offset the loss of traditional funding.
+What are individual donors' preferences regarding donating to legally besieged nonprofits abroad?
+We conducted a conjoint experiment on a nationally representative sample of likely donors in the US and found that learning about host government criticism and legal restrictions on nonprofits decreases individuals' preferences to donate to them.
+However, organizational features such as financial transparency and accountability can protect against this dampening effect.
+Our results have important implications both for understanding private international philanthropy and how nonprofits can better frame their fundraising appeals at a time when they are facing restrictive civic spaces and hostile governments abroad.
 

### 2025-01-22 R/funs_misc_analysis.R
Use stats:: prefix to stop warnings
Looks like I stumbled on this in May 2023 😂 https://github.com/ropensci/targets/discussions/1075

@@ -212,7 +212,7 @@ calc_cps_diffs <- function(participant_summary, cps_props) {
     model <- brm(
       bf(n_yes | trials(n_total) ~ 1),
       data = df,
-      family = binomial(link = "identity"),
+      family = stats::binomial(link = "identity"),
       prior = c(prior(beta(1, 1), class = "Intercept", lb = 0, ub = 1)),
       chains = 4, warmup = 1000, iter = 2000, seed = BAYES_SEED,
       refresh = 0,

### 2025-01-22 R/funs_data.R
Remove data from OSF

@@ -1,14 +1,3 @@
-get_from_osf <- function(osf_url, out_dir) {
-  library(osfr)
-  
-  get_osf <- osf_retrieve_file(osf_url) %>%
-    osf_download(path = out_dir,
-      conflicts = "overwrite",
-      progress = TRUE)
-  
-  return(get_osf$local_path)
-}
-
 make_clean_data <- function(path) {
   # Load original pre-anonymized Qualtrics data
   data_raw <- read_csv(path, guess_max = 1500, show_col_types = FALSE)

### 2025-01-22 README.qmd
Change title
Update readme

@@
 ---
-format: gfm
+title: "Navigating Hostility: The Effect of Nonprofit Transparency and Accountability on Donor Preferences in the Face of Shrinking Civic Space"
+format: 
+  gfm: 
+    wrap: preserve
+    toc: true
+  typst:
+    toc: true
+    toc-title: " "
+    include-in-header: README_stuff/better-layout.typ
+    author:
+    - name: Suparna Chaudhry
+      affiliation: Lewis and Clark College
+      orcid: 0000-0003-3506-7590
+      url: https://www.suparnachaudhry.com/
+      email: schaudhry@lclark.edu
+    - name: Marc Dotson
+      affiliation: Utah State University
+      orcid: 0000-0001-7846-3660
+      url: https://occasionaldivergences.com/
+      email: marc.dotson@usu.edu
+    - name: Andrew Heiss
+      affiliation: Georgia State University
+      orcid: 0000-0002-3948-3914
+      url: https://www.andrewheiss.com
+      email: aheiss@gsu.edu
 ---
@@
 library(emoji)
+
+manuscript_target <- targets::tar_read(manuscript)
+
+yaml_metadata <- rmarkdown::yaml_front_matter(here::here("manuscript", "manuscript.qmd"))
+title <- yaml_metadata$title
+abstract <- yaml_metadata$abstract
+
+if (knitr::pandoc_to() == "typst") {
+  # typst doesn't support emoji as of 0.11.0, so we include SVG versions from 
+  # Noto Emoji (https://github.com/googlefonts/noto-emoji) instead
+  emoji_out <- "![](README_stuff/noto-emoji-svgs/emoji_u1f910.svg){height=1em}![](README_stuff/noto-emoji-svgs/emoji_u1f325.svg){height=1em}![](README_stuff/noto-emoji-svgs/emoji_u1f6b6.svg){height=1em}"
+} else {
+  emoji_out <- emoji_glue(":zipper_mouth_face::sun_behind_large_cloud::person_walking:")
+}
 ```
 
-# Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy
+::: {.content-visible when-format="markdown"}
+
+---
 
@@
 
+---
+
 <!-- badges: start -->
+[![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fhu6a5-blue)](https://doi.org/10.31235/osf.io/hu6a5) [![OSF DOI](https://img.shields.io/badge/OSF%20project-10.17605%2FOSF.IO%2FR59XZ-blue)](https://doi.org/10.17605/OSF.IO/R59XZ) [![Code DOI](https://img.shields.io/badge/Code-10.5281%2Fzenodo.14220206-blue)](https://doi.org/10.5281/zenodo.14220206)
 <!-- badges: end -->
+
+:::
 
@@
 
-Non-governmental organizations (NGOs) are a core component of global governance.
-Over the last two decades, however, many host governments have cracked down on NGOs using a series of laws that adversely affect the availability and use of traditional NGO funding.
-In response to this dramatic shift in the funding landscape, international NGOs have increasingly turned to individual donors to offset the loss funding.
-Prior research on NGO fundraising has examined how financial transparency and organizational accountability influence individual donor behavior.
-How do these elements of private donor decision-making interact with structural-level factors such as worsening host country civic environments when deciding to donate?
-Using a conjoint experiment with likely donors in the US, we find that transparency and accountability can protect against the dampening effect of host government crackdown and criticism of NGOs.
-Our results have important implications for how NGOs can adapt to worsening civic environments.
+`r abstract`
 
-### `r emoji_glue(":zipper_mouth_face::sun_behind_large_cloud::person_walking:")`: Note on "silent skywalk" project name
+## `r emoji_out`: Note on "silent skywalk" project name
 

### 2025-01-22 README.qmd
Update Zenodo DOI

@@
 <!-- badges: start -->
-[![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fhu6a5-blue)](https://doi.org/10.31235/osf.io/hu6a5) [![OSF DOI](https://img.shields.io/badge/OSF%20project-10.17605%2FOSF.IO%2FR59XZ-blue)](https://doi.org/10.17605/OSF.IO/R59XZ) [![Code DOI](https://img.shields.io/badge/Code-10.5281%2Fzenodo.14220206-blue)](https://doi.org/10.5281/zenodo.14220206)
+[![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fhu6a5-blue)](https://doi.org/10.31235/osf.io/hu6a5) [![OSF DOI](https://img.shields.io/badge/OSF%20project-10.17605%2FOSF.IO%2FR59XZ-blue)](https://doi.org/10.17605/OSF.IO/R59XZ) [![Code DOI](https://img.shields.io/badge/Code-10.5281%2Fzenodo.14721277-blue)](https://doi.org/10.5281/zenodo.14721277)
 <!-- badges: end -->

### 2025-04-04 notebook/model-definitions.qmd
Explain/illustrate marginal means as coefs
Clean up some notebook stuff

@@
 
-TODO: Formal math for the models
+## Formal math
+
+$$
+\begin{aligned}
+&\ \textbf{Multinomial probability of selection of choice}_i \textbf{ in respondent}_j \\
+\text{Choice}_{i_j} \sim&\ \operatorname{Categorical}(\{\mu_{1,i_j}, \mu_{2,i_j}, \mu_{3,i_j}\}) \\[10pt]
+&\ \textbf{Model for probability of each option} \\
+\{\mu_{1,i_j}, \mu_{2,i_j}, \mu_{3,i_j}\} =&\ (\beta_0 + b_{0_j}) + \beta_1 \text{Organization[Greenpeace]}_{i_j} + \beta_2 \text{Organization[Oxfam]}_{i_j} + \\
+&\ \beta_3 \text{Organization[Red Cross]}_{i_j} + \beta_4 \text{Issue[Environment]}_{i_j} + \\
+&\ \beta_5 \text{Issue[Human rights]}_{i_j} + \beta_6 \text{Issue[Refugee relief]}_{i_j} + \\
+&\ \beta_7 \text{Transparency[Yes]}_{i_j} + \beta_8 \text{Accountability[Yes]}_{i_j} + \\
+&\ \beta_9 \text{Funding[Few wealthy donors]}_{i_j} + \beta_{10} \text{Funding[Government grants]}_{i_j} + \\
+&\ \beta_{11} \text{Government relationship[Criticized]}_{i_j} + \\
+&\ \beta_{12} \text{Government relationship[Under crackdown]}_{i_j} \\[5pt]
+b_{0_j} \sim&\ \mathcal{N}(0, \sigma_0) \qquad\quad\quad \text{Respondent-specific offsets from global probability} \\[10pt]
+&\ \textbf{Priors} \\
+\beta_{0 \dots 12} \sim&\ \mathcal{N} (0, 3) \qquad\qquad\ \ \text{Prior for choice-level coefficients} \\
+\sigma_0 \sim&\ \operatorname{Exponential}(1) \quad \text{Prior for between-respondent variability}
+\end{aligned}
+$$
+
+## R code
+
+```{r}
+#| eval: false
+#| echo: true
+#| code-fold: false
+#| file: "../R/funs_models.R"
+#| filename: "R/funs_models.R"
+```

### 2025-04-04 notebook/model-diagnostics.qmd
Clean up some notebook stuff

@@
 These are histograms of the ranks of the parameter draws across the four chains.
-If the chains are exploring the same space efficiently, the histograms should be similar and overlapping and no one chain should have a specific rank for a long time [@McElreath:2020a, 284].
+If the chains are exploring the same space efficiently, the histograms should be similar and overlapping and no one chain should have a specific rank for a long time [@McElreath:2020, 284].
 

### 2025-04-04 docker/misc/Rprofile.R
Put all Docker stuff here instead of maintaining two repos

@@ -1,0 +1,5 @@
+# Activate the silent-skywalk project when opening RStudio Server
+setHook("rstudio.sessionInit", function(newSession) {
+  if (newSession && is.null(rstudioapi::getActiveProject()))
+    rstudioapi::openProject("silent-skywalk")
+}, action = "append")

### 2025-04-04 docker/misc/determine-sysreqs.R

@@ -1,0 +1,29 @@
+# Read the renv.lock file and use {pak} to determine which system dependencies 
+# Docker needs to install before installing R packages
+
+if (!require("pacman")) {
+  install.packages("pacman")
+}
+
+pacman::p_load(
+  "dockerfiler",
+  "renv",
+  "pak",
+  "here",
+  install = TRUE
+)
+
+renv_file <- here::here("silent-skywalk/renv.lock")
+
+# This takes a while...
+dock <- dockerfiler::dock_from_renv(
+  renv_file,
+  FROM = "rocker/tidyverse", AS = "renv-base",
+  repos = c(
+    CRAN = "https://cran.rstudio.com/",
+    Stan = "https://stan-dev.r-universe.dev",
+    tinytable = "https://vincentarelbundock.r-universe.dev"
+  ),
+  use_pak = TRUE
+)
+dock

### 2025-04-05 _targets_packages.R
Add other fonts + newer targets packages

@@ -1,14 +1,12 @@
 # Generated by targets::tar_renv(): do not edit by hand
-library(bs4Dash)
-library(clustermq)
-library(future)
+library(bslib)
+library(crew)
 library(gt)
 library(markdown)
-library(pingr)
-library(qs)
+library(qs2)
 library(rstudioapi)
 library(shiny)
-library(shinybusy)
 library(shinyWidgets)
+library(shinybusy)
 library(tidyverse)
 library(visNetwork)

### 2025-04-07 manuscript/appendix.qmd
Stop applying tt_linebreak() twice (oops!)

@@
   mutate(contrast = ifelse(is.na(contrast), "*(Reference)*", contrast)) %>% 
-  mutate(across(c(nice, diff_nice), ~tt_linebreak(.))) %>% 
   relocate(feat_level) %>%

### 2025-04-12 README.qmd
Add replication instructions

@@
 
+> Suparna Chaudhry, Marc Dotson, and Andrew Heiss, “`r title`,” *Nonprofit and Voluntary Sector Quarterly* (forthcoming).
+
+---
+
 ## Abstract
@@
 `r abstract`
+
+## Replication
+
+To maximize replicability, we wrote our manuscript using [Quarto](https://quarto.org/), which allowed us to mix computational figures, text, and tables with the actual prose of the manuscript.
+This means that there's no need to rely on comments within code to identify the location of each appropriate result in the manuscript—all results are programmatically included when rendering the document.
+
+We use the [{renv} package](https://rstudio.github.io/renv/articles/renv.html) to create a stable version-specific library of R packages, and we use the [{targets} package](https://docs.ropensci.org/targets/index.html) to manage all the file dependencies and run the analysis.
+{targets} is especially helpful with long-running objects like the main models, which take ≈40 minutes to run—as long as upstream dependencies don't change, the models only need to run once, and can be loaded from {targets}'s data store thereafter.
+
+Because it can often be difficult to set up and configure version-specific libraries of R packages and install specific versions of Stan, we provide three methods for replicating our analysis:
+
+1.
+**Running a Docker container built and orchestrated with Docker Compose.** This builds a complete computational environment, including non-R software like Quarto, pandoc, LaTeX, dvisvgm, fonts, and other auxiliary elements.
+2.
+**Restoring a project-specific library of all required R packages on your computer with {renv}.** This is the next recommended approach, since {renv} will install package versions as of April 2025 when we ran this code prior to publication.
+However, you're responsible for installing all the non-R elements, like Quarto and LaTeX (detailed instructions are included below).
+3.
+**Installing the most current versions of all required R packages on your computer systemwide.** This is the least recommended approach, since the included script will grab the latest version of all R packages from CRAN and install them in your system library.
+As with method 2, you're still responsible for installing all the non-R elements on your own.
+
+The original pre-cleaned data for the analysis is accessible in `silent-skywalk/data/raw_data`.
+
+The complete {targets} pipeline generates two output artifacts:
+
+- **Manuscript**: HTML and PDF versions of the manuscript and appendix, located at `silent-skywalk/manuscript/output/` (or at [`http://localhost:8888/analysis/paper.html`](http://localhost:8888/analysis/paper.html) if you run the pipeline with Docker Compose).
+- **Analysis notebook**: A static website containing more complete details about the data, hypotheses, statistical methods, model diagnostics, and other information, located at `silent-skywalk/_site` (or at [`http://localhost:8888`](http://localhost:8888) if you run the pipeline with Docker Compose).
+
+### Method 1: Docker Compose
+
+The entire analysis can be run in a Docker container based on R 4.4.2, with all packages locked at specific versions defined in `renv.lock`.
+
+Here's how to do this:
+
+1. Install Docker Desktop on your computer (instructions for [macOS](https://docs.docker.com/desktop/install/mac-install/) or [Windows](https://docs.docker.com/desktop/install/windows-install/)).
+
+2. Make sure Docker is running.
+
+3. In the Docker Desktop settings, make sure you allocate at least 8 CPUs and 16 GB of RAM.
+
+   ![Docker Desktop resource settings](README_stuff/img/docker-resources.png){width=90%}
+
+4. Build the analysis with Docker Compose. There are two general approaches:
+
+   - **Using Visual Studio Code or Positron *(recommended)***: If you [download Visual Studio Code](https://code.visualstudio.com/) or [Positron](https://github.com/posit-dev/positron) and [its Docker extension](https://code.visualstudio.com/docs/containers/overview), you can right click on the `docker-compose-prebuilt.yml` file in the File Explorer sidebar and select "Compose Up".
+
+     ![Docker Compose contextual menu in the Visual Studio Code sidebar](README_stuff/img/docker-compose-sidebar.png){width=60%}
+
+   - **Using the terminal**: Using a terminal, navigate to this replication code directory and run this:
+
+     ```sh
+     docker compose -f docker-compose.yml up -d
+     ```
+
+5. Wait for the container to build. It takes ≈15 minutes to build the complete container (but only the first time you run this; subsequent runs of `docker compose` should be instant).
+
+6.
+Visit [`http://localhost:8787`](http://localhost:8787) and open an RStudio session inside the newly-built container in your browser.
+Any edits you make here will also be reflected on your local computer.
+
+7.
+Run the {targets} pipeline by running `targets::tar_make()` in the R console.
+Wait again; it takes ≈40 minutes to clean the data, run the model, build the statistical notebook website, and render the manuscript in multiple formats.
+Subsequent runs of the pipeline should be fairly instant, though.
+
+   ::: {.callout-tip}
+   RStudio Server automatically times out after 30ish minutes of inactivity, so you might see an ominous-looking error after running the model target:
+
+   ```default
+   Error in `get_result(output = out, options)`:
+   ! callr subprocess failed: could not start R, exited with non-zero status, has crashed or was killed
+   ℹ See `$stdout` and `$stderr` for standard output and error.
+   ```
+
+   That's a sign that the R session quit due to inactivity, since the model takes a while to run.
+
+   To fix this, refresh the browser page to reload RStudio Server and run `tar_make()` again to resume the pipeline. It won't have to run the model again—it'll continue from wherever it got stuck.
+
+   Alternatively, instead of running `tar_make()` to build the whole pipeline all in one go, you can run `tar_make(m_treatment_only)` to run the pipepline up through the model, and then run `tar_make()` to run the rest of the pipeline when it's done.
+
+   Thanks to the magic of {targets} this issue only happens the first time you run the pipeline—subsequent pipeline runs will be instantaneous.
+   :::
+
+8.
+When the pipeline is all the way done, visit [`http://localhost:8888`](http://localhost:8888) to see the analysis notebook and finished manuscript (at [`http://localhost:8888/analysis/paper.html`](http://localhost:8888/analysis/paper.html)).
+
+   You can also see these outputs on your computer: the analysis notebook is at `_site` and the manuscript and appendix files are at `manuscript/output/`.
+
+### Method 2: Run locally with {renv} and project-specific packages
+
+It's also possible to not use Docker and instead run everything locally in a special R package library that is separate from your system library.
+
+0. Install these preliminary things:
+
+   - **R 4.4.2** (or later) and **RStudio**.
+
+   - **Quarto 1.6.1** (or later). As of this writing, the current stable version of Quarto is 1.6.
+
+   - **A C++ compiler and GNU Make**.
+Complete instructions for macOS, Windows, and Linux [are available at CmdStan's documentation](https://mc-stan.org/docs/cmdstan-guide/installation.html#cpp-toolchain).
+In short, do this:
+     - **macOS**: Run this terminal command and follow the dialog that pops up after to install macOS's Command Line Tools:
+
+       ```sh
+       xcode-select --install
+       ```
+
+     - **Windows**: [Download and install Rtools from CRAN](https://cran.r-project.org/bin/windows/Rtools/rtools44/rtools.html)
+
+     - **Linux**: Run this terminal command (depending on your distribution; this assumes Ubuntu/Debian):
+
+       ```sh
+       sudo apt install g++ make
+       ```
+
+   - (*macOS only*): [Download and install XQuartz](https://www.xquartz.org/)
+
+   - **Fonts**: Download and install these fonts (or install them from `misc/fonts` in this repository). On Windows, install these as an administrator so that R and Quarto have access to them.
+
+     - [Libre Franklin](https://fonts.google.com/specimen/Libre+Franklin)
+     - [Linux Libertine](https://libertine-fonts.org/)
+     - [Libertinus Math](https://github.com/alerque/libertinus/releases/tag/v7.040)
+
+1. Open `silent-skywalk.Rproj` to open a new RStudio project.
+
+2. Run `renv::restore()` to install all the packages.
+
+3. Run `cmdstanr::install_cmdstan()` to install [CmdStan](https://mc-stan.org/users/interfaces/cmdstan).
+
+4. Run `tinytex::install_tinytex()` to install a mimimal LaTeX installation if you don't have one installed already.
+
+   TinyTex should install any additional LaTeX packages that it needs when it comes across anything that's missing.
+You can help it along by installing those non-core packages first with this R command:
+
+   ```r
+   tinytex::tlmgr_install(
+    # tikz things
+     c("dvisvgm", "adjustbox", "collectbox", "currfile", "filemod", "gincltex",
+       "standalone", "fp", "pgf", "grfext", "libertine", "libertinust1math", 
+    # template things
+       "nowidow", "tocloft", "orcidlink", "abstract", "titling", "tabularray",
+       "ninecolors", "enumitem", "textcase", "titlesec", "footmisc", "caption",
+       "pdflscape", "ulem", "multirow", "wrapfig", "colortbl", "tabu", 
+       "threeparttable", "threeparttablex", "environ", "makecell", "sidenotes", 
+       "marginnote", "changepage", "siunitx", "mathtools", "setspace", "ragged2e", 
+       "fancyhdr", "pdftex", "preprint", "endnotes", "tikzfill", "tcolorbox", 
+       "pdfcol", "fontawesome5")
+   )
+   ```
+
+5. *(Finally!)* Run `targets::tar_make()` to run the full analysis pipeline. This will take ≈40 minutes the first time.
+
+6. When the pipeline is all the way done, find the analysis notebook at `_site` and the manuscript and appendix files at `manuscript/output/`.
+
+### Method 3: Run locally with packages installed systemwide
+
+Finally, it's also possible to not use Docker *and* not use {renv} and instead run everything using R packages that you install systemwide.
+
+0. Install these preliminary things:
+
+   - **R 4.4.2** (or later) and **RStudio**.
+
+   - **Quarto 1.6.1** (or later). As of this writing, the current stable version of Quarto is 1.6.
+
+   - **A C++ compiler and GNU Make**.
+Complete instructions for macOS, Windows, and Linux [are available at CmdStan's documentation](https://mc-stan.org/docs/cmdstan-guide/installation.html#cpp-toolchain).
+In short, do this:
+     - **macOS**: Run this terminal command and follow the dialog that pops up after to install macOS's Command Line Tools:
+
+       ```sh
+       xcode-select –-install
+       ```
+
+     - **Windows**: [Download and install Rtools from CRAN](https://cran.r-project.org/bin/windows/Rtools/rtools44/rtools.html)
+
+     - **Linux**: Run this terminal command (depending on your distribution; this assumes Ubuntu/Debian):
+
+       ```sh
+       sudo apt install g++ make
+       ```
+
+   - (*macOS only*): [Download and install XQuartz](https://www.xquartz.org/)
+
+   - **Fonts**: Download and install these fonts (or install them from `misc/fonts` in this repository). On Windows, install these as an administrator so that R and Quarto have access to them.
+
+     - [Libre Franklin](https://fonts.google.com/specimen/Libre+Franklin)
+     - [Linux Libertine](https://libertine-fonts.org/)
+     - [Libertinus Math](https://github.com/alerque/libertinus/releases/tag/v7.040)
+
+1. ***Before*** opening `silent-skywalk.Rproj`, open `.Rprofile` and remove or comment out the line that says `source("renv/activate.R")`:
+
+   ```r
+   # source("renv/activate.R")
+   ```
+
+   This will disable {renv} and will make it so R doesn't try to automatically install all the packages specified in `renv.lock`.
+
+2.
+**Also before** opening `silent-skywalk.Rproj`, run `docker/misc/install_packages.R`.
+This uses {pacman} to install all required R packages.
+It downloads the latest versions of each package from CRAN and installs them systemwide.
+It will also install {cmdstanr} and LaTeX through {tinytex}.
+
+3. Open `silent-skywalk.Rproj` to open a new RStudio project.
+
+4. Run `targets::tar_make()` to run the full analysis pipeline. This will take ≈40 minutes the first time.
+
+5. When the pipeline is all the way done, find the analysis notebook at `_site` and the manuscript and appendix files at `manuscript/output/`.
 

### 2025-04-12 docker/misc/install_packages.R
Add systemwide package installation script

@@ -1,0 +1,47 @@
+# Use {pacman} to install all the required packages and avoid {renv}
+if (!require("pacman")) {
+  install.packages("pacman")
+  library(pacman)
+}
+
+pacman:::p_set_cranrepo("https://packagemanager.posit.co/cran/latest")
+
+p_load("renv")
+
+# Find all the pacakges used in the project
+pkgs <- renv::dependencies(here::here())$Package |> 
+  unique() |> 
+  (\(x) x[!x %in% c("base", "cmdstanr", "tinytable")])()
+
+# Install all packages and their dependencies
+pacman::p_load(char = pkgs, update = TRUE)
+
+# Install cmdstanr
+install.packages(
+  "cmdstanr",
+  repos = c("https://stan-dev.r-universe.dev", getOption("repos"))
+)
+cmdstanr::install_cmdstan()
+
+# Install development version things
+install.packages(
+  "tinytable",
+  repos = c("https://vincentarelbundock.r-universe.dev")
+)
+
+# Install LaTeX
+tinytex::install_tinytex()
+
+tinytex::tlmgr_install(
+  # tikz things
+  c("dvisvgm", "adjustbox", "collectbox", "currfile", "filemod", "gincltex",
+    "standalone", "fp", "pgf", "grfext", "libertine", "libertinust1math", 
+    # template things
+    "nowidow", "tocloft", "orcidlink", "abstract", "titling", "tabularray",
+    "ninecolors", "enumitem", "textcase", "titlesec", "footmisc", "caption",
+    "pdflscape", "ulem", "multirow", "wrapfig", "colortbl", "tabu", 
+    "threeparttable", "threeparttablex", "environ", "makecell", "sidenotes", 
+    "marginnote", "changepage", "siunitx", "mathtools", "setspace", "ragged2e", 
+    "fancyhdr", "pdftex", "preprint", "endnotes", "tikzfill", "tcolorbox", 
+    "pdfcol", "fontawesome5")
+ )

### 2025-04-12 README.qmd
Update Quarto version in Docker
ope there's only one model

@@
 We use the [{renv} package](https://rstudio.github.io/renv/articles/renv.html) to create a stable version-specific library of R packages, and we use the [{targets} package](https://docs.ropensci.org/targets/index.html) to manage all the file dependencies and run the analysis.
-{targets} is especially helpful with long-running objects like the main models, which take ≈40 minutes to run—as long as upstream dependencies don't change, the models only need to run once, and can be loaded from {targets}'s data store thereafter.
+{targets} is especially helpful with long-running objects like the main model, which takes ≈40 minutes to run—as long as upstream dependencies don't change, the model only needs to run once, and can be loaded from {targets}'s data store thereafter.
 
@@
 
-   - **Quarto 1.6.1** (or later). As of this writing, the current stable version of Quarto is 1.6.
+   - **Quarto 1.7.23** (or later). As of this writing, the current stable version of Quarto is 1.7.
 

### 2025-04-15 notebook/results-crackdown.qmd
Switch from iconify to regular fontawesome

@@
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 2~a~: Relationship with host government
+## {{< fa flask-vial >}} Hypothesis 2~a~: Relationship with host government
 
@@
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 2~b~: Organization and relationship with host government
+## {{< fa flask-vial >}} Hypothesis 2~b~: Organization and relationship with host government
 

### 2025-04-15 notebook/results-funding.qmd
Switch from iconify to regular fontawesome

@@
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 4~a~: Funding sources
+## {{< fa flask-vial >}} Hypothesis 4~a~: Funding sources
 
@@
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 4~b~: Relationship with host government and funding sources
+## {{< fa flask-vial >}} Hypothesis 4~b~: Relationship with host government and funding sources
 
@@
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 4~c~: Relationship with host government, funding sources, and issue area
+## {{< fa flask-vial >}} Hypothesis 4~c~: Relationship with host government, funding sources, and issue area
 

### 2025-04-15 notebook/results-issue.qmd
Switch from iconify to regular fontawesome

@@
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 3~a~: Issue area
+## {{< fa flask-vial >}} Hypothesis 3~a~: Issue area
 
@@
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 3~b~: Relationship with host government and issue area
+## {{< fa flask-vial >}} Hypothesis 3~b~: Relationship with host government and issue area
 

### 2025-04-15 notebook/results-practices.qmd
Clean up some notebook stuff
Switch from iconify to regular fontawesome

@@
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~a~: Financial transparency
+## {{< fa flask-vial >}} Hypothesis 5~a~: Financial transparency
 
@@
 $$
+
 ```{r h5a-calc-estimands}
@@
 ::: {.callout-tip icon=false}
-### {{< iconify fa6-solid flask-vial >}} Hypothesis 5~b~: Relationship with host government, organizational practices
+### {{< fa flask-vial >}} Hypothesis 5~b~: Relationship with host government, organizational practices
 
@@
 ::: {.callout-tip icon=false}
-### {{< iconify fa6-solid flask-vial >}} Hypothesis 5~b2~: Relationship with host government, organizational practices
+### {{< fa flask-vial >}} Hypothesis 5~b2~: Relationship with host government, organizational practices
 
@@
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~c~: Relationship with host government, organizational practices, and funding sources
+## {{< fa flask-vial >}} Hypothesis 5~c~: Relationship with host government, organizational practices, and funding sources
 
@@
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~d~: Relationship with host government, organizational practices, and issue area
+## {{< fa flask-vial >}} Hypothesis 5~d~: Relationship with host government, organizational practices, and issue area
 
@@
 :::
-
-## Estimand
-
-TODO
 
@@
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~e~: Relationship with host government, organizational practices, issue area, and funding sources
+## {{< fa flask-vial >}} Hypothesis 5~e~: Relationship with host government, organizational practices, issue area, and funding sources
 
@@
 ::: {.callout-tip icon=false}
-## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~f~: Accountability
+## {{< fa flask-vial >}} Hypothesis 5~f~: Accountability
 

### 2025-04-15 notebook/survey-irb.qmd
Switch from iconify to regular fontawesome

@@
 <a href="files/byu-irb-approval.pdf" class="btn btn-success btn-md" target="_blank" role="button">
-{{< iconify fa6-solid circle-check >}} &nbsp; BYU IRB approval
+{{< fa circle-check >}} &nbsp; BYU IRB approval
 </a> 
@@
 <a href="files/cnu-irb-approval.pdf" class="btn btn-md btn-success" target="_blank" role="button">
-{{< iconify fa6-solid circle-check >}} &nbsp; Christopher Newport IRB approval
+{{< fa circle-check >}} &nbsp; Christopher Newport IRB approval
 </a>
@@
 <a href="files/gsu-irb-approval.pdf" class="btn btn-success btn-md" target="_blank" role="button">
-{{< iconify fa6-solid circle-check >}} &nbsp; Georgia State IRB approval
+{{< fa circle-check >}} &nbsp; Georgia State IRB approval
 </a>

### 2025-04-15 manuscript/appendix.qmd
Final edits pre-final submission

@@
 short-title: 'Appendix for "Navigating Hostility"'
-date: "2025-01-22"
+date: "2025-04-14"
 author:
@@
 tar_load(c(
-  participant_summary, model_summary_table, feature_lookup, level_lookup, cps_diffs
+  participant_summary, model_summary_table, feature_lookup, level_lookup, 
+  cps_diffs, data_sans_conjoint
 ))
+
+details <- list(
+  n = nrow(data_sans_conjoint),
+  n_nice = label_comma()(nrow(data_sans_conjoint)),
+  combos = 2 * 2 * 3 * 4 * 4 * 3
+)
 
@@
 
+summary_notes <- list(
+  `*` = list(i = 0, j = 2, text = tt_md(paste0("N = ", details$n_nice, " respondents.")))
+)
+
 inner <- glue("
@@
   select(-category, -Question) %>% 
-  tt(width = c(0.6, 0.15, 0.15)) %>%
+  tt(width = c(0.6, 0.15, 0.15), notes = summary_notes) %>%
   group_tt(j = list("Demographics" = 1:3)) %>%
@@
   select(-category, -Question) %>% 
-  tt(width = c(0.6, 0.15, 0.15)) %>%
+  tt(width = c(0.6, 0.15, 0.15), notes = summary_notes) %>%
   group_tt(j = list("Attitudes toward charity" = 1:3)) %>%
@@
   select(-category, -Question) %>%
-  tt(width = c(0.6, 0.15, 0.15)) %>%
+  tt(width = c(0.6, 0.15, 0.15), notes = summary_notes) %>%
   group_tt(j = list("Politics, ideology, and religion" = 1:3)) %>%
@@
 
-To find the causal effects defined in each of our estimands, we calculate EMMs by finding the fitted probability-scale values for each cell in a balanced reference grid of all 576 possible combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding = 576 rows).
+To find the causal effects defined in each of our estimands, we calculate EMMs by finding the fitted probability-scale values for each cell in a balanced reference grid of all `r details$combos` possible combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding = `r details$combos` rows).
 We then calculate group averages and contrasts in group averages for each of the features of interest, marginalizing over all other features.
@@
 notes <- c(
-  "Estimates are median posterior log odds from a multinomial logistic regression model with three possible categories, and the columns for µ1, µ2, and µ3 represent estimates for each of the outcomes;",
+  paste0("N = ", details$n_nice, " respondents.
+Estimates are median posterior log odds from a multinomial logistic regression model with three possible categories, and the columns for µ1, µ2, and µ3 represent estimates for each of the outcomes;"),
   "95% credible intervals (equal-tailed quantile intervals) in brackets."
@@
 
-To convert EMMs and AMCEs to a more interpretable probability scale (rather than the original log odds scale), we generate predicted values (marginalized across the three µ terms) for each of the 576 unique combinations of feature levels.
+To convert EMMs and AMCEs to a more interpretable probability scale (rather than the original log odds scale), we generate predicted values (marginalized across the three µ terms) for each of the `r details$combos` unique combinations of feature levels.
 @tbl-grid-example provides an excerpt from this grid, showing six rows where accountability, organization, issue area, and funding are identical and held constant, while transparency and government relations vary.
@@
 notes <- list(
-  `*` = list(i = 0, j = c(2, 4), text = tt_md("Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.")),
+  `*` = list(i = 0, j = c(2, 4), text = tt_md(paste0("N = ", details$combos, " estimated marginal means collapsed into feature-specific means.
+Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets."))),
   `†` = list(i = 0, j = 5, text = tt_md("The probability of direction (*p*~direction~) is the probability that the posterior AMCE is strictly positive or negative—it is the proportion of the posterior AMCE that is the sign of the median."))
@@
 notes <- list(
-  `*` = list(i = 0, j = 2, text = tt_md("Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets."))
+  `*` = list(i = 0, j = 2, text = tt_md(paste0("N = ", details$combos, " estimated marginal means collapsed into feature-specific means.
+Values are on the percentage-point scale; single value is posterior median; 95% credible interval in brackets.")))
 )
@@
 
-This is an anonymized and condensed version of our full OSF preregistration protocol.
+This is an anonymized and condensed version of our full OSF preregistration protocol, which is available at <https://doi.org/10.17605/OSF.IO/HSBYD>.
 :::

### 2025-04-15 manuscript/manuscript.qmd
Remove this old profile stuff
Final edits pre-final submission

@@
 short-title: "Navigating Hostility"
-date: "2025-01-22"
+date: "2025-04-14"
 author:
@@
 csl: csl/apa.csl
-link-citations: true
-word-count: "10,149"  # Subtract 77 for the final statements at the end
+word-count: "10,077"  # Subtract 197 for the final statements at the end
 ---
@@
 
-tar_load(c(grid_treatment_only, level_lookup, feature_lookup))
+tar_load(c(grid_treatment_only, level_lookup, feature_lookup, data_sans_conjoint))
+
+details <- list(
+  n = nrow(data_sans_conjoint),
+  n_nice = label_comma()(nrow(data_sans_conjoint)),
+  combos = 2 * 2 * 3 * 4 * 4 * 3
+)
 
@@
 
-We fielded a conjoint experiment to a nationally representative sample of 1,016 adults in the US.
+We fielded a conjoint experiment to a nationally representative sample of `r details$n_nice` adults in the US.
 This experiment allows us to assess individual-level giving preferences among likely donors in the US towards NGOs abroad working in a variety of issue areas---human rights, environment, emergency response, and refugee relief.[^not-elite] More importantly, it allows us to directly compare the relative impact of host government restriction of NGOs and organizational financial transparency and accountability on individual donor preferences.
@@
 In standard factorial experimental designs, participants would ordinarily need to be shown all possible combinations of experimental attributes.
-In our experiment, we presented respondents with six possible treatments with randomized attributes for each treatment, yielding 576 possible unique combinations of features.
+In our experiment, we presented respondents with six possible treatments with randomized attributes for each treatment, yielding `r details$combos` possible unique combinations of features.
 Even with respondents answering twelve iterations of the experiment, not every combination was seen.
@@
 
-While the ability to select key attributes and marginalize over others provides us with analytic flexibility, it also raises possible issues with multiple comparisons, *p*-hacking, and selective cherry-picking [@BansakHainmuellerHopkins:2021], especially given the fact that we have 576 possible combinations of independent variables to explore.
-As such, before launching the survey experiment, we preregistered a subset of confirmatory and exploratory hypotheses at the Open Science Framework.
-These hypotheses deal specifically with our key research questions about the effect of transparency, accountability, and crackdown on the propensity to donate, along with comparison treatment effects for organization brand name, issue area, and funding sources.
+While the ability to select key attributes and marginalize over others provides us with analytic flexibility, it also raises possible issues with multiple comparisons, *p*-hacking, and selective cherry-picking [@BansakHainmuellerHopkins:2021], especially given the fact that we have `r details$combos` possible combinations of independent variables to explore.
+As such, before launching the survey experiment, we preregistered a subset of confirmatory and exploratory hypotheses at the Open Science Framework.[^prereg] These hypotheses deal specifically with our key research questions about the effect of transparency, accountability, and crackdown on the propensity to donate, along with comparison treatment effects for organization brand name, issue area, and funding sources.
 We also examine the interaction between transparency, accountability, and host-country relationships.
-Our preregistration protocol is available at `ANONYMIZED_URL` and in the appendix, and our data and reproducible code is available at `ANONYMIZED_URL`.[^prereg]
-
-[^prereg]: For clarity, we focus on our simplest, non-nested hypotheses, omitting many preregistered ones that overlap (e.g., the effect of branding and issue area and transparency and crackdown simultaneously).
+
+[^prereg]: Our preregistration protocol is available at <https://doi.org/10.17605/OSF.IO/HSBYD> and in the appendix, and our data and reproducible code is available at <https://doi.org/10.17605/OSF.IO/R59XZ>.
+For clarity, we focus on our simplest, non-nested hypotheses, omitting many preregistered ones that overlap (e.g., the effect of branding and issue area and transparency and crackdown simultaneously).
 Following @WillrothAtherton:2024, we outline all the deviations from our preregistration protocol in the appendix.
@@
 We also included an attention check question early in the survey and removed respondents who failed the question.
-Importantly, these screening questions were presented *prior to* the experimental manipulation to avoid post-treatment bias [@MontgomeryNyhanTorres:2018a].
-Following screening, we received 1,016 viable responses.
+Importantly, these screening questions were presented *prior to* the experimental manipulation to avoid post-treatment bias [@MontgomeryNyhanTorres:2018].
+Following screening, we received `r details$n_nice` viable responses.
 Tables A1, A2, and A3 provide a detailed breakdown of the individual characteristics of our sample.
@@
 
-At the time of designing the study, Charity Navigator---a large database of US nonprofit financial information---categorized international nonprofit activities into four general causes: (1) development, (2) humanitarian relief, (3) international affairs and human rights advocacy, and (4) environment.[^cn] Accordingly, we used four nonprofits that are stereotypical for each cause: the International Committee of the Red Cross (humanitarian relief), Amnesty International (human rights), Oxfam (development), and Greenpeace (environment).[^real-names] We also varied several other features, including four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), two organizational practices (financial transparency and third-party accountability audits), three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and three relationships with host governments (friendly, criticized by the government, and under government crackdown).
+At the time of designing the study, Charity Navigator---a large database of US nonprofit financial information---categorized international nonprofit activities into four general causes: (1) humanitarian relief supplies, (2) international peace, security, and affairs, (3) development and relief services, and (4) environment.
+Accordingly, we used four nonprofits that are stereotypical for each cause: the International Committee of the Red Cross (humanitarian relief), Amnesty International (human rights), Oxfam (development), and Greenpeace (environment).[^real-names] We also varied several other features, including four issue areas (emergency response, environmental advocacy, human rights advocacy, and refugee relief), two organizational practices (financial transparency and third-party accountability audits), three funding sources (many small private donations, a handful of wealthy private donors, and government grants), and three relationships with host governments (friendly, criticized by the government, and under government crackdown).
 
 [^cn]: See <http://web.archive.org/web/20170315000746/https://www.charitynavigator.org/index.cfm?bay=search.categories&categoryid=7>.
-Under the explicitly "International" category, Charity Navigator listed Development and Relief Services; International Peace, Security, and Affairs; and Humanitarian Relief Supplies.
-The "Environment" category is listed separately but contains many INGOs such as Greenpeace and the World Wide Fund for Nature (WWF).
 At the time of writing, Charity Navigator had changed its taxonomy to include 18 broader categories.
@@
 This choice indicated donation intention and reflected the option the respondent preferred most within that set.
-We then repeated the process eleven more times for a total of twelve randomized iterations of hypothetical combinations of attributes, resulting in 12,192 completed experimental tasks (12 iterations × 1,016 respondents).
+We then repeated the process eleven more times for a total of twelve randomized iterations of hypothetical combinations of attributes, resulting in `r label_comma()(details$n * 12)` completed experimental tasks (12 iterations × `r details$n_nice` respondents).
 This iterative process across twelve experimental tasks is typical of conjoint analysis and allows us to estimate individual-level differences using a multilevel model and determine both aggregate respondent preferences and the causal effect of each experimental feature on those preferences.
@@
 We analyze the results using a multilevel Bayesian multinomial model (see the appendix for complete model details).
-Our experimental data has a natural hierarchical structure, with 3 questions nested inside 12 separate experimental tasks, nested inside each of the 1,016 respondents, which lends itself to multilevel modeling [@JensenMarbleScheve:2021].
-Since it was impossible for every respondent to see every possible combination of all 12,000 experimental tasks, multilevel modeling allows us to pool together information about respondents with similar characteristics facing similar sets of choices.
+Our experimental data has a natural hierarchical structure, with 3 questions nested inside 12 separate experimental tasks, nested inside each of the `r details$n_nice` respondents, which lends itself to multilevel modeling [@JensenMarbleScheve:2021].
+Since it was impossible for every respondent to see every possible combination of all 12,000+ experimental tasks, multilevel modeling allows us to pool together information about respondents with similar characteristics facing similar sets of choices.
 Moreover, using random respondent effects provides natural regularization and shrinkage for our estimates---experimental tasks that happened to appear more often due to chance will be accounted for and their frequency will not bias the overall causal effect.
@@
 We do not work with the raw results of the multinomial model directly.
-Given the conjoint design, we instead create a complete balanced grid of all 576 combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding) and use the model to calculate predicted probabilities of choice selection for each combination of possible treatment values.
-We then collapse this set of predicted probabilities into estimated marginal means (EMMs) for specific features of interest while marginalizing or averaging over all other predicted variables [@LeeperHoboltTilley:2020; @BremerBurgisser:2023].
+Given the conjoint design, we instead create a complete balanced grid of all `r details$combos` combinations of feature levels (2 transparency × 2 accountability × 3 government relationships × 4 organizations × 4 issues × 3 funding) and use the model to calculate predicted probabilities of choice selection for each combination of possible treatment values.
+We then collapse this set of predicted probabilities into estimated marginal means (EMMs) for specific features of interest while marginalizing or averaging over all other predicted variables [@LeeperHoboltTilley:2020; @Arel-BundockGreiferHeiss:2024].
 This marginalization process allows us to isolate the statistical effect of each feature in isolation.
@@
 However, we are generally less concerned with the exact point estimates of our causal effects and instead focus on the direction and relative magnitude of their posterior distributions.
-For inference, we calculate the probability of direction ($p_d$), or the probability that the posterior AMCE is strictly positive or negative---it is the proportion of the posterior AMCE that is the sign of the median.
+For inference, we calculate the probability of direction ($p_d$), which indicates the proportion of the posterior AMCE that shares the sign of the median and the probability that AMCE is strictly positive or negative.
 
@@
 #| out-width: "80%"
-#| fig-cap: "Estimated marginal means for the four combinations of transparency and accountability."
+#| fig-cap: "Estimated marginal means for the four combinations of transparency and accountability"
 #| include: true
@@
 
-# Discussion and conclusion
+# Discussion
+
+These results have two important practical implications for NGO operations, fundraising, and survivability at a time when many INGOs are dealing with hostile host governments.
+First, while NGOs have little to no control over the legal environments of their host governments, they do have control over organizational practices such as transparency and accountability, and more importantly, public perception of these organizational characteristics.
+As a result, they may need to rely entirely on improving individual donor perceptions of organizational transparency and accountability and emphasizing the need for private donor funds at a time of shrinking civic space.
+These results provide insight into the importance of different framing or informational heuristics that can motivate such individual donor giving.
+In addition to voluntarily emphasizing or sharing this information with likely donors, nonprofits could also potentially brainstorm how to get more positive media exposure regarding these characteristics in restrictive civic environments.
+Moreover, we find that nonprofit transparency and accountability practices share the same causal effect, implying that donors might see these as interchangeable concepts.
+
+Second, our results also highlight the importance of brand recognition and goodwill---respondents were more likely to prefer donating to an organization when it was identified as the Red Cross, a signal to the ubiquity of its brand across the globe and its emphasis on neutrality in hostile environments.
+Previous research shows that both brand awareness and brand trust are critical to non-involved consumers [@YenCaskeyWarden:2023]---in this case, donors who have previously not donated to an organization.
+Others show that donors are loyal to brands whose values are congruent to their own [@SargeantFordHudson:2008].
+Our results thus have important implications on why nonprofits in hostile environments should focus on building brand awareness, as well as highlighting their values---to engage both likely and less likely donors.
+
+# Conclusion
 
@@
 Our results highlight the importance of organizational characteristics like transparency and accountability even in an era of closing civic space.
-
-These results have two important practical implications for NGO operations, fundraising, and survivability at a time when many INGOs are dealing with hostile host governments.
-First, while NGOs have little to no control over host government crackdowns over their organizations, they do have control over organizational practices such as transparency and accountability, and more importantly, public perception of these organizational characteristics.
-As a result, they may need to rely entirely on improving individual donor perceptions of organizational transparency and accountability and emphasizing the need for private donor funds at a time of shrinking civic space.
-This article thus provides insight into the importance of different framing or informational heuristics that can motivate such individual donor giving.
-In addition to voluntarily emphasizing or sharing this information with likely donors, nonprofits could also potentially brainstorm how to get more positive media exposure regarding these characteristics in restrictive civic environments.
-Moreover, we find that nonprofit transparency and accountability practices share the same causal effect, implying that donors might see these as interchangeable concepts.
-
-Second, our results also show the importance of brand recognition and goodwill---respondents were more likely to prefer donating to an organization when it was identified as the Red Cross, a signal to the ubiquity of its brand across the globe and its emphasis on neutrality in hostile environments.
-Previous research shows that both brand awareness and brand trust are critical to non-involved consumers [@YenCaskeyWarden:2023]---in this case, donors who have previously not donated to an organization.
-Others show that donors are loyal to brands whose values are congruent to their own [@SargeantFordHudson:2008].
-Our results thus have important implications on why nonprofits in hostile environments should focus on building brand awareness, as well as highlighting their values---to engage both likely and less likely donors.
 
@@
 Are the effects of transparency and accountability found in this paper still likely to hold true if the home country also starts smearing these NGOs?
-Finally, though this paper examined legal crackdowns on INGOs, this issue is even more challenging for local NGOs in Global South countries, where individual donors might avoid giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to unfavorable tax benefits or fear of retribution [@Brechenmacher:2017; @DupuyRonPrakash:2015; @Baoumi:2016].
+Finally, though this paper examined legal crackdowns on INGOs, this issue is even more challenging for local NGOs in Global South countries, where individual donors might avoid giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to unfavorable tax benefits or fear of retribution [@Brechenmacher:2017; @DupuyRonPrakash:2015].
 Future research should examine how local NGOs can overcome individual foreign donors' concerns about host governments' criticisms of and crackdown on these groups.
 
-# Data availability statement
-
-All data and replication code is available at `DATAVERSE DOI` and at `OSF DOI`.
-
-# Supplementary material
-
-A companion statistical analysis notebook with a fuller description of the data, modeling details and diagnostics, and additional explanations of the Bayesian multinomial modeling approach, along with links to the data and replication code, is available at `ANONYMIZED URL/DOI`.
-
-# Funding
+# Statements and declarations
+
+## Data availability
+
+All data and replication code is available at <https://doi.org/10.5281/zenodo.14721277> and at <https://doi.org/10.17605/OSF.IO/R59XZ>.
+
+We prereigstered our hypotheses and research design at the Open Science Framework (OSF).
+The full version of the OSF preregistration protocol is available at <https://doi.org/10.17605/OSF.IO/HSBYD>; a condensed version is included in the online appendix.
+We also include a list of deviations from the preregistration in the online appendix.
+
+## Ethical considerations
+
+This experiment was approved and deemed as exempt by the human subjects research committees at both Christopher Newport University (1436622-1), Brigham Young University (E19135), and Georgia State University (H19644).
+
+## Consent to participate
+
+We obtained written informed consent from each survey participant. The full text of the consent statement is included in the online appendix.
+
+## Consent for publication
+
+Not applicable.
+
+## Declaration of conflicting interest
+
+The authors declare no potential conflicts of interest with respect to the research, authorship, and/or publication of this article.
+
+## Funding
 
@@
 
-# Competing interests
-
-The authors report there are no competing interests to declare.
-
-::: {.content-visible when-profile="ms"}
-```{=latex}
-\newpage
-\begingroup
-\singlespacing
-\parindent 0pt
-\parskip 2ex
-\def\enotesize{\normalsize}
-\theendnotes
-\endgroup
-\newpage
-```
-:::
+## Supplementary material
+
+A companion statistical analysis notebook with a more complete description of the data, modeling details and diagnostics, and additional explanations of the Bayesian multinomial modeling approach, along with links to the data and replication code, is available at <https://stats.andrewheiss.com/silent-skywalk/>.
 

### 2025-04-16 README.qmd
Change name of docker-compose file

@@
 
-   - **Using Visual Studio Code or Positron *(recommended)***: If you [download Visual Studio Code](https://code.visualstudio.com/) or [Positron](https://github.com/posit-dev/positron) and [its Docker extension](https://code.visualstudio.com/docs/containers/overview), you can right click on the `docker-compose-prebuilt.yml` file in the File Explorer sidebar and select "Compose Up".
+   - **Using Visual Studio Code or Positron *(recommended)***: If you [download Visual Studio Code](https://code.visualstudio.com/) or [Positron](https://github.com/posit-dev/positron) and [its Docker extension](https://code.visualstudio.com/docs/containers/overview), you can right click on the `docker-compose.yml` file in the File Explorer sidebar and select "Compose Up".
 

### 2025-07-02 manuscript/manuscript.qmd
Final edits

@@
 How do organizational elements of private donor decision-making interact with broader structural limits on INGO fundraising?
-While there are many organization-level factors that can determine an NGO's impact, including organizational structure, financial transparency, accountability, leadership, and strategy [@MitchellSchmitzBruno-vanVijfeijken:2020], in this paper, we focus on the two factors that are most visible to donors outside of the organizations and on which information is available publicly---financial transparency and accountability.
+While there are many organization-level factors that can determine an NGO's impact, including organizational structure, financial transparency, accountability, leadership, and strategy [@MitchellSchmitzBruno-vanVijfeijken:2020], in this article, we focus on the two factors that are most visible to donors outside of the organizations and on which information is available publicly---financial transparency and accountability.
 
@@
 We fielded a conjoint experiment to a nationally representative sample of `r details$n_nice` adults in the US.
-This experiment allows us to assess individual-level giving preferences among likely donors in the US towards NGOs abroad working in a variety of issue areas---human rights, environment, emergency response, and refugee relief.[^not-elite] More importantly, it allows us to directly compare the relative impact of host government restriction of NGOs and organizational financial transparency and accountability on individual donor preferences.
+This experiment allows us to assess individual-level giving preferences among likely donors in the US toward NGOs abroad working in a variety of issue areas---human rights, environment, emergency response, and refugee relief.[^not-elite] More importantly, it allows us to directly compare the relative impact of host government restriction of NGOs and organizational financial transparency and accountability on individual donor preferences.
 The result of this experiment shows that both financial transparency and accountability increase individuals' willingness to donate to NGOs.
@@
 As a result, many INGOs worked to establish and enhance their accountability, responsiveness, and legitimacy [@edwardshulme; @GourevitchLake:2012].
-These actions were a result of many organization-level factors that can potentially impact nonprofit efficacy, including organizational and governance structure, leadership, strategy, transparency, and accountability.
+These actions were a result of many organization-level factors that can potentially affect nonprofit efficacy, including organizational and governance structure, leadership, strategy, transparency, and accountability.
 Organizational and governance structures define how decisions are made and who participates in decision making.
@@
 As such, donors rely on cues and heuristics when deciding to support an NGO.
-Compared to other organization-level factors, news about financial mismanagement and lack of transparency and accountability may be more easily available.
+Compared with other organization-level factors, news about financial mismanagement and lack of transparency and accountability may be more easily available.
 Many nonprofit scandals involve some form of financial wrongdoing [@PrakashGugerty:2010b].
-Notable examples include the United Nations' Oil-for-Food program, aimed at alleviated Iraq's sanctions-induced hardships in the 1990s, which was marred by revelations of widespred financial fraud, limited food distribution, and lack of accountability in 2004.
-Numerous other cases [see @GibelmanGelman:2001 and @GibelmanGelman:2004] demonstrate how financial mismanagement, embezzlement, fraud, and lack of accountability can decrease public trust and reduce donations to nonprofits.
+Notable examples include the United Nations' Oil-for-Food program, aimed at alleviated Iraq's sanctions-induced hardships in the 1990s, which was marred by revelations of widespread financial fraud, limited food distribution, and lack of accountability in 2004.
+Numerous other cases [see @GibelmanGelman:2001; @GibelmanGelman:2004] demonstrate how financial mismanagement, embezzlement, fraud, and lack of accountability can decrease public trust and reduce donations to nonprofits.
 Globally, around 5% of revenue is lost annually due to fraud [@ACFE:2021].
@@
 
-Thus, in this paper, we explore the effects of two possible categories of heuristic frames that can impact individual-level giving: (1) organization-level heuristics, reflected in practices of transparency and accountability, and (2) structural heuristics, particularly an NGO's relationship with its host country.
+Thus, in this article, we explore the effects of two possible categories of heuristic frames that can affect individual-level giving: (1) organization-level heuristics, reflected in practices of transparency and accountability, and (2) structural heuristics, particularly an NGO's relationship with its host country.
 We hypothesize that each type plays a role in shaping individual preferences for engaging in philanthropy.
@@
 We first examine the impact of two organizational practices---financial transparency and accountability---on individual donor preferences.
-Financial transparency, or the "degree of completeness of information provided by [organizations] to the [public] concerning [their] activities," [@VaccaroMadsen:2006, p.
-146] is one tangible heuristic that donors turn to when making decisions.
+Financial transparency, or the "degree of completeness of information provided by [organizations] to the [public] concerning [their] activities" [@VaccaroMadsen:2006, p.
+146], is one tangible heuristic that donors turn to when making decisions.
 Transparency can involve proactive sharing of information with stakeholders, participation in data transparency platforms, avoiding financial misconduct, and exhibiting trustworthiness.
@@
 As NGOs gain more prominence, stakeholders seek assurance that their donations will make a real difference---effective accountability can encourage NGOs to become more closely aligned with community practices and help expand stakeholder support [@Murtaza:2012].
-Problems with accountability usually occur when organizations ignore their stakeholders' preferences and use judgements or actions which may not align with one or more of their constituent groups [@McCambridge:2019].
+Problems with accountability usually occur when organizations ignore their stakeholders' preferences and use judgments or actions which may not align with one or more of their constituent groups [@McCambridge:2019].
 The absence of accountability is associated with decreased public trust, deteriorated reputation, and lower perceived quality [@Becker:2018].
 
-Though individual donors would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead [@HungHagerTian:2023], individuals interested in supporting charities cannot thoroughly vet every aspect of the organization [@Tremblay-BoirePrakash:2017; @ChaudhryHeiss:2021].
+Although individual donors would like to have some assurance that their resources will be used appropriately and organizations are not spending too much on overhead [@HungHagerTian:2023], individuals interested in supporting charities cannot thoroughly vet every aspect of the organization [@Tremblay-BoirePrakash:2017; @ChaudhryHeiss:2021].
 To more easily judge financial transparency and accountability, donors may use ratings by watchdog organizations like Charity Navigator and GuideStar as heuristics to guide their decisions.[^cn-multiple] Research shows that initiatives to address information gaps by these organizations can substantially increase donations [@Sloan:2009; @GordonKnockNeely:2009; @Tremblay-BoirePrakash:2017].
@@
 A global cascade of anti-NGO laws in recent decades has created barriers to entry, funding, and advocacy for civic organizations [@GlasiusSchalkDeLange:2020; @BakkeMitchellSmidt:2020; @Chaudhry:2022; @Heiss:2017; @DupuyRonPrakash:2016].
-The use of such anti-NGO laws, also referred to as administrative crackdown [@Chaudhry:2022], is different from regulations that simply set standards for appropriate organizational behavior and set penalties for violations [@North:1990].[^violent-crackdown] However, the anti-NGO laws discussed in this paper, such as the Russian Foreign Agent law, are not grounded in international legal principles and do not give nonprofits the freedom of association or access to resources [@Robinson:2024].
+The use of such anti-NGO laws, also referred to as administrative crackdown [@Chaudhry:2022], is different from regulations that simply set standards for appropriate organizational behavior and set penalties for violations [@North:1990].[^violent-crackdown] However, the anti-NGO laws discussed in this article, such as the Russian Foreign Agent law, are not grounded in international legal principles and do not give nonprofits the freedom of association or access to resources [@Robinson:2024].
 As a result, NGOs must spend more time, effort, and resources to ensure their survival---at the expense of pursuing their missions.
@@
 While multilateral donors do not reduce aid in response to anti-NGO laws, these laws are associated with a 32% decline in bilateral aid inflows [@DupuyPrakash:2018].
-Further, advocacy-oriented donors---i.e., those that fund democracy and civil society promotion activities---reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022].
+Furthermore, advocacy-oriented donors---that is,, those that fund democracy and civil society promotion activities---reduced their spending by 74%, but did not cut their spending on development projects such as education, health, water, and sanitation [@RightSpringmanWibbels:2022].
 
 However, previous literature has established that individual private donors do not make the same considerations as official donors when deciding to donate [@DesaiKharas:2018; @ChaudhryHeiss:2021].
-Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore, may be in a better position to respond to recipients' needs on the ground [@EasterlyWilliamson:2011].
+Private foreign aid does not have to deal with the same strategic and political considerations as official aid and therefore may be in a better position to respond to recipients' needs on the ground [@EasterlyWilliamson:2011].
 When a potential recipient NGO faces legal crackdown in its host country, private individual donors can respond by (1) increasing their donations as a sign of support and solidarity, (2) decreasing their donations, punishing the NGO for perhaps doing something to run afoul of its host government, or (3) not considering the host country legal environment and making no change in their donation behavior.
@@
 @ChaudhryDotsonHeiss:2021 explore how different combinations of donor characteristics determine which response individuals are likely to take when NGOs face crackdown.
-They find that donors with longer experiences with the nonprofit sector and high levels of social trust---i.e., those who frequently volunteer, regularly donate to charity, and trust political institutions---are more likely to maintain their support for international NGOs that face criticism or crackdown abroad.
+They find that donors with longer experiences with the nonprofit sector and high levels of social trust---that is, those who frequently volunteer, regularly donate to charity, and trust political institutions---are more likely to maintain their support for international NGOs that face criticism or crackdown abroad.
 Thus, anti-NGO laws may act as a heuristic to individuals donors that NGOs undertake crucial work abroad, which is why governments perceive them as threatening and seek to restrict their work.
@@
 For instance, in 2022, after the Supreme Court overturned Roe v.
-Wade, private philanthropy towards abortion funds skyrocketed [@PBSNews:2022]---a significant development as abortion funds rely largely on individual donors [@Cohen:2022].
+Wade, private philanthropy toward abortion funds skyrocketed [@PBSNews:2022]---a significant development as abortion funds rely largely on individual donors [@Cohen:2022].
 Therefore, we expect that anti-NGO restrictions imposed by host-country governments are likely to boost individual donors' inclination to donate to affected organizations.
@@
 
-Identifying the causal link between structural factors and donor behavior is more difficult than measuring the link between organizational factors and donor behavior because (1) NGOs have less direct control over their political environments, and (2) organizational characteristics like financial transparency and accountability can sour the NGO-government relationship---governments may be more likely to target NGOs that lack financial transparency and accountability.
+Identifying the causal link between structural factors and donor behavior is more difficult than measuring the link between organizational factors and donor behavior because (1) NGOs have less direct control over their political environments and (2) organizational characteristics like financial transparency and accountability can sour the NGO-government relationship---governments may be more likely to target NGOs that lack financial transparency and accountability.
 Moreover, states pass anti-civil society laws in response to broader political trends within their borders, and they regulate NGOs strategically to maximize the benefits and minimize the costs of working with international NGOs [@Heiss:2017].
@@
 In general, respondents were well balanced across all pre-treatment characteristics, including gender, age, education, income, and attitudes toward charity.
-Additionally, Table A4 compares sample characteristics with nationally representative estimates from the 2019 Current Population Survey (CPS).
+In addition, Table A4 compares sample characteristics with nationally representative estimates from the 2019 Current Population Survey (CPS).
 Our sample matches national proportions of age, marital status, and education, and contains slightly more men and slightly higher income levels than the general population.
@@
 After collecting baseline information on respondent demographics and attitudes toward charity and voluntarism, we showed participants a set of randomly shuffled hypothetical international NGOs described with randomly shuffled features or attributes.
-In this paper, we hypothesize and empirically test the effect of financial transparency, accountability, and host country relationship on the likelihood of donations.
+In this article, we hypothesize and empirically test the effect of financial transparency, accountability, and host country relationship on the likelihood of donations.
 In our experiment, we included a few additional treatments to aid with the interpretation and comparison of effect sizes for our treatments of interest.
@@
 Our experimental data has a natural hierarchical structure, with 3 questions nested inside 12 separate experimental tasks, nested inside each of the `r details$n_nice` respondents, which lends itself to multilevel modeling [@JensenMarbleScheve:2021].
-Since it was impossible for every respondent to see every possible combination of all 12,000+ experimental tasks, multilevel modeling allows us to pool together information about respondents with similar characteristics facing similar sets of choices.
+As it was impossible for every respondent to see every possible combination of all 12,000+ experimental tasks, multilevel modeling allows us to pool together information about respondents with similar characteristics facing similar sets of choices.
 Moreover, using random respondent effects provides natural regularization and shrinkage for our estimates---experimental tasks that happened to appear more often due to chance will be accounted for and their frequency will not bias the overall causal effect.
@@
 As seen in the marginal means in @fig-all-results, both transparency and accountability are strong signals of organizational deservingness.
-Respondents strongly prefer organizations that engage in either transparency or accountability---both treatments have a posterior marginal mean of roughly 30% compared to a baseline equally-at-random probability of 25% (transparency: `r mms$transparency_yes$nice_simple`; accountability: `r mms$accountability_yes$nice_simple`).
+Respondents strongly prefer organizations that engage in either transparency or accountability---both treatments have a posterior marginal mean of roughly 30% compared with a baseline equally-at-random probability of 25% (transparency: `r mms$transparency_yes$nice_simple`; accountability: `r mms$accountability_yes$nice_simple`).
 The AMCEs for each treatment show a roughly 10 percentage point increase in the probability of selection compared to organizations that do not engage in transparency or accountability (transparency: `r amce$transparency_yes$nice_full`; accountability: `r amce$accountability_yes$nice_full`).
@@
 When respondents see both as "no" simultaneously, the estimated marginal mean is lower than any of the individual treatments in @fig-all-results, at `r mms_ta$transparency_no_accountability_no$pct` (`r mms_ta$transparency_no_accountability_no$nice_ci`), or 9 percentage points lower than the baseline probability of 25%.
-When either transparency or accountability is set to "yes", the estimated marginal mean is essentially identical at `r mms$transparency_yes$pct` and `r mms$accountability_yes$pct`, respectively.
-When both treatments are set to "yes", the estimated marginal mean is `r mms_ta$transparency_yes_accountability_yes$pct` (`r mms_ta$transparency_yes_accountability_yes$nice_ci`), which is roughly the same as the overall estimated marginal mean for the Red Cross.
+When either transparency or accountability is set to "yes," the estimated marginal mean is essentially identical at `r mms$transparency_yes$pct` and `r mms$accountability_yes$pct`, respectively.
+When both treatments are set to "yes," the estimated marginal mean is `r mms_ta$transparency_yes_accountability_yes$pct` (`r mms_ta$transparency_yes_accountability_yes$nice_ci`), which is roughly the same as the overall estimated marginal mean for the Red Cross.
 Holding all other treatments constant, the effect of transparency and accountability practices on their own are generally the same, and when combined, the overall favorability of the organization increases substantially.
@@
 To test our second hypothesis regarding structural heuristics, we explore the effect of an NGO's host country conditions on the propensity to donate.
-Contrary to our expectations, respondents appear to prefer donating to NGOs with friendly host government relationships, with a marginal mean of `r mms$friendly_relationship_with_government$pct` (compared to a baseline of 25%; `r mms$friendly_relationship_with_government$nice_ci`).
+Contrary to our expectations, respondents appear to prefer donating to NGOs with friendly host government relationships, with a marginal mean of `r mms$friendly_relationship_with_government$pct` (compared with a baseline of 25%; `r mms$friendly_relationship_with_government$nice_ci`).
 Respondents are less likely to donate when an organization is criticized by its host government, and far less likely when an organization faces restrictions.
-Compared to other treatments, an organization facing restrictions elicits a similar negative preference among potential donors as an organization without transparency or accountability measures.
+Compared with other treatments, an organization facing restrictions elicits a similar negative preference among potential donors as an organization without transparency or accountability measures.
 However, an organization with a friendly relationship with the host government leads potential donors to perceive it as equivalent to engaging in transparency or accountability.
@@
 While donor responses have largely focused on navigating and adapting to legal restrictions, the use of such rhetoric raises broader questions about research and policy in the nonprofit sector: how is such rhetoric changing public attitudes and donations towards these groups?
-Are the effects of transparency and accountability found in this paper still likely to hold true if the home country also starts smearing these NGOs?
-Finally, though this paper examined legal crackdowns on INGOs, this issue is even more challenging for local NGOs in Global South countries, where individual donors might avoid giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to unfavorable tax benefits or fear of retribution [@Brechenmacher:2017; @DupuyRonPrakash:2015].
+Are the effects of transparency and accountability found in this article still likely to hold true if the home country also starts smearing these NGOs?
+Finally, though this article examined legal crackdowns on INGOs, this issue is even more challenging for local NGOs in Global South countries, where individual donors might avoid giving to organizations focusing on contentious causes such as advocacy, media freedom, and anti-corruption initiatives due to unfavorable tax benefits or fear of retribution [@Brechenmacher:2017; @DupuyRonPrakash:2015].
 Future research should examine how local NGOs can overcome individual foreign donors' concerns about host governments' criticisms of and crackdown on these groups.
